%!TEX root = ../crimson_throne_book_main.tex
% 2013-05-19
\section{11 Erastus 4703}

The next morning sees the three young friends on the doorstep of an abandoned theatre. This time they are joined by three fellow lambs, Edu and Lick, two fourteen year old boys, and the lambs' senior member, a kind girl of sixteen who goes by the name of Amarice. Overseeing today's operation are Lamm himself, his right hand man Yargin, a sour-faced wanna-be alchemist, and Lou, Lamm's personal bodyguard, a skinny, but lean swordsman.\\

{\itshape ``This place harbors our new goldmine''}, Lamm gloats as he knocked on the dusty door. {\itshape ``The three of you will go in first''}, he grins as he beckons Edu, Lick and Amarice closer. Yargin draws out two strange harnesses that he fits around the boys' necks. A leather skin has been stretched across a curved neck-sized wooden bracelet, leaving the inside hollow to form some kind of container.\\

{\itshape ``Inside this old theatre are dream spiders, creepy crawlies that are a bit bigger than the ones you are used to. We need you to milk them of their venom. Just let them bite into the leather and their poison will seep into the space inside''}, Yargin explains.\\

{\itshape ``Are you mad?''} Edu protests, only to be answered by Lamm's hard fist. {\itshape ``Bring their webs as well''}, Gaedran Lamm orders, as he shoves a blanket into Amarice's hands, {\itshape ``but be careful not to touch the silky threads, because they make you see strange things.''} He also hands the girl a lantern, before pushing the three guinea pigs into the main hall and quickly closing the door behind them. {\itshape ``Just give us a shout when you're ready''}, the old man mocks.\\

A few minutes pass before a burst of shouts erupts, followed by complete silence~\ldots Then someone pounds on the door: {\itshape ``Let me out! Let me out!''} It is Lick's voice. Yargin is in doubt: {\itshape ``What should I do, boss? What if there are spiders on the other side of the door?''} Since Lamm does not make a decision immediately, Sjo and Quint urge Yargin to let Lick out. The boy stumbles through the doorway, covered in cobwebs. As he faces Lamm, Lick falls back against the wall, warding off the old man while deliriously screaming: "Leave me alone, you nasty spiderman! He raises his arms in protection, but Lamm still hits him hard against the head, knocking him out. Lou swipes away the webs with his blade, noticing that the harness had not been pierced.\\

{\itshape ``A good thing we brought some extra fodder''}, Lamm remarks as he binds Lick's harness around Balian's neck. {\itshape Remember,''} he warns the boys, {\itshape ``do not touch the webs, unless you want to end up like this poor bastard.''} Then he shoves Balian, Quint and Sjo into the theatre.\\

The three boys look around anxiously. The former seating area stretches out before them, reaching a raised stage at the far end of the room. Toppled over benches are scattered across the floor, thickly covered in spider webs. Realizing they are unarmed, the boys tear off some planks from a broken seat, to use as makeshift clubs. Balian, who is holding the light, notices Amarice's abandoned lantern on the floor in front of the podium. There is no immediate sign of the two missing lambs.\\

While they are pondering what to do, a spider jumps out of nowhere and attacks the kids. The monster is huge, easily as big as a large dog. Swinging their wooden sticks, the boys quickly take down the arachnid, but not before it bites Sjo in his neck and shoulder. Part of its venom seep into the harness, but the Shoanti gets a serious shot of the poison in his shoulder as well, leaving him hazy and disoriented. While Sjo takes a minute to get his bearings, his friends successfully milk the dead spider's fangs for more venom.\\

Next the boys make their way to the stage. Dangling from the rigging above the podium is another spider. This specimen is so preoccupied with the cocoon it is weaving that it doesn't even noticed the kids approaching until Balian hammers it in the head. After defeating the spider, the boys cut down the cocoon and free their friend Edu from the webs. Before they are able to carry him off the stage, two more spiders leap down. One of them puts its fangs in Quint's leg and with only a wooden stick in their hands, the boys suddenly feel overpowered. Then a trapdoor in the floor of the stage bursts open and Amarice hops out. She knocks down one of the monsters, giving the boys a chance to finish off the other one.\\

After they have milked the arachnids of their poison, the lambs consider what to tell Lamm. The old man will not be pleased to learn that his goldmine has already run dry. If they lie and tell him the spiders are still alive, he will surely send them back in a few days and they'll be in all kinds of trouble then. So they decide to go with a colored version of the truth. Balian, who isn't such a schemer as his colleagues, strolls about on the podium while his friends are plotting. A smaller cocoon draws his attention when it quivers with a light spasm. Balian examines it and carefully unfolds the webs, discovering a black labrador puppy inside. The baby dog is still breathing, although it is unconscious, just like Edu.\\

Next the kids rejoin Lamm and his men, confessing that they have killed four spiders, but have at least managed to extract their venom. Moreover, they have seen lots of baby spiders inside, who will probably be full-grown in a few months. Sjo and Quint bring such a compelling version of the truth that Lamm completely buys it. They also manage to draw away the adults' attention from Balian, who is hiding the small pup under his clothes. On their way home Quint explains to Lamm how a small animal, like a rat, with a harness around its neck, would make for better bait than a human. Some kind of stuffed animal puppet might even be preferable. Lamm says he will consider this idea, but he doubts that much venom will seep into the container if no one is able to steer the bait.\\

Back in the clog shop the boys and Amarice are given the rest of the day off to recover from their ordeal. Although the kids decide that it won't be too hard to hide the puppy from Lamm and his men - the outhouse is big enough and the adults never come in for long - they do fear one of their own, Jecko, who has a rep for being a snitch. The boys try to come up with a suitable solution and also start to wonder what happens to lambs when they have ``finished'' their service to Lamm. Since none of their retired brethren have ever been seen or heard of again, they fear that riper teenagers are sold off as slaves to Cheliax, or even worse, killed. Amarice probably doesn't have much time left, since she's sixteen; it's her smallish stature that keeps her here for now.\\

When the other lambs return from their day's work, they convince the little traitor Jecko that ``Spyder'', as they dubbed the labrador pup, is their secret and that it will be Jecko's job to see to it that everyone keeps it.\\

That evening Sjo, Balian and Quint have to assist Lamm in the old shop. He is expecting a guest and needs Sjo and Quint to convince him the stupid neck harness plan didn't work and had almost killed them. Balian's job will be simpler, he'll be fetching food and drink.\\

Half an hour later the guest arrives. It is a truly ugly man, very skinny, with a crooked nose and a receding hairline. His skin is pale and blotchy from various scars. He's wearing a long leather apron that bulges with surgical tools and he has a chemical smell about him.\\

Lamm starts complaining how he almost lost a couple of his lambs to the dream spiders, but the guest, whose name seems to be ``Rolth'', tells Gaedran not to fret. He gladly collects the venom and the spider webs and hands Lamm a small bag in return. {\itshape ``I don't care how you get my stuff''}, the guest hisses, {\itshape ``we both know you love doing business with me if you can get Pesh for it. You'll let me know when you have more \ldots''} Then he leaves.\\

So this is what the boys have risked their lives for, Pesh. It is no secret that Lamm deals a bit of drugs now and then, but the lambs certainly do not feel it is worth their lives. Sjo swears he will make the old man burn in hell.\\

