%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-03
\chapter{Edge of Anarchy}

\section{20 Gozran 4708}

Almost five years have passed since the fateful royal wedding day, when a man with heavy muscles in his arms and shoulders steps through the city gates. His clothes are covered in dust from many months of traveling. His journey began in Cheliax, where he joined a small caravan north to Molthune. From there he made his way further up to Nimrathas in the company of lone merchant, providing the man with protection on the road.\\

There he started the most perilous part of his journey, traveling alone over the long forgotten merchant road through the Bloodsworn Vale. While the eerie sounds and morbid atmosphere of the valley troubled him, he managed to get through undisturbed, driven by the unrelenting will to reach Korvosa and find his sister.\\

When he had left Cheliax almost half a year ago, he had refused to travel north by ship, the normal way to get to Korvosa. He had had his fill of ships, having spent almost four years as a slave at the oars of one. A year ago a storm had surprised the vessel and thrown it on the cliffs. As it sank to the bottom of the sea, three slaves managed to survive and make their way to the shore of Cheliax. Young Balian was one of them. He remained in the company of his two fellow oarsmen for a couple of months, making enough money to buy a sword and armor. Then he found a caravan going north and said farewell to his companions.\\

Now he has finally reached his destination. As he steps through the gate, he smells the familiar scent of the city where he spent his childhood. This morning he awoke with a strange card in his pocket. Although he has never had his fortune read, he recognized it as a harrow card, cards used to predict the future by soothsayers. The card represented the Big Sky and portrayed a slave breaking free of his shackles under a big blue sky, a scene that was quite fitting for Balian's life. On the back of the card, written in bold ink, was a short message:  {\itshape I know what Gaedran Lamm has done to you. He has wronged me as well. I know where he dwells, yet cannot strike at him. Come to my home at 3 Lancet Street at sunset. Others like you will be there. Gaedran must face his fate, and justice must be done.}  Balian has no idea how the card ended up in his pocket, but the message suits him just fine. Gaedran is the crook who holds his sister and justice is long overdue. It is but a few short hours to sunset. Revenge will be his.\\

