%!TEX root = ../crimson_throne_book_main.tex
% 2014-08-02
\chapter{Seven Days to the Grave}

\section{16 Sarenith 4708}

A visit to Field Marshal Cressida Kroft does not yield more useful information. Quint maintains his doubts concerning Trinia's trial and confession, but Kroft can only reply that the city and the Guard are using all their resources to find the escaped girl and her cloaked rescuer. The castle has spread wanted posters all over the city, offering a substantial reward for Trinia's and Blackjack's capture: 5 000 gold sails if either of them is taken alive, half that if they are dead. Information that leads to their arrest is still worth 1 000 gold pieces. This prize money is enough to sweep most people's doubts off the table, but not the companions', who return home to ponder on how to proceed. It turns out the answer is already waiting for them.\\

Seated in a chair of their own sitting room is Vencarlo Orisini, the fencing master. He says he has picked up rumors that the companions have serious doubts about Trinia's guilt, which he more than shares. When the adventurers confirm their position, Vencarlo entrusts them with the fact that Trinia is hiding in his academy. Blackjack brought her there after saving her from losing her head. Orisini and the mysterious daredevil have worked together on more than one occasion in the past and they trust each other in times of need. Master Orisini also spent most of last night talking to the shaken young painter and has become completely convinced of her innocence. When Quint inquires how she was made to confess, Vencarlo urges him to ask her himself, tonight after sundown. That is when he wants the companions to come to his house, to hand over Trinia so they can smuggle her out of the city. The fencing master would do it himself, but his past criticism on the government has already made him one of the usual suspects, and he does not want to risk being caught and losing Trinia in the process. He asks the heroes to take the girl to a friend, who lives outside of the village of Harse, at three days travel from Korvosa. Of course, the four friends agree to help, after all, how can they refuse a lady in need?\\

