%!TEX root = ../crimson_throne_book_main.tex
% 2013-10-05
The companions head over to the theatre where Lick took his own life. The Korvosan Guard is already present and allows Sjo to take down Lick's body and examine it. The healer finds no traces of ill-treatment. It looks like the crazy bard first climbed up to the rigging to attach a rope to one of the beams. Then he made his way to the open stage, where he got on top of a ladder, slid the noose around his neck and kicked down the climbing tool. He did not break his neck falling down, but slowly suffocated. It puzzles the companions that Lick - who hasn't had a clear moment in five days - suddenly found enough clarity to perform this complicated suicide ritual.\\

With the Guard's permission the young friends transport Lick's body to the Gray District to deliver it to the church of Pharasma for burial. It turns out Lick is not the only artist who has died! Yesterday already saw the death by overdose of Guy Nolin, a sculptor, and this morning another suicide was brought in, Archibald Meerwater, a composer, who slit his own wrists.\\

The companions fear that these cases are somehow linked and approach Thousand Bones, asking him whether he can talk to the dead. The old Shoanti shaman confirms that such a power exists, but his divine arsenal do not include this option. He refers them to the priests of Pharasma. Brother Jasan is capable of performing the ritual, but the priest explains that it does not come cheap: 240 gold sails for one spell, no success guaranteed.\\

Hoping to uncover more on these mysterious deaths, Quint leads his friends to Citadel Volshyenek, where they gain another audience with Cressida Kroft. The Field Marshal certainly shares her visitors' concern, but the three apparent suicides have left her soldiers no workable clues. She allows the companions to perform their own investigation and hands them a document that orders her soldiers to cooperate.\\

Archibald Meerwater's home is a nice little villa in Southshore, the newest district in the city, where the up-and-coming live. His housekeeper is the one who found him early this morning in his bathtub, where he killed himself. Apparently something had happened to him last Starday, when he suddenly snapped. He just started screaming over and over again, going totally mad, so his housekeeper made him drink cabble tea to ease his mind. On Moonday, he finally made some sense, when he told her: "Lucienne, I'm lost." Meerwater has been successful for many years and his work was always performed in the Marble Dome. Lucienne claims to have little knowledge of music or culture, but she can confirm that her late boss's work was very heavy and over the top, although it never failed to move. His inspiration came mostly from old myths and legends.\\

The friends stop by the Marble Dome and meet the legendary director of Korvosa's opera house: Touran Palastus. The man is busy leading rehearsals, and snaps haughtily at his unwelcome visitors. He confirms that Meerwater was a brilliant composer, whose work was enjoyed in several corners of the world, including Magnimar and Cheliax. He is also familiar with Guy Nolin, who sculpted several exotic females that line the ceiling of the Marble Dome, although those must have been sculpted fifteen years ago or something. Palastus is not aware yet that Meerwater or Nolin have died, and although he regrets it, he is not distraught by the news: artists should go out in some tragic fashion!\\

Guy Nolin's residence is an old townhouse in North Point. The sculptor lived alone - as did the two other suicides Lick and Meerwater - although Nolin regularly had one of his models stay over. His latest subject was a young girl by the name of Sanja. According to the Korvosan Guard at the door she found the artist's body in his workshop yesterday. Nolin's work has only one theme: girls, usually in quite provocative poses. Despite their risqu\'e nature, the statues do possess an unmistakable quality.\\

The guard leads the companions to the young model's flat in Old Korvosa. Sanja is a pretty Varisian girl with long black hair. She's willing to talk to Sjo and his friends if they buy her lunch at the Traveling Man. She was with Guy in his private quarters when he had some kind of seizure last Starday. He complained of a terrible headache, which lasted for days and kept him tied to his bed. Yesterday he made his way to his workshop and overdosed on shiver.\\

Fearing that more artists might suffer from similar conditions and consequently take their own lives, the young friends head over to Salvator Scream's place. The mad painter was already knocked out by drugs last week, at the time when the other artists were struck by their mysterious fits. When the companions wanted to talk to him three days ago, he was unconscious again from taking cabble. So he might very well be similarly effected as his three unfortunate co-artists.\\

Salvator's shabby studio is located just a few streets from the Traveling Man. Today the painter seems to be awake, although his breath reeks heavily of alcohol. He also admits to having lost his inspiration the last couple of days. He cannot explain where his creativity used to come from, it just flowed from his brush. When asked to describe his source of inspiration in more detail, Scream cannot give a straight answer, he only knows that it's 'blue'. He further denies being inspired by a 'living' muse, as he is rather clumsy around women, or by a certain deity. He has some sympathy for Shelyn, the goddess of beauty, but he just as easily says a prayer to Abadar, Sarenrae, Pharasma or even Asmodeus, when it suits his purpose. Although Scream is similarly suffering from {\itshape artist's block} , he does not give the impression of going down the same road as his fellow artists. Maybe the fact that he was knocked out cold when the crisis hit, somehow spared him from the deepest desperation that leads to suicide. 