%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-03
"The same man who has greatly wronged all of you, has caused me terrible harm as well. You know of whom I speak, Gaedran Lamm, a man whose cruelty and capacity to destroy the lives of those he touches, are matched only by his gift for avoiding reprisal. You see, two months ago his little thieves stole my Harrow deck from me. It is very important to me, because it is an heirloom passed down through generations of fortune-tellers. It is also my sole means of support and it is possessed with a certain kind of family magic. I've been using an ordinary Harrow deck since then, but unfortunately I cannot get any decent readings from this mundane tool.\\

My son Eran, being the headstrong boy that he is, refused to accept the loss of the deck and tracked down the pickpockets. He discovered that they were petty thieves in the employ of Gaedran Lamm, the same crook who kept most of you as his child slaves so many years ago. Eran's discovery led him to Lamm ... and to his death." Zellara looks away as she speaks the words. "Yes, Gaedran Lamm murdered my son.\\

I sought help from the guard, but they turned me away, I asked around, consulted my new harrow cards in vain ... and finally, after talking to the right people and paying the right bribes, I discovered where he dwells: an old fishery north of here, at Westpier 17.\\

Now I need your help. I cannot hope to face this man and his gang on my own and live. The criminal has evaded the law for decades. You have each lived through his cruelties and survived, now it is payback time. Can I count on you?"\\

The five guests at the table immediately wholeheartedly agree. Lick wants to leave right now to see justice done, but Sjo preaches caution, suggesting to stake out the place for a couple of months. This way they might learn more about the strength of Lamm's force, and more importantly, they might spot Lamm's occasional visitor, the creep Rolth, who took Balian's sister Alika. Lick disagrees; Lamm has a way of making frequent victims among his lambs. Every day spent observing him is one more day he can end another lamb's life. Moreover, Lamm can be made to talk about where Rolth lives just as easily with a dagger pressing his throat. It is finally agreed upon to scout Lamm's hideout for a day or two, before springing into action.\\

The five men and the dog walk over to the old fishery, which is situated only a few blocks from Zellara's place. They want to get a first glance of the place: it is a weathered building on the docks that partly looms over the water. All the doors and shutters are shut and there is no sign of activity at this nightly hour, so the party decides to come back the next day.\\

