%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-24
\section{23 Gozran 4708}

The party spends its day-time hours in various pubs, trying to learn more about Rolth. Information is scarce: the man seems to be a drop-out student from the Academy. He must have been quite a freak, having been thrown out of the necromancy department for doing extremely nasty experiments on dead bodies. Sjo and Quint wonder out loud if he might have ... {\itshape buried} the corpses, not really sure on what kind of experiments would shock necromancers. Rolth is also rumored to have killed several people, although there is no hard evidence. No one knows where to find him. After being expelled from the Academy he went 'underground' and he has been eluding the law since that time.\\

In the evening the four friends return to Exemplary Execrables in Old Korvosa, the theatre where Lick's new play will be performed for the first time. Despite the theater's 'bad' reputation all the seats are taken. Even the private balconies are filled. One holds a smart gentleman with a neat haircut of thick brown hair which is starting to go gray at the temples. The man also has piercing eyes and a firm chin. Quint identifies him as Neolandus Kalepopolis, the seneschal of Castle Korvosa. According to the bard this gentleman holds more power than his humble title suggests. Another balcony seats the theater's owner Pilts Swastel in a crumpled red outfit. His buckteeth stick out from under his nasty moustache. To his right sits a gaunt man with hollow cheeks and numerous colored stains covering his hands and clothes. This must be the painter Lick was talking about, Salvator Scream. Swastel is constantly nagging to a small figure on his left, who looks like a gnome. The small creature takes the stream of insults and complaints without flinching his one good eye.\\

The lights go out and ominous music flows into the room in ever increasing waves. After the bombastic overture has exploded in an atonal finale, the curtains open. The stage shows wild hills under a almost living blue sky. To the left is a circle of standing stones.\\

A fresh, innocent-looking girl walks on stage, accompanied by her family, who have decided to live in the hills. The girl's father is a big brute, who forbids his daughter to wander around the ancient Shoanti graves. Still, the girl drifts off to the stones every night, where humanoid demons appear, whispering of the return of their god-made-flesh Donodarr. While the demons murder unsuspecting travelers, the girl undergoes a severe punishment at the hands of her father for disobeying his orders. Although there are no real-life fatalities, not all of the blood and violence on stage seem to be an act, much to the appreciation of most of the crowd.\\

At last the god Donodarr appears, played by Lucian Lycan (Lick) himself. He has the father torn to pieces by his demons and impregnates the girl in a steaming primitive ritual. Despite the bloody, frightening and even sickening nature of the play, the dialogues are ingeniously well written, though their brilliance escapes most spectators, who simply get off on the blood and sex. They cheer wildly during the gory scenes and the finale sees two aroused men and a woman with bared breasts climb on stage. The 'demons' grab them and wrestle them to the floor, giving one of the men a bloody nose in the struggle.\\

When the play is over the crowd goes wild, cheering and applauding loudly. Pilts Swastel appears on stage and takes in the waves of applause with Lick and the other actors. Despite his bandy legs and frail shoulders, the theater's owner seems to grow taller when the crowd starts chanting his name. "Swastel! Swastel!" With a final bow he thanks his public. Then the curtains are drawn.\\

As the party is leaving the theater, a young girl approaches them: "Are you Quint, Sjo, Balian and Puk, Lucian Lycan's guests? Please follow me."\\

She escorts them to the back stage dressing rooms. Lick is chatting with his fellow actors, dressed only in a loincloth. He sips from a glass of wine. "My friends, welcome. I hope you enjoyed the show", he smiles. Before Quint can give him his analysis another young girl throws herself at Lick, kissing him fervently while fumbling with his loincloth. "You'll have to forgive me," Lick sighs, "the price of fame! You know Eel's End, right? Give me half an hour and meet me there." Then he gets dragged into his dressing room.\\

