%!TEX root = ../crimson_throne_book_main.tex
% 2013-07-21
By seven o'clock the lambs leave for Endrin Square, where the circus has built a spectacular stage. Giggles remains behind with a skeleton crew to man the oyster bar. The boys and girls are excited, although some of them are plagued by nerves. The Varisian actors welcome their extra's with open arms. Alan informs them that he has found real rats for the show, so there will be no need for magic tricks and illusions to conjure an army of rodents. He also introduces the kids to an elderly lady with a yellow sheen in her eyes, Meep Gildenglare. Meep will be sitting under the stage to handle the rats. Alan warns the kids to leave the woman in peace so she won't lose control over her animal friends.\\

By 7.45 Jonah jumps on stage, dressed as the mayor, and addresses the crowd: "Dear people of Korvosa, ladies, gentlemen, boys and girls, he- and she-rats, baby rats and elderly rats, I bid you all welcome! For, if I'm not mistaken, this city counts a fair number of rodents amongst its inhabitants. Well, let me put your minds at ease, it can always get worse. Because once upon a time in East-Rikkan, a small town north of Westcrown in Cheliax, there lived rats ... a great many rats."\\

And so the play begins. The lambs can watch from backstage how the story unwinds, occasionally stepping onto the podium themselves to join in the action. Sjo has to jump round in a state of panic with a rat on his back and Eran, the small circus child, plays an endearing boy who begs his mother and beckons the gods to 'please get rid of the rat problem'. The rodents themselves enter and leave the stage through some holes in the floor. Sjo notices Meep's yellow eyes burning down below through the cracks and he hears her whispering to the animals in a peeping voice. Quint and Lick are also intrigued by the mysterious woman and dare the young Shoanti to sneak a peek under the stage.\\

When Sjo slips down to spy on the old lady, he's surprised to see a tail sticking out from under her skirt. When she turns to face him, his heart skips a beat: her face has morphed into the features of a rat. Apparently she is one of those dreaded 'wererat' creatures. Sjo quickly runs off to inform his friends of his discovery.\\

Meanwhile Alan is on stage, pleasing the people with his role of the Pied Piper. He pipes a light-hearted tune on his flute, apparently making the rats obey his every wish. The spectators applaud the rodents' antics. When the rats have been disposed off, the good people of Rikkan refuse to pay the piper. The children are up next. They follow the musician in a dancing queue and disappear behind a waterfall. Two of them are late, Quint and Sjo. Their stumbling and fumbling sends roars of laughter through the crowd.\\

When the show has finished, the lambs share in the joy of being applauded and cheered. Alan thanks all the kids and Liandra gives them each a kiss on the cheek. She also slips a gold sail into Sjo's and Quint's hand, to thank them for their excellent performance.\\

Shortly after the play the lambs return to the old clog shop to continue working at the oyster bar. Even after the sun has set the seats are still filled. Lots of alcohol has flown and many of the customers are drunk, as is Gaedran Lamm. When darkness has truly set in, fireworks light up the night sky. The spectacle ends with a series of heavy bangs and flashes, which blaze up in the shape of an enormous woman holding aloft a wand. She represents the gargantuan statue that once stood over the harbor, on top of the Gatefoot.\\

