%!TEX root = ../crimson_throne_book_main.tex
% 2013-06-02
\section{14 Erastus 4703 - Foundation Day}

That morning Lamm calls everyone into the courtyard. Flanked by his mates the old man is waiting for the children. "Today's party-time", he grins. "Today's Korvosa's 296th birthday! And obviously, little lambs, we'll be partying along!" Lamm expects an enthusiastic reaction, but when he doesn't get it, he shrugs and continues.\\

"Don't get too excited, you boneheads. Listen carefully. Today the king will make his annual visit to the Golden Market. The finest of Korvosa will celebrate and get very drunk. That means little alertness, but lots of money. That's how we like it! Spread out across town and pick as many pockets as you can. We will meet here tonight and you'd better bring me some hefty pouches! And of course, have a good time as well, it's a holiday after all." Lamm even manages a smile before sending the children off.\\

Although their master seems quite content now, Balian and his friends know that Lamm is one of the first to get drunk today and he expects his lambs to steal a serious amount of gold. If not, there will be hell to pay.\\

Sjo, Balian and Quint quickly make their way to the Golden Market. It is still early in the day, so the people who are visiting the market right now, are actually there to do some shopping. But since it is a holiday, the crowd is bigger than usual and also in a finer mood. Quint attempts some stand-up comedy, trying to weave the king and his harem into his jokes, but he makes only a few pinch. His efforts serve as a perfect distraction for Balian to pick some pockets, though. Seeing how well they have become at this job, the boys entertain the thought of building up their own private stash, in case they ever need it. They decide to hide it the sewers next to the old clog shop where they usually do their rat hunting. Especially the barred dead end would make an excellent hiding place, since the bars are only wide enough to allow a child to wriggle through.\\

By three in the afternoon the streets are packed with people who are psyched to see the king. The three boys have located a juicy target in the masses: Korvosa's magistrate of commerce, Garrick Tann, also known as the most hated man in Korvosa because he is in charge of taxes. Quint and Sjo move through the crowd to position themselves in front of the man, while Balian finds a spot behind the magistrate.\\

When the king comes into view on his beautiful black stallion, Sjo and Quint start screaming and jumping enthusiastically, distracting the man behind them. Balian seizes the opportunity to cut Tann's purse and also lift his dagger from its sheath. Then the boys sink into the crowd, trying to stay ahead of the approaching procession.\\

Although the monarch is getting older, he looks quite impressive in his ornamental gold breastplate and crimson cloak. The king is flanked by field marshal Cressida Kroft, the commander of the Korvosan Guard, and the seneschal of Castle Korvosa, Neolandus Kalepopolis. Twenty Korvosan guards on horseback fall back behind the trio and six members of the Sable Company keep a close watch from the sky, seated on the backs of their hippogryphs, much to Sjo's excitement, because the young Shoanti is fascinated by the black aviators.\\

Suddenly the crowd's cheering turns into a different kind of commotion. A beautiful young noblewoman on the other side of the street can't control her white mare and is thrown from the saddle. When the king sees her falling, he halts and slowly dismounts.\\

"By the gods," the king utters, reaching out his hand to the woman, "Shelyn truly blesses me today, what rare beauty crosses my path? Are you hurt, milady?"\\

"Lord Eodred, oh, I'm so ashamed. Forgive me for interrupting your procession with my clumsy behavior", the girl sighs. Her accent indicates she is from Cheliax.\\

"A welcome distraction on a boring day. Same show every year, put on a happy face and wave at the cheering faces. I know better ways to fill my days, but you know how it works: noblesse oblige and all that", the king confides. "Allow me to help you up."\\

"Oh, of course, silly me, I'm still lying in the dust in front of the king of Korvosa", the girl stammers. She elegantly reaches out for the king.\\

"You wouldn't be the first to crawl through the dust for me," the king smiles, "but in your case it's really not necessary. Would you do me the honor of joining me?"\\

"Oh," the woman blushes, "I'd love to, my lord." The crowd cheers when the noblewoman rides off at the king's side. While everyone is staring at the lovely couple, Quint's eye falls on something in the dust where the woman fell. He dives through the crowd and picks up a bejeweled brooch with a broken clasp. It is made of white gold and inlaid with small diamonds. There is an inscription on the back: "To my darling Ilie, dad". It must certainly be worth hundreds of golden sails.\\

When the king is gone, Sjo counts today's loot. Especially Tann's fat purse has given the boys a nice catch, over 12 gold pieces in value. On top of that they have a priceless jewel and a dagger that is expertly crafted.\\

The boys decide to hide the brooch and the masterwork dagger in the sewers and hand the money to Lamm, when he returns in the evening. Since there is no need to continue stealing, the boys enjoy the rest of the day off like normal children would. They also learn the name of the noblewoman who has enthralled the king: Ileosa Arvanxi from Cheliax.\\

