%!TEX root = ../crimson_throne_book_main.tex
% 2013-06-15
After the show the youngsters realize that the excitement made them forget to do their jobs and pick pockets. They decide to make amends and join a crowd that is gathered around a carni who's juggling burning torches and breathing fire. Balian lifts another pouch, but when he examines it, it turns out to be a meager catch of one silver shield and a couple of pinch. Suddenly a hand seizes Balian by the collar. A blue-eyed gypsy holds the boy in place with his firm grasp. "Excuse me, young man, master Terdal would like a word with you." The man is quickly joined by his colleague from Madame Mask's show. When the boys get ready to resist, the blue-eyed carni quickly pulls out a knife, which he gently places on Balian's throat. "I have no intention of hurting you, boy, if you just come along. All we want to do is talk." The lambs realize they are outmatched and follow the gypsies to a barrel-shaped wagon, where an older carni with a patient face kindly invites them to take a seat.\\

"Hello, my name is Alan, Alan Terdal", he says. "My companions have noticed your little ... antics, shall we say. You do understand that we can't have anyone picking pockets at our fair. It reflects badly on my kind, I'm afraid. So what shall we do with you, it would be a pity to hand you over to the guard, now wouldn't it?"\\

At first the boys are not inclined to negotiate, but when they finally agree to return the stolen money, Alan nods approvingly and makes them an offer. A Varisian circus like his is perpetually plagued with a bad rep for deception and petty theft, no matter how honest the carni's really are. Alan asks the lambs to act as his eyes and ears in the crowd, picking out other pickpockets from the visitors. He's even prepared to pay the boys for their services. When the youngsters agree, Alan impresses on them not to interfere themselves when they spot a thief, but to warn him or his companions, Jonah Blue-eye or Landro the Fiddle. The boys can also eat and drink for free or participate in any of the attractions.\\

Balian, Quint and Sjo enjoy the rest of the afternoon at the fair, eating and drinking as much as they want, but keeping their eyes open at all time. When Balian plays at the high-striker game, he smashes the heavy wooden mallet on a lever to sends a puck up to a lion's head on a pole. The puck fails to meet its goal and the head does not roar, as it did with the previous contestant. Instead it simply meows and licks its lips, to the amusement of the bystanders.\\

