%!TEX root = ../crimson_throne_book_main.tex
% 2013-06-15
The three boys take the road north, towards the Dwarfwalk gate. On the corner of Kroft Boulevard and Threemast Street they see the pawnshop, 'The Hefty Purse'. It is a sturdy stone building. In front of the shop is a small group of people. Five guards are talking to a grieving woman and a frowning man in chain armor. A child is standing behind the woman. When the woman notices her son listening in on the conversation, she gives him a hug before asking him to go and play while she's talking to "these gentlemen".\\

The child shambles down the street, where Balian, Quint and Sjo approach him. His name is Bastian Veldan. His father was murdered last night at the circus and his pouch and keys were stolen. His father's body has already been taken to the Gray District, where the priests of Pharasma will bury him.\\

His dad bought things from people who needed money. If they didn't buy it back within a certain time span, his father could sell these things off to someone else, Bastian says. The man in chainmail, next to his mother, is Gerbrand, the head of security in the shop.\\

The woman calls out for her son to join her and the guards to the Gray District and greet his father's remains. The head of security accompanies them as well, leaving the shop in the hands of one of his agents. After the woman closes the shop, the party leaves.\\

A couple of minutes later a shifty character sneaks up to the shop. He scans the street and pulls out a key ring, trying several keys before opening the door and entering. The lambs wait for a couple of minutes, before they move over to the pawnshop and peek through the window. They see a dead guard lying on the floor in a pool of blood. The youngster wait for another ten minutes. Then they see the burglar coming out again with a leather satchel around his shoulder. A severe limp betrays the fact that he is wounded. He scurries down an ally, making his way to a rundown sailing boat in the Eastshore docks.\\

Sjo and Quint alert two soldiers from the Korvosan Guard who are patrolling the harbor, informing them that a murderer is hiding on a boat close-by. The two guards, a man and a woman, accompany them to the ship and order the man to come out, before kicking in the door to the cabin. Sjo gets a better look at the man now: he is pale and skinny, has blood on his clothes and heavy bags under his eyes. He's still trying to get up from behind the table, seizing a bloodied garden hook in the process, when the guards burst in and knock him out cold.\\

Next they examine the cabin. The leather satchel is on the table and contains several items of jewelry. There is also a scroll on the table, which bears fresh bloody fingerprints. It's the deed to the ship, which is the property of Verner Salor. The blood on the garden claw looks fresh as well. The guards don't seem surprised when they find drugs on the table. Judging from the man's physical state, he is most likely an addict.\\

The female guard figures the man is a pesh addict, who pawned his ship for a loan, so he could sustain his addiction. When he couldn't pay back the money he owed, he must have killed the pawnbroker.\\

The two guards join the lambs to the Umbra Carnival, where they easily convince lieutenant Jalento that they have caught the real killer. Alan Terdal is very happy that the carnival's name has been cleared and invites the lambs into his wagon to thank them. He also confesses that Jherizhana, the sphinx, doesn't exist: she is just an illusion conjured by his daughter. That is why the sphinx could be the killer. When Alan tells the kids that the circus will probably be closed for a few days, out of respect for the man who was murdered, he notices that the youngsters are disappointed. When they confront him with the horror of their master, Gaedran Lamm, the old Varisian feels for them. Although he can't make any promises, Alan assures the boys that he will look into the case more closely.\\

He also hands them a magic wand, which holds cure spells. He suspects the lambs might have need of it from time to time. The gypsy is happily surprised to find out that Balian, Quint and Sjo all possess the magic inclination to activate the wand. When he sends the boys off, their predicament is still mulling through his mind.\\

