%!TEX root = ../crimson_throne_book_main.tex
% 2013-11-24
\section{16-18 Desnus 4708}

The heroes return to Korvosa in the company of a small convoy. Merchant Rollo and his two sons ride on wagons and each carry one of the culprits. Simo and Addie prove to be no threat and are quickly relieved of their bonds. Even Ozzy is not tied up anymore on the second day of travel. He realizes that his scheme failed and he's lucky to have gotten away with his life.\\

After three days of travel Korvosa finally graces the horizon. While approaching their home city, the companions note that several small plumes of smoke rise up and a great number of travelers has been stopped at the gate, creating quite a queue. When they join the line, Quint learns that the king has died a couple of days ago. The city has been in chaos ever since. All non-natives are being denied entry to the city, so the four young friends have to say goodbye to their fellow travelers, as they are the only ones who are allowed in.\\

The companions quickly make their way to the High Bridge. Houses in East Shore have all shut their doors and shutters and there are only a few people in the streets. The ones who are, rush to their destinations as quickly as they can and keep their heads down. Someone has chalked a message on the wall of an old building: "No whore for queen!"\\

When they reach the High Bridge into the city proper, Quint, Sjo and Puk question some guards to find out what is going on in Korvosa. They learn that the king died on the thirteenth of Desnus. Unable to regain his health, Eodred was finally felled by his mysterious disease. None of his doctors or priests managed to find a cure. Riots erupted shortly after the monarch's death as people protested against his incapable, power-hungry widow Queen Ileosa assuming the throne. No one actually knows if the queen has what it takes to take over power, but the general consensus seems to be that Ileosa is nothing more than the "sois belle et tais-toi" (shut up and look nice) type, not fit to rule. There is even more worrying news, as seneschal Neolandus Kalepopolis has disappeared shortly after the king's death. He is rumored to have died in the first riots.\\

Eodred's Walk, the square at the far end of the High Bridge, has been overrun by rioters. Several hundred protesters are pushing back Korvosan Guards in the direction of Citadel Volshyenek, the Guard's headquarters, shouting hateful words like: "Hang the b+$~#!" or "Down with the filthy usurper!" The demonstrators charge the soldiers and one of the guards loses his balance while his brothers in arms are trying to retreat. The crowd cheers and gets ready to tear the man to pieces.\\

Quint jumps in their midst and attempts to sway the attackers with words. He urges them to calm down and use common sense. He points to Korvosa's historical strength in unity. Both Puk and Quint recognize some dockworkers in the crowd whom they address in person. "Dorik, don't risk your life, your mother needs you!" "Gerrit, your wife's pregnant, don't do anything stupid!" Sjo throws in some religious motives: this riot goes against Abadar's need for structure, it undermines civilization. Quint also picks out the most hot-headed protestors and focuses his attention on them. Meanwhile Sjo and Balian pick up the unfortunate guard and return him to the safety of his brothers' ranks.\\

Quint's and Sjo's words persuade enough people in the crowd to step down and soon the mob disperses and the threat is averted. The last to leave are a number of head-strong troublemakers who look like the main agitators. But they also leave when they see that they have lost the crowd's support.\\

The companions join the guards to the citadel, where they meet up with Field Marshal Cressida Kroft. The leader of the guard looks tired, as she confesses to not having slept for a couple of days. Sjo offers to help and Kroft gladly takes him up on his offer.\\

She explains that a number of guards have failed to show up for duty. Although everyone was ordered to come in and serve, several soldiers refused, worrying more about their family's safety than the city's. While Cressida Kroft does not condone, she can understand why these guards have 'deserted'. Still she needs every able-bodied guard to be at his post right now. Moreover, this kind of behavior is bad for the morale of those who are present.\\

Yet, not all deserters have family. Some of them are simply using the riots as an excuse for personal gain. One such man is Verik Vancaskerin. Upon the king's death, he convinced several fellow guards of the queen's incompetence and together they deserted their posts. They have now set up shop in an old butcher's, All the World's Meat, in Northgate, handing out free meat to citizens in need, while spreading messages of hatred against Ileosa. Kroft does not dare to send in her own men to apprehend the deserters, fearing their talk of secession might infect even more guards. She also dislikes the idea of guards killing fellow soldiers. So she asks the companions to take care of the situation. She prefers the traitors alive, certainly Vancaskerin himself, as she wants to find out why he deserted.\\

After a quick stop in Zellara's house, where the remaining lambs are all safe, the companions head to the North Point district. As darkness is already upon them, they decide that it is not a good idea to go to the butcher's shop right now. Still, they use the first few nightly hours to gather some information on the place. The word is that a couple of guards have taken over the place and hand out free meat every morning. The deserters have taken to calling themselves the Cow Hammer Boys and rumor has it that you can hire them to get rid of small pests. Apparently they took care of Dicey Dewy, a local rogue, two nights ago. The thug has not been spotted since.\\

Someone else admits to having been inside the butcher's. A note on the wall says: "We provide what the queen can't", referring to the fact that most shops have been closed for the last four days and food has been getting scarce. There are four cow Hammer Boys: Baldrago, Malder, Parns and Karralo, all able-bodied and battle-hardened soldiers. Their boss, Vancaskerin, does not show his face very often. People say that he still wears his uniform. The companions decide to leave things for now. They will return in the morning and see if they can approach the deserters "peacefully".\\

