%!TEX root = ../crimson_throne_book_main.tex
% 2013-06-02
\section{13 Erastus 4703}

The sun hasn't risen yet when Balian wakes up. His little sister is talking to the pup Spyder: "Shht, be quiet ,Spyder. We have to be smart about it, not like those stupid boys. You have to stay here, no you can't follow them ..." If Balian asks Alika what's going on, she informs him that Jules and Jecko have left. They snuck out, first Jules and then Jecko. Spyder wanted to follow them, but Alika is keeping him here, because it's not smart to try and run away. Someone always ends up paying. Balian wakes up his friends, but before the boys can figure out a course of action, they hear heavy footsteps approaching their dormitory.\\

The door to the outhouse is flung open. Giggles tears into the room: "Ruaaah, wake up, little lambs, wake up! Outside! Now! Nooooow!" The kids scurry to the courtyard, where they come across a gruesome scene: Lou the swordsman is nailing Jules to the backdoor of the shop. Lamm and his men are gathered around him; Jecko is standing inside, trying to fade in the shadows as the first rays of sunlight hit the rooftops.\\

Lamm looks furious. He regains just enough control over his breathing to hiss between his teeth: "No one leaves without my permission. No one abandons me! This is what happens to little black sheep who think they can betray me! Observe and consider if this is what you wish for yourselves! And praise the gods, because if we hadn't caught this lousy deserter, one of you would be hanging here in his place!"\\

Lamm turns to face Jules. "So you think you've got enough heart to resist me?! I don't think so, dog!" Lamm pulls out his dagger and stabs the weapon into the boy's chest. While Jules gasps his life away, Lamm keeps carving, cracks open the boy's ribs and cuts out his heart. He holds up the bloody organ: "This is all the heart he has left! No one deserts me!" Then the old man barges into the clog shop.\\

The lambs are sent back into the outhouse, where they try to process what just happened. Alika is inconsolable and is shivering with fear and sorrow.\\

Sjo boils with anger, especially towards that little rat Jecko. But Quint serves as the voice of reason. He figures that someone else would have had to pay the price if Jules had gotten away, possibly Amarice, since she is the oldest. It is usually the oldest who is charged with the responsibility over the group and who ends up paying when things go wrong. So even though Quint doesn't like the fact that Jecko is a traitor, he has to admit that Jecko saved someone else's life.\\

An hour later Hookshanks Gruller enters the outhouse and addresses Sjo, Balian and Quint: "What's this, you lazy bums, you think you get the day off simply because one of you's dead? Come, there's work to be done!" The gnome takes the three boys to the courtyard and waves his hooked weapon at Jules' mutilated corpse. "Take it down!" Since Jules has been nailed to the door, there is no easy way to take him down, and the boys have to tear him loose. While the kids working, the gnome hums a popular nursing rhyme, slashing his hook around Sjo's and Balian's necks during the 'deadliest' parts of the song:\\

"On Croaker day, on Croaker day   On Croaker day, on Croaker day   Afterwards Hookshanks orders the boys to feed Jules' corpse to Gobblegut. The boys are disgusted while watching the alligator rip the body to pieces. Hookshanks adds to the drama by threatening Balian: "Maybe Gobble wants some more, what do you think? Or should we feed him something more juicy, like a little girl whose feeble attempts at labor will never be enough to pay off her father's debts? Har har har, pwak, pwak, you chicken, your day will come soon enough, mark my words! Now go and fetch the others, I've got some real work for you!"\\

The lambs have to sweep the city streets for the rest of the day, a simple job Lamm likes to perform for Korvosa once in a while. He's only paid a few pinch (copper pieces) for it, but it buys him a lot of goodwill, so his small-time operation is left in peace.\\

That night the three young friends contemplate what to do. Betraying Lamm to the Guard will not work, because the old man is not officially wanted. They could leave a trail while performing their own little crimes, but that would incriminate them as well. Moreover, if Lamm were to get wind of this treachery, his wrath would be terrible.\\

The lambs even involve Jecko into their conversation. When they confront him with the fact that he ratted out Jules, he defends himself, saying he saved their lives. Jecko is just being careful and refuses to pay for someone else's stupidity. He understands the urge to escape, but refuses to do so, because someone always pays. The only plan he has ever devised to escape Lamm's clutches, is befriending someone with means, who can buy his freedom. Lamm knows a good deal when he sees one, so if he was offered enough money to let a lamb go, he would definitely agree. And more importantly, no one would have to suffer or die. Sjo doubts Lamm will ever let anyone go, since he can't afford to have his victims freed. They could set up a lawsuit against him, providing personal testimony of Lamm's evil and illegal deeds. Jecko urges caution, he says that Sjo, Quint and Balian are in the typical age category when the lambs start thinking they can get out. He warns them to perish the thought, because no one has ever succeeded at this in over twenty years.\\

For now, the three friends decide to gather more information on the relationship between their captors. Maybe they can eavesdrop at night and find out who amongst Lamm's cronies doesn't fit in with the rest.\\

