%!TEX root = ../crimson_throne_book_main.tex
% 2013-11-01
 \section{10-13 Desnus 4708}

The companions follow the Jeggare river for three days until they reach the first fields and orchards of Heavengard. Suddenly they pick up screams and the smell of burning hay. Looking through a four-foot-high hedgerow, they notice three hulking scaly creatures leaning over a young halfling couple. The attackers are kicking a boy, while a girl with a torn dress is screaming her lungs out. Towering over the assailants is a smoking haystack, which was probably set on fire by the lizardman holding a smoldering torch. The two other lizardfolk have a wickedly barbed club in their hands.\\

The heroes intervene and Balian's greatsword chops down a lizardman warrior in one mighty stroke, while Sjo takes down a second enemy. The lone survivor turns and runs.\\

The halfling boy was beaten badly and has lost consciousness, a situation that Sjo's healing powers quickly rectify. The girl, Maisy Booginsfoot,  thanks her saviors profusely and claims that the reptilemen ambushed her and her friend Jacob Merrybrow while they were ... looking for a stray goat. Quint realizes that the halflings were probably fooling around in the hay and smiles.\\

The companions join the young halfling couple to their village. Jacob and Maisy know Sarai's and Lauro's grandmother well. Her name is Mother Grundy, the town' herbalist, although most people have taken to calling her Mother Grumpy since her son and grandchildren left. They are convinced that she will be overjoyed to see her grandkids alive, but they suspect that she doesn't know that her son Bono has passed away, so they advise the visitors to be gentle when breaking this news.\\

Heavengard is nestled in a picturesque valley between rolling hillsides full of fruit trees. The Jeggare River cuts through the heart of the dale and leads the travelers to a dozen low wooden buildings and two stone ones. Although it has been a long time, Sarai remembers the way to her nana's house. The thick, aromatic smell of herbs pervades the air. Sarai approaches the door and notices that it is slightly ajar. Carefully she pushes it open and gazes into the room. Dried herbs hang from the ceiling and a large cauldron bubbles noisily over the fire. An old halfling woman with a few teeth missing looks up, surprised to see strangers on her porch.\\

"Nana?" Sarai whispers, "it's me, Sarai ... and Lauro ... we've come back."\\

"Sarai? Sarai, is that really you?" A broad smile appears on the woman's face as she wipes her hands with her apron and rushes to the halfling children in her door. "Sarai! Lauro! Oh, Cayden Cailean be praised, my grandchildren have returned to me!" Tears roll over the halfling's cheeks as she pulls the children to her breast. "And where is my son, where is Bono?" she sniffs.\\

"Oh, nana, daddy's gone. He died three years ago. A bad man took us and made us work as slaves, but these heroes saved us!" The old herbalist buries her head between the children's shoulders and cries, while a crowd of halflings has gathered outside her house, staring at the wonderful spectacle.\\

A small chubby halfling with elaborate curly hair and rich, purple clothes steps forward. He makes an elegant bow: "Welcome to our humble town, strangers. Allow me to introduce myself, mayor Ossy Applebottom, I'm delighted to make your acquaintance. I believe we owe you our gratitude for saving and returning some of our own. Please, would you do us the honor of joining us tonight for a small celebration as a token of appreciation? I invite you all to my house after sunset."\\

Jacob Merrybrow introduces his saviors to his family and his mother kindly offers the companions a place to stay at their farm.\\

Later that evening the companions join the Merrybrows for the party at the mayor's mansion, one of the two stone building in town and easily the largest structure. Rosebushes climb up the walls to the left and right of the front door and circle around a stone sign above the door that reads 'Theatre' The whole village has gathered inside, in what looks like a small theatre hall, which is very high for halfling standards and offers ample head space for even Sjo. The room explodes in loud applause as the heroes enter the auditorium. Puk is immediately surrounded by a number of girls. Maisy's sister Frida is clearly infatuated with the courageous rogue and the young halfling appreciates the attention.\\

Mayor Ossy Applebottom thanks the saviors again and entertains the crowd with some music. Afterwards he makes his way to the companions and starts chatting cheerfully. It turns out he did a bit of adventuring himself when he was younger, with Simo Sideburn and Addie Lightfoot, two other halflings, but they are retired now. Since then he has grown a bit, Ossy smiles, patting himself on his large belly.\\

The heroes accept Applebottom's invitation to take to the stage themselves. The mayor even joins them in an improvised version of 'the pied piper'. Ossy is clearly over the moon with visitors who appreciate the fine arts of theater, which seems to be his passion.\\

Although the unexpected return of Sarai and Lauro, the spectacular story of their rescue and the wonderful play of 'the pied piper' excites the halflings, the small folk are preoccupied with another matter. The lizardmen's attack on Maisy and Jacob is not an isolated incident, it seems. While the reptiles from the Broken Axe clan have never felt the urge to leave their homeland of the Feverglades before, they did so twice during the last week. Six days ago Ossy Applebottom and his men were attacked by the scaly monsters at the border of the glades and today the lizards made it all the way to Heavengard! Ossy claims that he and his men were gathering wood when a group of Broken Axe warriors attacked them. They barely managed to escape with their lives and both Simo and Addie were gravely wounded.\\

None of the halflings knows a lot about the Feverglades, other than that it is a dangerous and soggy place where they shouldn't venture. They claim that their habit of avoiding the swamps is part of a mutual understanding with the lizardfolk: the halflings don't go there and the lizardfolk don't come here. But now the agreement has been broken, although no one has any idea why the Broken Axe clan suddenly turned aggressive. It's probably in the monsters' nature.\\

Ossy also knows that the peace agreement between Heavengard and the Broken Axe clan dates way back to the days of Harv Mulder. Mulder was a strange dwarf who lived here more than a generation ago ... well, not "here" exactly, but in the swamps. He got on well with the lizardfolk and negotiated the treaty for the halflings. Mulder lived in a mill by the Jeggare River, in a place where the current was much stronger than here in Heavengard. As far as Ossy knows, only two men have ever ventured into the Feverglades, this Mulder dwarf and - three centuries ago - Montlarion Jeggare, the famous explorer who gave his name to the river.\\

Ossy praises his guests' courage and skill in battle once again and asks them if they want to help protect Heavengard from the attacks of the lizardfolk. He does not understand why the reptiles turned hostile, but it is clear they have become a threat. Today's attack proves their evil intent and it will take more than some simple farmers to defend the town.\\

He offers the companions 200 gold sails form his personal fortune to locate the Broken Axe clan and renegotiate the peace treaty. If the lizardfolk can't be swayed, the heroes should explore other options to keep the village safe. If necessary they should chase away the scaly folk. Ossy stresses again that the halflings don't stand a fighting chance against the Broken Axe clan. Fortunately no villager has died yet, but halflings' luck and Cayden Cailean won't protect them forever.\\

It is late when the companions turn in for the night. Sjo, Puk and Balian quickly sink into a deep sleep, but Quint is plagued by nightmares. He is wandering around a huge keep with high walls and oppressing hallways. He feels tiny, but his hands are enormous. His breath surges loudly through his throat and reverberates in his head. Every dark room is empty and it feels like the stone maze is closing in on him, when he suddenly arrives in a huge hall. The room is bare, except for a fireplace to Quint's left. Flames dance around and throw scary shadows on the walls. One of the dark shades floats closer and takes the shape of a skinny, old man with thin gray hair and hollow cheeks. He is dressed in a long nightgown and looks almost like a ghost. Then the man open his eyes, his fiery gaze burning a hole in Quint's heart, as he sighs: "Finally I understand, brother. You have betrayed me."\\

