%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-16
Quint suggests holding off on the second reading until the next day. Zellara agrees, confirming that she is tired and would prefer to do the reading from the familiar surroundings of her parlor. Lick seems happy as well that no further fortunes are being told tonight. He abruptly takes his leave, wishing his comrades a good night's sleep and inviting them to have lunch with him tomorrow as he swings through the door.\\

Balian, Puk, Sjo and Quint take turns keeping a look-out, while the lambs sleep safely in their hammocks.\\

\section{22 Gozran 4708}

The first order of business is taking the lambs to the orphanage. Kester, the oldest of the boys, informs Quint that he and some of his mates would prefer to stay here, if possible under the protection of the heroes. In exchange the kids could help out with all kinds of jobs, like looking for the black-haired lady. It takes a bit of convincing, but finally it is decided that Kester, and four other lambs, Korwick, Heldrin, Mouse and Lerrim, can stay. Four of them immediately start cleaning up the old fishery, but Mouse has to stay in bed. The boy has a bad case of pneumonia and Sjo prescribes lots of rest.\\

The other ten lambs leave for the orphanage. Mama Mira is surprised to see so many children being brought in at once, but she promises to take care of each of them. Quint notices another guest in the orphanage, a woman of noble birth, Zenobia Zenderholm. She is the city's main judge and has a fierce reputation for passing merciless judgment, from which stems her nickname the {\itshape hanging judge} . Apparently she has a soft side as well, spending her spare time to help out with the orphans. Balian asks her if she has any information on the drug supplier Rolth or his new ally, the black-haired lady. When he tells the judge about last night's infiltration of Lamm's operation, she frowns upon the party's actions. Normal citizens should not take the law into their own hands! That is the Guard's duty. She has heard of this Rolth character, she admits, especially since he's also suspected of having killed a number of people, but she says he has managed to evade arrest so far. If Balian or his companions have any information on this man, they should tell the Guard. They should certainly not take the law into their own hands again! The black-haired lady means nothing to judge Zenderholm and the fact that she comes and takes young girls is not a crime as such, so if the lady is guilty of anything, Balian had better make sure to collect evidence!\\

