%!TEX root = ../crimson_throne_book_main.tex
% 2013-09-07
\section{24 Gozran 4708}

Mouse is finally on the mend: his fever is down and he is out of his bed for the first time in days. Lerrim, the Shoanti boy, is still as introvert as ever and Mouse wonders whether his friend might be 'sick in his soul'. He asks Sjo to get the boy in touch with his Shoanti roots, hoping that will help him snap out of his apathy. Still there are not a lot of barbarians in Korvosa and those who are, are either completely out of touch with their culture, like Sjo, or living among the poorest of the poor, failing to make it in both the wilds and civilization.\\

Quint confirms that there are only a handful of barbarians living in the city, and adds that most of them don't even live within the city walls, but rather in the two communities on the far bank of the Jeggare River, Thief Camp and Trail's End. Both settlements have an ill repute for being pauperized and unsafe. Varisian gangs rule the streets and Korvosans of Chelish blood had better not go there unprotected. Since Thief Camp is rumored to be even more dangerous, Quint suggests trying Trail's End. Still he would like to pay a visit to the House of the Sun first, to check up on Lick.\\

The temple of Sarenrae basks in the early sunlight during morning mass on this beautiful Sunday. Sjo leads his friends to the infirmary. Lick's condition has hardly improved: he's caught in a delirious sleep. Sjo talks to Iris, the priestess who tends to the sick, and asks her to have highpriest Ezekiel Sollux check in on the patient personally later today.\\

Next the young companions cross North Bridge to get to Trail's End. The settlement is dreary indeed, with crooked houses and battered piers. Dozens of unkempt onlookers shoot unfriendly glances at the visitors, who spot a tall, skinny man with a bald head and tattoos over his torso. This man is clearly a Shoanti, although there is little about his broken frame that reminds them of the heroic barbarian warriors. When they address him, he points out that he is not looking for trouble and laughs when they ask for his help. Then he bolts as a group of Varisian gangsters approaches, Sczarni!\\

One of the gangsters offers to help the strangers with whatever they need, provided that they surrender all their weapons and wealth. After all, "Batista's information" has a price, he smiles. Sjo does not feel like negotiating on these ridiculous terms and simply spits in the man's face; not a smart move, considering that the Sczarni outnumber the companions two to one. Balian does not waste time and draws his new blade, swinging it in a wide arch at the head brute. The man takes a vicious cut, but does not go down yet. Puk seizes the opportunity and slips his short sword between the man's ribs. This time he drops on the ground. This only serves to ignite anger in the other seven thugs, who draw their knives or clubs to attack. Quint takes two hits and goes down quickly, the Sczarni seem to have a serious punch behind their blows. Puk suffers the same fate, leaving only Sjo and Balian to face the seven opponents.\\

Out of the blue a strong voice resounds: "Get back, you thugs!" Two men come running in: one of them is a strapping fellow armed with a spear, the other one is dressed in the garb of the Korvosan Guard. With one well-aimed swing of his sword he drops another Sczarni. The brutes drop back in the face of such a skilled guard and when another of their companions hits the ground, they run off.\\

The guard introduces himself as Grau Soldado. The man with the spear is Bayan, his brother. They have just returned from the service in the cathedral of Pharasma and are heading to Bayan's place for lunch. Grau invites the young visitors to join him, claiming that the house is much safer than the streets. Inside Bayan's wife Tayce is cooking stew, while his three children, Charlo, Rello and Brienna, are playing and laughing in the bedroom.\\

Grau is surprised to learn that Sjo and Quint have come to Trail's end looking for Shoanti. The only barbarians that live here, are pathetic losers, not even worthy of the name barbarian. He has heard of a delegation of Shoanti though, who are currently staying in the Gray District. He advises his guests to pay them a visit, but not before they have shared a meal with Bayan and his family.\\

