%!TEX root = ../crimson_throne_book_main.tex
% 2013-11-24
\section{15 Desnus 4708}

The companions spend the night in the mayor's manor, while keeping the Ozzy and his two minions locked up in the cellar. When mornings comes, all the halfling villagers gather at the house. They are not pleased when they find out Ossy Applebottom is behind the problems with the lizardfolk and that he tried to fool all of them for his personal gain.\\

Quint suggests that someone else assumes the position of mayor and appoints mother Grundy. His inspiring speech gets all the villagers to agree. Then he explains that he and his friends will take Ozzy over to the Broken Axe lizardfolk in order to negotiate a permanent solution.\\

While they are making their way through the swamp again, Sjo and Quint intimidate the former halfling mayor with horror stories of cruel lizardmen rituals. Ozzy offers the heroes more money, simply for letting him go, but they refuse. When they arrive at the Broken Axe settlement, they are taken to the island with the tree stump again, only this time they can enter the cave through an opening in the back of the hillock.\\

The leader of the clan turns out to be a glistening water naga, who goes by the name of Naamani. She is furious when she learns that Ozzy thinks himself the owner of swamp land, but when she squeezes him between her coils, the halfling readily agrees to sign all marshland over to the water naga and her tribe. The lizardfolk reward the companions for their good work by giving them a beautiful pearl.\\

Next stop is the watermill. The dwarves and gnomes are still at work, draining the glades, when the companions arrive. Quint states that the swamp has a different owner now, who has ordered the trespassers to stop their work and leave the Feverglades. He adds that Ozzy will pay them what is owed upon arrival in Heavengard. Gilas, the gnome engineer, realizes that he has no other option than to agree. So the dwarves and gnomes join the young heroes for Heavengard, but only after they have buried the lizardfolk heads. Gilas also confirms that the water level in the glades will return to normal in a few months time. The engineer shuts down the draining system and Quint and Balian sabotage the pumps, so no one can restart them by simply pulling a lever.\\

It is late in the afternoon when the party gets back to Heavengard. The locals have not been idle either: they have decided to strip the three traitors of all goods and banish them. One of their own, the village merchant Rollo, will travel to Korvosa tomorrow with three carts of goods. He will take Ozzy and his men and release them in Korvosa.\\

Mother Grundy also rewards the party. Since the halflings have no desire to gain from Ozzy's banishment, they have decided to award Ozzy's confiscated ring and Simo's armor to the heroes. Using Zellara's harrow deck, Sjo finds out that both items are magically enhanced: the gold band is a ring of {\itshape protection +1} , which goes to Balian, while the small sized  {\itshape studded leather +1} fits nicely around Puk's chest. The party halfling also enjoys his last evening in Heavengard. The village youngster admire him as their personal hero and red-cheeked Frida is even more infatuated with him than before. Puk does not return to his bed that night.\\

\section{Level up: level 2}

