%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-16
When the party approaches the castle's main gate, the guards stop them and inquire about their business. They are allowed into the entrance hall, where they meet a tall man dressed in exquisite garb, at least ten times as expensive as Quint's new clothes. He has a haughty look in his eyes and scoffs at the young heroes. "What is this? Vagrants to meet the king? One would say that the Chelish ambassador comes first! I've been waiting here for two days!"\\

Next a shapely woman in full plate armor walks in. "Greetings, my name is Sabina Merrin. I'm head of the Queen's Gray Maidens. I hear you have something that belongs to her majesty. Well, do you?"\\

Before anyone can answer, the impatient ambassador interferes: "Miss Merrin, how inappropriate! You entertain these beggars while the ambassador of your most important ally is made to wait? Just imagine what will happen when I inform her infernal Majestrix Abrogail of this. She won't take kindly to this insult! I won't be held accountable for the consequences, I warn you. If you want to continue enjoying Cheliax' good graces and fine goods, you'd better ..."\\

The armored woman steps in front of the windbag, pushing her face in his. "Ambassador Amprei, now YOU listen to ME. We told you today, yesterday and the day before that the king is indisposed and cannot receive any visitors. How much clearer do you want me to spell it out: NO VISITORS! If you wish to hang around here all day and waste your time, that's your choice. For all I care, you can remain here until you wear a hole through the floor. As long as king Eodred is ill, he will not see you or anyone else. But if you think that you can come here and whine, whine and whine some more, you're mistaken! If you raise your voice one more time, I will introduce you to one of OUR fine goods: Korvosan steel!" At that Sabina draws her longsword.\\

The ambassador stumbles backward, obviously aggrieved. Still he seems to have got the message. He turns around and walks out, grumbling through his teeth: "Outrageous, you ignorant peasants ... never heard of manners, have you ..."\\

'I'm sorry you had to witness that", Sabina Merrin continues. "Ambassador Amprei has been getting on my nerves for three days now. He doesn't know his place. Still, back to you, you have something that belong to her majesty?"\\

When the party shows her the brooch, Merrin invites them in, sending the guards back to their posts. While she leads the way to the throne room, she curtly asks the visitors how they would like to be introduced to the queen: Quint and company. She also expresses her gratitude and relief for seeing such loyal and trustworthy citizens.\\

The throne room is huge, though there is scarcely any furniture. Three stained-glass windows show portraits of King Eodred I, Queen Domina and his majesty Eodred II. The inside walls are covered in tapestries and curtains of crimson silk. A huge fireplace stands in one corner, its mantle shaped like an enormous tree with its branches stretching out to the high ceiling. On a low dais of granite, sits the crimson throne, draped with red silks and crimson cushions. Seated comfortably is a celestial beauty with ginger hair and a clean alabaster skin. She nods kindly as her guests are announced. Quint and Puk notice that Sabina blushes ever so slightly when she addresses the queen. The Gray Maiden takes the brooch from Quint and hands it to the queen, then she takes up a position at the throne's left side as Ileosa lovely voice resounds:\\

"I lost this brooch a long time ago. I hadn't expected to see it again, to be fair. And still, in these trying times, with my husband ailing under his sheets, you prove me this kindness. As you might have deduced, it was a gift from my late father. It holds great sentimental value for me. Returning this brooch is an act of honor, but also a token of kindness. Please tell me how you came by it."\\

Quint explains that they found the brooch five years ago, on the day Ileosa met the king. The jewel was lying on the ground in the dirt. Quint picked it up and hung on to it, obviously convinced that it must be of great value to someone, but not linking it to the queen until they came by the old flyer earlier today. He immediately put on his finest clothes and hurried to the castle.\\

Ileosa is obviously very pleased. "I would like to reward you for your kindness", she concludes. "You are truly an inspiration and I feel humbled by your loyalty. Allow me to give you this." The queen signals Sabina to hand the PCs a silver chest which contains 12 gold ingots imprinted with the royal seal of Korvosa. At this point the queen excuses herself and the head of her bodyguard escorts the party back to the gate.\\

