%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-16
After the reading the friends return to the old fishery. The boys are hard at work cleaning the place. They say that someone came by with a message from Lucian Lycan. Sjo is quick to explain that Lucian Lycan is actually Lick, but Kester had already figured that out. Anyway, Lick expects his friends at the {\itshape Traveling Man} in Old Korvosa for lunch. The Travelling Man is a small tavern in the oldest part of the city. Despite its size it is well known for being close to one of the otyugh plugs used by the city to feed its otyugh 'allies'. These disgusting three-legged abominations aid in processing the city's filth and sewage. Lots of patrons flock to the Travelling Man every Oathday, when a small contingent of Korvosan Guards winch open the plug and throw in old meat and produce. The customers in the tavern are not interested in this feeding ritual itself, but once or twice a year an otyugh burst out of the plug and goes on a rampage through the streets, a spectacle the onlookers greatly appreciate. Inside the tavern all guest are safe, though, since the Travelling Man has a thick front wall and barred windows.\\

Lick is already present when his friends arrive. The crazy bard welcomes his guests enthusiastically and invites them to take a seat by the window. He points outside to the plug where the feeding normally takes place and joyfully recalls the one time he witnessed an otyugh outbreak. It has been five months since the last rampage, so making a wager on when the next outburst will be gets more interesting by the week. Luckily nothing happened yesterday, as Lick would have hated missing it. He also recommends the tavern's special, the otyugh burger, a kind of hamburger which, contrary to its name, is not made of the filth eating creature, only named after it.\\

During the meal Lick extends an invitation to his guests to come to his new play {\itshape The Hell Mother} , which opens tomorrow in  {\itshape Exemplary Execrables} . He refuses to reveal anything about the contents of the play, lest he spoil the surprise. It might be a bit macabre for some people's taste, Lick confides, but he hopes his friends are broad-minded and will appreciate it. He even hopes the play will catch the attention of Touran Palastus, the director of Korvosa's prestigious opera house, the Marbledome. Lick has a fantastic new masterpiece in mind, which he would love to see performed in the opera. His partner in crime in this new project is Salvator Scream, the painter who is also responsible for painting the backgrounds in the Execrables. Scream is a genius, Lick says, but also a complete lunatic. "Still, aren't we all?" he grins. He'll be sure to introduce his friends to the artist after the premiere. Lick also inquires what became of the little lambs the party saved. He apologizes for not taking care of any of the kids himself, explaining that Old Korvosa is no place to raise young children, unless they live within the walls of the Orisini Academy or palace Arkona. Vencarlo Orisini is a famous sword master who trains students in the elegant art of fencing and the Arkona's are probably the richest nobles in the city. They are quite popular in this district, because they provide out low-price lodgings to the poor, although they live in magnificent Vudran-style manor themselves.\\

Lick also advises his friends to go to the golden market to sell the loot they gathered from Gaedran Lamm. He apologizes for not joining them himself, but he needs to prepare for the play tomorrow.\\

At {\itshape Gemshare Jewelers} in the Golden Market Quint haggles with the two brothers who own the shop over the price of the valuables from Gaedran's hoard. The finally settle on 1,130 gold sails, a pretty sum for the young heroes. Balian, who is not really the negotiator type, wanders about the shop a bit and stumbles upon an old flyer on the wall. It has a drawing of the queen's brooch and promises a hefty reward for its return. He takes the note and shows it to his friends. Everyone recognizes the brooch they found five years ago, after Ileosa lost it falling off her horse. The young friends agree to take the jewel to Castle Korvosa. Quint pays a visit to  {\itshape In Style} first, to buy a new expensive 200 GP outfit. He wants to be well-dressed before making a royal visit. 