%!TEX root = ../crimson_throne_book_main.tex
% 2013-12-07
After their visit to Cressida Kroft, the companions return to the north of the city, to Old Korvosa, where they hang around in the local pubs looking for more signs of trouble in the city. They learn that the {\itshape Ironsooters} , the men and women who work in the Ironworks, are on strike. They protest against the fact that Korvosa bans guilds. The mastersmith, Baris Trenchlow, has always been in favor of guilds and seizes this time of civil unrest to voice his opinion. When evening arrives the young friends join Amarice in the Travelling Man. Their former lamb 'sister' is eager to learn what happened to them over the last four years. She also tells them that she joined the Guard almost immediately after they freed everyone, since she always dreamed of being a soldier and felt she would be safe from Lamm in the guards' ranks. She spent a few months in the Citadel's kitchens, but flirting with some of the soldiers sufficed to get her in the recruitment program. She has been a Korvosan guard for three years now. She has not stayed in touch with other former lambs, though.\\

She also enquired among her colleagues in the Citadel about Verik Vancaskerin and learned that he has a new girlfriend who has started seeing some three months ago. She does not know the girl's name, but rumor has it Verik is crazy about her.\\

After a lovely evening the companions return to {\itshape All the World's Meat} . They stake out the place for some time, until they see the four Cow Hammer boys leave. Puk follows the four deserters while his three friends make for the butcher's shop. Balian gets out his thieves' tools and picks the lock on the front door. The three companions quickly head upstairs and surprise Verik Vancaskerin in his private room. Verik is seated at his desk, carving the table with a dagger in his left fist while staring at a letter in his other hand. When the intruders reveal that they are here to arrest him, Vancaskerin draws his longsword and waits for them to attack. "  {\itshape Traitors sent by the queen} ", he hisses as he dodges under Balian greatsword and resists Quint's  {\itshape sleep} spell. He swings at Balian with both his longsword and dagger. The ranger avoid the long blade, but is cut by the sidearm. Then Sjo hits the sergeant hard with his burning morningstar. Quint's second attempt at  {\itshape sleep} is successful (finally!) and prematurely ends the fight. Balian and Sjo tie up the sleeping sergeant while Quint casts a  {\itshape detect magic} , discovering that Vancaskerin's cloak and dagger are magical. Then the bard examines the letter on the desk:\\

 {\itshape Dearest Verik}  Stirge Street 22 houses an abandoned butcher's shop. The former owner died in prison, where he rotted away for not paying his taxes. The building itself has been in the city's custody since then, awaiting to be sold to cover the tax debt. You undoubtedly are familiar with our government's inefficiency, so it won't surprise you that the shop stood empty for more than a year.\\

Behind the boarded windows you'll find a decent place of business. If you reopen it, you can do more good for Korvosa's citizens than by playing sergeant and suppressing the good people of our city. A dear friend of mine wants to help the common man, but requires assistance from someone trustworthy. I know no one I trust more than you, my love. My friend will supply a number of animals for slaughter, so you can distribute their meat for free to the man in the street. For the common man will be the first victim of this incompetent harpy on the throne. We can't allow for our fellow citizens to starve to death, so we'll just have to provide what the queen can't.\\

I love you to pieces and I'm eternally yours ...\\

S\\

