%!TEX root = ../crimson_throne_book_main.tex
% 2013-06-15
\section{21 Arodus 4703}

When Balian and his mates return the next day, they aren't allowed inside the circus grounds. The Korvosan guard is preventing anyone from entering or leaving the site. The bystanders are whispering that someone was murdered here last night, but no one knows any specifics.\\

The boys decide to sneak in the same way they did the day before. Sjo and Balian hide in Alan's wagon, while Quint uses prestidigitation to color his shirt brightly, making him look like a carni kid. He singles out Alan and waves him over to his wagon. The carni is relieved to see the lambs: "My young friends, I'm afraid I have some bad news. Someone was murdered here last night. The carnival is closed and one of us is under suspicion of the vile crime: Jherizhana, our sphinx. The victim appears to have been wounded by heavy claws. And to make matters worse, our 'bird' has flown: Jherizhana is missing. "\\

"Still, I'm absolutely convinced that Jherizhana is innocent. Don't ask me how I know, but trust me, I'm 100 % sure. My fellow carni's and I have been grounded, so I would like you boys to investigate the matter for me. Would you be prepared to help us out? If you can prove our innocence, I will reward you handsomely."\\

When the three boys agree, Alan continues: "The man who was murdered last night, was named Boris Veldan, a local moneylender and pawnbroker. He had been drinking heavily at the bar yesterday and was murdered later last night in another corner of the camp, behind the cage of the baby dragon and Madame Mask's tent. Apparently he had been ripped to shreds.\\

That is exactly why Jherizhana is a suspect, because the wounds on Veldan's body appear to come from her claws. Lieutenant Jalento of the guard, who's leading the investigation, seems to be convinced of her guilt. Moreover, the sphinx is no longer around, which only adds to the suspicion. Maybe her magic foresight warned her and made her fly off ... I'm not sure, but she has disappeared at a most inconvenient time.\\

Jherizhana would never hurt a fly, she's incapable of doing so. Her cage is only for show. I don't know why that Boris guy was murdered. Perhaps he was robbed, because his purse is missing. Or maybe the Szcarni had a score to settle with him. Those damned gangsters give all my fellow Varisians a bad name. This moneylender might have been a thorn in their side ... well, I just don't know, I'm not familiar enough with this city. I hope you can figure out what happened.\\

Lieutenant Jalento let slip that this Boris Veldan owns a pawnshop close to the Dwarfwalk gate. Maybe you can start your investigation there."\\

