%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-10
Using his healing magic, Sjo restores Jecko to consciousness. The coward claims he had no choice but to join Lamm's gang when the old man found him. It was this or death. Quint seems to feel some sympathy for the traitor's plight, but when Jecko shamefully admits to having been forced to kill other recaptured lambs, the bard quickly kicks him through the huge opening in the floor. The hungry crocodile Gobblegut welcomes this fresh meal.\\

Then the party interrogates Lamm. They tie him to a post and feed him his own drugs. Lamm starts rambling deliriously, fearing his captors are rat-faced miscreants. When asked about the filthy alchemist Rolth, who took Balian's sister five years ago, Lamm admits to not having seen the man in quite some time. He now deals with a beautiful young woman with long black hair instead, who comes by once every three months or so to take away the girls among his lambs, paying for the young females with pesh and shiver (drugs). Lamm doesn't know how to contact her, just like he never knew how to get in touch with Rolth in the past. They always come to him, he says, not the other way around. The last time the woman was here, was three weeks ago, so she won't be back for at least two months. Lamm doesn't know her name, but she is definitely of Varisian stock. That leaves the party little to go on: most Varisians have dark hair and the fact that she is 'young and beautiful' is quite relative when coming from an aged geezer like Lamm, since most women are young and beautiful in the eyes of old men.\\

With years of hatred flowing through their veins, Sjo, Balian, Lick and Quint have no mercy for their old tormentor. Puk's need for revenge rivals his new friends' rage, so the party is in total agreement to feed Lamm to his murderous crocodile. It will definitely be a deserving fate. They untie the drugged petty crimelord and dangle him over the pit where Gobblegut eagerly awaits his next prey. Then they let go ...\\

Lamm drops into the waters below. The crocodile rushes over, its sharp teeth glistening dangerously in its maw. What happens next takes the party by surprise: Lamm wraps his arms around the monster and orders it to swim away. Before anyone can react, they disappear in the dark  of the nightly river. Stupefied the young heroes stare at each other. This is quite the anticlimax to their successful enterprise. They can still take pride in the fact that they took out Lamm's gang, destroyed his operation and freed the lambs. Seeing how Lamm was already struggling to rebuild his former empire with his current operation, the party doubts he will ever succeed in starting over again without the help of his cronies of old. But his escape remains a bitter pill to swallow nonetheless.\\

Next the party focuses on their loot. They retrieve two masterwork daggers form their enemies' equipment, which will serve Puk as small sized shortswords. Studying Zellara's harrow deck suddenly frees the ghost of the Varisian soothsayer from the cards. She apologizes to young men for deceiving them earlier. She feared they wouldn't have helped her if they had known she was a ghost. She confesses that her son Eran didn't look up Lamm on his own, she was with him when he confronted the thief and she met a similar fate. She was decapitated and her body was fed to the crocodile. Still her essence lingered and bound itself to the magical harrow cards that had been in her family for many generations. Sometimes she can manifest like she is doing now, but it requires a lot of energy to do so. She can also communicate telepathically through her harrow deck and is able to identify magical items. She quickly explains that the oil the party discovered is an {\itshape oil of keen edge} and the wand holds 23 charges of  {\itshape feather step} , a bard or ranger spell that allows one to walk through difficult terrain unhindered for ten minutes. 