%!TEX root = ../crimson_throne_book_main.tex
% 2013-07-21
\section{31 Arodus 4703}

Saint Alika's Birthday is a holiday the lambs generally enjoy. They are never made to pick pockets, because Lamm opens up an oyster bar in front of the old clog shop. His children have to help him here. Lamm's superstitious nature somehow makes him believe that thievery doesn't fit in with the modest remembrance of Korvosa's selfless heroine Saint Alika. Still Lamm is not one to pass on an occasion to make money, which he does through selling oysters and wine.\\

The clog shop's central location makes it an excellent spot to participate in the festivities. Lamm has occupied most of the street in front of his home with tables and a large stall. He expects to do extra well this year because of the royal wedding. He also got hold of four free barrels of wine, a royal gift which are to be distributed for free. Being the business man he is, Lamm watered two of these down to four, keeping the remaining two barrels as his 'own' supply. He'll be offering these to paying customers.\\

The weather is excellent on this joyful day. In the morning Yargin returns with the smaller children from their 'holiday in the country', while the others are setting up Lamm's oyster bar. By noon most people leave for the Heights, hoping to catch a glimpse of the married couple at Castle Korvosa. Quint and Sjo beg Lamm to let them go watch as well. Since the old man is curious himself, he agrees, leaving Giggles behind to watch the shop and bar.\\

A vast crowd of Korvosans has made its way to the Heights, pushing and shoving to find a decent spot along Ramp Boulevard or on one of the streets surrounding the castle. Balian, Sjo and Quint climb one of the houses close to the castle to enjoy the spectacle from their 'front row seats' on the rooftop. At one o'clock all the bells in the city toll. The people cheer as the king and his new bride appear on the balcony to greet their subjects.\\

Trumpets blare and drums roll as a military parade makes its way along Ramp Boulevard from Kendall Plaza in the south. The soldiers halt in front of the castle, while fifteen hippogryphs fly overhead in a heart-shaped formation, strewing down red and white petals.\\

Field Marshal Cressida Kroft rides to the head of her troops. With a magically enhanced voice she speaks: "Your majesty, the Korvosan Guard salutes you and congratulates you on your wedding. We welcome your beautiful bride, our new queen Ileosa! (The people cheer.) To show our honor and loyalty, we would like to present her with a gift, her own private guard!"\\

At that exact moment the front ranks split and ten women in plate mail step forward. Their helmets are adorned with red plumes. "Behold!" Cressida Kroft shouts, "the Gray Maidens!" Another cheer arises from the masses. The king and queen nod their heads in approval as the Field Marshal orders her troops to move forward.\\

When the royals go back inside, the lambs hurry back to the old clog shop to work. Hookshanks is in charge of opening the oysters, the girls pour the drinks and the boys serve the patrons. Soon all the seats are taken. The free wine flows bountifully, but the oysters and housewine also move well, even though customers have to pay for them.\\

Twice Hookshanks cries out triumphantly as he finds a pearl in an oyster. He proudly hands the precious stones to Lamm, who tucks them away in his chest pocket. Several nervous looking people approach Lamm in the course of the day to buy tiny pouches. Many of his customers are young adults and most of them are decently dressed.\\

