%!TEX root = ../crimson_throne_book_main.tex
% 2013-12-07
\section{19 Desnus 4708}

Today marks the day that King Eodred II will be buried, but apparently it will not be a public event. So there is no way the companions will be able to witness the funeral, especially since - as Quint explains - the royal crypts are underneath the castle. Moreover, the king's burial will be a private ceremony within the castle walls, as the queen does not want to risk inviting more trouble in the city streets.\\

So the young friends are free to pursue their own little plot in North Point, where the butcher's shop known as {\itshape All the World's Meat} will be handing out free meat again to the unfortunate citizens who are finding it increasingly difficult to get food elsewhere. Quint suggests taking a diplomatic approach and after some deliberation the heroes decide to pose as sympathizers to the anti-queen movement. When they arrive in Stirge Street they find the butcher's shop overrun by dozens of people. Only a few customers fit into the shop itself, so most clients crowd the street in front of the building. Balian inspects the house and finds out that the front door is not the only way inside. A cattle pen is built against the left side of the building and since it is open to the air, Puk can stand on Sjo's shoulders to sneak a peek over the wooden fence. He notices a side door leading into the back of the house. Still, this early hour is not fit for a covert operation, so the companions decide to take a frontal approach.\\

Sjo joins the crowd waiting outside the shop and start pushing everybody into a line to create some order. While everyone is reluctant to queue at first, it quickly becomes obvious that this orderly manner of waiting is much more enjoyable for all those present. Meanwhile Quint sweet-talks his way into the building, by claiming he only wants to talk to the men inside and is not interested in getting free meat. When the bystanders see his expensive attire, they believe him and allow him to cut in line. Two men are behind the counter in the cramped shop, where customers are standing elbow to elbow. Quint recognizes the man with the bushy unibrow and flat nose from the descriptions they got last night as Baldrago. He introduces himself as a sympathizer to the cause and agrees on returning in a few hours, when today's meat has run out and there are no more customers.\\

The companions continue maintaining order outside and Quint entertains the crowd with a bit of music and jokes about the queen and her Gray Maiden lovers. By noon Baldrago and his mate send home the remaining people waiting outside, as there is no more meat to hand out. There are only a few pieces left in the shop window, covered in flies, but those will stay there until the sun sets, so they urge the unfortunates who have to leave empty-handed, to try again then. Next they invite the companions inside. A short conversation reveals that the four men working for Verik Vancaskerin, the so-called Cow Hammer Boys, are not all that interested in sabotaging the queen. They certainly do not seem to be hard-line political activists. But maybe their boss is. Quint and his friends are allowed to go upstairs to talk to the man in charge.\\

The companions arrive in a room with a round table and some bedrolls on the floor. A clean-shaven man dressed in Korvosan livery and armor walks in and greets them. Although he seems to be slightly more politically motivated than his mates, he still does not come across as a hardliner at all. He seems to be more interested in keeping the poor people fed than in feeding them hatred against the queen. He is mostly worried what will happen when his shop runs out of animals to slaughter. Quint wonders if Verik had any support setting up this shop, but the former sergeant of the Guard gets vague at this point. He admits to having friends who arranged his little set-up, but claims not to be able to contact them himself. He also refuses to spill any more information on this as he says it is a private matter. Sjo hints at Quint not to press the subject and next it is Verik Vancaskerin's turn to ask the companions some questions. He informs about their motives and plans. When they claim they want to support the cause in a way similar to Vancaskerin, he agrees to let his 'employers' know when the contact him, although he has no clue when that will be.\\

