%!TEX root = ../crimson_throne_book_main.tex
% 2013-10-19
\section{30 Gozran 4708}

30 Gozran sees a grim and rainy morning. A dozen friends and fans of the deceased writer Lucian Lycan have shown up in the Gray District, including Isha, Pilts Swastel, his one-eyed gnome Jabbyr and seneschal Neolandus Kalepopolis. The companions are present as well.\\

Archbishop Keppira d'Bear leads the service. Pharasma's high priestess is an older lady of Chelish blood. She covers her frail figure and long white hair in a heavy, gray cloak.\\

In a clear voice the bishop explains how Pharasma, in her capacity as deity of birth, gives life, which she later reclaims, being the goddess of death as well. When a mortal soul leaves this plane, it travels to Pharasma's Boneyard, where the Lady of Graves does not judge whether its death was justified or not. Instead she takes its complete life into consideration to decide in which heaven or hell the soul will spend eternity. Although the mistress of prophecy foresees where a particular soul will end up at the moment of its birth, she reserves her final verdict until the last possible minute, knowing that prophecies can be wrong of misinterpreted. While she believes in predestination, she also understands the need for vagueness to allow at least a hint of free will. The high priestess asks those present to share stories about Lucian Lycan to placate the goddess in her judgment.\\

Isha is the first to speak. Sobbing, she praises Lick's passion for art and his passion in love. Although he never said the words, she knows that he loved her, remembering a day, not too long ago, when she saw it in his eyes. It was last winter, when she had fallen on the ice and he had comforted her with words that could have featured in his best work.\\

Pilts Swastel continues, focusing on Lucian Lycan's genius, both as a writer and an actor. His plays were bigger than life itself and inspired many spectators, the owner of Exemplary Execrables proudly states. His life was filled with grand emotions, and, yes, lots of pain as well. The pain he had lived through so vividly in his youth was brilliantly reflected in his work. Swastel also adds that it is better to burn out quickly than to fade away.\\

Next Quint takes the floor. He reflects on Lick's youth, the harsh years under Gaedran Lamm's thumb. Although these years certainly left their mark on Lick, he also drew great inspiration from them for his work.\\

Finally Seneschal Neolandus Kalepopolis also has some kind words for the deplored artist. He counts himself lucky for having known this exceptional author. Although his themes were always dark and estranging, his work also showed unique literary talent, containing pearls that could move your heartstrings. The seneschal hopes that the writer will gain the recognition in death which he was denied in life.\\

Keppira d'Bear concludes the testimonies: "Oh, Pharasma, your servant Lucian Lycan needs your mercy. You have the power to condemn or reward him. If he was a devout and god-fearing man, reward him liberally. If he was sinner, please forgive him. We humbly implore you to look kindly on his soul."\\

After the ceremony everyone slowly walks to the Everyman Ward, where most Korvosans are buried. A number of younger priests entrust Lick's body to the earth. The high priestess hasn't joined the mourners, since Lick is not the only one to be buried today. The seneschal reveals that a fourth suicide victim is being buried today, an artistic glassblower, Harmon Hals, who set himself on fire. It has been a dark week for the arts in Korvosa, Kalepopolis admits.\\

The multiple suicides are confirmed in the latest edition of the Korvosa Herald. The two-weekly periodical also reports on the king's illness, which seems to be very hard to cure, and a girl from the small settlement of Sirathu, who has been speaking in strange voices. Some people claim she has the same talent for prophecy as Saint Alika, believing her to be blessed with Pharasma's gift of foresight as well. Last week her unconscious body was discovered next to an uncompleted fountain, which miraculously started flowing with pure and crystal clear water for the first time. The backside of the paper, which always contains tales from Korvosa's history, focuses on the battle against Shoanti chief Galstak Sevendeaths and the conquest of the mainland, which led to many families abandoning Edrin Island for the open space south of the narrows of Saint Alika.\\

