%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-10
Quickly choosing the door next to the filthy tank with fish offal, the young intruders enter the large hall in the back of the building. They obviously made the right choice, for Lamm and his gang are waiting for them inside, as are all the frightened little lambs.\\

The party is at the top of some stairs, looking down on another, even larger fishery work floor. There is another smelly vat with foul-looking fish brine. In the other corner of the room are wooden catwalks, on which Lamm's men are ready to spring a trap on their former slaves at the room's other entry points. The stupid fools have chosen the wrong doors, taking away any advantage of surprise they might have had! Sjo is the first to make it down the stairs, followed by his comrades. He notices Lamm staying safely on the catwalk, cocking his hand crossbow, while the other criminals make their way down to the floor. The half-orc Giggles storms over, trying to hit the young Shoanti in the head with his flail, sorely missing him. He is quickly joined by an ugly dog and young Jecko, who is trying to maneuver himself into an advantageous flanking position with the half-orc or the canine. Yet, before he manages to do so, both of them fall to the weapons of their adversaries. Sjo even sends flames through his mace, making Giggles' final moments extremely unpleasant. Jecko is next to follow, leaving a desperate Yargin, who attempts to throw a vial of acid on the furiously attacking ranger Balian, but to no avail. The ranger's greatsword cleaves through the air, doing massive damage.\\

Meanwhile the mean gnome Hookshanks steps forward from the shadows under the catwalk, where he was hiding between the scared lambs. He is holding a small halfling boy by the throat and threatens to kill the child with his meat hook if the party doesn't surrender. Quint reacts aptly by putting the evil little snake down with a sleep spell. Sjo hits the sleeping gnome with his mace, hurting him badly, but also waking him up. Hookshanks figures his end is near and rolls over to the hole in the floor, falling into the river waters below and swimming to safety under the cover of darkness.\\

Lamm realizes that his game is up and flees to the streets, with an enraged party on his heels. The old man doesn't get far. Moments later his unconscious body is dragged back inside by Balian. Quint uses his healing magic to make sure Jecko doesn't bleed to death, which leaves the party with two knocked-out prisoners: their nemesis Gaedran Lamm and their former untrustworthy fellow lamb Jecko.\\

Puk and Quint try to calm down the panicked children, assuring them that the nightmare is finally over. Kester, the oldest of the lambs, asks his saviors what will happen to them. Quint suggests taking the lambs to one of the city's orphanages tomorrow. Puk pays special attention to the halfling boy that Hookshanks wanted to kill. The boy's name is Lauro and his sister is called Sarai. They have both been in Lamm's gang since they lost their father three years ago. Sarai seems to be the only girl among the fifteen lambs. Apparently all {\itshape human} girls are taken away by a black-haired woman who comes by once every few months. The party retreats to Lamm's quarters, leaving the dog Spyder to watch over the children. The dog has never been combat trained, so he can provide little real protection, but the lambs seem to feel safe with the labrador at their side. In the old man's bedroom Puk opens the lockbox and discovers an assortment of valuables and money. He also finds a wand and a glass tube with magic oil. Meanwhile Sjo takes the lid off the fly-covered hatbox in Lamm's wardrobe. He is abhorred to discover Zellara's chopped off head inside: she has been dead for weeks! Her harrow cards lie under her decaying chin.\\

