%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-24
The party spends the rest of the afternoon looking for some new equipment. {\itshape Furin Ironguts} is an accomplished blacksmith from the dwarven city of Janderhoff, who's been living in Korvosa for many decades. He lost his right eye during his apprentice days and now he always wears goggles to protect his remaining eye. His shop is just within the city walls in the East Shore District, next to the Dwarven Gate. It's hot and smoky inside, not only from the furnace, but also the fat cigar in the dwarf's mouth. Sjo buys a new suit of armor and a shield, so he can return his current breastplate to the rightful owner, the Sable Company. He also procures a new morningstar of masterwork quality. Balian finds his fancy at Eodred's Walk: Slicing Dicers is the perfect place for a masterwork greatsword, while Trapper's Hole has a bow that can support his strength. After sunset Quint, Sjo and Balian pay a visit to Eel's End, hoping to gather more information on the creep Rolth, Lamm's drug supplier who took Balian's sister five years ago, or on the black-haired lady who collected all the young girls from the lambs. Puk, who's still recovering from his drug addiction, wisely decides to stay in the old fishery with Kester and the boys. He does not want to risk temptation so soon.\\

Eel's End is one of the seedier and rougher neighborhoods in Old Korvosa. It consists of a clot of ships at the first dock past the last bridge over the narrows of Saint Alika. The five vessels are permanently moored to the long pier. The four smaller ships that comprise Eel's End are the {\itshape Goldenhawk} , a flophouse for drunkards, the  {\itshape Twin Tigers} , a gambling hall, the  {\itshape House of Clouds} , a brothel and the  {\itshape Dragon's Breath} , a drug den. The largest of the five is the  {\itshape Eel's End} itself, a decommissioned warship that serves as an alehouse, but also as the headquarters of the site. Glowing lanterns in the shape of spiders greet Balian, Sjo and Quint as they cross the pier. Two grim enforcers in chainmail armor eye the visitors carefully, but allow them to pass. The sound of laughter, singing, cursing and debating booms from the colorfully painted ships at the end of the pier. Large signs hang from ropes or are nailed to the pilings, identifying each of the boats. The first ship to the right is the {\itshape Goldenhawk - No safer stay in Old Korvosa} . The single-masted Chelish sailing ship has seen countless repairs. It is doubtful it is seaworthy, but lashed to the pier, it seems stable enough. A gnome with a crumpled hat and patchy beard kindly waves hello from its deck. At his belt is a heavy key ring. The Goldenhawk provides entry to the next ship, the {\itshape House of Clouds - The caress of our lovelies will take you straight to heaven} . Across from the Goldenhawk, to the visitors' left, floats the  {\itshape Twin Tigers - Take the tiger by the tail and try your luck!} Two hut-like structures sits atop this barge, the raucous sound of laughter and periodic roars of victory sounding from within. Two enforcers patrol the deck. Beyond the Twin Tigers lies a red vessel. The sign reads  {\itshape Dragon's Breath Corridor - Dream the dragon's dreams at affordable prices!} A couple of glossy-eyed patrons loll about the deck, trying to catch a breath after having 'suffered' the drugs below decks. The largest ship is tied to the pier's end. It bears no sign at all, though its figurehead of a coiling eel with a woman's head leaves no question as to its name. This warship is obviously the {\itshape Eel's End} . Several patrons dance and drink on its open main deck. This large barge is the party's first destination. They settle at a table on starboard, which overlooks the drug boat. The double doors to the captain's cabin on the Eel's End bear the painting of a horrible spider. Quint strikes up a conversation with three young men on the deck of the neighboring drug ship, who are obviously under the influence of pesh. There seems to be a hefty entry fee of 5 gold sails, although once inside drugs are quite affordable. The owner is called Bezzeraty, a very small man who is a human nonetheless. He hates being referred to as a gnome or halfling. Hoping to find a clue to drug supplier Rolth's whereabouts, the three young heroes gain entry to the gaudy red barge. The so-called drug corridor is located belowdecks, where the open interior has been partitioned in smaller booths with comfortable couches. A skinny and very small human drives a cart to and fro, selling whatever his patrons desire. Quint and Sjo order some cabble tea and Bezzeraty tells them that his drugs, the finest in all of Korvosa, come from Eel's End's boss, Devargo Barvasi. The local crimelord runs a tight shift in his little corner of the city, making him rightfully respected and feared by his men, who call him the King of Spiders for the strange love he bears for the long-legged creatures. He even owns some dream spiders, allowing him to produce shiver. Still, Bezzeraty warns his inexperienced new guests not to try this last drug yet, since its effects are quite drastic.\\

Back on board of the Eel's End Quint tries to gain entry to Barvasi's quarters, but the enforcers on deck inform him the king of spiders is unavailable at the moment. Quint slips one of them a few gold pieces, trying to convince him to get him an appointment for another time.\\

Next Quint and Sjo visit the brothel aboard the House of Clouds, hoping to find out more about the missing girls or the black-haired lady who collected them. A single long tent-like hut sits atop the main deck with its entry hanging open to reveal a large room decorated with rugs and pillows. The scent of anise, rosewater and cinnamon pours forth from smoking bronze braziers set on silver stands carved in the likenesses of slit-eyed serpents and proud hunting birds. Scantily clad men and women loiter in the tent and welcome the visitors.\\

Sjo is charmed by a beautiful redhead, Danarella, and joins her in one of the rooms below for his 'first time'. Meanwhile Quint starts chatting to the owner, Madame Halvara, a middle-aged half-elven lady, who still looks stunning for her age. She has no information on the missing girls, insisting that all her girls are riper and that they are here of their own free will. She can also fill the inquisitive bard in on where Barvasi gets his drugs. He has his own chemist, someone named Arkul. Quint wonders if this Arkul might be Rolth in disguise, but when he learns that the alchemist is in fact a kobold, it is clear that he is not. Arkul is apparently the one who invented the new drug shiver five or six years ago, after numerous experiments on how to transfer the dream spider's hallucinogenic poison to a drug. Barvasi keeps some of these eight-legged creatures in the hold of his ship, but Madame Halvara refuses to spill the beans on how he harvests their poison. Obviously Quint is very curious , since he risked his life as a child trying to 'milk' some of these spiders, but the lovely half-elf reveals nothing.\\

Quint spends the next hour in the company of Madame Halvara's most exotic girl, a veiled Vudran beauty, Yuuna. His time with the chocolate skinned gem is pleasurable and confirms his suspicions that Eel's Enders don't know Rolth or his black-haired assistant.\\

