%!TEX root = ../crimson_throne_book_main.tex
% 2013-12-30
The young heroes transport Verik Vancaskerin to Citadel Volshyenek. This time at night the streets are mostly clear of people, so they reach their destination without any trouble. Field marshal Cressida Kroft is still awake, although she looks tired. She is just saying goodbye to another guest, a priestess of Sarenrae. Sjo recognizes the woman as Sadira from his days in the temple of the sun goddess.\\

The companions quickly brief Kroft on how they arrested sergeant Vancaskerin and hand her the letter they found on his desk. She has Verik locked up in the dungeons and Sjo and Quint enter his cell to interrogate him. Verik claims that he's been doing more good for the people in Korvosa by handing out free meat than he ever could have done as a sergeant in the guard. The price of bread has tripled in the last couple of days and the poorer citizens simply can't afford to pay for their food. The riots in the city have also caused numerous businesses in town to temporarily close their doors, so a lot of families are without income at the moment. Vancaskerin also believes that his good deeds in {\itshape All the Worlds Meat} probably created more order in that corner of the city than the entire Guard did. Sjo doesn't care about the man's motives, saying that nothing excuses breaking his vow to the Korvosan Guard. A word is a word! When Quint steers the conversation in a political direction, Vancaskerin freely admits that he has no love for the queen, seeing her as an incompetent little girl who only cares about her own beauty and luxury. If she is allowed to take the reigns over the city now, people will regret it later on. It's better to act sooner rather than later and have her removed from office now, before she can dig her nicely manicured claws into the position. Quint mocks the sergeant's na\"ivet\'e, as he doesn't even seem to know who he is working for. Verik replies that he'd rather have someone in charge who feeds the people than someone who lets them starve. The queen has never shown any interest in the people of Korvosa in the past five years and her failure to get a grip on the situation now, only proves her incompetence.\\

When asked about his girlfriend, Verik admits that she is of Vudran descent and that her name is Selena. He met her only two months ago and has been seeing her irregularly. Apparently he doesn't even know where she lives or how he can get in touch with her. But she knows how to find him and when she does, they seem to share the same ideas on life and politics. They have been sharing their concerns on the queen's incompetence to rule since the king got ill and when Verik received her letter to help to poor people of Korvosa five days ago, he immediately rose to the occasion. Since then he has been waiting for Selena to drop by, eager to show her the good job he did with the butcher's shop. Unfortunately, she hasn't shown up yet. Quint is just flabbergasted by the sergeant's short-sightedness. He can't see he is being manipulated and he has no ideas who is really pulling the strings. He doesn't want queen Ileosa to sit on the throne, but he cannot present an alternative ruler.\\

Before they leave the man to rot in his cell, Quint and Sjo want to know more about Vancaskerin's allies, the four other deserters. Verik doesn't really know them that well, other than that they had a reputation for being pig-headed. They were known for giving their officers a hard time and trying to avoid getting the harder or more dangerous jobs. When Verik overheard them complaining about having to risk their lives in the riots to protect that stupid, self-loving little b&#\\

