%!TEX root = ../crimson_throne_book_main.tex
% 2013-07-21
By midnight the oyster bar has completely sold out. In other parts of the city the feast is still in full swing. While Hookshanks and Giggles order the lambs to clean up, Gaedran invites Yargin and Lou for a trip around town. He charges Quint, Sjo and Balian to get three heavy chests from the front room and join them. The chests' marks have been burned away, identifying them as stolen goods. The boys have to be extra careful with them because their contents are extremely fragile.\\

Before they leave, Lamm goes inside to conclude some business, but the boys cannot make out who is in there with him. When he comes out, they leave for a bar in Midland harbor. On the way Yargin, who is quite intoxicated, bumps into Balian. The young boy stumbles but manages to hold on to his chest. Yargin is furious anyway and blames Balian for his incompetence.\\

In the bar Lamm and Yargin start gulping down a few pints of ale, though Lou abstains from alcohol, as usual. A few beers later a broadly smiling captain approaches. He exchanges a few words with Lamm, opens up one of the boxes and admires the ceramic plates inside. Then he has three of his men take away the merchandise, while handing Gaedran a pouch.\\

Gaedran and Yargin continue drinking heavily, while a kind barmaid gives the three boys in their company some milk and cookies. Lou tries to chat her up, but she skillfully wards off his advances. When Gaedran and Yargin are completely wasted, they join their customer, captain Korbat, and some other patrons in a game of chance. Lamm loses big. While his pile of coins slinks away, his temper rises. After having cleared Lamm of all his money and his last bag of drugs, captain Korbat prepares to leave. Lamm begs him for one last chance: "C'mon, cap'n. Give an old geezer one more shot. All you've taken from me against the boy!" Lamm points at Balian. "He's turning into a strapping lad, an excellent acquisition for your oars. Please, one more shot!"\\

The captain inspects Balian and answers amiably: "You've got yourself a deal, mister Lamm." He pulls out two dice. "Let's keep it simple; the highest roll wins."\\

Lamm throws the dice first. Double five! "Hah, ten! Try beating that, buddy!" Korbat takes the cubes and gently blows over them. "For chance." Quint watches him closely, trying to spot if the sailor is cheating, but he notices nothing out of the ordinary. Then Korbat throws the dice on the table. It's a double six. "Consider yourself beaten, old man." Three of his men jump up and grab Balian by his arms, dragging him outside. Lamm snickers in his seat: "You've brought me nothing but ill luck, boy! Good riddance!"\\

Then he claws at Quint's shirt: "Take me home, kid." Sjo is flabbergasted by what just expired and refuses to accept it. He swings at Lamm with his fist, hitting the old man in the face. His anger makes his hand burst out in sparks of fire. Meanwhile Quint tries to move towards the door, to follow the sailors who are carrying off Balian. Lou charges him and knocks him out with the flat of his sword. Sjo is also outmatched, getting cut by Lamm's dagger and receiving two splashes of acid in his face from Yargin's wand. While the acid burns in his eyes, he loses consciousness as well.\\

Quint awakens in the street when Lou empties a bucket of water in his face. Lamm and Yargin, who are both struggling to stand in their drunken stupor, order him to carry Sjo's unconscious body. But the Shoanti boy is big and heavy, and Quint can hardly support his weight, let alone move him. Yargin pulls out his wand again, threatening to burn the poor boy if he doesn't hurry up. Quint feels hopeless and pours all of his emotion into his hands, which suddenly glow with healing magic, restoring Sjo to consciousness. The Shoanti boy wakes up, but his sight is still blurry. Meanwhile Lamm and Yargin have grown tired of Quint's stalling and move forward to channel their frustrations on the boys once more.\\

