%!TEX root = ../crimson_throne_book_main.tex
% 2013-07-21
\section{23 Arodus 4703}

Early in the morning Yargin leaves with the younger lambs for the countryside. There they'll be picking red and white flowers for a week, that will traditionally be used on Saint Alika Day. Although Balian's sister will be joining Yargin, which means she won't get to play in the Pied Piper, Balian feels happy for her. This week outside of the city is usually quite enjoyable. The little lambs even think of it as their annual holiday.\\

The older lambs spend the day in the water again, diving for oysters and turning them in their beds, so they can grow larger by the end of the month.\\

That evening they are exhausted, but eager to visit the circus again. Alan asks Hookshank not to give the children dinner anymore. He will feed them during practice instead. This way they will save time, the old Varisian explains. Realizing how tired the children truly are tonight, Alan calls for food, drink and blankets. Everyone gathers around the campfire. Landro plays his fiddle while Alan tells the story of the Pied Piper.\\

Once upon a time there was an infestation of rats in the Chelish town of East-Rikkan. The desperate citizens hired a musician who claimed he could get rid of the rodents. Playing his flute, the Piper led all the rats to the river, where they drowned.\\

When the mayor refused to pay him, the musician grew angry and played his instrument again. This time the town's children followed in his wake and disappeared inside a mountain, never to be heard from again. Only two children remained to tell the tale. These two couldn't keep up with the others because one of them was a cripple and the other one hit his toe. Apparently Sjo and Quint will be playing those two roles.\\

Oyster farming and theater practice continue for the next couple of days, giving Quint and his mates some skill in acting.\\

