%!TEX root = ../crimson_throne_book_main.tex
% 2013-09-21
The young friends bid the Shoanti goodbye and head back to the old fishery. Sjo picks up his old armor, wanting to return it to its owners of the Sable Company. His friends join him to their headquarters in the Great Tower. This huge building was one of Queen Domina's wildly expensive projects, with which she tried to rival Korvosa's ancient monuments: the Pillar Wall in the south, the Gatefoot and the mastaba under Castle Korvosa. On top of that she hoped to outshine the Acadamae, the only new building project in the city that was truly monumental in scope. The tower was never fully completed, as Domina died before it was finished and her son, the current king Eodred II, chose to save the city's treasury by cutting short the project by some fifty feet, thus warding the city from bankruptcy. Still, the Sable Company's base is an impressive landmark despite its proximity to the imposing Acadamae grounds.\\

After handing over his old armor, Sjo gets permission to take his friends to the top of the tower, to show them where he used to work. The ascent to the 19th floor is exhausting, but the view from the landing platform on the top floor is truly breathtaking. Unfortunately, Sjo's limited eyesight does not allow him to enjoy that.\\

After this little tourist stop Balian urges his companions to find out where Spyder is. Although the black dog has lived with Lick for five years and looked healthy, Balian feels that it should have been taken care of better, remembering how ill-trained the animal was. He also fears that Lick's recent illness and subsequent stay in the temple of Sarenrae, has left no one to look after the labrador. Balian's suspicions prove correct and with Puk's aid, the companions gain access to Lick's apartment, where the abandoned dog is very happy to see them. Balian decides to take Spyder and to start training him.\\

