%!TEX root = ../crimson_throne_book_main.tex
% 2013-09-07
While Quint and his companions are waiting for Lick on the deck of the Eel's End, they notice the arrival of Cheliax's smug ambassador, lord Amprei. The overdressed peacock heads straight for the Twin Tigers, the gambling den.\\

Lick doesn't arrive for another hour. He invites his friends over to the Dragon's Breath Corridor, where he starts snorting pesh. Puk joins his friends here tonight, but he doesn't feel at ease. Still, he resists temptation. Another familiar face in the drug den is Salvator Scream; the painter is totally high, thinking all people around him are blue. He babbles incoherently until he passes out. Lick pays the skinny, short man who pushes the drug cart to and fro a couple of silvers, to have his friend brought to the Goldenhawk "to sleep it off".\\

Lick is definitely in fine spirits, still floating on a cloud from the success of his play. After his first batch of pesh, he gets ready to move to the House of Clouds, when he suddenly freezes, grabs his head and tumbles over. He is squirming on the floor, moaning and screaming in pain. Sjo has no other choice than to carry him to the temple of Sarenrae to be tended. The young friends worry that the crazy bard's performance on stage has actually awoken some kind of demon and that Lick is now possessed.\\

Afterwards Sjo asks his friends to return to Eel's End. They wants to drop in on the Chelish ambassador. Anpugit, one of the Vudran managers of the gambling hall, welcomes his new guests inside. The ambassador is playing cards with some merchants. He seems to be in a good mood because luck - or skill - is at his side tonight. He even withstands Quint's vexatious remarks, explaining to his boorish fans that his station in Korvosa is very important, both politically and economically.\\

Quint concludes the evening in the arms of exotic Yuuna in The House in the Clouds, while his companions return to the old fishery to sleep.\\

