%!TEX root = ../crimson_throne_book_main.tex
% 2013-07-21
\section{22 Arodus 4703}

The lambs spend the day in the Narrows of Saint Alika, working in the oyster beds. After a tiring day the kids are trying to catch their breaths over a plate of porridge in their dormitory. Yargin walks in, followed by Gaedran Lamm and a 'stranger', Alan Terdal, the leader of the Umbra Circus.\\

"Good evening, children. Allow me to introduce myself. My name is Alan Terdal. I'm a carnival artist and actor by profession. As you probably know, we're only a few days away from the birthday of Saint Alika and the king's marriage. In honor of the holiday and the wedding my group's planning a theater play, 'The Pied Piper of East-Rikkan', a lovely tale about a rat plague in a small Chelish town. I hear that Korvosa has its fair share of rats herself, so this piece might be enjoyed here.\\

We do have a problem, however, because the children of East-Rikkan play an important part in the story and since my group consists almost exclusively of adults, we're in dire need of some children. The kind mister Lamm here has allowed me to hire some of you. I'll be needed a dozen or so of you. Who would like to participate?"\\

Yargin immediately adds: "This play is by no means a way to escape your daily chores. Daylight hours are still for working. You can practice in your own time, in the evening! And those of you who'll be joining me in the country, come tomorrow, you're out! We'll be sleeping on a farm outside of the city, so we won't be around to play the fool on stage."\\

Almost all the lambs raise their hands. Yargin immediately rules out the smaller children, who will go to the countryside with him to pick baskets full of flowers for the feast of Saint Alika. This also excludes Balian's sister, Alika. In the end eleven lambs are chosen, including Balian, Sjo and Quint, but also Jecko, Edu and Lick. Alan Terdal convinces Lamm to let him take the children tonight already, for their initiation into the world of acting. The old miser agrees on one condition, Hookshanks Gruller, the gnome, has to join the play as well to keep an eye on the kids.\\

When the troupe arrives at the circus on Endrin Square, Alan's daughter Liandra welcomes everyone with open arms and immediately serves a decent meal to the skinny lambs. To learn the basics of acting, the children have to do some basic theater exercises, like acting out emotions, mirroring someone else's actions, practicing different ways of walking or improvising various characters who meet by accident on a steps of the temple. Some of the gypsies join in the fun, including Eran, one of the two children in the circus troupe. Although the six-year old is younger than any of the lambs present, he's already a fine actor and he actually gives the budding performers tips.\\

Sjo, Lick and Quint turn out to be naturals. Balian struggles a bit more, but no one is as bad as Hookshanks, who claims this acting business is plain stupid. The gnome refuses to fully commit to a role, fearing he will make a fool of himself, but his reserve only results in an even worse performance. The kids also employ every opportunity to make fun of the gnome. In all, the children have a great time and when they finally return to bed, their dreams are sweet for once.\\

