%!TEX root = ../crimson_throne_book_main.tex
% 2013-10-19
\section{4 Desnus 4708}

This morning Kester informs the companions that Mouse and Korwick have not come home from their scouting trip yesterday. The boys have been roaming the city in pairs for the last couple of days, looking for signs of Gaedran Lamm or Rolth. Since these trips take them all over town, it is hard to tell where the two boys disappeared. The companions ask the two remaining boys to seek shelter in Zellara's parlor, while they look around the city for the other two kids. The city guard can't help them and mama Mira from the orphanage has not seen the boys in days. Although they keep their eyes and ears open, the four friends find no trail of the missing children.\\

\section{5 Desnus 4708}

The next morning Mouse suddenly bursts through the front door of the old fishery. Panting heavily, he stammers how he and Korwick were captured by Gaedran Lamm two days ago. Unless he leads the companions to Lamm's new hide-out immediately, the old crook will take Korwick's life.\\

Mouse takes the four heroes to another spot in the harbor, an abandoned warehouse that used to belong to the exiled Porphyria family. On the way over there he explains what happened the day before yesterday. He and Korwick had spotted Rolth and the black-haired lady in the harbor, boarding a ship. They had a dozen young girls with them, all of them ex-lambs, and they were carrying some heavy suitcases. Mouse and Korwick turned around to go and warn the heroes, finding Gaedran Lamm and the gnome Hookshanks in their backs, who quickly overpowered them. They were kept prisoner for two days in a place by the water, while Lamm and Hookshank were preparing the site for what was - most likely - a trap. This morning Lamm let Mouse go and told him to get 'those trouble seekers NOW' if they ever wanted to see Korwick alive again.\\

The rundown warehouse used to be connected to a pier, which collapsed many years ago. Only the back part of the pier remains, leaving a platform that is disconnected from the shore. The old poles that used to support the woodwork in between, are still standing, and have been connected by planks, leaving several possible routes to the back part. While Balian takes up position next to a window, the other three companions enter the building. Mouse runs off to warn the Korvosan Guard.\\

The trap that Gaedran Lamm has set out for them quickly reveals itself. The shadow of a man moves over a catwalk inside the building, pulling a rope that sets free two dream spiders from boxes next to the heroes. Across the maze of planks on the remaining back part of the pier, the companions make out a crane from which Korwick is hanging above the water. A hungry crocodile is in the river below him: Gobblegut. Gaedran Lamm and Hookshanks are both hiding on this platform, and the gnome's first act is to set the rope from which Korwick is dangling on fire.\\

Balian reacts quickly and takes out the dream spiders with two well-aimed arrows. The man on the catwalk turns out to be a Korvosan guard, who aims an arrow at Sjo, but misses him. The Shoanti oracle storms into the post supporting the catwalk, but the structure holds. Meanwhile Quint focuses his attention on Lamm, trying to take him down with a sleep spell, but the old crook resists. Lamm returns fire with his crossbow, hitting Puk in the chest. The halfling retreats into the building to be healed by Sjo, while Balian tries to hurt Hookshanks with his longbow, but the gnome is too well hidden behind some crates to be hit. The ranger also tries to draw some fire from Lamm and Hookshanks, but it is Quint who gets fired upon. Luckily the bolts miss their goal. Puk starts making his way across the planks to the platform, trying to keep balance while hoping the boards under his feet will not break. Fortunately the lithe little halfling is so light that none of the planks crack. Quint, who doesn't share Puk's nimbleness, also tries to get across, but quickly ends up in the water, drawing the crocodile to his position.\\

Meanwhile Sjo runs into the supporting pole again. The structure is shaking, but still holds, still the soldier above him now drops his bow and readies his shield and sword. He jumps down and stumbles to the ground. Sjo blazes fire through his morningstar and hits the guard heavily on the shoulder. The man returns the favor by slashing the Shoanti with his blade.\\

Balian decides to change target, hoping that the human Lamm will be easier for him to hit since humans are his favorite enemy. And yes, a first arrow wounds the old man! But it is Puk who steals the show: the halfling runs across another plank and then jumps to Korwick who's still dangling in front of him, using his momentum to swing the crane and the boy back to the platform. The burning rope snaps, but Korwick lands safely on the remaining part of the pier. Puk lands on his feet and gets ready to face Hookshanks.\\

Meanwhile Quint manages to avoid the snapping teeth of Gobblegut and climbs out of the water on top of one of the poles. He also dodges one of Lamm's bolts, but when he tries to move closer he tumbles into the water again. Amazingly the crocodile's teeth and tail miss him again, even when he swims across to the back platform and clambers out again.\\

Inside the warehouse, Sjo ducks under the guard's next swing and knocks him out, stabilizing him immediately thereafter to avoid him bleeding to death. Puk quickly takes down the gnome and then faces Lamm, slashing and stabbing him with his little short sword. Balian also fires another arrow into Lamm's tired frame, while Sjo plunges into the water to distract the crocodile. His new armor withstands the creatures ferocious bite, as his morningstar explodes in flames on the reptile's back.\\

Dripping with the harbor's water, but still not a single drop of blood, Quint finally gets on the platform and charges Lamm, dropping his old master with a slash of his sword. As Gobblegut retreats into the river, the heroes realize they are victorious!\\

Quint prevents Lamm from bleeding out and returns his unconscious body to the warehouse. Sjo sends some healing magic through the old creep's limbs, which wakes him up. Lamm is abhorred to be captured by his former lambs once more. He confesses to having seen Rolth and confirms that the man has left town, but does not know where to. Quint decides not to repeat his mistake and let the old crook live, so he finishes off Lamm once and for all before the Guard arrives. The soldier who was aiding Lamm is still knocked out, but Sjo quickly examines him and discovers the man is a drug addict. The companions hand him over to the Korvosan Guard.\\

Then they follow Mouse to docks where he spotted Rolth two days ago. Some dock hands inform them that the ship left the same day, destination Cheliax. The boat's name was {\itshape The Delivery} . 