%!TEX root = ../crimson_throne_book_main.tex
% 2013-06-15
At 4 o'clock the doors to the Sphinx's tent open. The pavilion leans against a large wagon with an iron cage. Visitors gladly pay the one silver shield admission price for a chance to gawp at this creature of mythology. Two guards keep the visitors under control, preventing them from touching the curtains that cover the cage.\\

Alan Terdal welcomes the guests: "Ladies and gentlemen, what you're about to behold is something most of us can only dream about. The searing sands of far-away Orision are home to a fabled creature, half woman and half lioness. This sphinx is a marvel indeed, wonderful but capricious in nature. That's why we disturb her rest only a few times a day, but be warned, for if you do not succeed in solving her riddles, she might lose her patience ... Still, guess what she's describing and you get to plunder her treasures! So without further ado, here is Jherizhana, the sphinx" The gypsy pulls a cord and the curtains slide open.\\

Behind the bars of the cage stands a beautiful sphinx, surrounded by satin cushions and silk sheets. She shifts about nervously until she finds her peace, looks into the spectators' eyes and melodiously recites her riddle:\\

"At the sound of me, men dream or stamp their feet,  The visitors and the three lambs start shouting all kinds of wrong answers, obviously irritating the fierce lioness, who begins to pace from left to right and repeats the riddle twice, each time with less patience in her voice.\\

Suddenly Quint has an epiphany and cries out the solution: "Music!" The expression across the sphinx's face softens immediately. She beckons the young lamb closer and invites him to open one of the chests in front of her cage. Quint picks the fourth chest from the left, in which he discovers a small ball of golden cheese, a true delicacy for malnourished lambs.\\

Meanwhile Balian and Sjo notice a man who's trying to glide through the crowd, paying more attention to the visitors than the creature in the cage. The man spots a juicy target and lifts his purse during the highlight of the show, when Quint solves the riddle and the bystanders applaud his success. Sjo alerts Jonah, who signals Landro to intercept the thief. The pickpocket turns out to be one of the Szcarni, a gang of Varisian mafiosi who live in the poorer outskirts of Korvosa.\\

Alan's daughter Liandra returns the stolen pouch to the victim, a barrel-bellied man with grey sideburns and a cordial smile. She invites the lambs to come over and introduces them to the victim, Ausio Carowyn, the head of a minor noble family. He praises the youngsters for their honesty and awards them a gold sail each for their help.\\

At the end of the day the boys get even more money from Alan, who invites them to return the next day and continue their good work. The boys made a little over 9 gold sails today with mostly honest work. They have eaten well and had a very enjoyable day. They turn over 6 gold pieces and some petty chance to Lamm, storing 3 gold sails in their secret stash in the sewers. When they get back to the outhouse, they share the cheese with their friends.\\

