%!TEX root = ../crimson_throne_book_main.tex
% 2013-09-21
\section{25 Gozran 4708}

Quint suggests paying a visit to the Korvosan Guard, to find out whether they have more information on Rolth. Grau Soldado, the guard who saved them from the Sczarni thugs in Trail's End yesterday, is sparring in the courtyard with three other soldiers at once. A few moments later all three of them have bitten the dust. Several onlookers explain that Grau was trained in the Orisini Academy, where only the rich or very talented are schooled in the fine arts of fencing and swordplay. Needless to say Grau was one of the gifted ones. Rumor has it, though, that Orisini's current students lack the knack of his former pupils. Captain Jalento's son is one of those new trainees. The captain obviously uses his family's noble standing to get his son the proper education before introducing him to the ranks of the Korvosan Guard, since the boy is said to be somewhat of a wimp. Quint remembers Captain Jalento as the one who led the investigation into the murder of Boris Veldan five years ago in the Umbra Circus, although he was only a lieutenant back then. It seems that being of noble birth pays off when you work for the city.\\

After his exhibition Grau introduces the companions to his commander, Field Marshal Cressida Kroft. She confirms that Rolth is suspected of having murdered at least a dozen citizens over the last eight years, although there is no conclusive evidence. All of his victims were missing various body parts, probably enough to piece together a new corpse more than once over. Rolth started off as an Acadamae students at the necromancy department, but he was kicked out of the school for some unknown reason - after all, what happens in the Acadamae stays in the Acadamae. The man has proved most elusive and as yet no one has been able to discover his whereabouts.\\

A quick visit to the temple of Sarenrae teaches the companions that Lick's condition has not changed. Lick's girlfriend Isha has been at his side since he collapsed and hasn't slept yet. Balian and Sjo put Lick in a cart to transport him to the Shoanti in the Gray District, while Quint talks Isha into taking a little nap.\\

Thousand Bones, the Shoanti shaman, calls upon the spirits of his forefathers to tell him if Lick has been possessed by an ancient Shoanti ghost. While the medicine man is chanting in his tent over Lick's body, Lerrim tells his saviors that his fellow lambs paid him a visit earlier today. Sjo is very happy to see the young boy so active and talkative. An hour later Thousand Bones walks out of his yurt. The shaman rules out the idea of possession, claiming that Lick's condition is rather the opposite: there seems to be an emptiness inside of him. Since Thousand Bones' insight has proven to be the best so far, Quint suggests keeping Lick close-by, and has the ailing actor housed in the Cathedral of Pharasma.\\

Quint's bardic background teaches him that Lick's writings might actually hold a clue as to what happened to him. The companions make their way across the city once more to Exemplary Execrables in Old Korvosa, the theatre where Pilts Swastel holds all of Lick's manuscripts. The ratty patron of macabre arts quickly accommodates the companions, allowing them to go through Lick's last script and notes. With only the scenario in front of him, Quint is not distracted by all the gore and nudity like he was two days ago during the live play, and this time the literary brilliance of Lick's work does not escape his attention. When focusing on the ritual in the play which was used to summon the demon Donodarr, Quint feels like it is less of a Shoanti chant and more of an experimental poem. Moreover, Lick's notes contain a list of Shoanti names, some of which sound familiar. It appears to be an inventory of barbaric heroes and leaders who opposed the Korvosans in the course of history. Lick circled Donodarr, possibly because the name is less-known, but has a nice ring to it, the perfect name for his Shoanti demon. Pilts Swastel confirms that Lick spent quite a bit of time in the Leroung library to get background information on the Shoanti. He also explains where Greta lives, the innocent-looking girl who starred Lick's play as the vessel for Donodarr's seed.\\

Greta lives in a loft with a number of fellow actors. Most of them are even younger than Quint and his friends and Puk grows a bit pale when he sees that these budding actors are chilled out on drugs. Without Lick's brilliant words in her mouth, Greta makes a far less intelligent impression on the companions than she did two days ago, laying to rest any suspicions that she might have been involved in Lick's seizure.\\

The companions make one more stop before turning in for the night. Since the painter Salvator Scream cannot be found in Eel's End, the young friend locate his house on the Narrows of Saint Alika, a decrepit building resting between two of the many wooden bridges over the channel of water that separates Old Korvosa from the mainland. The locks on the doors are beyond Puk's skill to open, but Balian forces a window, allowing his halfling buddy to sneak in and open the front door from the inside. The painter's studio holds several gruesome paintings, with a recurrent theme of blue in each of them. Although some praise his work, Sjo and Balian feel like they could easily make something similar themselves. The painter's easel has been thrown on the ground, covering a trashed painting. Scream is sleeping in his bedroom, passed out from drugs. An empty teapot and a cup with a bottom of soothing cabble tea are by his side. It does not look like he will wake up soon. There are also many brightly-colored mushrooms growing outside of Scream's house. Although they are very poisonous, the artist uses them as pigment for his paint.\\

Upon returning to the old fishery Balian resumes his training sessions with the dog, while Sjo speaks with the four remaining lambs about their future. Since the boys have finished cleaning and tidying up the fishery, they offer to scour the streets of the city, looking for signs of either Rolth and his dark-haired companion or Gaedran Lamm and Hookshanks. They promise not to engage these enemies if they happen to find them.\\

