%!TEX root = ../crimson_throne_book_main.tex
% 2013-06-15
\section{20 Arodus 4703}

Hookshanks walks into the old clog shop, obviously in a good mood. He hands Lamm a flyer, telling him a nice opportunity has presented itself. The Umbra circus has come to town. They arrived yesterday and set up camp in Endrin Square in the East Shore district. A circus is the perfect place to pick pockets: easy targets and suitable scapegoats, because the carni's will most certainly be blamed for everything that goes wrong or gets stolen.\\

Lamm sends out Balian and his mates to Endrin Square because the boys performed so admirably at the golden market recently. He expects them to come home with fat loot and the children know their master is not easily satisfied.\\

The Umbra carnival is a colorful collection of circus wagons and tents. The boys, who have no money to pay the admission fee, sneak in undetected and gaze at the wonders of the carnival. Playful music drifts from a barrel organ, its sharp tones cutting through the hum of the crowd. Dozens and dozens of Korvosan citizens roam around to play at the high-striker game, have their fortune told or visit the magnificent Madame Mask. While mothers wave at their children on the carousel or take them to brave the baby dragon, fathers gather at the bar to get drunk, hoping their wives will leave with the children before the nightly peepshow starts. Still, the highlight of the circus is an enormous tent that opens only twice a day. A painted sign at the entrance announces a mythological animal with a capricious nature that offer riddles to be solved: a sphinx! Two carni's stand guard at the door.\\

Some early visitors to the fair have already started drinking at the bar. Quint and Sjo provide a distraction, allowing Balian to lift a hefty pouch, the first catch of the day.\\

Later the boys walk into a large and brightly colored pavilion tent to watch the show of Madame Mask. Three runways lead to a raised dais with a tall rectangular box, covered on all sides in mirrors. A nimble carni makes his way through the crowd to collect 5 pinch from every visitor: "Stare at Madame Mask's curves and make some money. Only five pinch! The fastest eyes win the pot!"\\

Then a beautiful woman with a silver mask strides into the tent. She uses the central runway to walk up to the dais. She doesn't talk, but nods and waves at the visitors. Her shapely body is covered in a risqu\'e blue gown. She is also adorned with various scarves, all kinds of jewels and flowers in her hair. She sends a few charming smiles into the audience before stepping into the mirrored box.\\

"I hope you've been paying close attention", the gypsy who collected the money shouts. "Now's your time to prove it!" Three doors open in the cabinet and three ladies step out. They are all Madame Mask, but each of them is dressed differently. "Each Madame Mask wears a different outfit from the original, but each of them wears a single piece that the original was wearing as well. The first one to identify all three items wins this money", the crier clarifies, holding up the sack of money.\\

The public stats shouting the names of all the items and accessories the women are wearing. The crowd quickly picks up on the white rose, woven into the left Madame Mask's hair, but it takes the young lambs a few breaths longer to lay their finger on the other two items: a fine silver chain around the waist of the lady in the center and a silver ankle bracelet on the beauty to the right. The prize money amounts to a little over two gold sails.\\

