%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-03
\section{21 Gozran 4708}

While the humans in the party get a table at a nearby pub with a view on the fishery, the sneaky halfling scouts the place itself. The doors are open now, providing him a peek inside a room where about a dozen children are slaving away on the smelly workfloor. Meanwhile his colleagues in the pub find out that Lamm buys up old fish and processes it to a slimy substance that is the main ingredient for 'dock-dumplings', a local favorite among poorer dock workers who cannot afford fresh fish. Several times during the day suppliers arrive with more unsold fish or fish offal, while other dealers come by to take away barrels filled with slimy processed fish slurry.\\

At noon three of Lamm's cronies visit the same pub where the PCs have taken refuge, to have a quick lunch. Yargin, Lamm's right-hand man, is accompanied by the silly half-orc Giggles and a young man who turns out to be the former lamb snitch Jecko. Lick also notices that Giggles' face is covered in burned tissue and he has lost his right eye, obviously a consequence of the fire Lick started five years ago.\\

Puk the halfling listens in on the three men's conversation and finds out that they aren't exactly happy with Lamm's current operation. The fishery is a filthy place to work and doesn't bring in the kind of money their activities in the past did. Maybe Lamm is getting too old. Still, it does not seem like the three would be willing to get rid of their boss; their protest is purely limited to complaining.\\

The five companions wait until well after dark before they sneak up to the old fishery. Puk has already discovered that there is an old rotten barge connected to the back of the fishery. Two slippery boardwalks lead to the vessel, one starting at street level and a smaller underpier under the back of the building. The underpier leaves just enough room for the halfling to stand upright and forces the others into a terrible crouch, especially the tall Shoanti Sjo. It hovers just a few feet above the river surface. A small door at one side of the walkway provides entrance to the understructure of the fishery's landbound half. At the other end is a small rowboat which the party uses to make its way to a large hole in the floor of the building's back half. Sjo lifts up the halfling, who peeks into the dark room above. It is a large hall that smells of bad fish. Pointing his ears Puk hears the breathing and snoring of several children, deducing from the sound that this is the place where the little lambs sleep. Since the companions wish not to involve the children, they decide to head to the small door instead.\\

