%!TEX root = ../crimson_throne_book_main.tex
% 2013-05-19
\section{10 Erastus 4703}

It is still early in the morning when Hookshanks bursts through the door of the outhouse of the old clog shop, the abandoned building Lamm and his cronies have occupied as their home base. Hookshanks is a gnome, a mean little bugger, small even for gnome standards. With an evil grin across his face he singles out three of the lambs, Balian, Sjo and Quint. "Time to go hunting, you fools. Gobblegut's hungry. If you don't want to be the alligator's next meal, you'd better get him some juicy rats. Now move along!"\\

Hookshanks leads the three boys to the alley around the corner, using his rusted meat hook to pull open the grating covering the manhole to the sewers. "There are supposed to be at least ten rats for every Korvosan down there, so it shouldn't be a problem to secure a healthy catch. Four's a nice number, I'd say, so you bums don't even think about returning with less. Happy hunting, and don't let the sewer monsters bite."\\

Armed with a simple kitchen knife, the three youngsters descend into the damp darkness. A foul smell welcomes them. Clutching a fluttering torch, Balian lights the way. He spots a couple of rats further down the ledge, next to the filthy muck. Quietly the boys creep closer, only to suddenly jump the surprised rodents and take out two of them before the rest scurries off into a large drain. Sjo never gets in a blow, since the unfortunate soul slips before he can make it to the fight.\\

Across the sewage Quint notices a cul-de-sac that is blocked off with heavy metal bars. A couple of small drain pipes in the ceiling trickle down their smelly contents, while two more rats are chewing on some rotten left-overs against the back wall of the dead end. If only he could squeeze through the bars, Balian would easily add two more critters to his haul. After covering himself with filthy mud and slime, the boy manages to glide through the iron poles and using his torch as a two-handed club, he knocks out the rats. It's a dirty job, literally, but two and two make four.\\

Urged by Sjo the boys set off into another branch of the sewers and kill two more rats before returning to the surface. Today Hookshanks is satisfied with their work, so there will be no repercussions. The gnome does insist that the boys bear witness to the alligator's meal, however. In the flooded cellar of the clog shop, Gobblegut tears through the rats' cadavers in no time, reminding the young hunters that they would never want to switch places with the dead rodents.\\

