%!TEX root = ../crimson_throne_book_main.tex
% 2013-07-21
"Stop this madness!" A calm but determined voice sounds from up above. Staring at the rooftops, Lou makes out the outlines of a cloaked man. His face is covered by a scarf. "Blackjack", Yargin moans, staring up at Korvosa's caped crusader.\\

Lou draws his blade. Lamm reaches for his crossbow but he is too drunk to cock it: "You dirty dog, no one orders me around. Just you wait ..." The mysterious hero somersaults down, landing next to Lou. The bodyguard lunges at the rescuer's back with his longsword. The vigilante ducks under his fierce swing: "Good sir, I have no wish to harm you. Just let these children go."\\

"I will be known as the man who killed Blackjack", Lou crunches as he swings at his opponent once again. Blackjack parries his hits easily: "I hate to repeat myself. LET (woosh, he cuts Lou's cheek) the CHILDREN (woosh, he wounds Lou in the shoulder) GO (stab, he hits Lou painfully in his side)!"\\

"Last chance to abort the fight", the masked man warns his assailant. Still, Lou refuses to quit and strikes wildly at Blackjack, who spins around, letting the longsword cut through the air beside him. Then he slaps the hilt of his rapier against Lou's hands, easily disarming the man.\\

"And now you will let these children go!" Blackjack pronounces each word carefully to let them sink in. He doesn't wait for the thugs to reply, but pulls the children up and pushes them towards safety. Lou uses the distraction to draw his dagger and lunges forward. Blackjack bends through his knees, swinging his own blade under his arm so it sticks out like a sharp thorn from his back. Lou sees his surprise attack transformed into a fatal rush toward the deadly point. Unable to stop his momentum, he throws himself on the blade. He drops down, dead.\\

"Now quickly, follow me!" Blackjack doesn't waste time and leads the children through a maze of alleys, until they reach a quiet spot on the docks. There the boys fill their rescuer in on what happened and urge him to help them free the other lambs from the old clog shop. If they don't, Lamm will make the remaining children pay, most likely with their lives, as retribution for their little rebel friends.\\

Blackjack immediately agrees to help. They hurry to the shop, where Giggles and Hookshanks are still up, catching a few more drinks in the front room. Blackjack knocks them out easily, while Quint and Sjo collect the lambs from the outbuilding. When the children learn they are free, the scurry off into the streets. Lick has more bad news: Balian's sister Alika is gone. The pale and blotchy alchemist who deals drugs with Lamm and who bought the dream spider's poison, came by and took the girl in exchange for more of the mind-numbing merchandise. Quint remembers the creep's name: Rolth. Blackjack has heard of him as well, but says no one knows where to find the man.\\

Then Lick urges his friends to leave the room. Sjo sees a flicker of madness in the boy's eyes, as he takes a lantern and drops it on the floor. The rugs catches fire and the last lambs run out of the house. Lick has the puppy Spyder under his arm. He nods at his rescuers before disappearing into the city, while the clog shop bursts out in flames.\\

Quint and Sjo hurry to the docks, in the hope of finding Balian, but captain Korbat's ship has already left. Blackjack asks the boys if they have some place to go. They want to try their luck in the Umbra Circus. Alan Terdal welcomes them with open arms and agrees to take them along when his troupe leaves the city, far away from the evil clutches of Gaedran Lamm.\\

