%!TEX root = ../crimson_throne_book_main.tex
% 2013-11-01
\section{14 Desnus 4708}

The next morning the adventurers prepare to head into the swamps. Mother Grundy makes them some lunch and warns them about the Feverglade mosquitoes. Those annoying insects transfer the feared swamp fever, but with Grundy's {\itshape smelly smear} , a repulsively reeking ointment, they can protect themselves. Grundy also hands the young friends a flask with a strange brown liquid. She calls it  {\itshape poison poison} , a very strong antidote against swamp fever ... just in case. Ossy Applebottom and his men accompany the heroes to the border of the glades, further down the Jeggare River. Ossy can't give them further instructions: since none of the halflings ever venture into the swamp, no one knows where the Broken Axe clan lives. He sends the companions off with a hearty farewell and reconfirms his hopes for a peaceful solution.\\

The swamp is initially less dirty than the travelers suspected. The Feverglades are not as stagnant as other swamps. The Jeggare River flows through its center and provides the entire area with plenty of fresh water. Fortunately today's water level is quite low, which will facilitate trekking through the marshes.\\

Still, not all corners of the swamp are equally accessible and after a few hours the paths become fewer and narrower. There are indeed a lot of mosquitoes, just as mother Grundy predicted, but the smelly smear keeps the pests away.\\

Suddenly the path gives way to stepping stones across a stretch of water. The big stones have been carefully placed to allow a creature with a stride similar to a human to cross. The surface of the stones shows the occasional scratch, which Balian believes were made by lizardmen feet. He also notices that the stones are sticking out more than one foot above the surface of the water and the brown and withered moss on their sides suggest that the water level used to be higher.\\

While making his way across the stones, Quint loses balance and tumbles into the filthy muck, where he is immediately attacked by an alligator. Balian jumps in next to him and cuts open the creature's leathery skin, but the ranger sees his friends missing their attacks and is violently snapped into the alligator's maw. Unable to wrestle from the sharp teeth, Balian is pulled under water as the swamp killer performs its feared death roll. He loses consciousness as his friends further attempts to harm the alligator or put it to sleep with magic fail horribly. The ranger is barely clinging to life when Sjo, who has joined him in the filth, sends some healing through him and finally kills the predator with a lucky swing of his burning morningstar. It takes four charges from the healing wand to return Balian to health.\\

