%!TEX root = ../crimson_throne_book_main.tex
% 2013-11-16
The companions resume their trek across the stepping stones. Past the crossing they see a small cluster of huts, made of wood and woven bulrushes. Wooden racks sport fresh fish drying in the sparse sunlight. Several lizardfolk with spears and clubs await the visitors around some kind of shrine in the center of the village: four standing axes arranged in a circle with their heads touching. Necklaces and personal items hang from these rusted weapons.\\

There are about two dozen lizardfolk present, including the women and children. Although they seem suspicious, they do not attack the strangers entering their village. One of the males slips into the water behind the huts and swims away in the direction of a small hillock, some 200 yards to the north. A single blackened tree stump sits on top of the mound.\\

Another lizardman with broad shoulders and a wicked club on his belt raises his hand as a peace sign. He also grumbles something in draconic to his fellow clan members in an effort to calm them down and keep them from attacking. Although he cannot speak common, he uses gestures to invite the visitors over to a wooden raft. When they have boarded, he slips into the water and pushes the primitive boat over to the hillock with the tree stump.\\

As the heroes climb the mound, they notice that the stump is hollow and hides the entrance to a dark cave. Below they hear the sound of something moving in the water, followed by a hissing voice: {\itshape Sssss, I don't know whether to welcome you or curssssse you, ssstrangersss. You come here from that clan of falsssse little folk, I sssssee you even bring one of them to my home ... ssssss. We've never had any quarrel with them, that issss until resssssently. Two moonssss ago they entered our territory and they have been draining our ssswamp ever sssssinsssss.}  Firsssst we waited for them to ssssstop, then we tried talking to them, but they killed our negossssiatorssss. Then we ssssent our warriorssss to the wheelhoussssse, but they were defeated.\\

Sssso a couple of dayssss ago I ssssent sssscoutssss to the little folk'ssss village. Although they alssso met with violensssse, I do believe that you are the anssswer to my sssscoutssss' pressssensssse. We are not looking for a war, sssso I will give you the opportunity to sssay your piessssse, but do not missstake thisss kindnesss for weaknessss, for if we have to, we will kill every one of thossssse ssssmallfolk, ssssss.\\

