%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-16
Next on the party's agenda is finding Balian's sister. Since Rolth and his black-haired woman were drug suppliers, they want to examine the drug scene in Korvosa. Puk, being a recovering drug addict, does not know where to get drugs in Korvosa, since Gaedran Lamm was his sole dealer. The party is quite sure that Lick knows where to get drugs, since the crazed artist admitted to using substances to expand his mind and creativity.\\

Balian and his companions head over to Lick's place of work in Old Korvosa, {\itshape Exemplary Execrables} . Refurnished with gaudy gold-colored paint and massive glass gems, the former temple of the now dead god Aroden has found a new life as the home of a perverse and detestable theater of all things foul, gore-slicked and unnaturally pornographic. The theater's owner is a repugnant sore-covered man, the infamous Pilts Swastel. Puk notes some sort of museum attached to the theater. Its billboards speak of "Two-dozen-and-three severed heads", "Unwanted fetuses" and "Instruments of torture and murder". This last billboard proudly displays a guillotine, which is supposed to be "in working order". Other billboards at the theater's doors announce Lick's play, the "Hell Mother", and show an intriguing half-demonic head with blue eyes that burn with rage, a naked woman in the background.\\

The party enters the theater where rehearsals are in full swing, but Lick ushers them back out, adamant to keep the play secret until opening day tomorrow. He does indeed know where to get high, just down the street, at the drug den in Eel's End. Quint knows of the place, but usually steers clear of it, since Eel's End does not have the best reputation. It consists of five ships, all moored at a pier, here in Old Korvosa. The boats provide all kinds of nightly entertainment, but rumors persist that most activities border on the illegal and are merely a front for even worse crimes. The young friends decide to pay the place a visit this evening.\\

While waiting they also have a look inside the "museum" connected to Exemplary Execrables. The macabre exhibit excites only Puk, whose enthusiasm peaks when he sees the guillotine, although his fervor does not extend to visiting the drug den tonight. The former addict fears temptation and figures he had better avoid drugs altogether for now. He offers to watch over the kids at the fishery instead.\\

