%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-03
At sunset Balian enters the small fortune-telling shop at 3 Lancet Street. As he walks into the fragrant haze of flowers and strong spice, he is happily greeted by a big black labrador. He immediately recognizes the dog as Spyder, the puppy he saved five years ago from the dream spiders.\\

"Well, well, if it isn't my friend Balian, it's good to see you alive. How did you get here?" At the round table in the center of the room is a man with a bewildered look in his eyes. It is an older version of Balian's former fellow lamb, Lick. Apparently he now goes by the name of Lucian Lycan and works in a theatre in Old Korvosa. He also received a harrow card, the one with the Courtesan, containing the same message on the back. When Balian asks about his sister, Lick is sad to tell him that she was taken on the same night he disappeared, the same night that Blackjack freed the other lambs. Lick knows who took her too, the creepy, blotchy man who was Lamm's drug supplier, Rolth. No one has seen her or heard from her in years.\\

The next moment a new visitor enters the shop. It is a halfling none of the two men at the table have ever seen before. He introduces himself as Puk and waves about another harrow card depicting the Juggler, with the same invitation on the back. Unlike the two gentlemen present he is not a former lamb, but he also had a bad run-in with Lamm. He confesses to occasionally buying drugs from the old crook, until he and his sister were forced to take something stronger, probably to make them addicted to more expensive stuff. The bad trip threw him into unconsciousness, but ended even worse for his sister, who overdosed. Since then he has sworn off all drugs and spent the last couple of weeks going cold turkey, detoxicating his body. Although he claims to be clean, Balian can't help but notice that even the strong smell of the incense burners troubles him.\\

Finally the last two invitees arrive. One is very tall, dressed in a breastplate, clutching the harrow card of the Marriage. The other one has a dashingly handsome face and treads with a much lighter step. He has the Unicorn card in his hand. These two are no strangers to Balian. They are his former 'partners in crime', Sjo and Quint. They fill him in on the terrible events on Saint Alika day five years ago, explaining how they tried to fight Lamm after he had sold off Balian to captain Korbat. It wasn't until Blackjack, the caped crusader, interfered that they got the upper hand and were able to get away from their tormenters. The fabled hero also aided them in freeing the other lambs, after which Lick burned down the old clog shop. Unfortunately Balian's sister Alika wasn't there anymore, as Lamm had sold her to Rolth earlier that evening.\\

The two youngsters had also tried to locate Korbat's ship at the docks, only to find out that the smuggler had already left, using both the dark and the distraction of the feast to get away unnoticed by any harbor patrols.\\

Quint and Sjo joined the Umbra Circus, where Alan Terdal and his fellow carni's welcomed them with open arms. They traveled with the gypsies for three years, before returning to Korvosa. There Quint started frequenting the local pubs and inns, slowly building a reputation for entertaining the crowd with humorous tales and throws of stand-up comedy. Meanwhile Sjo went into apprenticeship at the temple of Sarenrae, discovering after several months of harsh study that the path of the sun goddess wasn't his. After that he spent a year in the Great Tower of the Sable Company, initially training to become an elite soldier. After wounding an officer during archery practice, he had to admit that his sight was very limited. He had never fully recovered from Yargin's acid in his eyes, although several priests had tried to patch him up. They had finally told him that it wasn't anything physical that was preventing him from getting better, but that it seemed to be his fate, or curse, that his vision should be clouded.\\

Anyway, his bad eyesight prevented him from ever being able to become a marine in the Sable Company, as the friendly, but just lieutenant Illrem Bromathan explained to the disheartened Shoanti. Sjo accepted the officer's offer to work in the hippogryph stables instead, located on the highest floors of the Great Tower. This place was rumored to offer a marvelous view of the city, but being limited to an eyesight of no more than 30 feet, Sjo never got to enjoy the panorama.\\

This morning Sjo decided to quit his job. As he was wandering through the streets of the city, trying to figure out what to do next, fate intervened, putting a mysterious card in his pocket with a message, inviting him to come to Lancet Street. He had seen this harrow card before. Three years ago, Zellara, the fortune-teller in the Umbra Circus, had read his fortune. Although she declined to give him a full reading - as she only did that for grown-ups - she had agreed to show him his soul card. The Marriage depicted a water and fire elemental with a baby. It stood for things that should never have been united, but still, even an impossible union could result in a new power. Sjo's legacy would force him to choose between the powers flowing through his veins, a choice that he had already made when his hands had burst out in flames as he struck Gaedran Lamm on their final night together. It was this choice for fire that would later lead him to the church of Sarenrae, an unsuccessful path as time revealed, just like his new career at the Sable Company. Already it was becoming clear what Zellara had predicted: that Sjo would spend his life wrestling to overcome and unite impossible differences, both in himself and in the world around him.\\

Sjo also knew what he would find at 3 Lancet Street, since Zellara now lived here. She left the circus three years ago, claiming that life on the road was not suited for her young son Eran, who was eight at the time. How wrong she had been ... for the last person to arrive in the fortune-telling parlor is the card reader herself. She walks in through the door in the back of the room and thanks her guests for coming. She then explains what happened to her.\\

