%!TEX root = ../crimson_throne_book_main.tex
% 2013-11-01
The companions go look for the harbormaster and ask him what he knows about {\itshape the Delivery} and its cargo. The man says that the boat carried no goods, apart from food and supplies. Its only cargo was maybe two dozen passengers. The man denies knowing anything about girls being carried off against their wills, but confesses that the authorities can't check everything. The young friends also pay a visit to field marshal Cressida Kroft. They explain to her what happened with Gaedran Lamm, only leaving out that the kept him alive at first and then finished him off anyway before the guards arrived. Kroft confirms that she doesn't like types like Lamm, who live on the edge of legality, and - by paying their vice taxes - are allowed to continue their shady business in the city. She assures the heroes that she will take care of the red tape and make sure that they will not get into trouble for carrying out justice.\\

When the companions tell her that Rolth has left town on a Chelish vessel with a dozen children, she fears that the girls will be sold as slaves in Cheliax. Quint wonders if the skinny creep has made more trips to the south over the last couple of years. Maybe that is why he was so hard to locate, because he wasn't always around.\\

\section{6 Desnus 4708}

The following morning someone knocks on the door of the old fishery. While Sjo is joking that adventure just comes knocking, he is surprised to find the sour-looking magistrate of commerce on his doorstep, Garrick Tann, Korvosa's tax collector, also known as the 'most hated man' in the city. He is accompanied by eight guards and two men wearing the colors of Abadar. The companions immediately recognize the magistrate and also remember that they lifted his purse when they were children, including his masterwork dagger, that now hangs on Puk's belt. Sjo shoves that halfling out of the way, while making polite conversation. Tann states that the companions owe the city ten percent of their income. Having heard that they were given 1 200 gold sails by the queen, he is here to collect 120 GP.\\

When the heroes don't pay him right away, Tann informs them that they have until the end of the month to pay up. They also have to declare any other income they have. They can do so in his office, which is located in the shadow of Citadel Volshyenek. The magistrate also notes that the friends are staying in an abandoned building, which by law should go to the city and can't just be taken over by anyone who feels like it. Still, these matters are not his to handle, although he will inform his colleague.\\

To avoid future embarrassment with another officer of the law, the companions and the four children living with them decide to move to Zellara's house in Lancet Street for now. They also go and pay their taxes, to avoid having Tann track them down again.\\

\section{9 Desnus 4708}

On the ninth of Desnus Mama Mira contacts the companions and invites them over to the orphanage. She wants to talk to them about Sarai and Lauro, the two halfling children they saved from Gaedran Lamm's lambs. She suspects that the children's grandmother is still alive and well, living somewhere outside the city She asks the heroes return the children to their family. Apparently the siblings' father Bono came from the small town of Heavengard. He moved to Korvosa after his wife had died giving birth to Lauro, when Sarai was only three years old. The girl still remembers playing with her old {\itshape nana} under the apple trees. Three years ago Bono passed away himself and orphaned Sarai en Lauro ended up in Lamm's clutches. Since Mama Mira cannot leave her flock in the orphanage, she implores the heroes to take the brother and sister home. Heavengard is a cozy halfling settlement in a fertile valley at the foot of the Willspin Mountains, nestled quietly on the banks of the Jeggare River. Journeying there takes three days.\\

