%!TEX root = ../crimson_throne_book_main.tex
% 2013-08-03
Puk uses his skills on the lock, expertly opening the door. Inside is a large room with a huge opening in the floor that drops away to the river and shore a few feet below. In the water underneath is a creature that the former lambs immediately recognize: the ruthless alligator Gobblegut. The animal roars and snaps its giant jaws in the air, being too far below to reach the intruders. Spyder the dog starts barking loudly at the foul beast. As the companions try to calm the dog down, a door at the other end of the room opens and a bent corpse of a man with yellowed eyes and speckled skin looks out. It is the hunchbacked old snake Gaedran Lamm. Quint jumps into action, hurling a sleep spell at his former master, but Lamm seems unaffected by the magic. Recognizing the danger on his porch, Lamm quickly retreats into his chamber, but not before Puk hits him with a sling stone. By the time the party makes it to the other side of the room, the door is firmly locked.\\

Balian pulls out his thieves' tools to tinker with the door, trying to unhinge the bolt on the other side. It is a tedious job that takes him about a minute. In the meantime Lick is shouting and yelling at Lamm, trying to draw out the old coward, much to the displeasure of Quint, who sees his chances for a sneaky infiltration further diminished by all the noise.\\

When the door finally opens, the companions discover a small abandoned bedroom. Sjo casts a detect magic and sees the slightest hint of magic seeping from a strongbox at the foot of the bed. Above a wardrobe in the corner a trapdoor has been opened. Unless Lamm is hiding in the cupboard, he must have fled through there. Just to be sure Quint opens the doors of the wardrobe. It is filled with moth-eaten clothes and blankets. The middle shelf holds only a hatbox, surrounded by a cloud of flies. It reeks of death. Still, the party has no time to lose and quickly climbs up the cupboard and through the hole in the ceiling, to reach the workfloor of the fishery above. The three doors are all shut and there is no sign of Lamm. Where did the bleeding bastard run off to?\\

