%!TEX root = ../crimson_throne_book_main.tex
% 2013-06-02
\section{12 Erastus 4703}

The Narrows of Saint Alika, the small channel between Endrin Island and mainland Korvosa, is famed for its tasty oysters. The mixture of salty sea water and sweet river water makes for an excellent breeding ground for the shellfish, providing both the perfect temperature and salinity.\\

Supervised by Lou the swordsman and Giggles the snickering half-orc, a dozen of Lamm's children have been diving into the murky water all day to locate and dislodge oysters. While Quint is struggling to meet the quota, Sjo and especially Balian do much better and have oysters to spare, dividing them among their closest friends to avoid punishment. Jules, an eleven year old lamb, is having an extremely terrible day. His weak constitution and a lingering cold have him slogging and cursing all afternoon. By the end of the day his hands are raw and cut, and he feels cold and out of breath. On top of that he gets a beating at the hands of Giggles for not meeting the required number of oysters.\\

When everyone stumbles into his cot in the outhouse of the clog shop that night, Jules is still cursing and swearing to finish off Lamm once and for all. Alika, who doesn't like bad language, closes herself off from his harsh words and occupies herself with her favorite pass-time, carving little wooden soldiers. Still, her hands are sore from farming oysters, so her efforts don't amount to much and she quickly joins the others in sleep.\\

