%!TEX root = ../crimson_throne_book_main.tex
% 2014-12-06
Puk takes Madam Nesia to the villa while his friends follow up on the body carters who were going in the wrong direction. A vagrant at the side of the road calls out and asks them if they want to buy a cloak of rat skins. Sjo gives the man some silver, but immediately burns the filthy cape. For some extra coin the bum reveals that the carters pass by regularly. "They always disappear down a dark alley over there." The man points out where it is.\\

The high walls of the surrounding buildings throw the awkwardly bent Racker's Alley into constant shadow. The hidden sideway is rich with the stomach-turning stench of rot. Heaped against the wooden back wall, behind an empty cart, rises a pile of dozens of plague victims and hundreds of dead rats. The entry to a door has been left clear: it is the back entrance of a small rundown shop called {\itshape Giotorri's Toys} . The front door and windows have been boarded up, making the place look deserted, but the back door seems to be unlocked. Balian puts his ear against the wood and hears voices inside. The ranger pushes in, surprising two body carters in the shop's backroom. Sjo calls out to them: "In the name of the law, lay down your weapons!" But the fools do not head his words and make for their clubs. While Quint starts mocking them with his {\itshape satire} , Balian jumps forward and whirls his greatsword in a devastating arch, gravely wounding both men. (Double critical hit on a cleave.)  {\itshape burning hands} spells from Sjo and Balian's cleaving blade take them down. One of the carters makes it outside, but Spyder and Quint halt his escape. The final opponent surrenders. In the front room Balian discovers a stain of dried blood, no older than two days. The lone survivor confesses that he and his colleagues were tired of making the many long runs from north to south across the city with the corpse carts. So they started ditching the dead rats and bodies in this shady back alley. They thought no one would mind, but then it turned out that someone still lived in the boarded-up shop next to their perfect little dumping ground. Toymaker Giotorri had locked himself in his shop to keep the plague out, so he obviously wasn't too keen on having the infectious cadavers piling up against his back door. The carters tried giving him money, but when he refused, things got out of hand and they killed the old man. That is why they attacked the companions, because they were trying to hide a crime ...\\

Our friends take the murderer to prison and swing by the university to talk to its professor in alchemy, Sirtane Leroung. They ask her to examine Lavender's Luxuriant Liniment, hoping she can tell them whether the ointment really works. Sirtane seriously doubts it, even at first glance, since the substance can hardly even be called an ointment, looking more like grease. The professor in turn asks her visitors if they have heard of anyone recovering from the disease, or even better, of anyone who is immune. Since she cancelled her classes to avoid the danger of spreading the plague, she has been studying the pestilence, hoping to find a cure. Knowing that people actually recover from it, would be a great support. But the real clue to fighting the deadly malady could come from those who possess a natural resistance to it. The companions promise to ask around and keep her informed. They pay a quick visit to Field Marshal Kroft and the temple of Pharasma to report on the carters' scheme in Racker's Alley, before retiring to the comfort of the villa.\\

Puk has already taken Nesia to the tailor's and she is in the bathroom right now, getting ready for dinner. She may have lost her memory, but she certainly did not forget how the dress up: she looks absolutely stunning. Sjo offers the lost girl his bedroom and spends the night at Larella's.\\

\section{29 Sarenith 4708}

The children are still sick and Quint is feeling worse as well. Sjo on the other hand feels great, it looks like his body has fought off the infection. Balian is still as healthy as a fish and Nesia is in excellent physical shape too, but her mental problems persist as she still has no recollection of who she is. Balian and Sjo spend a couple of hours tending to the sick, including their daily visit to little Brienna. After lunch they talk to Sirtane Leroung again. The alchemy professor confirms her suspicions: Lavender's Luxuriant Liniment is nothing more than animal grease, mixed with weeds and some cheap perfume to make it smell less revolting. It has no healing properties whatsoever, apart from the potential placebo effect.\\

The companions report the matter to Field Marshal Kroft, but she lacks the manpower to do anything about Lavender's Luxury herself. She implores the four friends to attend to the case personally. She trusts them to handle the matter in whatever way necessary, but they have to close the shop, because all those people in the queue infect each other. This place offers no cure, on the contrary, it is a serious health hazard.\\

