%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-22
A few breaths later the doors fall open to reveal a large room. Malgar's corpse hangs from the rafters at the end of his spiked chain, a pool of blood on the floor beneath his swinging boots. From the looks of it this space used to be a lounge with comfortable couches and a mahogany table, all covered in a thick layer of dust. Several portraits line the walls, each obscured with a sheet of cobwebs. There is a cabinet in the corner with a few bottles and glasses perched atop it.\\

Sjo contacts Zellara's spirit through the Harrow deck. The gypsy soothsayer confirms that this place is haunted. There are spirits here that do not sleep. They are out for revenge!\\

Feeling it is time to confront the other jurors, Sjo summons everyone to the lounge. He wants to know what is going on. The jurors had better tell the truth lest they end up like Malgar Hurkes! Sjo stares down the former members of Mord's jury one by one. Hal Five-Toes starts shifting nervously, his breathing is irregular and fear speaks from his eyes.\\

"Speak up, man!" Sjo pushes him.\\

The limping blacksmith raises his hand and points at Malgar's swinging corpse: "He ... he made me! He forced me to find Mord guilty ... cut off my toes, he did, and still I refused to give in."\\

"So he paid you, did he?" Sjo sighs.\\

"How dare you say that! I would never ... no. He went after my children, is what he did. Kidnapped them and threatened to kill them if I didn't do what he said. I had no choice. But now ... the croaker will be after me. I wronged him, he'll want revenge, oh no."\\

"Hmm, does anyone else have anything to confess? Now's the time!" Sjo shouts to the rest. He steps up to Patrissa Vrakes, the voluptuous woman in the red silk gown. "I only did what I believed to be right", she claims while fondling nervously with her necklace. "I genuinely thought he was guilty, all the evidence certainly pointed in that direction. If I was wrong, I didn't know it. I do not deserve to die for that!"\\

"Were you forced or did anyone pay you?" Sjo pushes on.\\

"That will suffice!" sir Rekkart Cole interferes. "The man was clearly guilty! If he's out for revenge, it is because he was evil at heart, not because we were wrong! And leave this woman alone, she's been through enough tonight already!"\\

"So you claim to be honest, do you?" Quint asks.\\

"Well excuse ME, young man, I'm not sure you know how paladinhood works. We cannot cheat, we must always abide by the truth and the law, if not, we lose our powers! Which I never did, so my conscience is clear!" sir Cole retorts.\\

"I guess he is right," Zenobia Zenderholm confirms, "I've never known him to have fallen from Abadar's grace."\\

The next to suffer Sjo's scrutiny is Tablark the dwarf, but the ex-miner denies the accusations, declaring that Jarbin Mord was "nuthing but a filthy child-murderer and wife-killer! Hanging was too good for the likes of him. Should have let me give 'm a taste of dwarven justice, with the same axe he used to butcher his loved ones, you hear!"\\

Then Quint looks Ebin Bazel straight into the eyes. The failed jester clearly gets uncomfortable as droplets of sweat draw lines in his white make-up. "Well, we all know who is next, don't we?" Quint spooks him. "I wasn't forced or bribed, I wasn't!" Bazel defends himself. "Maybe you weren't," Quint insists, "but there was something, wasn't there?"\\

"Let's be clear, there was enough evidence, the man was guilty ... but, yeah, I didn't like him. It's true. He embarrassed me once in a pub ... can you imagine. They said that even 'death' was funnier than me. A stupid, ugly moron he was, this Mord guy, and he upstaged me! They laughed and clapped at what he said ... and he wasn't even trying to be funny! They threw me out in the street, knocking out this tooth right here", Ebin lisps, pointing at one of the black holes in his mouth. "But he was guilty and I voted to have him killed! I'm not sorry I did. He deserved it, mister hilarious hangman!"\\

"Yeah," Quint grunts, "Croaker's gonna get you next!"\\

Sjo turns his attention to Madge Blossomheart, encouraging her to open her heart. The young acrobat stares back at him with her big green eyes and her innocent face. "I didn't do anything wrong. Mord was a cold-hearted killer. He deserved to die." When she speaks those final words, Quint notices a mean little twitch  in her face, if only for a split second.\\

"And that leaves you, Paltreth", Quint says, facing the mustached man. "What were your motives for convicting the executioner?"\\

"I don't know ... I was pretty sure Mord did it. But there was some doubt in my mind, I'll admit. Still, the others all were convinced, so I just followed them. It had to be a unanimous vote, you know." The man straightens his worn-down jacket and pulls out a bottle of liquor, taking a sip, before calming down.\\

"That's easy for you to say now," sir Rekkart Cole snarls, "I didn't hear you protest back then ..."\\

"You're right, maybe I should have", Paltreth confesses.\\

"OH, MY GODS! It can't be!" Hal Five-Toes is standing by the cabinet in the corner. His whole body is quaking. When he turns around, he's staring at a glass jar in his hands with a look of utter disbelief in his gaze. Inside the jug some indistinct forms are floating in a semi-transparent liquid. "It's ... it's ... my toes. How did they get here? My toes."\\

"Looks like pay-back is a b*\&*!", Quint coldly establishes. "The croaker wants to punish you all! You'd better fess up if you want him to stop."\\

"I can't believe you, you are so misguided", is sir Rekkart Cole's response. "There is the man who was responsible for what happened in his courtroom!" The paladin points at a painting on the wall, although the many cobwebs make it impossible to tell who's on it. Quint whispers a {\itshape prestidigitation} to clear away the webbing. When he recognizes judge Silman Trabe's face from his vision, he is suddenly pulled back into his daydream. ---\\

The stocky magistrate coughs and stands up, facing the culprit: "Jarbin Mord, for the brutal and savage slaying of your wife and six-year-old boy, it is the verdict of this jury - with which I concur wholeheartedly - that you shall hang by your neck until dead. May the gods take mercy on your blackened soul." Silence falls over the courtroom in the wake of this pronouncement of doom. The faces of the assembled crowd grow solemn as everyone feels the finality of the sentence, but there are a few exceptions. Three jurors show a schmuck grin on their face: Malgar Hurkes, Ebin Bazel and Madge Blossomheart.\\

---\\

The vision takes but a few seconds. Then Quint turns to the jury members again, staring down each of them. "I know who you are", he whispers, allowing both the incompetent jester and the lithe acrobat a slightly longer look. There is a curt hint of fear in Madge Blossomheart's glance, but the experienced street performer quickly regains her bearings.\\

"Anyway, if you don't want to die, you'd better stick with us", Sjo orders the self-conscious jurors. "On the other hand", Zenobia Zenderholm disagrees," wouldn't it be better to stay together in a {\itshape safe} room, instead of wondering around this place. Who knows what else we might run into?" "Maybe you're right, lady Zenderholm", Quint concurs. "Take these people to the courtroom where we found them. They'll be safest there. Here, take Spyder with you, while we try to find out more about this place and the mysteries it harbors. But let's be methodical about it. Let us start at the bottom and make our way up. Is there a cellar?"\\

