%!TEX root = ../crimson_throne_book_main.tex
% 2014-04-26
The question on many lips is who will be the future power behind the throne. Since Queen Domina's arrival in the city House Ornelos has grown in influence, providing various councilors who had the monarch's ear, both Domina's and her son Eodred's. As Domina came from Cheliax, where contacts and contracts with devils are common, no one was surprised to see House Ornelos rise under her rule. What happens behind the walls of the Ornelos Acadamae is mostly shrouded in mystery, but one thing everyone knows is that the House specializes in summoning infernal creatures from Hell in the truest Chelish tradition. The many imps that plague the city are proof of that. Akmelek Ornelos, lord Toff Ornelos' grandson, is even showing off his personal little devil at this very feast.\\

Akmelek turns out to be just as unlikeable as the critter he summoned from Hell. He wants to use the companions to put in a good word with Marguerite Jeggare for him, since he wasn't exactly successful at impressing her himself. He feels an alliance between two of the most powerful houses in Korvosa would benefit both families. When he learns that the four young flavors of the month have never met the beauty, he is disappointed and starts trashing Amin Jalento instead. He claims Jalento is being groomed to follow in his father's footsteps and become a captain in the Guard. Although the boy's been training with fencing master Vencarlo Orisini for many years, he shows little promise and couldn't even stand up to a couple of ruffians in the street recently. Amin Jalento clearly lacks his father's talento! The companions stand up for Amin though and when Akmelek feels he has outstayed his welcome, he goes off seeking an easier audience.\\

A few moments later Paris Ornelos, Akmelek's sister, apologizes for her brother's lack of manners. She is also happy to learn that the companions did not encourage his stupid infatuation with Marguerite Jeggare: she is clearly out of his league. Their families might both be powerful, but Akmelek is just a creep, while Marguerite is the catch of the century in Korvosa. Paris is much nicer than her brother or grandfather. Like any other member of her family she has been trained in the arcane arts, but she has never summoned an infernal servant and does not like the prospect of having to do so for her graduation. Paris has also picked up a rumor that the king might not have died of natural causes. His widow, the queen, is even said to have ordered a secret investigation into the circumstances of his death, but she's keeping the inspection quiet for fear of causing another riot. Paris wonders whether the companions know anything about this. She even suspects them of being these secret investigators, but Quint has to disappoint her on both accounts.\\

Later in the evening captain Artan Jalento seizes the opportunity to thank the companions for saving his son's life and encourages the boy to seek friends like 'these heroes' if he aspires a place in the Guard. Again our friends come to Amin's defense, claiming he was sorely outnumbered. Amin tries to hide his annoyance and embarrassment caused by his father's comments.\\

The companions also meet professor Cyril Fordyce, husband to the headmistress of the university, lady Eliasia Leroung. As a specialist in history he claims that {\itshape The Passion of Saint Alika} is a heavily romanticized version of the truth. He had the good fortune of studying the real Alika Epakena's diaries. There is no mention of a love triangle whatsoever. Alika's father did indeed set her up with a Varisian trader, but she never objected to the relationship. She never made it to the wedding, however, since the Shoanti killed her before she could get married. Her  {\itshape visions} were real, but usually quite 'common' in nature: she predicted when it would rain or storm, or where the breeding grounds of certain animals were located. The story about her death is obviously not described in her own diaries, but there are various other sources detailing the great fire and Alika's demise, although the professor feels that these also stretch the truth, like the opera. Cyril Fordyce finds a fan in Quint, who is very interested in reading Alika's diaries himself. 