%!TEX root = ../crimson_throne_book_main.tex
% 2014-09-06
\section{23 Sarenith 4708}

The next morning sees some commotion in the kitchen. Heldrin and Korwick are accusing Mouse of having placed a dead rat under the table, something which the smallest of the three boys vehemently denies. Sjo and Balian examine the rodent and conclude that it died either from disease or poison. They bury the tiny cadaver in the garden. Sjo also purifies the food, just to make sure there is no poison, but even that cannot freshen stale bread, so they head to the baker's for some fresh loaves instead.\\

In the street they run into Grau Soldado, their sergeant friend from the Guard. He looks a lot cleaner than when they last met him, when he was drunk and depressed for having lost a few of his men and his brother in the riots. Still, he has an air of worry about him as he hails over the companions: "Friends, I was just looking for you. My little niece has come down with something. She's covered in red spots and can't hold down her food. She was very feverish all through the night and, to be honest, I'm concerned. Her mother wants to take her to the Bank of Abadar, to be cured, but she cannot afford the fee. I remembered your kindness and skill and was hoping you could help her out. Little Brienna is such a sweet girl. Can you make her better?"\\

Sjo replies that he does not master magic to cure diseases, but he will certainly have a look at the girl to see if there is anything he can do to help. The companions follow the guard to Trail's End. On the way over there Grau expresses his admiration for his sister-in-law. Being a single mother with three children is hard and everyone has to chip in to make ends meet, even little Brienna, who cleans houses in North Point. Grau visits them a few times a week to ensure they are safe and have everything they need.\\

When they arrive at the house, Grau's nephews are playing quietly in the living room. Tayce, Grau's sister-in-law, is upstairs with her daughter. One corner of the ground floor serves as the kitchen. A man in Abadarian garb is working at the stove, brewing some concoction that smells of cinnamon and anise. His skin is tanned, but not quite as dark as his high priest's, Darb Tuttle, who is a full-blooded Vudran. Upon seeing the man Grau is obviously displeased and rushes upstairs. Puk and Balian overhear him scolding Tayce for racking up a bill with an expensive and worthless healer when he said he would handle things.\\

Quint and Sjo head over to the priest of Abadar. Quint greets him in Vudran and he replies with a smile. He says his name is Ishani Dhatri. He is trying to help, but he has trouble recognizing the combination of the girl's symptoms and fears she might be suffering from a new disease. He is not allowed to use his healing magic, as that requires a fee to the Golden One which these simple folk cannot afford. So he's making due with his mundane healing skills. Sjo picks up that Ishani feels guilty about his church's doctrine and is doing what he can within the rules. He suggests having a look at the girl himself and goes upstairs with Balian to see Brienna.\\

The creaky steps open up into a bedroom loft above the main room of the house. A young girl with auburn hair lies in a big bed, her slight form dwarfed by the size of the mattress and the pile of pillows. Splotches of angry red rash cover her face and arms, appearing in irregular shapes and sizes. Her restlessness is interrupted by a violent fit of hacking coughs that jerk her entire frame, lifting her off the bed. The spasm passes, dropping her back in the sheets, but seemingly having done little to ease her breathing. Sjo and Balian examine her more closely and conclude that she will probably die within two or three days if she does not receive proper treatment. Sjo can already ease her suffering a bit by magically restoring some of the stamina she lost. He also tends to the rash on her skin and applies the ointment that Ishani made.\\

Since he can offer no help here, Quint decides to consult the library in the villa to see if he can find out more about this disease. The symptoms seem to coincide with those of a rare disease that was reported a few years ago in soutwestern Varisia, in a small town along the Lost Coast, Sandpoint. {\itshape Vorel's plague} put much of the town in bed sick, but despite its fierceness, it was rarely lethal, so almost all those infected survived. Quint hopes Brienna will survive as well, but remembering that Sjo gave her only two to three days if she didn't receive healing, has him worried. 