%!TEX root = ../crimson_throne_book_main.tex
% 2014-09-20
Sjo, Balian and Puk meet up with Quint and head to North Point to talk to Brienna' employer. While making their way across the city, Sjo takes the Harrow deck in his hands to consult Zellara's ghost about the strange disease. He gets a mental answer that she is not familiar with it, but maybe a new reading of the cards later today will offer some insight. When they reach the address where Brienna cleans, Sjo talks to the lady of the house. She has no symptoms and seems to be mostly worried about how long Brienna will be out. Asking around in the neighborhood does not unveil more information about sick people.\\

The companions also cross the bridge to Old Korvosa to pay a visit to Vencarlo Orisini. When the fencing master sees them arriving, he ends his lesson prematurely and sends his students off to clean up. He is very pleased to learn that Trinia is now safely in Harse with his old friend Jasan and thanks the four young men for their help. In fact, he has a reward for them. A long time ago he and Jasan were members of a band of adventurers, but they parted company with the Blackbirds over a conflict about what to do with the loot from an ancient dwarven tomb. While their friends decided to keep the treasure, Vencarlo and Jasan went to the city of Janderhoff to return their share of the loot to the dwarves. The Janderhoff people greatly appreciated their gesture, but still allowed them to keep what they had found. In Vencarlo's case it was a weapon, but preferring blades himself (especially the rapier), he never used it. Still, he never got rid of it either, promising himself that he would not sell it for profit, but rather put it to good use. Now he has found such a purpose in Sjo, who is well trained to wield it. Vencarlo disappears upstairs for a couple of minutes and returns with a heavy mace in his hands. Sjo is a bit shy about accepting it, but then he promises to use it to help defend the city. The metal feels quite cool to the touch as the weapon turns out to be made of cold iron.\\

That evening, after dinner, Sjo pulls out the Harrow cards and summons Zellara's ghost for a reading. The fortuneteller feels that Sjo's earlier questions about sickness and health would be best suited with theshield  {\itshape the trumpet} , which represents an archon blowing a horn in an overt declaration of power. This display of force clearly calls for Sjo to face the dire situations ahead with similar confidence. Quint picks  {\itshape the brass dwarf} which shows an azer who is unaffected by the flames that surround him. Likewise Quint will have to find the strength to withstand whatever dangers will cross his path. Balian's card is  {\itshape the waxworks} , a place of helplessness which dangles a bound man above a steaming vat of molten wax. If he is plunged into the boiling goo, he will be frozen in place for ever in eternal torture. Balian will have to be extra careful not to be caught in the inability to move or act himself, so this card serves as a dire warning. Despite his small build, even for a halfling, Puk draws  {\itshape the mountain man} , signifying that he might be a giant amongst men. The towering giant also stands for a huge force that is very hard to control, so hard even that it might be wise not to get carried away by it, if you want to survive its destructive power. Next Zellara puts the shield cards back in the deck and performs a full reading for everyone. Puk still needs to come at peace with his past, as shown by both the {\itshape inquisitor} and  {\itshape juggler} card. There is tragedy that he still hasn't fully accepted, as if he can't admit the truth about his own involvement, not even to himself.  {\itshape The wanderer} in his present acts as a collector of things that are valuable to him, even when others consider them useless. Puk has also shown a great knack for acquiring items, as he is possibly the best equipped member of the group. His days to come turn up two misaligned cards.  {\itshape The rakshasa} reveals the threat of a force that wants to enslave the bodies or minds of others, but the fact that it is in the opposite corner indicates that Puk might play an important part in casting off this enslavement. The empty throne suggests that this threat originates in an ancient past, whose restless ghost reaches out to the present. Balian's past is under the sign of the winged serpent, pointing out that the ranger has always known when the time to act had arrived. Apparently Puk is not the only giant amongst men, because {\itshape the mountain man} in Balian's present reveals that he is an equally impressive force.  {\itshape The beating} also indicates that the companions are constantly being threatened from multiple sides, making it hard to tell who is a friend and who is the enemy. The future turns up the  {\itshape unicorn} and  {\itshape the hidden truth} , although the third card in this column, which remains uninterpreted, is  {\itshape the idiot} , which obviously elicits some snickering from Balian's friends. The unicorn stands for someone who will offer help to uncover the real truth, although the hidden truth predicts that this truth might be something you had rather not known. Quint's cards reveal little. Just like in his first reading he does not draw a single card from the suit that blesses today's session.Characters gain a Harrow point for every card they draw from the chosen suit, which was  {\itshape The dance} in the bottom row of his past seems to indicate that Quint has always struggled to fall in line and follow the pace that was imposed on him.  {\itshape The tyrant} in his present is a ruling force that could be harmful to all, but the fact that it is in the upper row suggests that Quint is capable of detaching himself from that force.  {\itshape The big sky} in the bottom row warns that casting off the shackles of one master might quickly see new manacles from another lord.  {\itshape The crows} in the future are a dangerous bunch of enemies who violently take what they want and destroy that which is loved. The companions might be the only ones who can avert the threat of these long-beaked villains. Sjo has the misaligned {\itshape demon's lantern} in his past, as a sign that he had a hard time finding his true path, but the card's position suggests that he finally saw the light and he is on the right track now.  {\itshape The theater} in his present is misaligned as well. Sjo continues to play his part in the playhouse which is life, but he has to be careful to remain true to himself, so he doesn't play the wrong part. The future cards have a true match:  {\itshape the uprising} . A force stronger than the companions threatens to grab the city in its clutches. The crown on the pitchfork of the rebel in the drawing signifies an overthrowing of that force, whatever it may be ... 