%!TEX root = ../crimson_throne_book_main.tex
% 2014-10-18
When the companions get back to Citadel Volshyenek the Chelish guests have already arrived. They are in Kroft's office, so the heroes have to wait in the courtyard, where more and more soldiers are arriving. The Field Marshal has apparently ordered all troops to gather here for a big announcement. Some Gray Maidens are there as well and stand guard at the doors of the main building. When Quint asks them something, he can tell from their Chelish accent that these must be some of the Maidens who came from the old country, Cheliax. Grau Soldado joins his friends in the crowd and tells them  that his niece Brienna had a bad night again. He doesn't know anything about these doctors, but he suspects that their magical healing capacities - if any - will be limited, so they will mostly have to rely on mundane healing skills. Not all civilians are as lucky as his niece, who can also benefit from Sjo's magic to keep her strength up. The look in Grau's eyes expresses a gratitude that words could never encompass.\\

It takes over an hour before Cressida Kroft finally steps out. At her side is a middle-aged gentleman in a simple black overcoat with streaks of white gracing the sides of his short dark hair. He has a soft, concerned look in his eyes and tightly grasps a heavy doctor's case. They are followed by a more ominous looking group: men wearing cowled robes of oily-looking leather, supple gloves and wide, black hats. Their faces hide behind dark-goggled masks tapering to a pointed beak. Kroft climbs a weathered wooden platform and orders her troops to silence. She introduces the man at her side as Doctor Dave Saulus, the leader of the queen's physicians. The guards will have to escort these doctors in their royal duties, wherever they may take them. They will go into the city to help the sick, but if they want to get a grip on this disease, people will have to cooperate and do what the doctors order them to do!\\

Then Kroft's tone grows grimmer: "There is something else ... you are to consider orders from any of the queen's Gray Maidens to be as binding as any superior officer in the Korvosan Guard." A murmur of protest rises up from the dozens of red-and-gold-armored guards in the courtyard, but Kroft commands them to be quiet. "You are guardsmen of Korvosa, you have a duty to the citizens of this great city. These are dire times and our people need you and they certainly need these healers. You will do as commanded! Now, all patrol leaders to me for your assignments!" Quint makes his way through the soldiers and approaches Doctor Saulus. He offers is assistance in escorting the doctor himself, but the kind man replies that his job consists of coordinating his physicians work, so we won't be needing a personal escort. He does thank Quint for his kind offer, though, and tells him that he might call on him if the need arises.\\

When the patrol leaders have been given their orders, they take their men and leave the citadel with two of the new doctors in tow. The companions also depart, heading to Trail's End to see Grau's niece Brienna. As they travel through the streets of East Shore, a gaunt man with only one eye preaches to them that this plague is the wrath of Urgathoa, the goddess of disease, who is displeased that she has not been given her own spot in the Pantheon of the Many, Korvosa's temple to seventeen different gods, spread out over seventeen small shrines in a huge building in South Point. The Pallid Princess is not among these seventeen, which obviously vexes her. The old man claims that Urgathoa will not stop until every house has lost someone to the plague! The companions ignore the mad man's rambling and focus on aiding sick little Brienna instead. Her mother has already informed two of her former employers that she will be leaving, there is one more person to go before she is free to work at the companions' villa instead. Of course, that will have to wait until her daughter gets better, Tayce says. Sjo and Balian take their time to give the girl the necessary care. When they are finally done, they want to drop by Meep Gildenglare, the wererat seamstress, to see if she can offer any insight or help. On their way over there they notice new posters all over town:\\

 {\itshape "By Decree of Her Royal Majesty, the Radiant Queen Ileosa I, all citizens and members of the Korvosan Guard are to aid and admit the newly established Queen's Physicians in this time of urgency. These royal agents will extend healing to the sick and organize defense against the spreading affliction. They are to be allowed access to any home or building they deem necessary in the course of their duties. All those suffering from disease or disorder are to submit themselves to the Physicians for treatment. To aid in the duties of the Queen's Physicians, know that the order of the Gray Maidens has been established to provide military support as needed. The Maidens answer directly to the Crimson Throne, and will be called upon as necessary to augment and strengthen the peace where simple city guards will not suffice. Impeding or distracting the duties of the Queen's Physicians or the Gray Maidens is punishable by imprisonment. Impersonating one of the Queen's Physicians is punishable by death. Knowingly harboring or hiding the infected is punishable by death. Purposefully spreading the plague is punishable by torture, then death. The Queen's Physicians will be making rounds of every city district henceforth until Her Majesty deems this misfortune abated."}  Meep's {\itshape Gilded Needle} is a cute little shop along Burnt Bridge Boulevard. Meep is still the same kind old lady the companions met five years ago, though she doesn't immediately recognize her visitors. Quint reminds her of the play and refers to her 'power' over the rats. He wonders if she would be able to talk to the animals to find out more. She claims to be very worried about the rats dying recently, as she has four tame rats running around her shop whom she loves very much. She fears for their safety and has decided to keep them indoors for the time being. She confirms that she can exert some influence over them and their kin, but the rodents only possess animal intelligence, so they cannot speak, not even in a secret rat language, Meep smiles. "I can only get them to understand some basic, commands", she continues, "pretty much like you can with your dog. I fear that my aid in fighting this plague will be limited to laying low and hoping that the disease skips my door. I'm sorry I cannot be of more help." 