%!TEX root = ../crimson_throne_book_main.tex
% 2014-01-05
These set-ups were done outside of the game session. We play at a friend's house, because I live far away from everyone else, so my scenery stuff is usually in his apartment, but I brought it home for the holidays to test out my new camera.During play we only set up the areas where combat takes place, to allow for the strategic movement. It takes a fair few minutes during play to set up a scene, more so since I've been expending my collection and now I need to browse through more boxes to gather the pieces I need. I've been reorganizing a bit to try and improve this situation in the future, but since I do not play at home, I cannot set up scenery in advance, so that is a pity. Setting up these larger sceneries requires even more time, especially when you add the time to take pictures and rebuild things to make a second floor or something. Still, the fact that I have all this wonderful material urged me to try something like this for once. I also photographed some scenes that are still to come, so I'll be adding more pictures in the future. Get ready to see my version of the Marbledome opera house, the Shingle chase or the courthouse from As far as the repetitive issue is concerned, I've never been bothered by that, even when I had less material. During our previous campaign our DM used print-outs of the battlegrounds, but in my opinion nothing compares to the modular 3D options of Dwarven Forge and Psomminiature pieces. 