%!TEX root = ../crimson_throne_book_main.tex
% 2014-07-24
The companions deliberate what to do with Gaekhen's body. They have found the different parts of the young Shoanti warrior's corpse in the horrible dead warrens, but it is in no shape to present to his family. They decide to carefully wrap the body parts in sheets and transport them to the temple of Pharasma. If any site in Korvosa holds a mortician who specializes in preparing the dead for viewing, it will be the Cathedral of the Lady of the Graves. Bishop d'Bear immediately agrees to help her friends and tells them to return tomorrow.\\

Next the heroes pay a visit to the small Shoanti encampment to inform Thousand Bones of their findings, but they learn that the old shaman is with the Field Marshal in the Citadel, so they head over there instead. Thousand Bones, his {\itshape daughter-husband} Fergal the Fang and his  {\itshape daughter-sons} Arowan and Erogar are in Kroft's office. Since the tidings are so sensitive, Quint asks to speak to Thousand Bones alone, without Gaekhen's father and brothers. The bard realizes there is no easy way to inform the old Shoanti that his grandson was cut to pieces, but he and his friends manage to weave enough subtlety and bravado into their story to break the horrible news to the grieving elder. In the end Thousand Bones appreciates what the companions have done. This whole episode has badly hurt his people's confidence in Korvosa as a community, but at least Sjo, Quint, Balian and Puk have acted as honorable allies who even showed the spark of true Shoanti warriors. The shaman pulls four small bones from the collection hanging from his clothes. He marks each of them with a small rune and hands them to the heroes. He explains that the symbol stands for {\itshape nalharest} , which translates as "brother of the Shoanti", the highest honor a tshamek or outsider can hope to achieve among the Shoanti. Although the four young men are strictly only brothers in Thousand Bones' tribe, displaying this nalharest trophy to other Shoanti, will be of aid when interacting with them. When the shaman has left, Cressida Kroft awards the adventurers with a bag of 600 gold sails. Selling the scrolls and spellbook they discovered in Vreeg's chambers finally raises enough money to pay off their debts to the tax collector's office. Sjo also uses some of the gold to have a beautiful bouquet of flowers sent to Larella Semyr, the beautiful priestess of Shelyn, planning to pay her a visit tomorrow ... provided that "adventure does not come knocking at the door".\\

