%!TEX root = ../crimson_throne_book_main.tex
% 2014-03-29
Heading back to the main hall the party of heroes and jurors passes the only other door in this edifice that should actually lead outside and to everyone's surprise, it opens easily. Rain and wind welcome the companions to a large open-air chamber, overlooking the stormy waters of the bay. Unfortunately it is a cage that bars off escape on every side, even overhead. The space is divided in two by another set of bars, with a rusted cage door providing access to the second half. Hollow indentations in the ground mark the shallow graves of criminals who were executed here in the past. There are no name tags or tombstones to identity the poor wretches.\\

Sjo walks up to the cage door and pulls it. Rust flakes jump off the hinges as the iron grate creakingly swings aside. Madge Blossomheart suddenly steps past the Shoanti with a blank stare in her eyes. Sjo grabs her by the arm, preventing her from entering the second half of the potter's field, but at the same moment rotted hands claw through the dirt: six corpses burst out of the ground! "Daddy? Daddy? I'm here ..." Madge moans as she tries to pull free off Sjo's iron grasp, reaching for the worm-infested ghoul on her right. The creature welcomes her embrace by tearing a huge chunk of flesh out of her belly. Some of the other undead assault her as well, quickly making her go limp in Sjo's hands. The Shoanti pulls her back and closes the gate, while his companions take care of the ghouls on this side of the fence. Still, the undead reach for Madge's unconscious body through the bars, clawing at her guts that are now spilt profusely over the ground. Anger wells up in Sjo's chest as he pulls the grate door open again and leads his friends in a short, but decisive charge against the three remaining ghouls. Then his rage give way to a touch of despair, as he realizes that death comes for the jurors, no matter how hard he and his friends work to prevent it.\\

Ebin Bazel, the failed jester, comes to the same conclusion. "Why are we still following these so-called heroes? Are we supposed to be safer around them? The undead are picking us off one by one! And they don't even have to come looking for us, because we just come to them! Why didn't we stay in the courtroom? Whose stupid idea was it to join them?"\\

"Well, I genuinely felt we would be safer around them ..." Patrissa sighs, still shaking from the gruesome butchery she has just witnessed. "Maybe we will be in less danger  in the courtroom where we woke up", Sir Rekkart Cole admits as he puts his arm around Patrissa's shoulder. The ample-bosomed woman nervously toys with her necklace and agrees. Judge Zenobia Zenderholm, the dog Spyder and Killian Paltreth join the other jurors to the courtroom where this nightmare started.\\

Quint and his friends continue their search of the building on the first floor. The lounge where tonight's first victim, Malgar Hurkes, was hanged from his own chain sports a set of stairs and two more doors. One of these doors leads into the barrister's offices, a large area partitioned into smaller cubicles by wooden walls. Most of the old desks have been emptied long ago, but there are still some documents and books lying around. One of the offices apparently used to belong to {\itshape public prosecutor} Zenobia Zenderholm, while another desk was the working space of someone called Alastir Wade, a barrister. In a drawer Quint finds a red scarf of Varisian silk. Balian says that it looks a lot like the clothes worn by Malene, Mord's murdered wife. When the ranger saw her in his vision, she was dressed in a similar fashion. Quint also discovers a buyer's receipt for a string of 12 fire opals, made out to this Alastir Wade guy. The necklace's description matches the one Patrissa Vrakes is wearing. It was quite expensive, at 2,500 gold sails. It must have been a very generous gift indeed. The second door from the lounge opens up into a long hallway with a small set of wooden stairs in the corner and a door to the baliff's office, a dank room with mold-covered couches, some wooden cabinets and a weapon rack with some rusted arms and armor. Quint weaves a {\itshape detect magic} and notices some slivers of green light emerging through the cracks of a coffer in the corner. When Balian unlocks the lid, the coffer bursts open revealing a wretched corpse of a man in a faded blue uniform. A handaxe protrudes from his chest. It lurches forward and bites into Quint's flesh, before it is finished off by Balian's greatsword and Puk's little blades. The magic Quint discovered traces back to eight  {\itshape potions of cure light wounds} on the bottom of the coffer. 