%!TEX root = ../crimson_throne_book_main.tex
% 2014-05-03
\section{6 Sarenith 4708}

The fourth act of {\itshape The Passion} is all about the Shoanti. It takes place in their encampment in the wilds and features only the actors who portray Korvosa's original inhabitants. Sjo is the only one among them who has real Shoanti blood flowing through his veins and gets to play the leader, a formidable warrior known as Garak the Brute. The music in this relatively short scene is wild and Touran Palastus continually fires his actors on to be wilder and more barbaric. Leiny, his assistant somehow manages to be in his way every time he believes something goes wrong, which is often. There seems to be no end to the abuse coming her way today. Dario is bored. His presence in the audience only serves to enrage the people on stage, who get ridiculed by the foppish actor every chance he gets. While he believes his haughty attitude makes him popular with the ladies, Aisha has obviously had enough of him.\\

Mercival Jeggare joins Quint and Balian in the audience and asks for their input in an idea he's playing with. He wants to organize some sort of promotional campaign for the opera, but he's not sure how to do it. They finally decide on a public event, previewing a number of songs and a massive battle scene, in the Kendall arena. It will have to take place in two days, since that is the only day the cast can spare the time. Mercival will ask the Leroung university to print out flyers, inviting all Korvosans to see the preview for free. They will also hand out 20 tickets for the real opera.\\

Rehearsals are over by noon, since the fourth act is rather short, giving Quint and Sjo more time to train their voices with Xerxes and Auralia Lazanne. After practice Quint traces down the building where his mother was murdered. It is a cheap apartment building, owned by the Arkona family. He finds rent master Barad in a bar, but the man has only been in this position for nine years, since his predecessor Lenzo died. Quint asks around in the local pubs, but no one seems to remember a woman by the name of Leana Castel, who lived here 18 years ago.\\

\section{7 Sarenith 4708}

This day promises to be a long one, since the fifth and final act is also the hardest. It is very long and the songs are full of passion and tragedy. It starts off with a beautiful love song between Alika and Kallan, which Aisha and Dario perform brilliantly. Then it's Quint's turn, playing the enraged trader Garamon, who has to separate the lovers and attack Kallan. Alika throws herself between the rivals as the music swells to a feverish pace, at which point the girl receives her vision of the great fire, a beautiful illusion summoned by the hunchback Dargo.\\

The young girl warns the other inhabitants of the fort of the impending threat and Waydon Endrin promptly sends an envoy to Cheliax for aid. Panic rises in the fort. Palastus demands more devotion: he needs to feel the doom! Then a lone cry breaks through the thundering rhythm of the song. It's Balian's {\itshape one} second of fame, as he gets to shout: "Fire!" Both illusionists, the hunchback and the gnome, summon images of a raging fire, bathing the stage in a bright red blaze. The Shoanti leap through the flames and hurl themselves upon the defenders of the fort. By now everyone is so fired up by the atmosphere and the music, that getting into the role is easy. The wildest scene is also the most spectacular one. Touran Palastus turns into a master of the dramatic, showing a keen eye for where everyone has to stand and who has to shine during which part of the song. Sjo carries a lot of today's action and awes the director with his thrilling enactment of the barbarian leader. His singing lessons also pay off as he manages to support his swirling over the stage with a decent vocal performance. The sounds of battle are intertwined with Alika's cries of distress as she tries to usher the civilians to safety. At the height of the song Sjo defeats the leaders of the Korvosan army, Field marshal Waydon Endrin and his wife, while Alika desperately searches for her love Kallan.\\

When she finally finds him, the music quiets down. The lovers are given but a few short moments before Garamon interrupts them. Quint now matches Aisha's and Darnas's level, turning this part of rehearsals into an instant of brilliance. The two rivals resume their bickering, while Puk beats his heart out of his tiny frame on the percussion, announcing Sjo's arrival behind the unsuspecting girl. Dargo the Hump and Rimando Lumenos draw their illusionary flames up in Sjo's back, emphasizing the threat, as the Shoanti lifts his heavy club above his head. When he strikes down Alika, Puk beats his loudest drum, killing all the music for several seconds.\\

Only three people remain standing in a sea of bodies. Sjo as Garak bellows out his anger, sending Quint running with his tail between his legs. Although the bard is not happy with this part in his role of Garamon, he plays it to perfection. Meanwhile Kallan refuses to be intimidated by the hulking brute and engages the barbarian. The young soldier shouldn't stand a chance against the imposing chief, but his passion makes him fearless and determined. Time and time again he avoids defeat by ducking or jumping out of harm's way, until he sees an opening and plunges his blade in the barbarian's side. Of course Dario Darnas does not really hurt Sjo, but as his sword misses Sjo's torso by an inch, Rimando Lumenos is supposed to summon the illusion of a mortal blow, but conjures up an explosion of flowers instead. Sjo is then allowed the most elaborate death scene in the opera, after which Kallan kneels down at Alika's body. Dario Darnas cries out his pain in a dark song as the grim reaper appears behind him on stage. The herald of Death swings his scythe to collect the souls of the fallen and drives back Kallan, since mortals hold no sway over Death. Kallan sings out to the gods and sees his plea answered by a bright light from heaven.\\

Finally Auralia Lazanne, the diva from Cheliax, can show off her skill. Although she is down with Puk and the other musicians in the orchestra pit, her voice is so powerful that it more than compensates for her absence on stage. Dargo the Hump nimbly jumps across the rigging above the stage and pushes pulleys and counterweights to activate the flying rig supporting Ali\"ena Fochs. The actress descends from the heavens in the guise of a winged angel, while joining Auralia Lazanne in song. As she lands on the ground, she takes Alika by the hand, at which point Aisha starts singing as well. Leading her back to the back of the stage, the two women step into the flying rig and ascend to the heavens. While the three female voices bring the closing song of the opera to a climax, Touran Palastus is moved to tears. The director has not spoken a single word during the last few minutes of practice, which is a new experience to the cast. Now he bursts out in applause, praising his 'ladies' over and over again. "Marvelous, truly marvelous! This is a divine finale!" he cries as he falls into Auralia's massive arms. "Well, it ain't over 'till the fat lady sings", Rimando Lumenos chuckles, earning himself an angry look from the overweight diva.\\

Of course, being a perfectionist, Touran insists on doing the songs over and over again. By the time rehearsals are over, everyone is exhausted, but content. Leiny tells Quint, Sjo and Puk that they are expected again tomorrow morning. Auralia Lazanne wants to continue practicing the songs. In the afternoon it's time for the promotional tour. Dress rehearsals are in two days and starts early.\\

