%!TEX root = ../crimson_throne_book_main.tex
% 2014-06-14
\section{12 Sarenith 4708}

Today marks the coronation of Ileosa, to which the companions have been invited. They clean up and make for the castle by ten o'clock. The streets are already packed with hundreds of Korvosans who don't want to miss a thing. The invitees include a lot of the people who were present at the opera as well. While everyone gathers on the terraces on top of the mastaba, the companions recognize many of their new acquaintances, Zenobia Zenderholm, Mercival Jeggare and his nephew Xerxes, Eliasia Leroung with her family, including Aisha, and all the other nobles as well. Touran Palastus is present as well, as is Vencarlo Orisini, the fencing master.\\

By twelve o'clock all the bells in the city start ringing. The crowd begins to cheer and applaud, as the gates of the castle open and Ileosa appears, dressed in a sober white gown. A number of people follow in her wake, including Archbanker Darb Tuttle of Abadar, bishop Keppira d'Bear of Pharasma and Field Marshal Cressida Kroft. The queen strides to the end of the terrace - which looms as a balcony over the streets below - welcomed by the warm ovation from the citizens that have gathered in South Seneschal Street and Ramp Boulevard.\\

Darb Tuttle mounts the small podium that has been constructed there, taking up position on the right-hand side of the empty crimson throne. As he raises his hand, the crowd falls silent.\\

"People of Korvosa," he booms with a magically enhanced voice, "the untimely death of King Eodred II was a shock to us all. A deep sense of sorrow took hold of us and threw its shadow over the city. Still, such feelings of bereavement are natural when a beloved father passes. And while some of the events in the last couple of weeks have chilled our hearts, it also warmed my soul to see how much Korvosa loved its king and how hard it struggled to cope with its grief. And so, through the shadow shines a brightening light. Your fire is like the fire of the phoenix who arises from the ashes of mourning.\\

I was at Eodred's side during his last days. He was deeply troubled by the fact that he hadn't given the city an heir to take over his task. Even on his deathbed he was more worried about his people's future than his own faltering health. He shared this concern with me many times and it does him honor, just like your concern for our future would do him proud. If only Eodred had known how hard his death would affect Korvosa, he would have been elated.\\

But Korvosa is strong. It has proven numerous times that the will of all Korvosans combined makes us into an impregnable fortress. We, Korvosans, know how to survive. And that is something we do united, not divided. So let us become as one again, let us take the strength of each of you and forge it into a spear of unity.\\

By Korvosan law the king's power passes to his widow, lacking a naturally-born heir. Lady Ileosa has been found willing to pledge her life in the service of the city and its noble inhabitants. Korvosa places a heavy burden on her shoulders, which she accepts with humility and a sense of duty.\\

And that is why, people of Korvosa, I ask you to bear witness to what happens here today, under the eyes of the gods. Because it is from your hands that the queen receives her crown. So let us become one hand that anoints, one voice that blesses and one will that crowns. Citizens of Korvosa, become one heart that welcomes your future ruler!"\\

Tuttle raises his hands to the heavens and the crowd bursts out in joy while Ileosa steps onto the platform. She gives the highpriest of Abadar a warm smile as she kneels in front of him. The Archbanker faces his queen and the people hush once more.\\

With his palms directed to the sky, he solemnly proclaims: "Ileosa Arvanxi, also known as Ileosa Arabasti, do you swear to govern the whole of Korvosa according to its charters and customs?"\\

Ileosa solemnly replies: "I do."\\

"Will you to your power cause law and justice to be executed in all your judgments?"\\

"I will."\\

"Do you promise to maintain and honor the laws of this city to the utmost of your power?"\\

"I do."\\

The highpriest approaches Ileosa, dips his hands in a chalice of oil and anoints the kneeling woman on the forehead, the temples and wrists, while declaring: "The almighty and ever-lasting gods pour their spirit in your soul, judgment and actions. May you govern this city with wisdom, keep the peace and serve its people and lands."\\

As the young woman rises, Keppira d'Bear steps forward to hang the red robe of state over her shoulders. Then Ileosa takes a seat on the crimson throne, watching how Cressida Kroft walks up to Darb Tuttle, carrying a velvet cushion with the crown of Korvosa. Tuttle gently takes the shining jewel in his hands and displays it to the crowd. Then he turns towards Ileosa and holds the crown above her head: "Ileosa Arvanxi Arabasti, may the gods who have given you this royal honor in their divine providence, grant you the wisdom to banish all wrongs from Korvosa, to lead your people to prosperity, to bring comfort where it is due and to serve the laws of this city." Then he places the crown on the new queen's head, raises his hands to the skies and calls out: 'In the name of the gods and the people, I crown you, Ileosa Arvanxi Arabasti, queen of Korvosa and all her inhabitants, you and no other!" Next he kneels at her feet: "Long live Queen Ileosa! Long live Korvosa!"\\

Everyone on the terrace drops to his knees as well and repeats the words, as do the citizens in the streets: "Long live Queen Ileosa! Long live Korvosa!" Then a cheer arises that resounds far beyond the city walls.\\

Finally Ileosa stands up and speaks: "People of Korvosa, witness my first act as your queen. I hereby declare the twelfth of Sarenith an official holiday. Today you will eat and drink for free! Celebrate, my subjects, enjoy this day, for it is truly a glorious one!"\\

At the same time a patrol of hippogriff riders appears from behind the castle. As they fly over the crowd, they throw down silver pieces. Ileosa waves to the crowd, basking in the joy and enthusiasm of the people, before returning to the castle. A handful of able-bodied servants take the throne and follow her. Then the rest of the people on the terrace can go inside for the banquet.\\

