%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-01
\section{28 Desnus 4708}

Now that they have a classy home in South Shore the companions realize that their clothes have to match their abode, especially since they'll be meeting with the leaders of the city later that day. So they spend most of the day buying a new attire and having their outfits fitted to perfection.\\

At eight in the evening they make their way to the palace again and meet the bigwigs of Korvosa, who have all gathered in the throne room. Cressida Kroft waves the heroes over as they enter and introduces them to Commander Marcus Endrin of the Sable Company, Lord Mercival Jeggare, one of the richest men in the city, and Lord Valdur Bromathan IV, who has broken with his family's tradition of military service in favor of a career as a priest of Sarenrae.\\

Also present is Archbanker Darb Tuttle of the bank of Abadar, the city's most powerful priest, who is locked in conversation with two magistrates, Syl Gar, the Magistrate of Expenditures, and his 'counterpart' Garrick Tann, the Magistrate of Commerce. While Syl Gar is responsible for spending levied taxes on the city's behalf and is thus greatly loved all over, Garrick Tann is the chief tax collector, who is often referred to as {\itshape the most hated man} in Korvosa. The companions met this man before and already dread their next encounter, as they will have to pay a ton of taxes for the various magical items they have recently acquired and for their new home. Another familiar face is that of Zenobia Zenderholm, the high judge. She is talking to another noblewoman, Eliasia Leroung, the head of the university of Korvosa who responsible for printing the Korvosa Herald. The third person in their company is a handsome man with a clever look in his eyes, Glorio Arkona, the only nobleman who lives in Old Korvosa, where he is considered somewhat of a hero by the poor, for whom he provides cheap housing.\\

There is one more person in the room, a sour-faced old man with a long white beard and purple robes. He is seated all alone by the hearth. Quint recognizes Lord Toff Ornelos, the headmaster of the Acadamae and possibly Korvosa's most powerful arcanist. The bard greets the loner and kindly inquires about the Breaching Festival, the annual competition in which students and a number of invitees attempt to break into the Acadamae and breach its many magical defenses. Tomorrow is the 29th of Desnus, on which this festival normally takes place, but Quint has picked up rumors that the holiday will be cancelled this year. Lord Ornelos confirms the news, groaning that it wouldn't be proper to celebrate while people are killing each other in the streets.\\

Next Sabina Merrin, the commander of the Gray Maidens, steps into the room. "Ladies, and gentlemen, I give you ... the queen!" The leaders of the noble families bow, while the two magistrates and the four young heroes get to their knees. Queen Ileosa walks in, as glorious as ever. She is no longer dressed in black, but strides forward in a flowing green silk gown which is once again complimented with her father's brooch. She glides over to the throne and takes a seat, allowing herself a few breaths to let her eyes wander over her guests. When she speaks her voice is calm but strong: "Ladies Zenderholm and Leroung, my lords Jeggare, Bromathan, Arkona and Ornelos, Commander Endrin, Field Marshal Kroft, Archbanker Tuttle, Magistrates Tann and Gar, sirs Quintillian, Sjo, Balian and Puk, I bid you all a warm welcome."\\

The guests are all ears as Ileosa continues: "I have convened the council to discuss the state of things in Korvosa, and for this occasion I have asked a few advisors to join us. Would you all please follow me to the royal reception room so we can commence healing our wounded city?"\\

