%!TEX root = ../crimson_throne_book_main.tex
% 2014-04-05
The high judge realizes that she has to take charge now. She checks the front door one more time, but when she still finds it closed, she beckons everyone to follow her to the courtroom. Quint acts as the prosecutor and calls Patrissa, judge Trabe and his companions to the stand, where they all repeat their confessions and visions. Wade still denies all the accusations and screams that he does not recognize the authority of this court. He still refuses to confess and laughs at the evidence. A silk shawl in his desk? There are hundreds of women in Korvosa who wear those. A gift to Patrissa, well, she is quite attractive, or at least, she used to be. A knitting needle and a scar that come together in a dream. Don't be ridiculous! Still, when everyone has said his piece and judge Zenderholm asks Wade to defend himself, he rejects this court again and refuses to speak any more.\\

"Then, in light of the evidence, Alastir Wade, I see no other choice but to find you guilty for the murder of Malene and her son Gabe, and indirectly for the death of Jarbin Mord. The penalty for such heinous crimes, under Korvosan law, is death." Zenderholm strikes her hammer on her desk as she delivers judgment.\\

Sjo wastes no time and drags Alastir Wade to the gallows. A new rope already dangles from the crossbeam as they enter. The Shoanti forces Wade's head through the noose. "Have any last words, murderer?" he asks.\\

"Damn you! Damn you all!"\\

"Yeah, whatever", Sjo shrugs. He turns to the lever that makes the floor drop from under the convict. A shadow has appeared there. The ominous figure's head still lolls obscenely to one side on its broken neck. The darkness in its face barely reveals one milky eye peering through a hole of its executioner's mask: it is the croaker. Slowly he reaches for the lever. He gives Wade one last look, then he pulls the bar. The rope snaps tight. Wade starts kicking and twisting freakishly, trying to regain his footing. He finds only air. As the seconds go by, the twitching lessens, until it stops altogether.\\

The shadow of the Croaker changes into the ghostly appearance of a man. He does not look handsome, but he has an air of honesty about him. He nods in gratitude and turns around. As he walks away he is not alone anymore. A beautiful woman is holding his left hand and a child walks to his right. After all these years the Mords have finally found peace.\\

Suddenly the atmosphere doesn't feel as suppressive anymore. It is as if a sigh of relief emanates from the courthouse. Sjo pulls out the bottle of Chelaxian Daemon-Spirit and uncorks it. He passes the bottle around, allowing everyone to take a sip. "I will even indulge myself and have a real drink for once instead of water", Sveth smiles. "So, when you were suffocating earlier tonight, that was fake as well?" Sjo informs. Sveth nods: "It was. A necessary deception, I'm afraid. I'm sorry for misleading you." Sir Rekkart Cole does not join in the fun; he seems to be upset about having convicted an innocent man to the gallows ten years ago. He also avoids Patrissa's company for the first time tonight, obviously blaming her for manipulating him.\\

When the companions try the front door again, they find it unlocked. Balian, Puk and Sjo make sure judge Zenderholm gets home safely. She promises them to take care of the loose ends: the bodies in the courthouse, the red tape and judge Silman Trabe. Meanwhile Quint escorts Patrissa Vrakes home and sweet-talks his way into her bedroom. He has some stress to release.\\

