%!TEX root = ../crimson_throne_book_main.tex
% 2014-04-19
\section{31 Desnus 4708}

When Quint returns to the villa the next morning, he picks up a copy of the Herald. An advertisement calls for actors, singers and musicians in the Marble Dome for {\itshape The Passion of Saint Alika} , reminding the bard that this afternoon marks the auditions for the play that has to promote the city and her new queen. He will have just enough time to squeeze in a few hours of sleep before showing impressing the high and mighty of Korvosa's cultural scene with his talents. Sjo pays a visit to the tax office first, where he is immediately allowed into magistrate Garrick Tann's office. Having your own villa in South Shore has its perks, or maybe just having to pay a s***load of taxes does ... Tann welcomes his guest and asks him to declare which valuable possessions his group acquired over the last month. He already knows about a couple of things and is content to hear Sjo mention those. Then he starts making all kinds of calculations and ends up with a sum of 6,006 gold sails, which he kindly rounds down to 6,000. Sjo manages 1,500 gold pieces already, promising to come back later next month to pay the rest.\\

The companions also sell the magical rapier they took off Alastir Wade, since the barrister won't be needing the weapon anymore. Furin Ironguts, the dwarven smith from East Shore, is happy to take the fencing blade off their hands. With the money they make, they buy a new {\itshape wand of cure light wounds} in the temple of Sarenrae. Then they head for the opera house. The Marbledome is probably the grandest opera house in Varisia, rivaled only by the Triodea in Magnimar. This gleaming temple of music is situated in the upscale Heights District, just a few streets south of Castle Korvosa. Patron of the arts in the city and owner of the Marbledome is House Jeggare, whose abundant funds also flow to the Jeggare Museum. The head of this noble family, the friendly and enthusiastic Mercival Jeggare, is the one who invited the companions to join the auditions; he even insisted on their attendance. Rumor has it that Touran Palastus, the director, is a tyrannical, bile-spewing sadist who treats his performers poorly and whose productions bleed gold. Still, everybody who wants to be somebody on stage, has to put up with his foul moods to make it to the top, because Palastus makes or breaks the career of actors and musicians in Korvosa.\\

The theater is already buzzing with activity when the companions arrive. A gray-haired gnome with a goatee welcomes all would-be actors curtly and puts their names on a list. Then the waiting starts, seeing long hours in which a lot of nervous and insecure candidates, but also a few confident and even cocksure artists are called into the grand hall. A self-conscious girl with long black hair walks in every few minutes and calls out the next name.\\

One of the more relaxed people waiting around is a nonchalant young fellow with a disarming smile. When he spots the heroes, he walks over: "Good afternoon, sirs Quintillian, Shaoban, Balian and Puk, I presume? Allow me to introduce myself, my name is Xerxes Jeggare. I've heard impressive tales about you. I'm thrilled to see you have accepted my uncle's invitation." Xerxes is an accomplished, well-known musician in Korvosa and he makes for enjoyable company. He is in charge of the orchestra and will be playing the piano. He gives his take on the main cast; he reckons that up-and-coming star Aisha Leroung will be playing the lead, Saint Alika, while Dario Darnas will feature as her beau, the Chelaxian soldier Kallan. His rival, Varisian trader Garamon, will probably be portrayed by Dierderik Lodann, a fast-talking merchant himself by trade. Xerxes points to a ginger-haired man across the room, who is eliciting 'ohs' and 'ahs' from a couple of bystanders while fabricating some marvelous stories. "Of course," Xerxes admits, "I don't know what you are capable of. I don't see any competition for the part of Alika among you, but who knows ... maybe Darnas and Lodann should watch their backs. Of course, your participation in the play is already assured, my uncle insists on that at least. He's in the jury and will make sure you get cast, even if it is just as a face in the crowd. And if all else fails, you are always welcome to help out behind the scenes, if you can put up with Rimando over there", Xerxes smiles as he wave hello to the grumpy gnome with the gray beard. "Oh, and one more thing, when you're in there, be nice to the fat lady. She can be quite critical, but charming her will get you a long way."\\

When the black-haired girl enters next, she calls out the names of Quint and his friends and beckons them to join her in the main theater. As they climb the stage, they see Mercival Jeggare's friendly face on the first row. Next to him is a nervously shifting busy-body of a man with a monocle, who is waving about his walking stick furiously as he is lamenting to the tremendous woman to his other side. An extravagant dress hugs her enormous curves as she nods in agreement with every word that flows out of her neighbor's mouth. A thick layer of make-up paints her face alabaster, contrasting heavily with the stress-induced crimson neck and face of the man seated next to her.\\

"Huh, Leiny, what is this? Are we calling them in in groups now?" the aggravated man hurls at the shy girl who tries to hide beneath her black locks. "Maybe it's for the better, we might just see this horrible day end a bit sooner!"\\

"Relax, dear Touran," Mercival Jeggare graciously declares, "these are the heroes of Korvosa I've been telling you about. The ones who turned around the negative vibe in the city"\\

"Heroes, you say? Rabble of the street, you mean. I don't see how bringing in these thugs will aid our play, as if I don't have to work with enough amateurs as it is already?"\\

"Don't fret, my friend. They may show some talents yet. You might just be surprised", Mercival pats the director on the back. "Welcome my friends, I've been looking forward to seeing you here. Time to put on a little show", Mercival winks at the companions.\\

Eying Sjo, Palastus immediately recognizes his Shoanti looks. He asks him to take off his shirt and nods. "A fine barbarian, right there." Sjo impresses the jury with his impersonation of a Shoanti who tells his tribe about his latest victory, but his singing obviously still needs work. Quint also scores when asked to imitate a merchant who got robbed, but the long night and short sleep give him a coarse voice today, so his song falls short as well. Balian's effort at acting is acceptable, but singing is not the ranger's cup of tea, so he doesn't even give that a shot. Puk's talents are better suited for the orchestra, which the halfling proves with an excellent performance on the percussion instruments.\\

Mercival Jeggare is quite pleased with the companions' artistic achievements. He tells them that the jury will put up a list tomorrow morning at the doors of the Marbledome with the names of those selected and the roles they have to play. Rehearsals start at 3 o'clock in the afternoon.\\

