%!TEX root = ../crimson_throne_book_main.tex
% 2014-07-24
\section{14 Sarenith 4708}

At breakfast Mouse tells his masters that there is a guest at the door: Cressida Kroft has decided to pay the heroes a visit for a change, instead of having them summoned to her office in citadel Volshyenek. She is impressed with the villa, calling it a wonderful gift, but Quint and Balian claim that taxes alone on this expensive building have cost them so much that it can hardly be considered a 'gift'.\\

The Field Marshal has news about Trinia Sabor, the girl who was accused of having murdered the king: she has confessed to her crimes! As prescribed in the Charters of the city, she will have to repeat her confession "under the sky", in front of a judge and two witnesses. This law was installed long ago to prevent people from procuring confessions through torture: when someone admitted during questioning to having committed a crime, he had to repeat this confession outside of the prison where he was interrogated - "under the sky". If he confirmed his guilt, he was indeed found guilty, but if he withdrew his words, it became obvious that his confession had come about under duress. Custom changed this law somewhat: nowadays the suspect still has to repeat his confession to a judge and two witnesses, but it usually takes place in the courthouse as well, and not outside "under the sky", although the law is still known by this name.\\

Today however, Trinia will not speak to only one judge and two witnesses. Since the crime concerns regicide, more people are invited to bear witness to her confession, including the companions, since they were the ones who captured Trinia Sabor. They have to be in Castle Korvosa at one o'clock.\\

Quint and his friends are very worried by this news. Trinia's confession does not fit with how passionately she denied having killed the king only three days ago. When they learn that Trinia was not being held in the Longacre Building, but was transported to Castle Korvosa for "safety reasons", their concerns grow even more. They wonder if Sabina Merrin, the commander of the Gray Maidens, is somehow involved and has manipulated or forced the young painter to confess.\\

To find out more about the legal procedure, they swing by high judge Zenobia Zenderholm's office. Lady Zenderholm will actually be leading today's interrogation and although she carefully listens to the companions' concerns, she tries to put their worries to rest. She will be using her clerical abilities to summon a {\itshape zone of truth} around the suspect, which is not a watertight system since it can be fooled, but it certainly adds another level of assurance. She also claims that compulsion magic to have someone sign his own death warrant would have to be extremely strong, a simple  {\itshape charm person} would never suffice. She also tells the heroes to take into consideration that the girl might actually be guilty: they only spoke to her once and she might have fooled them with her claim of innocence. Finally the four friends accept that they will have to trust in Zenderholm's expertise. Quint and Sjo also look through the books they discovered in Vreeg's lair if they find any reference to the poison that was supposedly administered to the king, but they find nothing. The companions also look up Trinia's friend Nisha to check if she has not been kidnapped to force Trinia into confessing, but the tiefling stripper is still at home. Wrapped in her bed sheet she answers the door. She cannot understand why Trinia would confess to something she didn't do and blames the young men at her door for Trinia's current predicament. They convinced her that justice would triumph if she gave herself up! Nice display of justice this turns out to be!\\

