%!TEX root = ../crimson_throne_book_main.tex
% 2014-09-20
\section{24 Sarenith 4708}

When the companions walk down the street the next day, they see dead rats everywhere. People claim that they saw rats dying under their eyes. The animals convulsed in desperate spasms until they stopped moving. Asking around in the temple of Pharasma, our friends learn that half a dozen people have come in sick today with the same symptoms as Brienna. Sjo wants to swing by the Shoanti camp to give Thousand Bones the pendant he found in the Shundar-Quah tumulus. He is surprised to find out that the visitors from the Cinderlands have left town. Gaekhen's family was very angry about his death and the defilement of his body. There were also rumors that the Shoanti on the Storval plateau are gathering for war and Gaekhen's father was eager to join them, while Thousand Bones felt his mission should take him there as well, but then with the purpose of trying to prevent such a war.\\

Puk and Sjo use the privacy of the old fishery to examine some dead rats. Puk shaves them so Sjo can study their skin. They also have red spots, which have even turned into terrible sores with pus and blood. They clearly died from the advanced stages of the same disease that some citizens have contracted. The companions scour the pubs in the harbor to find out more about the ship that sank in the river, fearing it might be connected to the sick rats. There is no sign of other dead animals, the fish and birds all seem to be unaffected. If anyone knows more about the ship, it's the Sable Company. There were some hippogryph riders in the air when the vessel went down.\\

Since Balian is not the smoothest talker, he chooses to sit at a quiet table while his mates are gathering information. As he is enjoying his drink, he sees a shapely woman approaching. She is very beautiful, has a tanned skin and shiny dark hair. "You're Balian, one of Korvosa's new heroes, are you not?" she smiles while she bends forward, offering the ranger a peek into her cleavage. "I would like a word, but you have to promise me not to get mad and let me finish." Balian sighs, suspecting that this is the Vudran schemer he and his friends have been looking for.\\

"Our paths have crossed in the past, although we never actually met", she continues. "My name is Selena, but you already guessed that, I suspect. I hope you give me the chance to clarify something in a civilized way. I am indeed the one who set up Verik Vancaskerin in All the World's Meat, so he could feed the starving people of the city."\\

"With human meat", Balian grunts.\\

"Verik was not responsible for the actions of the goons that went with him ... those cow hammer boys had their own agenda. He did not know about their evil deeds. A most unfortunate circumstance that was, but Verik's intentions were true, as were mine, with the butcher's shop.\\

Anyway, I am part of ... an organization that has never trusted the queen, from the early start. We believe her to be a power-hungry manipulator who orchestrated the king's death to claim the throne for herself. A month ago you were still willing to give her the benefit of the doubt and help her secure her position. But lately, if I'm not mistaken, some cracks have started to appear in this confidence. I've been following your exploit from a distance and I suspect that you also have some doubts about the queen's true intentions ... or at least that is what I would think of the men who helped free the falsely accused murderer of the king from the queen's clutches." At these words the woman peers deeply into Balian's eyes. "Yes," she claims, "I have my resources. But don't worry, your secrets are safe with me, including the location where the girl is hiding right now."\\

"But enough of that for now. I fear the queen has been concocting new evil plans to tighten her grip on the city. She will strike among those who can still oppose the most, the city's nobles. Tomorrow night, there is a party at the Carowyn residence where the young scions of the noble houses will be present, a masked ball, to be exact. Cedrik Carowyn, the family's son is hosting the event in his villa in South Shore, which is quite close to your place, actually.\\

Two days ago one of the Carowyn servant girls visited the castle ... twice. She moved through the streets in a highly suspicious manner and normally there would be no reason at all for her to go to the palace, so naturally I got curious as to why she'd gone there. I tried looking her up yesterday, only to find out that she hadn't survived the night. Apparently she was captured by the Grey Maidens and killed while 'resisting arrest'. I can't help but feel very uncomfortable about this ... I smell the queen's scheming and I fear she will put her plans to fruition at tomorrow's little ball.\\

The four of you are well liked and well connected, so I would like to think that you could easily get yourselves invited. Moreover, you are skilled enough to interfere if things go wrong. Several of your friends will be there as well, Aisha Leroung and Xerxes Jeggare, to name two. I'm not asking you to help because of my beautiful eyes, but I would hate to see anything happen to those innocent youngsters while the queen tightens her grip on the city and its people. I would also like to think that heroes as yourself want to keep their friends from harm.\\

I tell you again ... I'm not sure what the queen is up to, but my gut tells me it's nothing good. You are my best hope of keeping the situation under control. And, even if nothing happens, you get to enjoy a nice party and rub elbows with with the future bigwigs of the city. I can imagine worse things."\\

Balian lets the woman finish, but that does not imply that he trusts her. "And why should I trust you? Who says you're not luring us into a trap or trying to keep us away from something else?"\\

"Did you have plans for tomorrow, then, that I'm keeping you away from anything?"\\

"We might ..."\\

"Well, the strange thing is ... we've been fighting on opposite sides, while I think we've been in the same camp all along. We both want what is best for Korvosa. I give you this information freely because you might offer a hand if needed. Check it out and then judge me. I, for one, hope that this meeting signals a new beginning for us."\\

"And how do we contact you?"\\

"You don't, I'll contact you. But if you desperately need to get in touch with me, just ask around in the harbor. I'll know soon enough. For now, young ranger, I bid you adieu. I'll be seeing you." At that Selena gets up and disappears in the crowd.\\

Balian quickly informs his friends. They are mad at him for letting Selena go so easily. Why didn't he ask about the assassination attempt in the opera? She claims to be a 'good guy', so how does she explain that? They are also worried that she claimed to know about Trinia and her new hiding place. She didn't actually say she knew where Trinia was, but she certainly hinted that she did. They wonder how she found out. Only Vencarlo and Blackjack are in the loop. Is she connected to either one of them? Or is she Blackjack? Everything about the caped crusader points at a 'man', his build looks and his voice sounds male, but that could all be a clever ruse.\\

Later that day the companions visit Tayce Soldado again. Brienna has been getting worse once more. Sjo attempts to cure her with an application of {\itshape restorative ointment} , but the magic fails. Next he strengthens her health again with  {\itshape lesser restoration} and gives her the necessary care. Balian aids him while Puk cooks up some dinner for the family and plays with the boys.  Afterwards the companions go to the Great Tower, the headquarters of the Sable Company. From his former colleague Max Sjo learns that the ship that sunk was on fire, although it went down so fast that it couldn't have been the fire alone. Stranger even was the fact that he saw no one on board. It was as if he was flying over a ghost ship. The last stop of the day is House Jeggare. Xerxes is happy to receive his friends and will see to it that they get invited to the Carowyn party. If they procure their outfits, he will make sure they get in. 