%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-08
\section{29 Desnus 4708}

This morning sees bad weather with rain pouring down endlessly. The young friends decide to stay in, enjoying the comforts of their new home. Balian and Puk train with the dog and the children, while Sjo and Quint hit the books in the library, working on their language and knowledge skills.\\

Late in the afternoon a carriage arrives. A man jumps out and hurries through the rain: Mercival Jeggare, the head of one of the most powerful houses in the city, is at the door. He is actually on his way to the second, smaller council in the castle, but he came up with an idea he wants to run by the companions. Mercival likes the thought of a big coronation party, but agrees with Quint that this celebration should not take place too soon. Citizens have to soften up to the queen first and the city has to resume an atmosphere of peace and quiet before a large celebration can be thrown.\\

Still, Mercival thinks that there might be a way to introduce something festive on a smaller scale sooner. His family is a patron of the arts and Mercival would love to organize a musical in the Marble Dome opera house: {\itshape The Passion of Saint Alika} . This play celebrates the life of one of Korvosa's most popular heroes, Alika Epakena. It has not been performed for over a generation, but according to the nobleman it is a magnificent play that will certainly ignite the love for Korvosa and make people forget about the recent trouble. Although the common man will not get to see the musical, as the Marble Dome cannot house the entire city, Jeggare expects  {\itshape The Passion of Saint Alika} to create a buzz all over Korvosa. To add to the positive vibe that the play might generate, Jeggare would like the new heroes of Korvosa to join the cast. He already knows that Quint likes entertaining crowds and believes there might be a role for his friends as well. The nobleman is happy to learn that the companions like his idea and is sure that their consent to appear in the play will be enough to sway his peers at the council.\\

