%!TEX root = ../crimson_throne_book_main.tex
% 2014-10-18
\section{26 Sarenith 4708}

Mouse has a good night and is doing a bit better the next morning. The companions decide to go to the temple of Sarenrae to buy a new wand of {\itshape cure light wounds} . On the way over there they come across an old man in rags who is hanging from a pole. His hands have been tied together above his head and his back is badly scarred from a whipping. The wounds suggest that the lashes were delivered last night. A woman in the streets says that his name is Lombard. He sweeps the streets and makes some extra money selling rats for food to the poor. He was punished by a mob of citizens yesterday for trying to sell diseased rats. The companions cut him loose, heal him a bit and send him on his way, warning him not to pull his stupid stunts again. The seriousness of the plague also becomes clear when a mourning family carries out a heavy body bag and lays it down in front of their house. The city's body carters will be transporting more than just dead rats today. Ezekiel Sollux, the highpriest of the temple of Sarenrae, is glad to see Sjo. He informs his former acolyte that the situation is very bad. The temple has already been converted to an improvised hospital, but the scale of the disease is making it impossible to care for all the sick. He sends out his priests to make as many house calls as possible, transporting only the worst cases to the church. There is some magic available, but that is quickly spent, so the priests have to rely on their mundane training in the arts of healing instead. Sollux asks Sjo to help out a bit and the Shoanti agrees immediately, as does Balian.\\

Meanwhile Quint and Puk pay Cressida Kroft a visit. The Field Marshal gets a full report of what transpired in the Carowyn Manor last night. Quint also reveals that they were warned of danger by the Vudran rabble-rouser Selena. She claimed that the queen is responsible for whatever evil was planned at the party. Kroft can only conclude that this Vudran lady has to be brought in as soon as possible. If she was not responsible for planting the shadow at the party herself, she must at least have more information on who did. Kroft also feels unhappy about the manipulative ways of the dark-skinned woman, whatever her schemes are, they always lead to trouble, so she must be stopped. The Field Marshal also has some news. The queen has summoned doctors from Cheliax to help fight the plague. They will arrive here today through teleportation and Kroft will have to employ her troops to assist these healers as they go into the city. She actually expects them to arrive any moment.\\

Sjo quickly swings by the temple of Shelyn to see his girlfriend, priestess Larella Semyr, but he only finds closed doors. He meets up with his friends and as they head back to the Citadel to see the queen's new doctors for themselves, he ponders on the time when he, Balian and Quint participated in the Pied Piper play while they were still kids. He explains to Puk that they performed the play with real rats on stage. An old woman was hiding underneath the boards, controlling the rodents. Although they were forbidden from doing so, the boys sneaked a peek at the lady while the play was in full swing. That is when they saw her for what she really was, a wererat! Alan, the kind leader of the Varisian theater troupe, told them afterwards that the lady could indeed transform into a rat, but that she was 'one of the good ones' who could do that. Meep Gildenglare still lives in the city; she owns a seamstress shop called {\itshape The Gilded Needle} in North Point on Burnt Bridge Boulevard. Maybe she can shed some light on the rats and their disease. 