%!TEX root = ../crimson_throne_book_main.tex
% 2014-03-29
Quint convinces his friends to head back downstairs. He wants to question Patrissa about her necklace. As the companions walk across the great hall on the ground floor, the chandelier in the middle of the room swings ominously and breaks free, smashing down on Balian, Puk and Quint and pinning them on the floor.\\

Sjo, who remained out of harm's way hears a disturbing gurgle coming from behind. Madge Blossomheart's disemboweled cadaver draws closer, dragging her entrails behind her. As the bloated horror approaches, she is followed by the corpses of the three other jurors who lost their lives tonight: Malgar Hurkes, Hal Five-Toes and the dwarf Tablark Hammergrind. Strips of Madge's innards have wormed their way into the back of the heads of these three unfortunates, causing them to jerk about wildly like marionettes. More of miss Blossomheart's guts fly around her like sticky tendrils that suddenly lurch at the companions. One of the entrails lashes out at Sjo and wraps around his shiny new armor, which wonderfully protects him from the first bites and claws of the three undead puppets, but provides little protection against the more tentative way Madge's bowels attack. Puk and Quint wriggle free from under the chandelier, but the halfling is so nauseated by Madge's appearance that he has to empty his stomach first. Balian also pushes free and jumps to his feet, drawing his greatsword from its sheath. The gutdragging lurcher's entrails lash out at everyone now while her three servants attack viciously. None of the companions escape the repeated assaults unharmed and Quint and Sjo have to resort to healing to keep everyone standing. Balian feels a bit disoriented: he wastes precious moments hitting thin air before his sword swings true. Malgar Hurkes' husk is the first to fall. Meanwhile Sjo is struggling to free himself of the bowel that is creeping over his body, trying to force itself into his mouth. Quint makes for the source of the attack by leaping across the battlefield to Madge's position, but Five-Toes claws tear at his flesh while he does so. Madge's insides strike left and right and swirl around everyone's upper body now, moving up to try and choke them.\\

The sound of battle has alerted the people in the courtroom. Sir Rekkart Cole opens the door, clearing the way for Spyder to join the fray. The dog charges forward, aiding his master in the fight. While Sjo is working hard to hold off Hal Five-Toes clawing corpse, the others now focus on Madge. Sir Cole prays to his lord Abadar and sends waves of positive energy through the air, healing the companions of their worst wounds. Still, this is not enough to save Sjo, who can't ward off Five-Toes bashings any longer and goes down. The Shoanti did his utmost best to protect his friends by drawing as many enemies on himself as possible, but even his new suit of armor couldn't withstand this tidal wave of attacks.\\

Balian is more successful now, hitting down Hammergrind and cutting through Madge with the same tremendous swing. Quint thrusts his blade in her corpse as well and even Spyder tears flesh from her bones. But, as is so often the case, it is the smallest combatant who strikes the final blow. When Puk stabs his short-swords in Madge's disfigured torso, she fall to the floor, never to move again.\\

