%!TEX root = ../crimson_throne_book_main.tex
% 2014-11-15
With no sign of brother Cedrik in this end of the complex, the companions retrace their steps to the first crossroads chamber with the small pool. Having explored the right side, they now dive into the left tunnel, which slopes down across a hard stone surface. Centuries of water trickling down have worn the steep floor smooth, making it treacherous to navigate.\\

The passage ends at a cavern with a domed ceiling, cramped with stalactites. Several of these hanging formations have grown together with the stalagmites on the ground, making up one colossal pillar. At the foot of this beautiful column a large clear pool has formed. Quint tosses a {\itshape light} stone into the water. It looks quite deep, at least seven feet. A man-shaped shadow rests against the stone pillar below the water line: the calcified remains of a long forgotten man. Two tunnels lead off into the darkness, one just around the corner to the right and another at the far end of the cavern. Reaching the other tunnels is hard without getting wet. Sjo decides to head back to a spot with even footing, where he can take off his plate armor. Meanwhile Puk, Quint and Balian investigate the right corridor. They come across three more ghasts, but they dispose of the undead easily. Balian peppers them with arrows from the back line, while Quint tries to trip them with his whip, giving Puk the opportunity to stab them with ruthless efficiency. The tunnel ends in a stone door at which the undead have obviously been scratching. The left bottom corner of the door is missing, revealing a small room beyond in which some scared rats have taken refuge. So the ghasts were after more rodents to eat! Balian pulls the door open. The room looks manmade and is strewn with the decayed remains of wooden crates. Apart from three diseased rats there is nothing here worth noticing.\\

When they return to the pool cavern, Sjo joins them in nothing but his shirt. Quints digs up a wand with {\itshape mage armor} to boost the healer's defenses a bit. One more tunnel remains, but to reach that, the companions have to cross the water. Balian and Puk manages to keep to the side of the cavern, but Sjo and Quint lose their footing and glide off into the center of the pool. They use this opportunity to examine the skeleton at the foot of the pillar and discover a gold bracelet on his right arm. Before climbing up the final tunnel, Quint weaves a {\itshape prestidigitation} through his fingers to dry everyone's clothes. Puk leads the way into a shadowy cavern. A dark shape jumps forward from an alcove in the opposite wall, splashing water over the halfling and shouting: "Stay back, you fiends! In the name of Pharasma!" It is brother Cedrik, still a bit wet and tired. He has caked blood on his forehead. When the wide-eyed priest understands that the intruders are there to save him, he is overcome with relief and spills the beans on what happened. He was tasked with working in the morgue and he remembered the chalice that was there. Since he had always been told that it possessed certain magical abilities, he wondered whether it might be helpful in fighting the plague. So he looked up some information in his books, but he came up with nothing of real interest. His next best guess would be to examine the cup itself. Upon arriving in the morgue, he went into the backroom to look at the chalice. He was surprised to hear strange sounds coming from below the floor, underneath the stone altar. Trying to pull the heavy block of stone aside, he accidentally pressed the secret button in the bas-relief, triggering the opening mechanism. The altar slid away, making the chalice on top topple and fall down the hole that was revealed underneath. Ashamed at his clumsiness Cedrik jumped into the dark to retrieve the cup, but the drop was deeper than he had estimated, so he hurt his ankle. His arrival in the underground chamber was met by hungry growls and grunts from a host of undead. Before they could reach him, Cedrik snatched up the chalice and ran off into the only available exit. He stumbled down the steep, slippery tunnel into the pool chamber, hitting his head before plunging into the water. As he heard the ghasts coming after him, he quickly climbed out of the pool and hid in the far corner of the cavern, keeping his flask of holy water at the ready. He spent a very scary night there, but fortunately, the undead never came for him.\\

There is one more exit from this final cave: a heavy stone door marked with Shoanti runes. They talk of {\itshape Shemnoata the traitor} , who led the  {\itshape intruders with the long, white knives} into his home camp, resulting in the slaughter of 58 warriors, women and children. Sjo feel uncomfortable disturbing the passage, but Quint and Puk are eager to explore it. Balian pushes at the door, but when it finally gives way, he almost falls down the sinkhole that is beyond, for indeed, the roughly circular cavern has no floor, but rather drops away into the dark. Jutting from the far wall are seven evenly-spaced spears. Mounted at the end of the shafts are jawless human skulls, all turned to face the door. They boom in old Shoanti: "Begone! Let the one who betrayed his brethren rest!" Balian notices that the sinkhole has some kind of alcove about thirty feet down. Puk climbs down a rope and discovers a small secluded compartment in the side of the sinkhole which holds an unadorned stone tomb. Balian and Quint join the halfling and the bard casts {\itshape detect magic} . He sees a slight sheen of magic emanating from beneath the heavy lid. Together the three young men push aside the cover a bit and look upon the leathery face of the body inside. With a low-pitched sigh the corpse opens its eyes and stares back at the adventurers. Balian reacts immediately and plunges his blade in the dead man's face, tearing apart his jaw. Quint and Puk are hindered by the lid that still covers most of the tomb and thus protects the corpse. Then Shemnoata's gaze takes its true effect, confusing both Balian and Puk, making them either hurt themselves or babble incoherently. Quint tries to hold back the undead with  {\itshape cure light wounds} touch attacks, while Sjo quickly makes his way down the rope to help his friends: "You fools, I hate to be the one to say I told you so, but ... I TOLD YOU SO!" Shemnoata throws off the stone lid, making it disappear in the sinkhole, and stands up. By that time Sjo arrives and hits the risen dead hard with his heavy mace. Quint's short sword finishes him off once and for all, simultaneously ending the insanity that has taken hold of Balian and Puk. Quint casts another {\itshape detect magic} , which gets a much brighter reaction now, coming from the corpse's silver belt. With Zellara's aid Sjo identifies it as a  {\itshape belt of physical might} , which enhances both one's strength and stamina. This powerful item is perfect for a swordsman like Balian. Puk remarks that the girdle is of Chelish make, so it probably was the traitor's payment. That would explain why he was buried with it, for none of his brethren would have wanted the cursed item after they'd killed him. With the underground complex completely explored the companions return to the morgue. Sjo and Quint ask Zellara's insight in the mechanism that kept the undead locked in. It seems like the proximity of the chalice acted as some kind of key to seal undead into the silvered room. Now they can finally reconstruct what happened. The diseased rats somehow made their way into the old underground complex and disturbed the undead's slumber by providing them with food for the first time in centuries. The ghasts' loud meal alerted Cedrik, who accidentally managed to open the secret passage and who jumped into the hole to retrieve the fallen chalice. There he saw the undead, not realizing that they were still locked into the silvered room because the chalice was still close-by. The panicked priest grabbed Pharasma's holy cup and ran off, thus removing the 'key' from the holy barrier and breaking its magic. The undead were finally free after three hundred years. Fortunately for the clumsy priest the ghasts were more interested in food and made off after the diseased rats, leaving the chamber where Cedrik had sought refuge in peace.\\

