%!TEX root = ../crimson_throne_book_main.tex
% 2014-05-31
Puk collects his friends and leads them to Nisha's flat. On the way over there Sjo is trashing on the tiefling woman with racist talk, much to Quint's surprise, who thinks a Shoanti in Korvosa should know better than to shut out people based on their race. The Shoanti calls Nisha an 'Asmodean whore' and claims that followers of the Dark Prince perform terrible rituals in his star-shaped temple on the Heights. He admits to having lived and trained there for three months, trying to figure out whether his gift for the divine and his command over fire were related to the Lord of Darkness. They clearly weren't, but the healer witnessed several horrible deeds when he was in training there, deeds he does not wish to recall.\\

The companions climb the stairs to Nisha's door and hear two hushed voices speaking inside. Puk attempts to pry open the lock, but fails at it, thus alarming the residents. Quint pulls out the Key-Lock killer's bell and rings it, magically unlocking the door, while Puk knocks twice, repeating Nisha's ritual before she entered. The tiefling woman stands in the middle of a small flat, trying to hide her surprise at her unexpected guests. She does not appear dazed, though, as this is probably not the first time she has had to deal with pushy customers, and firmly makes for the door to close it. Quint puts his foot inside and inquires about Trinia again. Nisha denies knowing anyone by that name, but then Sjo moves over to force his way in. The exotic dancer is quick to react and conjures up a shower of sparkly, colored lights that fascinate Quint. Puk slips into the room through the enthralled bard's legs and spots a blond girl through the window, hiding behind a water barrel on a small terrace outside. When she realizes she's been made, the girl leaps to her feet and climbs the roof of the next building, trying to make her escape across the rooftops of the Shingles. Sjo assaults Nisha, but she returns the favor by {\itshape charming} him with her bardic magic and urging him to talk rather than fight. Puk, Balian and Quint head off in pursuit of the fleeing girl, who leaps across the street to another building. Then she climbs the steep roof to the top and balances over the crest to the other end of the house. Realizing that speed and mobility are of the essence, Balian cast his first spell ever, increasing his own pace with {\itshape longstrider} , while Quint enhances the ranger's ability to move through uneven terrain with a  {\itshape feather step} from his wand. Puk has already started the hunt, nimbly dancing over the Shingle's slates and crossing the gap to the next roof. He almost catches up to Trinia, but fails his daring leap to grapple her. In his momentum he slips off the side of the building and barely manages to grab a hold. Balian is not so lucky, missing his jump across the street, plummeting down to the cobbled stones below. He quickly regains his feet, though, and clambers up the gutter to continue pursuit. Quint casts another  {\itshape feather step} , on himself this time, and chases after Trinia as well. He also threatens to miss his jump to the second building and has to throw in a  {\itshape gallant inspiration} to reach the edge, barely avoiding a deep drop. Meanwhile Trinia glides off the other side of the building and balances across a small pole to another apartment block. She squirms through a narrow window, surprising the people inside the flat with her presence. Her quick, but gentle words astound the inhabitants enough to let her pass unmolested. Balian leaps across to the window as well, but his broad shoulders and breastplate make it hard for him to fit through. As he notices Trinia slipping out another window at the other side, he decides to make for the roof and run across the edge instead. Puk has no trouble plunging through the window, but finds it more difficult to handle the people in the flat. Lagging behind, Quint realizes that he will never catch up and attempts to take Trinia down with a {\itshape sleep} spell, but the painter is unaffected by his magic. She climbs unto another roof, scales the steep climb to the crest and worms her way around the chimney. Balian risks life and limb blindly charging after her and finally catches up. He grabs her by the wrist before she can glide down a washing line and tightly pins her to the gray slates. "I'm sorry we scared you," he whispers, "but we're not the bad guys, we just want to talk." 