%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-08
The doors behind them are now shut tight and won't budge. Another door to the right stands slightly ajar and suddenly reveals the groans of several people. As Balian pushes the door open, he discovers one of the old courtrooms. Eight people are spread over the jurors' box. They look disoriented as they wake up from unconsciousness. Fear grips them while they realize where they are and who they are with.\\

Sjo quickly takes in the rest of the room. Two sturdy tables are on a platform on the far side of the room, in front are benches for spectators, an evidence table which still holds a large axe rests against the left wall and the jurors' seats are located to the right. A shadowed mural decorates the ceiling above. It depicts the goddess of justice Iomedae in her shining plate mail of gilded sunlight, locked in mortal combat with Norgorber, Calistria and Asmodeus, the gods of greed, trickery and tyranny.\\

Quint hails the strangers, who he recognizes as the jury from his vision. These are the people who condemned Jarbin Mord to death a decade ago. Zenobia Zenderholm is familiar with one of these men as well, a paladin of Abadar whose name issir Rekkart Cole Patrissa Vrakes A burly man with broad shoulders and a leather apron comes over to introduce himself, walking with a slight limp. He says his name isHal Five-Toes Killian Paltreth Quint is not pleased when he notices that one of the eight people in the room isEbin Bazel Madge Blossomheart Two men remain; the first is a short-framed but muscular macho in leather armor, who fails to introduce himself. He has a glare of distrust and annoyance in his green eyes. Balian has heard of him before, a local thug and small-time gang leader,Malgar Hurkes Tablark Hammergrind While everyone is getting to know each other, a large piece of plaster breaks free from the mural in the ceiling with a loud crack. The heavy chunk of debris falls onto the evidence table and sends the double axe which lies on it spinning through the room. The weapon sinks solidly into Balian's shoulder. Sir Rekkart Cole rushes to his side and when he sees that the ranger survived the impact, he pulls the axe out of his shoulder. Quint uses the {\itshape wand of cure light wounds} to heal his friend while Cole hangs on to the axe as his sword seems to be missing from his scabbard. Everyone now moves to the front door to see if they can get out. The dwarf Tablark joins Quint to examine whether a mechanism is holding the doors shut, but he cannot find anything. Quint also fails to find traces of magic around the entrance. Meanwhile Sjo wanders deeper into the hall and discovers an impressively large grandfather clock against the center of the left wall. The carvings show guilty souls suffering Asmodeus' torments. Zenobia Zenderholm does not remember the clock being so big and containing such elaborate infernal detail. The wooden figures seem almost alive.\\

Sir Rekkart Cole and his blond friend Patrissa Vrakes venture into the second courtroom, the one opposite the first. While they are in there Patrissa suddenly shrieks in fear. The companions rush to her aid and find her and the paladin beset by an immense swarm of undead carrion birds. The ghoulish birds of prey peck at their flesh to satisfy their morbid hunger. Balian swings his greatsword in great arcs through the murder of undead crows. Feathers, bones and rotten flesh fall on the ground at his feet. Quint tries to skewers as many fluttering pests as possible on his rapier while Puk's tiny swords and Sir Cole's axe make more victims. It doesn't take long for the heroes to disperse the swarm and send the surviving birds into hiding in the nooks and crannies that line the walls. This courtroom looks much worse than the first; its furniture is in shambles, the ceiling looks is full of cracks and holes and the windows are crisscrossed with heavy boards. Where nails breach the plaster around the windows, rust stains seep like bloody wounds from the walls. Quint uses the wand to patch up his allies who sustained some minor wounds from the storm of tiny beaks and claws. Everyone is still alive, but the bard can't help but wonder about how strange it all is: no mechanisms, no magic. This shouldn't be possible. They could be in here for a long night!\\

