%!TEX root = ../crimson_throne_book_main.tex
% 2014-04-26
The celebration also turns out to be a perfect place to learn the latest rumors. Marguerite Jeggare, lord Mercival's oldest daughter and {\itshape the most beautiful girl in Korvosa} , is still single. Not for lack of suitors, though, because Akmelek Ornelos and Cedrik Carowyn are both very interested, but the girl keeps them at arm's length. She is never mean or haughty about it, but politely (though firmly) gets rid of her admirers. She prefers to remain in the company of other girls, like her younger sister Alika and her niece Maud. By the end of the evening she is finally spotted at the side of a male guest, Aaron Endrin, commander Endrin's son and heir. Aaron's father, lord Marcus, spends most of the evening talking to Valdur Bromathan. Both families have been close allies for generations and the two lords are good friends. Endrin apparently worries about seneschal Neolandus Kalepopolis, who's been missing for weeks. The commander does not like that fact that he has lost his eyes and ears in the castle, since the seneschal is always a decorated officer from the ranks of his military organization and is tasked with keeping an eye on the monarchy. It troubles him even more that the city lacks its seneschal in these difficult times.\\

While Sjo appreciates Marguerite's beauty, he is more intrigued by the red-headed Larella Semyr. This priestess of Shelyn oversees a small but dedicated temple to the goddess of beauty, love and art. She makes for amiable company and attentively listens to Sjo's interpretation of his own 'alternative' divine powers, which function differently from normal priests and might actually be related to the powers of Shoanti shamans.\\

Puk spends most of the evening wandering through the crowd unnoticed. He is the only halfling present and on those rare occasions when someone does speak to him, they usually want him to bring them another drink. Still, being almost invisible gives him to perfect opportunity to overhear gossip. Some people are questioning lord Glorio Arkona's support of the queen. The nobleman's love for Korvosa itself is even disputed, since he sent his own children to the other side of the world to be raised in distant Vudra. He has also chosen to skip this celebration, leaving his sister Melyia to observe his family's honors tonight. Still, when the companions talk to her, she simply explains that her brother wasn't feeling well. When the conversation with Melyia shifts to lady Zenderholm, Quint quickly refutes the rumors that the hanging judge was attacked in the streets by Sczarni gangsters in an act of vengeance. The bard and Sjo don their storytelling cloaks and give a juicy report of the events that lady Zenderholm was mixed up in: the horrific night in the old courthouse where they finally put the Croaker to rest. The two young men turn their tale into quite a spectacle and gather an eager crowd of listeners.\\

Another noble girl who stands out by not being there, is Aurelia Bromathan. The girl only recently returned to Korvosa, after a year of absence. No one knows where she went, but rumor has it she got pregnant and left the city to give birth to a child in secret, quite a shame for her father, lord Valdur, who is a pious priest of Sarenrae.\\

