%!TEX root = ../crimson_throne_book_main.tex
% 2014-11-01
Keppira d'Bear also has a request: yesterday brother Cedrik did not return to his cell to sleep. No one knows where he is, but as the temple is swamped, there is no time to look for him. D'Bear asks the companions to help locate the missing man. Sister Fryda shows the companions to Cedrik's bedroom, but nothing seems to be out of the ordinary. Cedrik's prayer book is still by his bed. He would never leave it behind, Fryda claims. She also adds that Cedrik is a as devout as they get, so he would never just run away or something. Since he came here at the age of twelve, he has never even set foot outside of the Gray district. He is also a very diligent man, never late and very precise in everything he does, which is why he is the church's accountant. He mostly works in the office, keeping the books, but yesterday he was tasked to help out in the mortuary.\\

By the way, this sidetrek adventure is based on a cute little Quint and Puk also have a quick look around Cedrik's office. His desk is piled with dozens of documents that still need processing, listing names and relevant data about all those who have died. Under the pile is a book that has been opened to a page detailing Pharasma's holy chalice. When sister Fryda sees the drawing, she claims that the cup is in the very mortuary where brother Cedrik was sent to yesterday. Our friends decide to pick up Sjo first before continuing their investigation. The Shoanti has been in bed for the last two hours, vainly trying to catch some extra sleep, though frustration made it feel like it lasted much longer. It takes some convincing, but fearing more endless hours in bed, Sjo gives in and joins the quest for Cedrik.\\

Fryda leads the companions to a smaller building behind the cathedral, the mortuary. She takes them through a small chapel with beautiful stained glass windows to the preparation room in the back, where the chalice should be. There are two stone tables, each the resting place of a dead body, covered in a white sheet. A small stone altar stands in the corner, it has nice stone carvings in the sides, depicting Pharasma's Boneyard. The altar holds nothing, but a distinct circular discoloration in the stone suggests that something round has been on top for many years. The chalice, however, is missing, Fryda notices. Balian examines the small altar more closely and finds recent scratches on the floor which indicate that the stone altar can swivel forward. A skull in the boneyard bas-relief on the side of the stone block can click, propelling the altar away from the back wall and revealing a hole in the ground underneath. Fryda screams in surprise, she didn't know that the altar could do that. Quint conjures up some light to shine down the opening: there is a 15 foot drop into a small natural cavern below which wafts forth a foul odor of earth and mold.\\

Puk retrieves a rope from his pack and ties it to the stone table. Sjo is the first to go down, trusting his darkvision to warn him of any danger. He ends up in a small cave with two exits: a rough archway leads into a larger chamber in front of him, while a tunnel slips off to the right. Still, it is the chamber that draws his attention. The light falling in from above reflects in thousands of tiny specks of light. The entire frame of the door and all the walls, floor and ceiling of the chamber beyond are covered in a silver dust coating. The step of the archway is also inscribed with silver runes. When his friends have joined him Sjo uses a {\itshape read magic} to decipher the mystical writing: a powerful spell meant to block the passage of undead. Quint detects that the magic was broken very recently. The companions step into the rectangular chamber, which was obviously manmade, unlike the cave and tunnel behind them. The air in the room is stale. The silvery floor is covered in dry brown dust and holds the heavily gnawed bones of two rats. Despite the fact that the bones have been picked clean completely and most of them have been chewed to pieces, Balian can tell that they are recent, very recent even. No more than a few days ago these rodents must have been very much alive.\\

Leaving the chamber behind them, Puk and Balian lead the way down the tunnel to a small cave that seems to be little more than a deviation point. A slender stalagmite rises floor to ceiling in the far end of the room with a steady stream of water droplets running down its side. A pool has collected at the bottom, trickling away to the left in a shallow stream of water down another tunnel. A second tunnel winds away to the right. As the floor is quite uneven and wet, Quint pulls out his wand of {\itshape feather step} to grant everyone more stability in difficult terrain. Sjo scratches a cross in the wall, marking the way out. Ignoring the tunnel with the trickling water the companions head the other way through the winding tunnel that leads into a vast cavern. The ceiling does not extend much higher than the top of the tunnel, but the ground drop down in a number of stone tiers to a treacherous floor. A narrow chasm cuts across the middle of the cave from left to right, roughly cutting the room in half. While Sjo makes his way down, Balian shouts out a word of warning. Something is moving in the shadows along the wall. Suddenly a foul creature bursts from the dark; it is clearly humanoid in shape, although its nails and teeth look unnaturally long. Its pallid grey flesh stretches tightly over its starved frame. Quint jumps to his partner's aid and pierces the creature's dried out innards with his icy short sword. The undead hits the bard in return with its sharp claws. Two more ghasts break from the darkness up ahead, hungry for fresh meat. One of them sinks its pointed teeth in Balian's shoulder, but the other misses the nimble halfling by a long shot. The undead fight and bite fiercely, drawing some blood from the heroes, but they go down quite easily. In a few seconds the brawl is over. Puk discovers the remnants of some kind of uniform on the ghasts' upper body, on which Quint can barely make out the former shield of Cheliax. It dates back to the days of the settlers, three centuries ago, that Chelish soldiers walked Korvosan soil. Whoever these undead were in real life, they must have been here a long time.\\

This side of the complex ends in another large, irregular cavern, where two more ghasts attack the companions. The walking corpses are easily defeated. One more undead has stumbled into a pit in the floor, unable to get out. Balian simply finishes it off with his bow. There are more rat cadavers on the floor, but this time the remains have been only half eaten. A number of small holes dot the north wall: tiny tunnels through which diseased rats made their way into the complex. Balian figures that the disease forced the rodents to retreat deep into the ground and that the rats unwittingly provided the famished ghasts with a food source for the first time in centuries.\\

