%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-08
The judge and her protectors make their way across the city. Rain is still pouring down and they are completely soaked when they reach their destination. A leaning monument to the landslide, the old courthouse is a crumbling marvel of cracked plaster and chipped marble. What used to be a shining white beacon of justice turned into a crushed dream. Rainwater mixed with mulch oozes from ruptures in the walls like puss seeping from a wound. The bell tower tilts perilously as if it could collapse at any moment. Two massive pillars frame the double doors in the front. The wooden panles in the archway sags like the drooping eyes of a madman.\\

The salt wind blows up from over the sea, making the whole building groan, its tortured lamentation fading into a rasping hiss as the wind ebbs. Still, the croaking murmur never seems to fade away completely. The sun sets over the water, the last slivers of twilight painting the courthouse blood red as darkness creeps in.\\

Examining the mud in front of the entrance Balian makes out several tracks leading into the building. The sagging doors open with surprising ease. Puk's lantern and Quint's light spell reveal part of a great hall supported by enormous marble pillars. Years of dust cover the floor. A moan builds up from the darkness ahead as a sudden gust of wind slams shut the doors behind the heroes' back. The hoarse sigh swells to become a deafening scream, forcing the companions to cover their ears. Darkness overtakes them ...\\

---\\

Quint suddenly finds himself in a courtroom, abuzz with nervous anticipation. Dozens of eyes from the crowd behind him and from the jurors' box across the aisle focus on him. Their expressions range from contempt to pity. A magistrate slams down his gavel, snarling for silence. The murmur quiets down as the stocky magistrate draws up to his full height, smoothing his silver moustache with his left hand. He sets down his gavel and focuses on Quint with his shining green eyes: "Jarbin Mord, for the brutal and savage slaying of your wife and six-year-old boy, it is the verdict of this jury - with which I concur wholeheartedly - that you shall hang by your neck until dead. May the gods take mercy on your blackened soul.\\

---\\

Puk hears the clack of wood on wood, followed by a whip crack of rope drawn taut. The crunch of vertebrae echoes off the walls. He sees a man's booted feet twitch freakishly as his last breath rasps from his ruined throat in a choking death rattle. Puk suddenly realizes that he is staring at his own twitching legs. The crowd cheers with delight and laughs as he rasps his last.\\

---\\

Balian finds himself in a small attic. A voluptuous woman with dark hair sits in a rocking chair, swaying as she hums and knits a sweater for a small child. She looks up, alarm on her face, as Balian draws closer. Looking down he notices a heavy axe in his hand. When his shadow falls over the woman, the look in her eyes changes to one of pure horror.\\

---\\

Sjo is on his knees in a dark, dreary corridor. His right hand is working feverishly, sawing away at something with a bloody shortsword as he gibbers: "Show me the way, Sashrala, use your magic to get me out of here. I love you so much, please, just show me the way!" With a final wet snap blood pools appear around his knees as he hefts the gory head of a beautiful woman. "Thank you, Sashrala, I love you ..." Sjo cries as he kisses the blood-covered lips and thrusts her head forward like a lantern.\\

---\\

The visions fade as suddenly as they appeared. Blinking their eyes, the companions take a few moments to gather their bearings. Sharing their weird daydreams, they realize they have just relived some key moments of the horror that ended this courthouse's glory.\\

