%!TEX root = ../crimson_throne_book_main.tex
% 2014-05-24
Director Touran Palastus looks angry indeed. Having just witnessed a completely different ending to his opera, he directs his anger at the companions, demanding an explanation. Quint and Sjo start weaving a story about how they felt they had to improvise, wanting to add the symbolism of young Korvosans who dared challenge death itself. They also shower Palastus with compliments, since only his excellent leadership and his ability to inspire to greatness allowed them to improve the story as they did. Palastus is flabbergasted, but when lord Mercival Jeggare joins the fray, complimenting Palastus on this brilliant new finale, the director is so overwhelmed and charmed that he drops his protest.\\

Next Sjo and Quint pull aside Aisha Leroung. She still looks shocked by what just transpired, having been stabbed for the first time in her life. The companions explain what happened: a new oracle of Pharasma warned them during the break that she would be in danger during the final act, so they watched over her and prevented the assassin from killing her. Since the killer's goal was to sow chaos, they took that away from him by integrating their actions into the show. Of course, this requires everyone to act as if what happened on stage, was nothing more than a bit of improvisation. In other words, Aisha cannot tell anyone she was attacked for real, because doing that would still play into the hand of the attacker. The girl understands and agrees.\\

Meanwhile Balian has pulled Eric Brolan's unconscious body into a small alley behind the Marbledome. He now hails his friends over to question the man. He has already stripped the assassin of his gear, which includes a short sword of frost and a magical cloak and ring. A bit of Sjo's healing suffices to wake Eric up. Quint is very angry with him and presses him for answers. After some initial hesitation Eric Brolan confesses: he was {\itshape forced} into killing Aisha. His sister and her children have been kidnapped and if he did not comply to the assassination, he would never see them again. Eric does not know why he had to kill Aisha, nor does he know the name of the person who ordered the hit, although he can describe her: a beautiful Vudran woman with long black hair. Quint is abhorred: so the rabble-rouser Selena is still at work! He had hoped to have heard the last of her after the riots ended, but apparently she continued to plague the city with her feeble efforts to rekindle the fires of chaos. Well, fortunately he and his friends were around to thwart her foul plans, again! The companions contemplate what to do. They finally decide to take Brolan to the old fishery and spread the rumor that he escaped custody. Maybe his {\itshape employers} will feel threatened by the fact that Eric is still running free. If they try to eliminate this 'threat', they will find the companions on their way! Balian leads Brolan away, while Puk, Sjo and Quint head to the afterparty. They want to include Field Marshal Cressida Kroft in their plans and they hope to find her at the reception. Kroft is indeed present, but the companions do not get the opportunity to talk to her privately, since everyone loved their brilliant performance and wants to congratulate them. Even the queen offers them praise. Quint also notices that fencing master Vencarlo Orisini is staring dreamily at her majesty's personal guard, Sabina Merrin. The bard remembers having heard that the commander of the queen's Gray Maidens was once a pupil at Orisini's sword fighting academy. Maybe they have some history. It is not until an hour later, when Kroft leaves, that our friends manage to intercept the field marshal. She readily agrees to play along with their plans. Although it is already the middle of the night, Quint, Sjo and Puk want to check out Eric Brolan's apartment sooner rather than later, so they gear up and head over to Old-Korvosa, where the man lives. His flat looks dark, but when Puk uses his skill to open the door, Quint spots people inside. A lantern lights up and a middle-aged woman with two children at her side shouts: "Surprise!". It's Eric's sister, who denies having been abducted. She says that a Vudran woman approached her six days ago and took her to lovely little house in North Point, claiming this was to be Eric's payment for his 'leading role' in the opera. However, the house did need some TLC, so the woman suggested that Eric's sister used those six days to tidy up the place, so she could surprise her brother when he returned. The sister's story seems to be genuine, so the companions decide not to trouble her more than they already have, and simply explain that Eric is with a friend of theirs and that he probably won't be home tonight. Then they leave for their beds. It is a puzzling thought, this Selena works in mysterious ways: a sword in one hand and a velvet glove on the other. She does not shy away from having people killed, while she is surprisingly considerate of others. How weird ...\\

