%!TEX root = ../crimson_throne_book_main.tex
% 2014-01-11
That evening the companions get into their disguises again and head to {\itshape The Bountiful Mermaid} . Tonight they are lucky, as one of the patrons is Birold. The good-looking dockworker is in the middle of a game of darts. The target is a roughly-hewn likeliness of the queen, on which the more deadly areas have been painted red and yellow, granting more points when they are hit with a dart. Birold wins the game of  {\itshape death to the whore} and treats his comrades to a drink afterwards, toasting to a quick downfall of the queen. Quint joins them and introduces himself as a dockworker from Old Korvosa. He challenges the winner of the previous game to a new round of darts and comes out the victor, leaving him to pay for the next round of drinks. He notices that Birold does not finish his mugs so as not to get intoxicated. During their conversation Birold spills that something is going down tonight and that he will have more to offer supporters of the just cause tomorrow. If Quint is interested, he should probably come back then. At half past eleven Birold leaves. Puk stealthily follows him, with the others hanging back even more . The dockworker makes for a warehouse, where he is joined by four more laborers. By midnight a dashy fellow arrives in the company of two bodyguards. While the man slips through the doors, the guards take up position outside and watch the area. Curious to know what is going on inside, the companions decide to act. Quint manages to take out the two guards with a successful sleep spell, giving Puk and Balian the opportunity to sneak into the depot. There are plenty of crates where they can hide and listen in on the conspirators, who have gathered in the back of the building.\\

The dashing man is addressing the dockworkers: "Friends, the whore still hasn't understood. She continues wallowing in the luxury that our sweat provided. We have to raise our voices even louder. Tomorrow we'll organize another march against the usurper. Gather as many sympathizers as you can and bring them to the Gold Market and Eodred's Walk. There we will issue our complaints once more. The market and its stores will be the regrettable target of our actions, as grievances are only heard when it hurts! The power of merchants in the city will serve as our coin in this confrontation.\\

Just like in the demonstration against Citadel Volshyenek you will be joined by others, hailing from all over the city. Once more I have to stress the importance of keeping our destination a secret until the last moment. We don't want the Guard to be in the loop.\\

We also feel that civilians have to be well informed on what is going on. That is why our men infiltrated the university of Korvosa last night and started the presses to print a special number of the Korvosa Herald, the Korvosa Rascal. I've brought a few hundred copies for you to hand out among your friends.\\

I also fear that we'll be opposed again, by both the Guard and the Hellknights. It is too bad that these bucket-heads can't see what is really going on, they are so blind in their obedience. But when they face us with sharp steel in their grasp, we cannot afford to stand empty-handed. I've brought clubs that you can distribute among your strongest supporters. Here!"\\

At that the man pulls the sails off a cart, revealing numerous weapons inside. "Don't get me wrong, friends. I abhor violence, but if that is the only language they understand, we have to be prepared. Remember, comrades, if your mighty voice erupts, all of Korvosa stops! Death to the Chelish whore! For a free Korvosa!"\\

The dockworkers join in as they gather around to get their copies of the Korvosa Rascal and the clubs. By this time Quint also sneaks into the building, but when Sjo follows him, one of the men inside hears something and notices that the front doors are open. "Feldon, why aren't the doors closed?" he asks the dashing gentleman. This is the companions' clue to spring to action.\\

Quint overtakes one of the dockworkers with another successful sleep spell. Balian and Sjo attack from the right and knock down one of the conspirators. Birold is the first to counter; he draws his mace and smashes it down hard on Spyder's back. Balian reacts furiously and cuts heavily through the man's chest, but Birold is tough and remains afoot for now. Quint has less success on the left side, as he gets hit twice by a club. The dockworkers might not wear any kind of armor, but their muscled arms can dish out some serious damage. The bard tries to hold the left flank, aided by Puk's stinging short swords, but both of them get wounded seriously while taking down an opponent. Feldon, the dashing gentleman, mumbles the words of a spell and blinds Sjo, Balian, Spyder and Birold with a splash of golden particles. He joins the fray and thrusts his flashing rapier twice between Balian's ribs, badly wounding the ranger. Still, the two blinded friends quickly regain their sight and take out one more enemy.\\

Quint manages to disarm another adversary and Puk can finally take him out. When Feldon sees that most of his supporters have been defeated, he decides to run for it. He catches Balian and Sjo in a spot of slippery {\itshape grease} , dropping them both to the floor, as he makes for the door. While the ranger and healer drag themselves out of the greasy area and overpower the final dockworker, Quint uses his last spell to stop Feldon. For the third time tonight he mutters his incantation and for the third time in a row the magic hits home. Feldon stumbles to the ground and lays down his head, slipping away in the warm embrace of slumber. 