%!TEX root = ../crimson_throne_book_main.tex
% 2014-04-05
Since two more rooms in the building remain unexplored, the companions decide to search those first. Maybe they will find more clues there ... The tower above the courtroom's entrance is wet from the rain and salt wind blowing through the arrow slits. An old rust-covered bell hangs from rotting wood beams. Puk sneaks a peek inside the clock, but Sjo pulls him out, fearing the heavy bell might crash down. Still, nothing happens. Looking out through the narrow windows, the companions see the nightly storm continuing to rage over the city. Darkness limits the view, but on a beautiful day the tower probably provides an excellent outlook on Korvosa.\\

Next is Mord's attic apartment. The small room is a mess. A double bed sits in one corner, toys of carriages, horses and knights are strewn over the floor and a rocking chair has fallen over. Balian's eyes turn white as he receives another vision. At the same time Puk, Sjo and Quint see how the shadows behind the rocking chair stir and a dark shape frees itself from the wall. The shade is obviously female, her seductive hour-glass figure is wrapped in swirling veils. The shape of her head is less attractive, though, having been cut off at a slanted angle. Quint urges the shadow not to attack: "Miss Malene, how can we serve you? We are here to help. Can you tell us who killed you?" With a sigh the shadow takes on a less aggressive posture. The graceful fingers on her dark hand point to something on the floor in front of the rocking chair, a knitting needle. Then she disappears.\\

"Why do you all look like you've seen a ghost?" Balian suddenly asks when he notices the surprise on everyone else's face. "I am the one who just had a vision, not you guys ... I wasn't babbling or anything, was I?" It is obvious that the ranger missed the episode with Malene's ghost completely. The others smile and urge Balian to tell them what he just witnessed. The ranger found himself in the killer's body again, standing over the beautiful woman in the rocking chair. As he raised his axe to strike, she jumped up defiantly, knocking over her seat in the process, and lashed out with her knitting needle. With his left hand he touched his cheek; his fingers came away bloody. Then he struck!\\

So, that is it, then. The man with the scar on his left cheek is the killer! The same man Puk saw in his vision. But this man was blond and his description doesn't match anyone who is locked up in the courthouse tonight. So how can they make the murderer pay if he is not here?\\

