%!TEX root = ../crimson_throne_book_main.tex
% 2014-10-18
Panic slips through the crowd in the great hall of the Carowyn Manor. The dark creature that has just crawled from the chimney looms before Sjo and Quint, who realize that almost all of the invitees to this party have been gathered in this one room. The ease with which this lightless threat took down its first victim could very well be the preface to a bloodbath. Fortunately the creature's own tactics prove helpful in getting the noble guests to safety. Weaving its inky magic the shadow blasts out an aura of fear that strikes terror in the hearts of half the people in the room. Overcome by mortal dread Balian makes for the front door and pushes it open, freeing the way for the other guests to flee the scene, even those who have not been affected by the creature's fearful magic. Sjo is also among the unfortunates who are panicked initially, but he recovers even before he makes it out into the streets. Quint, Puk, Xerxes Jeggare and Christina Leroung are the only ones who stand their ground. Quint engages the shadow, taking on a defensive stance, while Christina shouts out that this enemy is extremely hard to hit: you need magic weapons made of cold iron or {\itshape force} magic to hurt it, and even then its incorporeal state and many protection will be an obstacle. She immediately proves her point by sending two magic missiles at the creature that do not penetrate its magic resistance. Puk's first swing also gets lost in thin air. The shadow rewards three of his four remaining adversaries for their bravery by engulfing them in an explosion of green and yellow flames. Not recognizing the magic for what it really is, an illusionary shadow version of a {\itshape fireball} , they are hit to the spell's full effect. Puk relies on his roguish adeptness at avoiding similar magical explosions and evades to lick of the burning tongues altogether, but Quint and Christina are not so lucky and get seriously burnt. Although he is badly damaged, the bard is still on his feet. The fierce daughter of House Leroung does not have enough vitality to survive the blast though and goes down in a smoking heap. Xerxes, who was in the other corner of the room, did not get caught in the burst of yellow and green fire. His mundane rapier will be of no good against this foe, so he rushes to Christina's side to make sure she is still alive. Another ally appears at the top of the stairs, Perishial Kalissreavil, the elven ambassador. He also recognizes this creature for what it is and throws his dagger to the ground: "Take it, it is made of cold iron", he shouts as he fires two magic missiles from his fingers as well. This time the  {\itshape force} arrows penetrate the creature's defenses, delivering some real damage at last. While Quint retreats to administer some much needed healing to his own wounds, Sjo turns around and charges the shadow, using his new dwarven mace. The cold iron from which it was forged proves its worth as the Shoanti tears away some of the threatening shady curls. Puk picks up the elf's dagger, but his feeble swing hardly hurts the opponent. With Balian running wild in the street and Puk being able to only inflict the tiniest amounts of damage, Sjo is the only one who stands some chance at beating back this shadow. His full plate armor provides no protection whatsoever against the incorporeal claws of his enemy, making him an easy target. The creature tears at the Shoanti as if he were naked. Puk finds that his nimbleness provides more protection, but is hit nonetheless and suffers the sting of the cold tendrils. Perishial throws a healing potion down Christina's throat, saving her from death's embrace and pushes the girl into Xerxes' arms, who carries her outside. Quint rejoins the fight and bolsters Puk's fighting prowess with {\itshape heroism} , while the halfling finally manages to slip into a flanking position. His hopes of delivering some serious damage now with his sneak attack prove futile as he finds no weak spot to hit. So he continues picking away at the shade's life force one smoky sliver at a time. Sjo fares better, even though half of each smash is also lost to the air and his blows are answers by smoky claws that totally ignore his mighty plate. At this rate he will never outlast his opponent, so Quint helps out by healing his friend, more or less keeping pace with the damage that is being delivered. Perishial casts his last two {\itshape magic missiles} and shouts he is out, stepping into the next room. A moment later Christina Leroung reappears in the front door. She still looks very weak - she was probably just nursed back to consciousness with some potions - but her sorcerer powers allow her to throw more magic  {\itshape force} missiles at the shadow. Despite the small amounts of damage that everyone is inflicting, the combined efforts of the defenders are slowly wearing down the dark outsider. Somewhere out in the street, already a block away from the manor, Balian snaps out of his panic and stops fleeing. He glares up at the moon, deciding he doesn't like it so much - don't ask - With Quint's healing now balancing out the shadow's strokes, Sjo, Puk and Christina gain the upper hand. The Leroung sorceress blasts two more {\itshape magic missiles} into the swirl of black coils and Sjo calls out to Sarenrae, begging the sun goddess to aid him in defeating the darkness. He hits the shadow twice in rapid succession, ripping the final shred of shade apart. What happens afterwards is a bit of a blur to the Shoanti. His head is still light from the rush of the fight and the drinks that Puk and Quint pour their friends to recover from the excitement. He notices that Cedrik Carowyn returns with a patrol of Korvosan Guards in his wake. Fortunately Xerxes offers to talk to the captain, freeing the companions from the task of making a report. Puk also discovers some kind of rune on the inside of the chimney breast. Whatever this thing was, it was summoned by powerful magic through this magic mark. Since the party is obviously over, the companions head back home again for a good night of sleep.\\

