%!TEX root = ../crimson_throne_book_main.tex
% 2014-01-26
\section{25 Desnus 4708}

In the afternoon Puk, Sjo and Quint return to Eel's End. They are allowed into Devargo Barvasi's cabin, which has been converted into a throne room of sorts. The walls are covered in webs which hold dozens of spiders, some as big as a man's fist. Two sturdy oaken tables with chairs flank the door and seat half a dozen burly blokes. On the other side of the room a wooden stage supports a large throne; in it rests a tall man in black leather armor with steel spider-shaped ornaments. His legs are casually slung over the right arm of his seat while he's petting a hairy spider on his chest. He smiles lazily at his guests and invites them to take a seat. Sjo also notices the desperate look in the eyes of a tiny purple dragon in an iron birdcage hanging from the ceiling next to the throne.\\

Quint immediately cuts to the chase and says they are not here to join the enforcers, but rather to talk to the spider king. Barvasi reacts by remarking how tall Sjo is and invites the Shoanti to entertain him with a small game of {\itshape knivesies} , a pirate tug-of-war from Riddleport. Knivesies has two contestants standing opposite each other on a wooden table. Their right hands are bound together with a wet leather strap and they have an empty belt pouch strapped to their belts. Fifteen gold sails are put on the table between them, as is one dagger. The person who ends up with most coins in his purse wins. Sjo is bound to one of the enforcer candidates and figures he has the best chance in an honest fight without weapons. Being the first to act, he tries to kick the dagger off the table, but it has been planted in the wood firmer than he expected and the big Shoanti only manages to partly dislodge it, thus providing his opponent with the opportunity to pull the small weapon out of the table. Still Sjo feels confident that his armor will protect him and decides to make a show of it, sending jolt after jolt of flaming fire through his hand until his opponent drops to his knees. The poor man only managed to nick him once with the slightest of cuts. Sjo recovers the knife, cuts through the leather strap and stabilizes his adversary before reaching for the gold and placing the sails into his pouch, one by one. When his purse is full he tosses it at Devargo Barvasi, who smiles contentedly. The King of Spiders weighs the pouch in his hand and then gives it back to Sjo: winner's keeper's! Next he sends out the candidates, giving his three other guests a private audience first.\\

Quint impresses his host by recognizing his Riddleport accent and by pointing out that the big spiders are much more harmless than the small brownish specimen in the webs behind him. The poison of that 'recluse spider', or 'violin spider' as it is also called, can lead to skin necrosis. Fortunately these spiders are rarely aggressive, unless provoked.\\

Barvasi appreciates Quint's little display of knowledge and asks him why he is here. The bard tells him that he tried to contact him before, in vain that time, to talk about Rolth, a drug brewer. As he senses that the spider king dislikes the man Quint continues by saying that he has now left the city and is out of the picture for the moment. Today however he has a different agenda: he would like to know more about the troublesome ambassador Amprei. Devargo replies that he's met the Chelaxian a few times in person and - as he feels the companions bear the foppish nobleman no love - he lets on that he has some power over the man that he'd be willing to sell to his guests, for the right price, of course.\\

Sjo offers him 500 gold and Devargo claps his hands in delight: "I love the way the world works, you invest 15 gold in a game of knives and get 500 in return, marvelous!" He asks his visitors to wait while he goes below. When he returns he's holding two letters which he hands to Quint. Both sheets bear a whiff of perfume and contain an overtly sexual message from someone called Verania Tvastiox addressed to her secret love Amprei. Quint knows her as the wife of Agmanar Thrune, a mighty conjuror and cousin to Her Infernal Majestrix, Queen Abrogail II of the Thrice-Damned House of Thrune in Cheliax. If the ambassador has been sleeping around with this powerful man's wife, evidence to the fact would surely destroy him. Barvasi admits to having stolen the letters from the ambassador and selling them back to him at the rate of one every few weeks. By paying 500 gold sails the companions have just secured the last two copies in Barvasi's possession. The spider king bids his guests good luck with their new acquisition and says goodbye.\\

Realizing that these compromising letters give them a real hold over Amprei, the companions hurry to citadel Volshyenek, where they report their findings to the Field Marshal. Cressida Kroft is very pleased, and while the scandalous nature of the letters sends a blush of red to her cheeks, she states that they should work perfectly as leverage against the cursed Chelaxian. She will contact the castle and make arrangements for the companions to be received there tomorrow at ten o'clock. She is also very grateful for the fact that the heroes' actions with the rioters have had such great results, as order is slowly returning to the city. Yesterday and today have been the first two relatively quiet days since the king died. She repays her agents the 500 gold sails they spent procuring the letters and hands them another 500 gold as a reward.\\

