%!TEX root = ../crimson_throne_book_main.tex
% 2014-06-21
The companions quickly make their way to the Gray District, where they meet with Archbishop Keppira d'Bear in the Cathedral of Pharasma. She informs them that no Shoanti body has been brought in and refers them to a man named Elkaris, who usually transports the deceased from East Shore, Thief Camp and Trail's End.\\

Our friends easily trace the body carter to a pub, where some other patrons are making him pay for their drinks. Sjo buys these drunkards another round, while he leads Elkaris to a corner table for a private conversation. Apparently Elkaris is quite the simple spirit and he quickly confesses to sometimes carting off bodies to a certain corner of the Potter's Ward, "dead 'uns' no one cares about, you know. I leave them at this old statue, a fighter guy with a sword, but he has fallen over and he has no head, over by the old forgotten deadhouses at the end of Potter's Ward. When I do this, there are some gold pieces in my wheelbarrow the next morning." Elkaris is ashamed to find out that the Shoanti he brought over there, was not a loner. He does not know who takes the bodies: he was approached by a thin man years ago who offered to take the corpses of the forgotten off his hands for a nice fee . He doesn't really remember the man, as it was dark, and he has never seen him again, but even after all these years the deal still stands, because he keeps getting paid.\\

Balian has no problem locating the toppled statue by following Elkaris wheelbarrow trail. There he discovers tracks of small humanoids, although the footprints are much finer than Puk's sturdy halfling feet. They also bear only four toes instead of five. They could be derro, especially since they lead to the dark entrance of a partially collapsed mausoleum.\\

Quint summons some {\itshape light} and leads his friends down a set of stairs into a large room supported by four stone pillars. The ceiling arches in a dome nearly twenty feet overhead and the walls are lined with skeletons caked into the mud. Two large pits to the left and the right are filled with a large heap of bones, some of which animate and attack the intruders. One of the walking ribcages towers over six others and his beaked skull identifies the creature as a dead owlbear. Although it takes the heroes some time to dispatch of the bone assailants, since only Sjo's mace is effective at rattling these carcasses' cages, it is an easy fight. A passageway leads off deeper into the darkness, splitting to the left and right. Following the freshest tracks on the left-hand side, Balian suddenly signals his friends to stop when he hears some voices jabbering ahead. As he pricks up his ears, he notices that the conversation has abruptly ended. Maybe the creatures heard his noisy party approaching. Sjo peeks around the corner and as set upon by five red flying insectoids with double bat-like wings. Two of them attach themselves to the Shoanti's chest and pierce his flesh with their needle-like beaks, draining some of his blood and making him feel somewhat weakened. Sjo channels a burst of flames from his hands and burns two stirges to ashes, while badly incinerating a third one. Balian jumps to his friend's aid and expertly cleaves the attached bloodsuckers in two. The last partially burned pest follows soon after.\\

The room ahead holds three large tables. There is a large open cage on the first, probably the stirges' nest, and a dead body on the second. From the look of the corpse's face and clothes he was a vagrant. Two of his legs and one arm have been cut off, post mortem, Sjo concludes. There are several butcher's tools on tables, both fit for Puk's size and his taller friends, and two exits on the other side of the room. Exploring the one to the right takes Quint to a foul pit of stinking cadavers. Two sniveling derro order their waste disposing otyugh ally to charge the intruders; keeping to the back of the mud island in the middle of the room. Quint retaliates with a {\itshape sleep} on the deformed underdark dwarves, but his magic cannot break through their innate magical resistance. Balian engages the three-legged monster, but the cramped quarters make it hard to swing his large blade efficiently. The otuygh sinks his filthy teeth in the ranger's flesh and the derro fire some poisoned bolts at the heroes. One hits Spyder, who is ordered back to make room for Quint and Sjo. Puk pulls out his staffsling and fires on the monster from the second row, but is quickly frustrated with the puny damage he inflicts and decides to tumble through the corpsefeaster's legs instead, to a flanking position on the far end of the mud island. Now he can truly hurt the creature! Quint backs up Balian's assault with healing, while Sjo vainly burns through all his charges to set his weapon aflame, hitting nothing but air. The otyugh's bite and tentacles draw blood several times before the foul beast is finally slain by Sjo's first true strike of the fight. The two derro are disposed off next without too much effort. As Quint heals his friends, Puk makes a gruesome discovery: the broken legs and hips of Gaekhen are in the pit. Sjo and Balian dig through the rotten body parts some more and are rewarded for their efforts by a few trinkets left over from the otyugh's meals: an amber necklace worth 350 GP and a potion in a metal flask. Using Zellara's deck Sjo identifies it as an  {\itshape elixir of vision} , which makes the imbiber more perceptive. As he hates paying taxes on every small find, Balian quickly gulps down the potion and throws the flask aside. He also casts  {\itshape longstrider} on himself, complementing the earlier  {\itshape heroism} boost he received from his bard ally. The companions head back to the room with the tables and take the other exit, which leads to a long corridor with hundreds of skulls in the walls. Even with all his buffs active Balian fails to notice the magical trap that has been woven in the bony heads, which spew some acid on him and his friends. Fortunately the biting liquid causes only minor damage. A closed door seems to be the only way out. Balian quietly places his ear against the wood and listens. He perceives at least three derro voices on the other side. This time they have not spotted Sjo's clattery approach, so our friends have the benefit of surprise.\\

