%!TEX root = ../crimson_throne_book_main.tex
% 2014-08-09
So how do you smuggle a wanted murderer out of the city? The best way is probably right under the noses of the guards. The first plan the companions come up with is to leave Korvosa as merchants. Rather than joining a real caravan as bodyguards and subsequently abandoning these people once they are outside the city, our friends deem it wise to impersonate traveling traders themselves. They could buy a couple of mules and get some goods they can sell in Harse, like salt, painted cloth or tools. Of course they would have to be disguised, which might cause a problem when trying to hide a Shoanti who is six and a half feet tall, a halfling, a dog and a young girl ... well, the plan might need some adjusting.\\

A couple of hours after sunset Puk knocks on the door of the Orisini Academy. The fencing master sees his four nightly guests inside and offers them the comfort of his living room, where they take a seat in the large sofas by the fireplace. When he calls in Trinia, the girl eyes the companions with suspicion, but Quint quickly puts her troubled mind at ease by reassuring her that he and his friends continue to believe in her innocence, a statement that Vencarlo is eager to confirm. When the bard asks Trinia why she confessed to the murder, she claims to have no memories of the fact. She remembers being taken to a cell in the Longacre building. Only hours after her imprisonment the queen herself visited her in her prison cell. That is the last thing Trinia remembers ... everything after that is a big blur, until she was thrown into another cell, somehow knowing that she had been convicted to die. The next 24 hours awaiting the execution had been the most desperate in her life.\\

Vencarlo Orisini asks the companions to smuggle Trinia out of Korvosa and escort her to a good friend who lives outside of the village of Harse, on a horse ranch. His name is Jasan Adriel and he and Vencarlo used to be in an adventuring company together more than twenty years ago, called the Blackbirds. The fencing master also has a coded letter for his friend, which he hands to Quint. He encourages the four heroes to act fast: as a known critic of the government Orisini is on the list of the {\itshape usual suspects} and Trinia remains in danger as long as she stays under his roof. Some guards already did a cursory search of his academy today and he suspects they will be back soon for a more thorough investigation. He also gives the companions 500 gold sails when he learns they will try to impersonate merchants, but still need to buy pack animals and merchandise. Before they leave Vencarlo warns the companions to be very careful: the Guard is looking everywhere for Trinia, the Sable Company controls the skies and the river and the sword master has even picked up a rumor that the accursed Hell Knights have been called back to aid in the manhunt. The companions hide Trinia in the old fishery for the night and finally decide on a different plan to get her out of the city: they will leave as themselves, with Trinia taking the place of Quint, whom she resembles most closely physically. The bard will disguise himself as a regular John Doe and leave Korvosa on his own, meeting up with his friends outside of the city walls. To facilitate Trinia's impersonation of him, Quint hits the town heavily that night, making sure to show up in every bar that frequently hosts soldiers of the Guard, buying them drinks and getting {\itshape really drunk} with them, all the while complaining about Puk. Apparently his small friend wants to leave civilization tomorrow to head to the backwater halfling hole of Heavenguard for a someone's birthday. How dull is that? And of course the little bugger promised his cousin that the great Korvosan performer Quintillian would accompany him, leaving Quint no choice but to join him on this uncomfortable trek into the wilds ... The bard also picks up the general sense that most Korvosans believe Trinia to be guilty. It turns out that he and his friends certainly succeeded in restoring faith in the monarchy over the last few weeks, as people tend to trust Queen Ileosa now and share her hate for the late king's killer! 