%!TEX root = ../crimson_throne_book_main.tex
% 2014-04-19
\section{1 Sarenith 4708}

That morning the names of the cast are listed in the Marbledome. As predicted Aisha Leroung lands the lead role of Alika Epakena and Dario Darnas gets to play Kallan, the Chelaxian soldier who loves her. Quint is Garamon, the Varisian trader who is Kallan's rival for Alika's affection, an important role, though not the most likable character in the play. Sjo portrays Garak the Brute, the leader of the Shoanti. Balian name is among the Chelaxian marines and Puk gets his seat in the orchestra.\\

By 3 o'clock the companions returns to the opera house and meet the rest of the people who got cast. Everyone beams with excitement as they enter the building and take a seat.\\

The first session consists of a run-through of the play. Mercival Jeggare takes the stage: "Welcome everybody. First of all I would like to congratulate you all on making the cut! Competition was fierce, so I'm overjoyed to see we get to work with the finest Korvosa has to offer! Today, we're going to have a look at the story we'll be enacting. Leiny Ranstro, our lovely assistant, will hand each of you your personal script. Make sure to study your roles meticulously, so rehearsals will run smoothly. After all, we only have one week to pull off this colossal feat. Come 10 Sarenith, you'll be on this very stage impressing the cream of Korvosan society.\\

So, what is {\itshape The Passion of Saint Alika} about? This opera is a heavily romanticized version of one of our city's earliest moments of glory. It tells the tale of the first Varisian woman to ever acquire Chelaxian citizenship - albeit posthumously - for the bravery she displayed and the crucial part she played in our history. Her name was Alika Epakena, better known as Saint Alika. We did not choose this opera by chance, as we hope that the story of one of Korvosa's most popular heroes will contribute to healing the wounds the recent riots and unrest inflicted on our lovely city. We need something to rekindle the 'Korvosa feeling' in our good citizens. Now, I know that the common man will not get the opportunity to see this wonderful play, but everybody who is anybody will be present, as will her Majesty, Queen Ileosa! So, without further ado, I give you the maestro of Korvosan entertainment, your director, Touran Palastus.!" The monocled man walks on the platform, swinging his cane vigorously as he accepts the applause of the complete cast. A hunchbacked man with stringy white hair follows in his wake, obviously less at ease in front of a crowd. His name is Dargo 'the Hump', who is in charge of the set and the special effects in the Marbledome. As he describes the various background sets and the illusions he will summon, Touran Palastus walks his cast through the story. He emphasizes that this is an opera and most of the interactions are sung. He also mentions who will play which part and asks the actors to stand up so everyone can see them.\\

The first act will show a wooden palisade and some crude houses. It starts with commander Waydon Endrin, another famous hero of the city, giving a speech to the settlers of the new fort. Varric Bedar will portray the commander, being a retired soldier himself, he should be a perfect fit. The commander discusses the hard times the young Korvosans have had to endure and the many Shoanti raids they have suffered. Still, he focuses on their successes. His wife, Keyra Palin, captain of the frigate {\itshape Merciless} and played by Arianna Evenland, managed to fight off yet another barbarian assault. More and more children are being born here as well, he proudly claims, including his own son Lucien and his daughter Mina. They are the best guarantee for Fort Korvosa's future. The first child to be conceived and born in the camp has already reached adulthood, Endrin beams, pointing to a beautiful lady in the crowd, Alika Epakena. After his speech Alika remains on stage with her parents. Her father introduces her to Garamon, a successful Varisian trader, who is to be her husband. The shy girl is taken aback by this news. Alika's role will be in the capable hands of Aisha Leroung, Diederik Lodann is her father and Quintillian will play Garamon. In the second act Alika seeks refuge in the wilds, calling to the gods for aid. She does not love this Garamon and feels reluctant to marry him. She promises the gods to spend her life in their service if they help her. The next moment a handsome Chelaxian soldiers walks on stage, who will be portrayed by the crowd's favorite, Dario Darnas. He is out hunting and hopes to find a suitable prey, a magnificent animal that can only be found in the wilds, not in the civilized Cheliax he used to call home. Then he notices Alika. She is indeed of unparalleled beauty, although she is hardly the prey he was expecting. He approaches the girl and introduces himself as Kallan, a marine who arrived here recently aboard the Merciless. As the two meet, sparks fly and it immediately becomes obvious that it is love at first sight. Alika confides in Kallan that her father promised her to an old merchant, but the fiery young soldier ensures her that he will change her father's mind. When the two move closer for their first kiss, Alika suddenly receives her first vision: the image of an attacking Shoanti appears in the air above her. When she breaks from her trance, she yells a warning. Kallan is quick on his feet and reacts by drawing steel, just in time to block the attack of a Shoanti assassin, a role for Marco Ebhart. He kills the barbarian in a whirling fight, after which he leads Alika back to the camp.\\

In act three Kallan bears witness to having seen Alika's gift, but he is taken for a fool, especially by Garamon, who leads the mockery. The trader claims Alika's only gift will be cleaning his house and bearing his children. Life nor the gods have any bigger role for her in store. He challenges Alika to prove her new-found power: the settlers on Endrin Island are in desperate need of a water source, let the girl show them where to find one! While Garamon and his friends are laughing heartily, Alika receives another divine premonition: the image of spraying water appears above her as she falls to the ground. When the vision fades, she claims that there is a source of water below her. Kallan jumps forward and hammers an iron pole into the ground. When nothing happens, Garamon resumes his taunts, but he is interrupted by a flash of lightning that announces a heavy storm. Another bolt of electricity crackles down and hits the iron pole after which water bubbles up out of the ground.\\

When the storm is over, terrible news reaches the encampment; the Merciless has sunk. The mood changes to hopeless. The discouraged settlers abandon the stage, leaving only Alika and Waydon Edrin there. The commander wonders how the fort will survive this setback, with Alika trying to comfort him, while she gets yet another vision that the frigate survived the tempest. Waydon Edrin is torn between disbelief and hope until a freeing cry of joy resounds from the docks. The Merciless has returned home. A few moments later the ecstatic commander is reunited with his wife. He acknowledges publicly that Alika has the {\itshape gift of Pharasma} . Act four takes place in the encampment of the Shoanti, who are dancing like madmen around a bonfire. They spit out their hatred for Fort Korvosa and plan a vicious attack on the settlement, swearing to set it on fire. They prepare canoes filled with pitch. Their leader, Garak the Brute, whips up passions and boasts that he will kill all intruders with his greatclub. Touran Palastus is proud to have found a real Shoanti for the part, Sjo, although the 'actor' is quick to correct his director by stating that he is just {\itshape half} Shoanti. The fifth and final act kicks off with a secret meeting between Alika and Kallan. The two youths circle each other cautiously until they can no longer hide their true feelings and glide in each others' arms for their first real kiss. That is when Garamon storms on stage, pushes a surprised Kallan to the ground and challenges him to a duel. Kallan draws his blade, but Alika steps between the two rivals and tries to calm them. Then she strikes over backward while the vision of an inferno flames up above her. The other settlers arrive and Alika warns them that the Shoanti will burn down the fort. Waydon Endrin no longer doubts her words and reacts immediately by sending a small barge to Cheliax asking for reinforcements.\\

The Shoanti are faster, though. The messenger has only just left, when someone cries out: "Fire!" This will apparently be Balian's job, just shouting it though, no singing required. The palisade lights up and the fire fills the stage. Raging barbarians leap through the flames and attack the settlers. While the soldiers try to make a desperate stand, numerous defenders go down under Garak the Brute's club, including Waydon Endrin and his wife Keyra Palin. Meanwhile Alika risks her life rescuing inhabitants from their burning houses and urging others to seek refuge.\\

While the common settlers run for cover, Alika starts searching for Kallan who she lost sight of in the thick of the battle. When she finds him, Garamon appears as well and maliciously attempts to backstab the soldier. While Alika tries to separate the fighting men again, Garak the Brute suddenly appears behind her. Kallan and Garamon are equally surprised when the object of their affection drops at their feet under the barbarian's club. The towering barbarian now focuses his attention on the two of them. Kallan engages the brute while Garamon flees the scene. The soldier from Cheliax dodges under the Shoanti's greatclub and jams his blade in Garak's ribs, killing the chieftain.\\

Next Kallan kneels down in desperation at Alika's body. The stage is now filled with cadavers. While threatening music plays, Death himself enters, given form by Eric Brolan. He waves his scythe over the fallen, collecting their souls, drawing ever closer to Kallan and Alika. The soldier recoils in horror as Death looms over his beautiful lover. At that moment a flash of light falls from the sky and a radiant angel descends from heaven, wielding a flaming sword that scares off Death. The angel, or rather Ali\"ena Fochs, picks up the body of Alika and while she ascends with the young girl in her arms, a heavenly choir chants. Auralia Lazanne, the stout Chelish diva who is now the Marbledome's vocal coach, will be singing this beautiful aria from the orchestra pit.\\

Leiny Ranstro, Touran Palastus' personal assistant, gives everyone his personal copy of the script and informs them when they have to come by tomorrow for a fitting with Delindra the seamstress. The companions have their appointment set at half past four.\\

