%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-02
Ugh, they have to pay a tax on their villa, and on all their magical items? Helps explain why more nobles don't have hoards of magical items, from inheriting them, if from nothing else.\\

How much, in taxes, do you think the party will be paying each week/month? They might have to open up, or buy, some legitimate business, beyond that of murder hobos, to keep their taxes in order. Will you be using the Downtime system for this? Or something else?\\

Your pictures of the scenery are, again, fantastic! That 'eavesdropping on a secret meeting' one gave me pause at all the loose material, crates, barrels and such, that you've collected.\\

Have you assigned each NPC a specific model? Do you set them aside so they aren't lost or broken for future use?\\

 I really liked the whole Council aspect and that the nobles weren't just immediately willing to dish out money. Nobles are nobles after all. The exception being Glorio. Are you trying to play him off as a kind of 'philanthropic noble' so the party doesn't get an 'obviously evil' vibe?\\

I wonder how you will play off Doctor Davaulus? Will he still be her personal physician, or perhaps someone else? I tried to play him off as the 'family physician' from Cheliax, but one who is strongly opposed to Krovosa being independent from Cheliax and would like to see it fall. He was there before the plague started, and was the instigator from inside.\\

Also, I notice you had Toff cancel the Breaching Festival. I remember you're planning on skipping Scarwall completely, but about what time frame do you expect this part of the campaign to start? Because if you give it sufficient time, it's possible the students of the Acadamae will be able to 'double up' on protections from the previous year, if you wish to make it a little harder.\\

