%!TEX root = ../crimson_throne_book_main.tex
% 2014-04-05
As they make their way down again, the companions hear the sound of clashing steel from the great hall. Two unknown men are locked in deadly combat. An old man with silver hair and a drooping moustache staggers backward as he defends himself from a tall, lean opponent with a top hat, a full black beard and a flashing rapier to match his intense blue eyes. Their blades clang and cast silvery sparks as the tall man launches another barrage of nasty thrusts. The heavier man's silver moustache drips beads of sweat while his green eyes show terror and strain. He can barely turn aside the attacks and ends up with a gash in his arm.\\

"What is this, in the name of the gods, stop this!" Sjo bellows. The four companions appear at the top of the stairs, causing the duelers to stay their hand and step back from the fight.\\

"There, judge Trabe ... HE is the one who lured me here! Threatening to sully my reputation with his lies concerning the long-closed case of Jarbin Mord. Here's the letter to prove it", the tall man exclaims. From his pocket he produces a piece of paper: "See this. Allow me to read it to you: 'I know which part you played in the case of Jarbin Mord. Bring 1,000 gold sails to the old courthouse if you want to assure yourself of my continued silence. Be there at 4 in the morning or suffer the consequences.' Signed by Silman Trabe."\\

"Well, I'll be damned. That is the letter YOU sent to ME, mister Wade, word for word", the old man retorts. He digs up a similar scrap of paper from his waistcoat. Quint takes both letters and compares them, they are in the same handwriting, although one is supposedly signed by Silman Trabe and the other by Alastir Wade.\\

"Hmm," Quint muses, "looks like you were both lured here by the same person, just not each other." The bard studies the two newcomers' faces and notices a slight scar peeping through Wade's facial hair. "So you must be Alastir Wade. We've been expecting you. Why don't you tell us how you killed Mord's wife and child?"\\

"I don't know who you are, young man, but I will not stand for this insult", Wade throws back as he launches an attack at Quint and draws blood. Balian and Puk storm forward for a fight, but Quint beats them to the punch by putting his assailant to sleep with his magic. In the meantime Zenderholm and the former jurors have joined the commotion.\\

"We've got the killer", Quint tells the high judge, pointing at Alastir Wade, while Balian and Puk tie him up. "We'll need proof, obviously", Zenobia Zenderholm replies. "We've seen it in our visions", Sjo remarks. "It's hard to prove anything based on a daydream. But we have to act quickly. Wade has to hang before dawn, lest we all perish."\\

"Let's start with that man over there," Puk interjects, "mister Silman Trabe. According to the late judge Felgor you knowingly sent an innocent man to the gallows. Care to explain?"\\

The old judge shuffles back nervously. "Wade here told me that Mord was innocent. But we needed to solve the matter quickly. An unsolved murder case in the courthouse would certainly blemish our good reputation. So he convinced me to let him see Mord and talk him out of getting legal aid. I don't know how he did it, but he made sure Mord didn't want a lawyer and he forced me to go along with that. I also had to put some names on the jury list."\\

"How did he {\itshape force} you exactly?" Quint inquires. "That doesn't matter, suffice to say that he had the power to do so."\\

"Judge Trabe is right", Patrissa confesses. "Wade was the one pulling the strings, mine as well."\\

Sir Rekkart Cole looks disappointed: "Patrissa, what are you saying?"\\

"I'm sorry, Rekkart. But I have to come clean, our lives depend on it. Wade bought me the necklace in return for condemning Mord to the gallows. And he got me to manipulate you and Tablark Hammergrind to vote the same way. I thought Mord was guilty anyway, so I didn't see the harm. The opals were just a bonus for doing a job I would have done anyway."\\

"There you have it," Quint concludes, "looks like we have all the evidence we need. Time to finish it."\\

"Finish what? Have you suddenly become the judge here?" The sleep spell on Alastir Wade has ended. "I demand you set me free, I am innocent! And I can't be convicted without a proper trial."\\

"That is why we have the high judge present here tonight", Killian Paltreth reacts. Everyone looks at the older gentleman in the worn suit. His dull eyes suddenly gleam with renewed energy and his shoulders don't sag anymore. "The way I approached her, might have been a bit rough, I'd like to apologize for that, miss Zenderholm, but I was running out of time, and I needed Korvosa's most trustworthy judge to be here."\\

"You ... are Sveth?" Quint asks.\\

"That is my real name, yes", Paltreth replies, as he takes off his frayed top hat and pulls the broad handlebar moustache from his face. "Mord was my friend. When they took him to be executed, I stayed behind in his cell. That is when I discovered his message on the wall, asking me to avenge his unjust death after ten years. But I didn't know who was guilty, so I got everyone here who might have been involved. If I had known Wade was the murderer, I would have gotten him here earlier, but I already had my hands full getting the seven jurors here, so I had to improvise."\\

"And where is the real Paltreth?" Sjo asks.\\

"He's been dead for years", Sveth answers. "He hated himself for sending Mord to meet his maker. During the trial he caved under the peer pressure, just like I told you. Seven jurors were convinced Mord did it, and Paltreth was all that was in the way of a unanimous decision, so he gave the others what they wanted. After the trail he started doubting Mord's guilt more and more, so he turned to drinking ... a lot. It took three years for the alcohol to kill him."\\

"Well, the pieces of the puzzle are definitely falling into place", Quint muses. "Still, there is one thing that eludes me ... why ... why did you kill her? She was such a lovely woman. Why, Wade?"\\

"She was more than lovely, a rare beauty. I never understood what she saw in that dim-witted monster", Wade retorts. "He didn't deserve her ... but, that doesn't mean I killed her! This ... what you are doing ... it is a charade. I demand a real trial!"\\

"It is true that we need a fair trial", Sjo nods. "But if we do, and you are found guilty, I'd happily hang you myself. Judge Zenderholm, how should we proceed?"\\

