%!TEX root = ../crimson_throne_book_main.tex
% 2014-08-09
\section{17-19 Sarenith 4708}

The next morning Quint helps Trinia into his own clothes and fixes her face and hair to make her look like him. As she will be playing a hung over bard, she will be able to keep to the background and hang her face low. Meanwhile Sjo writes a letter to Larella Semyr, his beautiful priestess girlfriend, and another missive to Field Marshal Kroft. He asks the boys to deliver the first note to the shrine of Shelyn, but keeps the second letter on his person, taking it with him as he heads for the Bloodsworn Gate with Puk, Balian, Spyder and Trinia. There is a small line of people waiting to get out of the city, and the guards do a scrutinizing job of checking everyone who leaves. When the companions are up, the soldiers visibly relax: these are the trusted heroes of the city! They chuckle at the hung over bard and easily accept Sjo's explanation that they are traveling to Heavenguard for a birthday, you know how halflings like their parties ... The Shoanti also hands the guards the letter for Kroft, asking them to deliver it to their commander since he didn't have the opportunity to inform the Field Marshal of his and his friends' absence himself. Feeling honored the guards quickly let the heroes pass. Quint has no trouble slipping through the checkpoint a couple of minutes later - as no one is looking for a single man - and meets up with his friends at the next crossroads.\\

The journey north takes three days, during which Trinia proves to be a spirited little girl. Despite the traumatizing experience she has been through, she is excited and thankful to have escaped with her life. She recounts with gusto how she fled with Blackjack over the rooftops of Korvosa, down small allies and even through the sewers. The caped crusader knew his way around the city well and led her unerringly to Vencarlo's fencing school in Old-Korvosa. While she waited outside in the shadows for a few minutes, Blackjack went inside to convince his friend to take in the girl. She witnessed their brief but heated discussion, before the grey-haired swordmaster invited her in and offered her his protection. He turned out to be the perfect gentleman and host, worrying over her like a father-figure.\\

Trinia suspects that Neolandus Kalepopolis, the missing seneschal of Castle Korvosa, is behind Blackjack's mask. His position allows him to dethrone an illegitimate or unjust monarch in times of need, but that power also makes him a target of such an individual. Trinia is convinced that Queen Ileosa is a false and dangerous snake who forced the seneschal into hiding. Since his life would be in danger if he appeared publicly, Kalepopolis had to resort to his Blackjack alter ego to fight the treacherous usurper. Being an ex-officer of the Sable Company, Neolandus Kalepopolis certainly has the skill to be the caped crusader, heck, he's probably even hiding in the Great Tower, the headquarters of the black garbed guards. That would definitely explain why commander Marcus Endrin has been so suspicious of the new queen as well ...\\

The young painter also unfolds that painting was not her first profession of choice. Being the daughter of a Varisian couple of traveling acrobats, she originally trained in her parents' skills at tumbling and jumping, which explains why she was so agile fleeing from the companions over the shingle rooftops. When her parents froze to death during the terrible hunger winter six years ago, she decided to quit her life on the road and focus on another talent: painting. She settled down in the poorer parts of the city and made enough to survive, although she admits that she is not very good with money. She never had a lot, but whenever she had some, she spent it quickly, not only on herself, but also on her neighbors, since there were always people around who needed it more than she did.\\

The companions can also witness with their own eyes that the Korvosan Guard no longer patrols the Korvosa's holdings outside the city walls, although they do not run into any of the highwaymen that are supposedly plaguing the countryside.\\

By the end of the third day, the travelers reach the Falcon River and take the ferry across the water. They ignore the town of Harse completely and head straight for Blackbird Ranch, some thirty minutes north of the village, off the beaten track. The horse ranch sits comfortably in the cleft of two low hills topped with copses of fir trees. A barrel-chested man, flanked by two youths, greets the companions as they approach. His bow is strung, but hangs idly over his shoulder. Still, it looks like it is within easy reach. The man's initial apprehension instantly evaporates when he learns that his friend Vencarlo sent these travelers to his doorstep and Quint hands him the fencing master's coded letter as proof. He warm-heartedly welcomes his guests into his home. Blackbird Ranch is a large place, but also houses a large family: Jasan Adriel himself, his wife Lisanna, his sons Ted, Gerald and Bruno and his daughters Mari\"en and Romy. The rancher takes the visitors to the basement, where he keeps a couple of spare beds and brews his own beer, which he offers freely.\\

Jasan informs about the situation in Korvosa and when he learns of all the recent trials and tribulations, he explains that such troubles are exactly why he chose to relocate down here and not in the city. At least here he can talk frankly without worrying about his family, because, just like Vencarlo Orisini, Jasan can be quite critical about people in charge and likes to speak his mind.\\

After a couple of pints the retired adventurer also talks about the past he shared with Orisini. The two of them were members of an adventuring party known as the Blackbirds. They broke up more than two decades ago over an unfortunate argument involving the rights to treasure looted from a dwarven tomb - while Jasan and Vencarlo wanted to return the weapons they recovered from the haunted grave to the dwarven offspring in Janderhoff, the others in the group wanted to keep the loot and sell it in Korvosa. The conflict came to blows and in the end Jasan and Vencarlo opted to retire from the adventuring business altogether. The remaining Blackbirds vanished without a trace in the obscure dungeons below Kaer Maga not one season later, so both the ranger and the sword master counted themselves lucky at having quit while they were alive. The two former party members have always stayed in touch, writing each other as often as possible, using the secret code they developed in their adventuring days, more out of fun than any real need to hide their messages, although it allowed them to be critical of Korvosa's government without the fear of anyone else reading about it.\\

Since the companions changed their plans on how to get out of the city, they never needed Vencarlo's money to set up a merchant guise, so now they offer the pouch to Trinia. The girl sees no need for the gold while she is hiding in a basement and suggests to give the money to Jasan instead. Although the ranger is pleased with his guests' generosity, he responds that he requires no payment for helping his best friend and only agrees to take the money if the companions accept riding animals in exchange. Since Jasan Adriel breeds some of the finest horses around, this sounds like a great deal, but it will have to be concluded tomorrow, as the hour has grown very late.\\

