%!TEX root = ../crimson_throne_book_main.tex
% 2014-05-24
\section{11 Sarenith 4708}

It is almost noon when the companions get up. They want to make sure the assassination plot does not go public, so they send out the boys with invitations to all those who know the truth: Field Marshal Kroft, Archbishop Keppira d'Bear, Lord Mercival Jeggare and Aisha Leroung. The message implores those people to come over at four o'clock for tea to 'discuss the opera's final scene'.\\

At one o'clock the doorbell already rings: it is Leiny Ranstro, Touran Palastus' personal assistant. She is here with the companions' payment for playing in the opera, 380 gold sails in total. Since the friends did not know they were being paid, this is a pleasant surprise.\\

A little before four o'clock Aisha arrives. She has slept well and explains that she does not feel traumatized, in spite of the dangers she faced last night. She owes that to the companions' timely and competent intervention, which made her feel safe. Lord Mercival Jeggare and archbishop Keppira d'Bear of Pharasma are next to arrive. When Cressida Kroft still hasn't shown up at 16.15 h., the companions decide not to wait any longer. They explain everything that happened during the opera and with Eric and his sister. Now they wonder what to do: do they seek justice against Eric, which requires going public, or do they hush up the assassination attempt? Aisha says she cannot speak from a legal point of view, but personally, she is willing to forgive Eric. He was obviously forced and seeing him imprisoned - or worse - will not punish the real culprits. The best way to oppose their evil schemes is to act as if nothing happened.\\

By five o'clock a soldier from the Korvosan Guard arrives with a message from Cressida Kroft. Urgent business demanded her attention, keeping her from 'tea party'. She summons the companions to the citadel right away! Pressing the guard for answers, Quint convinces him to spill the beans: the king's killer has been found!\\

When the companions get to Kroft's office she gets right down to business: "My friends, I presume you've picked up rumors that the king was murdered. I regret to have to tell you that this is more than mere gossip. Eodred was cravenly poisoned. The Gray Maidens managed to find out the name of the killer. A young painter who was commissioned to make Eodred's portrait is responsible for his death. One of my own men who was on palace duty aided her. The man has already been questioned and he confessed to the crime. He even repeated his statement in my presence.\\

The murderer is one Trinia Sabor who lives on the Slope in Midland, Moonstreet 42 b. The Guard went to her house to arrest her just a few hours ago, but the bird had already flown. My soldiers got little cooperation from the neighbors, who claim the girl is too sweet to be the king's assassin. They don't believe she's guilty.\\

I don't know how word of her involvement got spread, but right now a large mob is looking for the girl. The streets of Midland are overrun by angry citizens who are demanding justice. If they find the young painter, I'm afraid she won't survive. We can't let this happen, one act of chaos might be enough to rekindle the fires of unrest in the streets. We've worked so hard to get things under control. Let's make sure to keep it this way.\\

It is of the utmost importance that we find this Trinia Sabor alive. We have to find out how and why she poisoned the king, and if she was working for someone. My soldiers have their hands full controlling the angry mob and they are too conspicuous to conduct a quiet investigation. Moreover, those who know Trinia are reluctant to give them any information. That's why I need your help to track her down."\\

The companions agree to help and also fill the field marshal in on what they discussed with lord Jeggare, Keppira d'Bear and Aisha Leroung. They suggest hushing up the Brolan case, so as not to fuel those 'fires of unrest' she also mentioned. Kroft agrees to whatever solution the companions find morally acceptable. Then she urges them on their way.\\

The Slope Ward in Midland is densely populated. Houses crowd each other and are built upward rising up to five stories high. The leaning tenements house flats with tiny windows, narrow walkways and rickety stairs. The streets look more like open gutters and are presently overrun with agitated hotheads. The Guard is doing its best to calm the mob, but only elicits booing and hateful comments. Since some of the protesters demand to know where this cowardly killer lives, the companions conclude that the crowd does not know Trinia's address yet. They quickly make their way to the building. Two guards by the door and two more in the hallway let them pass and send them to the second floor.\\

As the companions climb the stairs, they meet Trinia's down stair neighbor. A sullen, portly lady with three children at her skirt gives them an angry stare. She refuses to believe Trinia is the king's murderer. The girl is a gem who wouldn't hurt a fly ... and generous too. Whenever she can afford it, she gives the kids some copper pieces and recently she used the money she got for painting the king's portrait to buy food for everyone in the building. Trinia has a heart of gold, she would never kill anyone. The neighbor has no idea where Trinia fled to, and even if she knew, she would never tell.\\

Trinia's apartment is a mess. Several pallets with paint, empty canvases, hundreds of sketches, a dozen half finished painting and three easels fill the room. A small bed has been squeezed into the corner and a tiny table sits in front of the window. Half a loaf of fresh bread is testament to the fact that the girl was here earlier today.\\

Searching the room reveals no clues and no traces of poison. Quint does find a letter, dated Pharast the 17th, asking Trinia to paint his majesty's portrait. The letter is signed by Neolandus Kalepopolis, who was still acting seneschal of the Castle three months ago. It mentions a payment of 1 000 gold sails, but none of this gold seems to be in the apartment.\\

When the companions look out the window, Balian notices an old lady across the street peeking from behind her window. When she sees she's been spotted, she quickly retreats behind her curtain, only to sneak another glance a few breaths later. Sjo and Quint decide to question her and cross the street. She seems suspicious of the two young men, but is nonetheless happy to share her distress with the neighborhood's decline. She claims that the young girl who lives across the street is no good, keeping the company of that {\itshape devil woman} from the nasty strip joint around the corner. That girl sports horns and a tail; she's an affront to the human race and all those who mingle with her can't be trusted. The {\itshape Voluptuous Vixen} is just around the corner. A grim dwarf guards the front door and refuses to let anyone in until the joint opens in an hour and a half. Since the bullheadedness of dwarven door guards is legendary (a running gag at our table since this is not the first dwarf to refuse PCs entry in our roleplaying history) 