%!TEX root = ../crimson_throne_book_main.tex
% 2014-05-03
\section{8 Sarenith 4708}

The main characters in the opera work on their vocal performance in the morning with their coaches. After lunch everyone gathers for the promotion tour in the Kendall arena. The benches can hold over one thousand people and it looks like every seat is taken. Although Sjo's limited vision does not permit him to see the audience, he hears the cries of Korwick, Mouse and Heldrin in the crowd. It doesn't take long for Puk to point the three kids out.\\

The preview is a great success. The cast brings several songs from the opera, including Sjo's wild dance scene. Although people love his performance, some spectators find it hard to hide their dislike for Shoanti. Hatred for Korvosa's enemy of old still runs deep.\\

At the end of the show Aisha Leroung randomly hands out twenty free  tickets for the show in the Marbledome, making some people extra happy. Mercival Jeggare is happy as well, having achieved his goal of bringing the show to the common man. Although the arena lacks the fine acoustic qualities of the opera house, its shape still carries sound well, so he is very satisfied with today's performance and the audience's reactions.\\

Back at the villa the companions experience how happy the common man really is to have seen this preview, when the kids shower them with praise and can't stop talking about the show. Heldrin also picked up another rumor today: some people are saying that the queen killed her husband. Quint tells the boys not to listen to gossip.\\

