%!TEX root = ../crimson_throne_book_main.tex
% 2014-06-14
\section{13 Sarenith 4708}

It is already past noon when the companions get up. Sjo wants to sells a couple of valuable items no one is using: a magical short sword and rapier and a masterwork chain shirt. The dwarven smith Ironguts happily takes the merchandise off their hands and the money is immediately put towards paying off another part of the tax debt. While the companions pass by Citadel Volshyenek, adventure comes looking for them again. A soldier invites them in, saying that Field Marshal Kroft needs to talk to them a.s.a.p.\\

As they make their way to Kroft's room, the companions come across some of the warriors from the Shoanti delegation that is staying in the Gray District. The men do not look happy and barely acknowledge Sjo and his friends as they walk by. The Field Marshal explains what is going on: Gaekhen, the grandson of the Shoanti shaman Thousand Bones was attacked in the streets by some racist fools. He did not survive the encounter. The murderers were immediately arrested and will be put to trial, but Gaekhen's body disappeared in the commotion.\\

Kroft asks Thousand Bones to join them. The old shaman speaks with a deep voice, his words carefully chosen, but delivered with a barely restrained anger: "Tshamek, my people have worked hard to understand yours, yet it seems each day we see new examples of how your people work just as hard to foster old hatreds. My daughtersson is dead, beaten to death by cowards in your city street. I do not blame you, yet still Gaekhen is dead, and my son and his kin are not so forgiving as I. They wish to return to the Skoan-Quah in the Cinderlands, to join with the Sklar-Quah and rally to war against Korvosa. This would be disastrous, for both our peoples. Amends must be made.\\

Our ways are not as yours. If a body does not go to the fires of the gods, the smoke of a warrior's spirit cannot rise to the Great Sky. If I could send Gaekhen's body to the Great Sky with honor and dignity, his father and brothers would listen to me and stay their wrath--the talks of peace between my people and yours can continue. But he was not just murdered. His body has disappeared. I have spoken with the spirits, and they have revealed to me that Gaekhen's body has been taken to a place below your boneyard.\\

With this knowledge, I could surely lead a group of my finest warriors into your boneyard to retrieve Gaekhen's body, but this would be seen as an act of aggression by your people and it would violate the hospitality we have been offered by the church of Pharasma. No, it falls to your people to make amends for what has been done. Of all the Korvosans we have met, you come the closest to what we call {\itshape nalharest} or friends, so I ask you to bring me Gaekhen's body, lest we be forced to recover him ourselves. And although it pains my heart to say it - we will not be gentle if it comes to this." After his request the old shaman takes his leave. Kroft tells the companions Gaekhen was murdered in the East Shore District and she urges them to contact the church of Pharasma before they start snooping around in their graveyard.\\

