%!TEX root = ../crimson_throne_book_main.tex
% 2014-11-30
\section{28 Sarenith 4708}

The next morning Mouse is still feeling ill and Quint, Korwick and Heldrin are a bit under the weather as well. That means that all the kids and both Sjo and Quint have been infected. Only Balian and Puk are still feeling healthy.\\

Soon the guests for the breakfast meeting arrive: Valdur Bromathan of Sarenrae, brother Aldrick of Pharasma, Archbanker Darb Tuttle of Abadar and Ornher Reebs of Asmodeus. These four representatives of Korvosa's most important churches are joined by Doctor Dave Saulus of the Queen's Physicians and Sjo's girlfriend, Larella of Shelyn, who spent the night in the villa for the first time. Sjo welcomes everybody and leaves the guests to come to their own agreement. Darb Tuttle immediately takes charge and the others let him. When it becomes clear that the heroes signed a contract with the highpriest of Asmodeus, promising him 50 % of all the funds raised, there is some discussion, but the medic council finally decides to discuss that matter at a later date. For now they agree to place collection boxes in all the temples and they also decide on a text to be printed in the Herald.\\

When the guests have left, Sjo and Balian see to all the sick in the house. By noon they go to Trail's End to take care of little Brienna as well. The girl still hasn't recovered, although Sjo's healing has kept her relatively well. Brienna's mother Tayce inquires if the companions have already heard of the {\itshape cure} that is supposedly available somewhere in the Heights district. They obviously haven't, but a potential medicine certainly piques their interest, even if - which they suspect - it turns out to be a sham. Some information gathering quickly points them to Lavender's Luxury, a perfume boutique. The shop stands in a row of tightly packed houses in Summoning Street, just south of the Acadamae. The owner is a Chelaxian woman named Vendra Loaggri, who is famous for her avant-garde creations and brazen promotions, like her "Free Imp with every purchase" stunt last year. A long queue of eager Korvosans waits in a line that stretches far around the corner. Several of those waiting bear the obvious blistered symptoms of the plague. A strong man guards the door and eyes every customer that enters closely. A customer leaves the perfumery and immediately applies a greasy ointment on his neck. He refers to it as Lavender's Luxuriant Liniment and claims that he already feels better, even though Sjo notices no changes in the man's red spots and Quint detects no magic. Quint wants to sneak a peek inside, but dreads the thought of having to queue for hours, so he decides to start a new line for those who want to buy perfume instead of the cure. While most queuers throw angry glances at the bard, his fast-talking overwhelms them enough so he can get away with his little scheme. About fifteen minutes later he is inside the shop, where a happy-looking dockworker is giving his unbiased personal testimonial of how the luxuriant liniment cured him of the plague. A woman with clear blue eyes asks Quint what he wants when he reaches the counter. The bard recognizes her as Vendra, Loaggri, the shop's owner. From her he learns that Lavender's Luxuriant Liniment has already been around for a long time, but the merchant only recently became aware of its special plague healing ability when a customer who had used it got better. Quint finds it hard to determine whether the woman is lying of whether she truly believes the ointment works. He ends up buying a bottle of perfume and Puk picks up a dose of the cure, because he wants to have it examined.\\

Back in the street Quint teases Sjo about his new girlfriend, giving the big Shoanti the impression that he is a bit jealous. As the two young men are harrying each other, they suddenly hear a loud scream. A group of people have gathered down the road and Quint can tell that are crowding a woman who is clearly in a state of panic. The frightened girl has blond hair and is dressed in a white sheet with no clothes underneath. Sjo gets the bystanders to give her some space while Quint calms her down. When they ask her for her name, she doesn't know ... she doesn't remember who she is or how she got here! An old lady tells the companions that she noticed the girl staggering down the street in naught but a white sheet, looking disoriented. When she asked the girl if she was okay, she started wailing like a madwoman. Still, she seems to be in fine physical order, very fine even as she looks very attractive. Quint wants to get the poor thing some clothes and convinces the old lady, who lives close by, to sell him a skirt and a blouse. Despite this sober attire the girl looks stunning when she puts on the clothes, especially when they prove to be a bit tight around the chest. Sjo and Quint continue to quiz her to see if she remembers anything. When they talk about Sarenrae, Asmodeus or Abadar, she recalls the names and portfolios of those gods, although she cannot name any godhood spontaneously. They lead her down the neighborhood to try and trigger her memories, but nothing comes back. When Puk mentions food, she realizes she is quite hungry, as are the companions, who haven't had lunch yet.\\

Balian suggests grabbing a bite in {\itshape The Travelling Man} in Old Korvosa. The girl shows table manners while eating her burger, indicating that she is not from the lower classes, although she does not display the elaborate etiquette of the nobility either. The girl is very worried and every question the companions ask her sends her into a state of alarm. Is she a criminal? Or someone who was about to be sacrificed in the temple of Asmodeus? Did she rise from the dead or did she use to be a statue that was turned to flesh? She hasn't got a clue. During the conversation Quint notices some men in the square who are pushing a cart with a dead body. It is not until they have disappeared from view that the bard starts wandering why the body carters were going west instead of east, to make for the bridge south for the Gray District, where all corpses have to be delivered. Still, the pleasant company at his table soon makes him forget his contemplations for more agreeable worries, the pretty girl's lot. Focusing his gaze on her shapely curves, the bard casts a {\itshape detect magic} which reveals a hint of magic on her. Sjo joins in with his own spell and reads a touch of transmutation in the lingering magic. The two men try to get the girl to imitate some of their simple spells, to see if she masters the art of spellcasting. It yields no success, although the girl admits to feeling some familiarity to spell weaving. The companions also experiment with the girl's reflection in the window, but seeing a mirrored version of herself triggers no memories. Finally Sjo proposes naming the girl, since it is hard to talk to someone without a proper name. Balian comes up with a nice suggestion, Madam Nesia, the lady who suffers from Mad Amnesia.\\

