%!TEX root = ../crimson_throne_book_main.tex
% 2014-03-08
Quint realizes that no one has ever found a shorter path to revenge. He has only just learned that his mother was murdered by the key-lock killer and already he faces the culprit, albeit in undead form. Determined to end the miserable creature once and for all, the bard spins into the room. His friends join him - with Puk finishing off a first of the four zombies - but are then overcome by a sense of dread emanating from the horrible serial-killer. They immediately flee the morgue, making their way up, leaving the bard alone, surrounded by four undead. Although his raging heart withstands the key-lock killer's aura of fear, Quint sees and feels the precariousness of the situation as his mother's murderer viciously cuts through his flesh with a clawed hand. The dashing comedian strategically retreats, but suffers another grievous wound, leaving him just breaths away from the grave himself. Fortunately the walking dead don't follow the heroes upstairs, so they have a moment to regroup, heal and wait for Puk, who ran all the way to the great hall before coming to his senses.\\

Sjo informs his friends that the four undead who crawled out of the compartments in the wall are zombies, who can be damaged with slashing weapons like Balian's and Puk's blades, but have a certain amount of resistance to his blunt morning star or Quint's piercing rapier. The key-lock killer is something different though. While the Shoanti can't put a name on it, he understands that the undead's physique is probably vulnerable to bludgeoning weapons and magic. He enchants Balian's greatsword with a {\itshape magic weapon} for this purpose. The companions make their way down once more. Puk quickly puts down a second zombie in the hallway and this time only Balian falls victim to the key-lock killer's fearful aura. While the ranger flees upstairs again, the halfling continues his zombie slaying spree. Sjo uses his healing magic to burn the key-lock killer, but it is Quint's rapier that runs the poor wretch through, setting him free for his journey to a probably very unpleasant afterlife. As the undead abomination falls down, he whispers: "Forgive me."\\

The halfling, Shoanti and the bard search the room, but find nothing more than bones and decayed corpses, before they realize that the ranger still hasn't returned from his second {\itshape retreat} upstairs. As they make their way back to the great hall, they find their friend locked in conversation with the former jurors. The sound of running and the cries of fear alarmed them, so they came out to find out what was going on. The dwarf Tablark Hammergrind tells his fellows not to worry, but Patrissa feels safer staying with the heroes. There is one more room that connects to the great hall that the companions haven't examined yet. Zenobia tells them it is the jury deliberation chamber. It contains a large table and a dozen rickety chairs. Quint's keen eyes spot some words carved in the side of the table: "Who's laughing now, Mord? E.B." How typical, the stupid jester Ebin Bazel thought it was {\itshape funny} to convict someone to the gallows, did he? As the bard grunts with frustration, screams erupt from the hall. Hammergrind's voice loses its steely resolve as the dwarf sighs in total fright: "It ... it's him ... the croaker has come for us ..." The grizzled old miner drops to his knees as the companions rush to his side and notice a lumbering shadow at the top of the stairs. The thing's head jerks obscenely to one side atop a broken neck. Its face is covered in a rotten death shroud, a milky eye peering through one hole and its black teeth visible through another rent in the fabric. A horrid rasp of air croaks out pain and misery from the thing's crushed throat. The dwarf moans like a tortured animal and Quint is horrified to see that he is clawing at his own eyes. The bard grabs the old miner and tries to restrain him from hurting himself, but the frightened man struggles like a rabid dog and gives Quint a head but square in the nose. As the bard abandons the grapple his friends surround the panicked dwarf and try to knock him out, but he slips under their attacks and turns around to flee. Blinded by the blood Hammergrind can't see where he's going and slams into the huge chandelier lying in the ground. Losing his balance the dwarf trips. Blood spatters as the unfortunate creature impales his head on one of the candle spikes. His brain has been run through ...\\

Meanwhile Sir Rekkart Cole charges up the stairs and swings at the hulking headman with his own executioner's axe. "May the might of Abadar strike you down!" As he connects with the dark form his weapon hits nothing but air, revealing the shadow to be a mere illusion. Stupefied he returns to the others to calm down lady Patrissa, who is still trembling. Sjo and Balian pull the skewered dwarf from the chandelier and place his body in the deliberation room. When they come out, Madge suddenly notices that Hal Five-Toes is missing. He must have run off during the chaos and panic. But where did he go?\\

