%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-22
It turns out the old courthouse actually had a small cellar, where the archives were kept. While judge Zenderholm leads the jurors to the courtroom near the front door, the companions head into the basement. The record room is submerged in fetid water. Row upon row of bookshelves hold thousands of old court documents. There is a nasty smell of rot and mold in the air. The archives are filed chronologically. The most recent case discusses the key-lock killer. There are no records on the Jarbin Mord trial, though. Quint starts reading through the files on Korvosa's notorious serial-killer. The key-lock killer was a man called Bornan Ragus, a soldier in the Korvosan Guard. Some of his colleagues testified at his trial, describing him as a loner and a self-mutilating creep with a strange fondness for blood.\\

He committed his first three murders in 4690, gaining the nickname of the key-lock killer because he murdered his victims behind locked doors, making it seem as if he had come in through the keyhole. His first victim was a prostitute, Leana Castel. The files on her murder state that her killer got into her room and butchered her in a way that would become his trademark, by cutting her to little pieces. Apparently there was a witness to the murder, because a little baby was lying in a cradle next to the bed where his mother was cut up. Quint wonders whether this might have been Madge Blossomheart, but the records say that the child's name was unknown. The baby did have a distinctive feature, though, a birthmark on his shoulder in the shape of a scorpion.\\

Quint is suddenly lost for breath. Shocked he rereads the words: "a birthmark in the shape of a scorpion"! Quint's hand slides to his shoulder where he sports the mark described in the files, a curled-up scorpion, the spot Gaedran Lamm used to refer to as the {\itshape devil's touch} . 4690, that is 18 years ago, so that checks out. This Leana Castel was his mother? And the key-lock killer murdered her? The bard quickly resumes reading. The child was taken by a soldier from the Korvosan guard, a man named Nimor Seelen, who took it to the orphanage. While Quint takes a moment to process this information, his friends leaf through the rest of the key-lock killer's case. The man continued his crimes, killing more beautiful young women in the confines of their own rooms, getting more productive over the years: three victims in 4690, 4691 and 4691, one more in the two following years, then five, then six, amounting to nine in 4697. He committed his last murder in 4698, when he was caught in the act and arrested. He used a magic bell to open the doors to his victims' rooms and close them again when he was done. Bornan Ragus appeared before court later that year where he was prosecuted by Lady Zenobia Zenderholm, who wasn't a judge yet in those days. He was condemned to hang by a jury under the supervision of judge Rayndros Felgor, the man who was strangled in his own office ten years ago. Jarbin Mord executed the sentence, his last hanging safe for his own.\\

While the companions leaf through the rest of the files, Puk, who is a bit too short to reach the higher shelves, examines the lower ledges. He finds the key-lock killer's bell, a small magic device that resembles a {\itshape chime of opening} . Ringing the bell opens a locked door once per day. Ringing it again closes that same door. Jarbin Mord's name turns up again and again in the records. Each time someone was condemned to death, Mord carried out the sentence, mostly by hanging them, in a few rare cases by beheading them. One more file draws the companions' interest: the case of Daben {\itshape Blossomheart} , who was condemned for robbing a diplomat and stabbing him to death in 4693. He was hanged for his crime by Jarbin Mord. If he was Madge Blossomheart's father, it would explain why the street performer wanted Mord dead. She must have been twelve or thirteen at the time her father was executed, still a child. Five years later she would get a shot at revenge when she was chosen to sit in Jarbin Mord's jury. The record room reveals no more useful information, so the companions turn their attention to the other door in the basement. It leads to the morgue: a cold room with rows of small steel doors in the walls. One body lies on a stone table. The corpse twists and slowly rises, while four more zombies climb out of the compartments in the walls. When the first corpse glares at Quint, it groans: "Leana's boy, so you have finally found me. Have you come seeking vengeance? Destroy me and put me out of my misery ... I beg you!"\\

