%!TEX root = ../crimson_throne_book_main.tex
% 2014-07-12
Sjo kicks open the door and surprises four derro in what looks like a crude laboratory. One wooden tables is stacked with vials and beakers, while a second leans awkwardly on a hastily repaired leg and hold nothing but shards. Three cauldrons sit against the far wall, filled with rancid fluids. One of the derro slings a {\itshape sound burst} in the hall where the companions stand at the ready, while another moves in to block the entrance. A third runs to a door in the south wall, while the fourth pours a sickly green liquid on his blade. Puk and Balian quickly dispatch of the little critter in the doorway and move over to the one with the poisoned blade. They now have a clear view of the south wall, where the third derro has opened the door to release a horrible monster: a creature consisting of stitched-together body parts, most of which are partially decayed and rotting. Balian notices that its relatively 'fresh' arm is covered in Shoanti tattoos. As the monstrosity emerges, it hammers the derro in its path to kingdom come. Balian and his mates meet the golem head on. The ranger swings his blade wide, striking down the derro with the poisoned blade and hitting the golem in one swooping arc. The last surviving derro slips away in a natural tunnel at the other side of the room as the companions circle the foul-reeking golem and hit the horrid creation from every angle, taking it down before it can hurt anyone. There is no time to recover, though, as the last derro returns, hounding a hideously deformed creature in front of him. The lumbering brute has a bloated cabbage-like face and a contorted frame, but none of the companions have ever seen such a creature before. It slams its bulging fist on little Puk, sending the rogue reeling. As the 'intruders' surround it, the creature bellows that it will take their heads to {\itshape Vreeg} , pummeling both Puk and Spyder with strong blows. Sjo steps in to heal his halfling friend with a powerful surge of salving energy while Balian moves between the monster and the pale-skinned dwarf. His greatsword cleaves through the deformed enemy's flesh before it embeds itself in the small derro's head, ending his annoying Undercommon rambling once and for all. The brute withstands a much harder beating and manages to slam its fist into Balian's head and break some of Quint's ribs before it goes finally down. The companions heal up and examine the room and their slain adversaries. They find a couple of flasks with poison and a dirty chain shirt on the deformed brute's frame, which radiates light magic. Quint cleans it up with a {\itshape prestidigitation} and dons it, finding it  {\itshape a bit 'wide' around the chest} , making a mental note to visit the dwarven smith Furin Ironsguts to have it fitted properly. The tunnel ahead splits to the left and right. Weak moaning resounds from the right and when Balian and Puk examine it, they find a foul-smelling cavern, bordered on three sides by ten-foot deep pits. These pits hold decaying bodies and excrement, as well as two frightened, malnourished humans, a woman and a girl. The girl is completely apathetic, rocking to and fro with her hands clamped against her head, but the woman reacts relieved to the presence of the heroes. Tears pour down her face as she realizes her nightmare has come to an end. She says her name is Tiora and explains she was captured by some derro a couple of days ago while snooping around the graveyard. The ugly dwarves threw her in this pit with the hideous ogrekin Cabbagehead as her jailor. The little girl was here already and hasn't uttered one sane word, so Tiora has no idea who she is. She also knows that the derro's current leader is called Vreeg, a cruel little necromancer, who normally answers to a man named Rolth, who is absent at the moment. The information that this lair is Rolth's hiding place is new to the companions, but seems to fit the bill of what they knew about the man.\\

The heroes look through the corpses and body parts in the pits for Shoanti markings, but find nothing. They do discover a hidden cache with some gold and gems. Then they quickly escort the two women to the safety of the cathedral of Pharasma, running into two more derro on their way out, who came from a bedroom they bypassed on their way in.\\

The last part of the warrens contains some sort of operation room with another stitched-together body on the operating table. The patchwork creation has not been animated yet, but would stand at least seven feet tall if it rose. The head is strangely small for this massive frame and bears a distinctive scar on its left cheek, identifying it as Gaekhen's head. With one arm, both legs and the head recovered, all that is missing is the Shoanti's torso and right arm.\\

The companions surprise three derro in the next room, but are taken aback themselves when they see the small necromancer Vreeg in the connecting bedroom. The white-haired wizard weaves some protective magic before throwing a mighty {\itshape fireball} on the heroes as they are finishing off his final minions. The explosion sends Sjo to the brink of death, but luckily the healer has a slight resistance to fire, which saves him, allowing him to patch up with a  {\itshape cure moderate wounds} spell. The necromancer lashes out desperately with his foul magic as the heroes try to take him down. He weakens Balian with a well-aimed  {\itshape ray of enfeeblement} and next  {\itshape blinds} him. His  {\itshape vampiric touch} and a final  {\itshape sound burst} almost take down Sjo again, whose frantic healing averts defeat. The side-effect of the sound burst stuns all the companions, giving Vreeg the opportunity to flee the scene, but his short legs cannot outrun the 'invaders'. Quint lashes out with his whip, tripping the fleeing derro, after which Puk expertly plunges his short sword in the prone opponent's body. Taking their time to examine the rooms more carefully, the companions find Gaekhen's last body parts, as well as some interesting loot: a {\itshape wand of mage armor} , some potions and five applications of  {\itshape restorative ointment} . There is also some gold, Vreeg's spellbook and a small library with tomes on necromancy, the art of golem crafting and diseases and plagues, which Quint wants to move to the villa. One of the books also has a couple of scrolls wedged between its pages. 