%!TEX root = ../crimson_throne_book_main.tex
% 2014-10-04
\section{25 Sarenith 4708}

That morning Korwick and Heldrin inform Sjo that their friend Mouse is running a fever. The Shoanti examines the boy and finds him ill with the first symptoms of the mysterious disease that is plaguing Korvosa. He gives the lad proper treatment and orders him to stay in bed. After that he and Balian make their way to Trail's End to take care of little Brienna. Body carters are at work in the streets to clean up the dead rats and a woman almost empties her chamber pot on Balian's head, but the ranger's quick reflexes save him from a smelly shower. There is a dead rodent in the filth as well.\\

At Brienna's house Sjo is happy to learn that the girl is doing better today, although she hasn't conquered the disease yet. While he is there he offers Brienna's mother Tayce a full-time job in the villa, promising to pay her half more than what she's making right now. When Brienna gets well, she can join her mother as well. Tayce happily accepts, but asks some time to inform her current employers that she will be making a career change.\\

Meanwhile Quint and Puk swing by the opera house to ask for a favour from Delindra, the old elven seamstress who looks over the Marble Dome's large collection of costumes. She immediately agrees to help her friends with their outfits for the party at the Carowyn residence. Puk wants to be a dwarf, Quint will go as a male erinyes devil, while Sjo will dress up as a Hellknight and Balian as a bone-themed Shoanti. The kind elven needleworker tells the companions to return in three hours for a first fitting.\\

Over lunch Quint muses about Amarice, their one time fellow lamb who joined the Grey Maidens. He is curious how she's doing, but is even more interested in finding out more about the Maidens themselves. The companions still know very little about this new military force, they don't even know where the armor-clad soldiers are staying. Quint decides to write Amarice a letter, inviting her to breakfast.\\

When they return to the Marble Dome, the companions come across a struggle in the street. Ishani Dhatri, the half-Vudran priest of Abadar, is the victim of a broad shouldered man who is pressing a dagger to his back: "I'll tell you one more time, priest, if you don't heal my son, things will turn ugly!"\\

"But I already used up all my magic for the day. I CANNOT help you today ... but maybe if you go to the temple, they'll be able to help you out ..." the desperate priest tries.\\

"I've already been to your stinking temple. They want money, lots of it, or they don't care about you. That is how pious your Abadarian brothers are!"\\

"I suggest you back off immediately", Quint interferes. "I don't see how killing a man helps your son. It will only get his father thrown in jail while this is the time he needs you most to take care of him."\\

"You should try the other churches", Sjo adds. "Go to the temple of Sarenrae and ask for Nathan. Tell him Sjo sent you."\\

The burly man backs off, realizing that his current actions will only get him into trouble. He mumbles a faint apology to the shaken priest and makes off to the Sarenites instead. Ishani thanks the companions for their aid and informs about Brienna. He is obviously pleased to learn that she is doing better.\\

At the Marble Dome Delindra has everyone try out his costume for this evening. Although the garments seem to fit nicely, Delindra is a perfectionist and pulls out a few needles and pins for some last minute adjustments. She has the four young men return to her at half past six, to help them get dressed and made up.\\

