%!TEX root = ../crimson_throne_book_main.tex
% 2014-05-31
After procuring Kroft's permission to interrogate the guard who aided the king's murderer, the companions head to the Longacre prison. The accused is a sergeant by the name of Zack Alderman who freely repeats his testimony. The king's portrait painter, Trinia Sabor, was a pretty and lively young girl. When she first arrived at the castle, he was on duty. They chatted for a while and Zack felt like they connected, so he arranged to be on duty again the next time she came, and the next ... and the next. That is how the Gray Maidens who were investigating the case found him out, because he had traded all his shifts to be on guard when Trinia Sabor was present. When she started her commission the king was already ill, although it wasn't so bad yet. One day Zack caught her concocting a drink for his majesty. When he confronted her about it, she claimed it was some kind of tea, meant to make the king feel better and Eodred happily consumed it. Still, Trinia asked Zack not to tell anyone about it: the king's healers might not approve of this simple, but effective cure, preferring their own complicated and expensive remedies instead. Sometimes a simple answer is all that is required, she had smiled, so Zack had kept his mouth shut.\\

But Eodred kept getting worse and after a couple of weeks things got so bad that Trinia wasn't allowed to visit with his majesty anymore. About a week later the monarch died. That's when Zack started suspecting that Trinia's drug might have been something different entirely: a poison. Still, he was afraid to come forward, because if he was right, he would be blamed for not having reported this earlier. He might even have prevented the king from dying! So he shrouded himself in silence, until the Gray Maidens confronted him.\\

So this guard's crime went no further than omitting to report something ... and there still is no proof that the drug Trinia had given to the king was anything other than a natural cure. That is why Field Marshal Kroft was so adamant to take the girl alive and not allow the lynch mob to seek its own justice. It was by no means certain that she was guilty!\\

By the time the companions return to the stripper's bar where Trinia's 'devil' friend works, the joint is open. The same ginger-haired dwarf is at the entrance, oblivious to the jolly music that comes from within. His shoulders are as wide as the door and his head seems too small for his body. He demands three gold sails admission fee per person before stepping aside.\\

The {\itshape Voluptuous Vixen} hosts a bar with scantily dressed waitresses and a stage with a pole. When the companions enter a sweet blond girl in the guise of a shepherdess is dancing to a merry tune. Less than a dozen men make up the customers, mostly sailors. When the blond shepherdess is finished, she goes into the room to give lapdances, while a dancer in a white wig and a transparent suit follows her act on stage. The new girl is being announced as Pearl. Next up is Nisha. She appears in a puff of smoke and light. On the sensual tunes of a Varisian song she shakes her hips, swirling her colorful silk scarves and ringing the little bell that hangs from the tip of her tail. She rhythmically beats a tambourine and shows her nimbleness by doing tricks on the pole. Her lush brown hair sports two horns, which - together with the tail - clearly mark her as the {\itshape devil woman} . When she's done, she also joins the customers in the room. Quint immediately hails her over, but when he starts quizzing her about her personal life, she refuses to address the matter. She goes silent when Quint says that her friend Trinia is in danger and she finally repeats that her private life is not something she discusses with customers. When Sjo and Quint press the issue, she gets up and walks away to the backroom. Balian and Sjo try to follow her, but a big man blocks their passage. Sjo tries to hit him in the face, but he deftly avoids the Shoanti's fist. Next Balian draws steel and things threaten to get out of hand quickly. Quint cautions his friends to calm down and lashes out with his whip to pull Balian's greatsword from his grasp. While the human security guard at the backroom door engages Sjo, the ginger-haired dwarf charges over from the front door and grapples the disarmed ranger. Like his bard friend, Puk also refrains from fighting, pulling out the pickled head he stole from the curiosity {\itshape museum} at  {\itshape Exemplary Execrables} instead in an attempt to daze the onlookers'. His trick only serves to frighten the girls in the room even more. Sjo casts a  {\itshape hold person} on the bouncer, who resists the magic and Quint throws a  {\itshape sleep} spell into the fray, which only affects Balian, who goes limp in the dwarf's arms. The broad-shouldered guard starts dragging the ranger to the front door and throws him out in the street. The other bouncer is still blocking the door in the back and he firmly insists that the companions leave. He appreciates Quint's interventions, but he cannot allow trouble seekers to stay in the club. Quint's warnings that they are here on official city business do not sway him and the companions decide it's better to go. The bard quickly picks up Balian's greatsword and presses the dwarven muscle another gold sail in his hands, a fee for a job well done! Then he steps into the street as well. Figuring that this building probably has a back door, Puk charges off to the left to make his way around the block, while Balian and Quint try the other side. Sjo remains at the front door, making sure the tiefling dancer does not leave through there. The halfling is lucky, finding a small alley that provides a shortcut. As he reaches the back of the building, he spots a cloaked shadow disappearing around the corner: a silhouette with a tail! He races off in pursuit, but keeps to the shadows when he catches up to the woman, who is looking over her shoulder anxiously to make sure no one is following her. Then she climbs the outside stairs of an apartment building to the third floor, knocking twice on the door before opening it with her key and stepping inside.\\

