%!TEX root = ../crimson_throne_book_main.tex
% 2014-09-06
\section{22 Sarenith 4708}

Late in the afternoon the companions arrive back at the gates of the city, making sure to approach the city from the east rather than from the north, as if they came from the halfling town of Heavengard. While soldiers are still strictly checking everyone who's leaving or entering the city, the heroes get in easily and find the atmosphere inside Korvosa much more relaxed than a couple of days ago. Today is the 22nd of Sarenith, which is a popular local holiday known as Riverwind Festival. At the start of summer the winds shift for a few weeks, bringing down a cooling breeze from the Mindspin Mountains. This break from the stifling heat is typically celebrated with games and drinking and the festivities are already in full swing.\\

The companions head straight for the villa to freshen up and stable their new mounts. Korwick, Heldrin and Mouse are excited to see the horses and are eager to take care of them, but Sjo can tell that they have been taking it easy while he was away, as the house is a bit of a mess. He has the boys help him prepare a bath so he and his friends can clean up before they dive into the streets of Korvosa to join the festival. Balian convinces his comrades to compete in a friendly tug o' war competition against four baker's apprentices. The companions are almost taken by surprise as their opponents throw all their strength and weight into an early attempt at victory, but they manage to turn the tide and end up pulling the four flour covered men into the muddy ditch in the middle.\\

Quint and Sjo also chat with some of the bystanders and find out that the search for Trinia raged quite heavily until yesterday. Today's 'holiday spirit' apparently changed the mood and things are starting to feel normal again. The only exception are the Hell Knights, who've been conducting their own search, automatically expecting everyone to cooperate freely and rough handling anyone who doesn't. People are also saying that a ship burned out and sunk in the middle of the river yesterday, without ever making it to the docks.\\

The highlight of today's festivities is the Riverwind Race. Runners make their way through the streets of the city from east to west, mirroring the direction of the wind. The race starts on North Bridge and makes for Jeggare Circle over Norhtgate Avenue. From there Dead Shoanti Way and Academic Avenue take the contestants to the finish in the shadow of the Acadamae. Balian and Quint give it a shot and join the contest. Quint worms himself into the front row between last year's top six: two members of the guard, Cressik and Ringo, a ranger and a stable master, called Nalia and Vardin, the son of a trader, Daramir and a tall Shoanti, Portok Eagle-Eye, who was the winner of the previous edition.\\

Quint immediately sprints into first position, but is quickly overtaken by the guard Ringo who stays in front until Jeggare Circle comes into view. By that time Quint is already lagging behind, but Balian is dividing his efforts more evenly and never stays more than a few yards behind the person in the lead. Then Cressik, the other guard, takes over and sprints away from the competition. Ringo and Balian do their best to keep up, while the rest of the playing field loses more distance. It looks like Cressik is in for the win, but he overestimated his own vigor and slows almost to a halt in the final stretch. Ringo spurts by his colleague, leaving him to bite his dust and taking Balian by surprise. The ranger pulls out a final sprint and ends up a couple of yards short of the winner. Still, he lands a very respectable second place. Nalia the ranger comes in third and Portok the Shoanti takes the fourth place. Cressik ends up fifth and Quint is sixth, although he left quite a gap.\\

