%!TEX root = ../crimson_throne_book_main.tex
% 2014-11-30
After having procured the cooperation of all the major temples in Korvosa to combat the plague together, Sjo has little difficulty in convincing his girlfriend, Larella of Shelyn, to join in the effort, although her contribution will be very limited. She has only just reached the power to cast {\itshape remove disease} and her chances to fail at getting someone better are still bigger than her chances to succeed. Still, she's more than happy to help. Next the companions want to pay a visit to Dave Saulus, the Chelish doctor who leads the Queen's Physicians. They learn from Cressida Kroft where to find him: he's setting up a hospital in an empty warehouse, just a block away from Zellara's old fortune-teller's shop in the harbor area. Dozens of laborers are getting the building ready; a newly painted sign at the door identifies the place as {\itshape The Hospital of the Blessed Maiden} , a reference to Saint Alika. Doctor Saulus is in an office on the first floor and listens quietly as the young men inform him of their plans to form a medic force by having all Korvosan temples pull their resources. Saulus confirms that the number of diseased people certainly justifies a second hospital in Korvosa and agrees that it is best that both medical centers gear their activities for one another. The companions decide to invite all the parties who are fighting the plague in their own villa the next morning for breakfast. This first meeting will launch the medic force, and hopefully it will go on to lead a life of its own without the heroes' further involvement. Cyril Fordyce, the editor of the Korvosa Herald, even agrees to print a public call for help and funds in his periodical's next issue. Quint says he will get his final text tomorrow, after the meeting in the villa.\\

