%!TEX root = ../crimson_throne_book_main.tex
% 2014-04-05
After everyone has healed up Quint informs about the name they discovered in the upstairs office: Alastir Wade. Zenobia Zenderholm confirms the man is a lawyer and Patrissa says she might have met him; she has had so many suitors. When the bard confronts her with the buyer's receipt for the string of fire opals around her neck - which were paid for by this illusive Alastir Wade - she admits to having dated him a couple of times. He gave her the necklace and she still wears it today, not because Wade was precious to her, but the piece of jewelry itself is the most precious and beautiful piece she owns. It should not sit idly in a jewelry box. Although the companions doubt Patrissa's story, they cannot catch her in a lie.\\

Quint also wonders how Mord's jury was formed. It can't have been a coincidence that two jurors already had a grudge against the executioner before they were called upon to judge the man: Madge Blossomheart blamed him for hanging her father and Ebin Bazel hated Mord for outshining and thus humiliating him in public. Zenobia says that Korvosan citizens are normally selected for jury duty at random by a courthouse clerk. The prosecutor and defense attorney can reject certain candidates if they feel those people are biased, but since Mord chose not to have a lawyer, Madge and Ebin made it to the final eight. Judge Zenderholm has no knowledge of foul play in the selection process, but admits it could surely happen if the clerk was manipulated.\\

Ebin Bazel tires of Quint's accusations: "As far as I know I was selected fair and square. Yes, I didn't like Mord, but the man was a heartless executioner and a crazed killer, who deserved to hang! It is obvious that Mord is not just out for revenge against ME, for I am still alive while others have already died. Even the four of you, so-called defenders of judge Zenderholm, have been under attack, several times already! I mean, that fire-wielding healer guy almost died just now", Ebin spits out, pointing at Sjo. "A great job you have done protecting us, half the jury lies dead, killed twice over! And I'm still here, so I'm not the one to ... (cough), I ... I'm not the ..." The jester's face contorts and he looks as if he's about to be sick, sticking out his tongue in an effort to clear his throat. Then he bites down. Blood pours from his mouth and streams over his chin as his tongue falls to the floor. He has bitten it off!\\

At the same time the shadow of a hanged man glides over the wall and both Patrissa Vrakes and Killian Paltreth grab for their own throats as well. Miss Vrakes is clawing at her necklace, which seems to be strangling her, while Paltreth drops to the floor, foaming heavily at the mouth. His flask of brandy tumbles from his grasp, emptying its remaining fluid over the floorboards. Ebin also sinks to the ground, coughing wetly, convulsing and gurgling through the current of gore pouring down his own throat.\\

Puk pounds Killian Paltreth on the chest in an attempt to get the man to breathe. Quint and sir Rekkart Cole rush to Patrissa's side. Her necklace is squeezed to tightly around her neck that they barely manage to get the tip of a dagger behind it. Snap! The next moment twelve fire opals scatter over the floor and Patrissa grasps for air. Balian draws his greatsword and shouts for Mord to show himself, while Sjo smashes his mace into the shadow on the wall, chasing it from existence.\\

Paltreth also starts coughing and breathing again, but Ebin Bazel is not so lucky. The jester has suffocated in his own blood. Another juror lies dead, although it is the first time that the companions managed to save someone as well.\\

"What happened?" Quint wonders. "Did Paltreth's brandy suddenly turn to poison?" The bard kneels down next to the fallen flask and dips his finger in the spilled fluid. When he brings his fingertip to his lips, he does not taste any poison at all, in fact he tastes very little of anything. It seems to be water. He also wants to know if this latest attack was magical in nature, still resisting the idea that vengeful spirits can control reality through sheer will. The bard casts {\itshape detect magic} and while he finds no traces of magic in the air or the building, he sees that judge Zenderholm is wearing a magical ring. Sir Cole's chain shirt also radiates some blue light and Paltreth has some magic shining from under his clothes. 