%!TEX root = ../crimson_throne_book_main.tex
% 2014-12-20
Today there is another long line in front of Lavender's perfumery, but the companions do not approach the people in the same manner they did yesterday. Quint announces to everyone that Lavender's ointment does not work against the plague and Balian adds that they are here to officially close the shop. Since the customers have probably been waiting in the queue for hours, they are not inclined to leave just yet and stay put for now. When the guard at the door sticks out his head to enquire about the commotion Sjo order him to lay down his weapon in a very commanding tone. His words clearly affect the man, but he is still separated from the companions by a small crowd of people, so he chooses the safety of the inside instead and retreats in the shop. Weapons are drawn and now the bystanders realize that the situation is both serious and dangerous, which sends them running. The young heroes follow the guard and while Sjo orders most of the surprised customers out, Quint repeats that they are here to close the shop under the orders of Field Marshal Cressida Kroft. Tensions rise as the three bodyguards raise their weapons: the most burly of them threatens with his greatsword, while the other two wield a sword and shield. They defend the way to the counter, where the owner of the business, Vendra Loagrri, questions the four intruders' authority. For all she knows they are mobsters who want to steal her money. Sjo steps forward, booming that he's arresting her for obstructing justice, while Quint gives the three guards a final chance to surrender.\\

The man with the greatsword, obviously the leader of Lavender's security, slips his boss a quick glance before sending his mighty weapon in a sweeping arch on Quint. The bard staggers backward, bleeding profusely from a gaping wound. Balian tries to return the favor, but the fact that there are still a handful of customers left in the shop, cowering in the corners, makes him too cautious and allows his opponent to block his attack. Vendra jumps over the counter and pulls out a dagger that she flings in Quint's direction. Fortunately for the gravely wounded bard, the projectile misses him. Her other two guards bare down their longswords on Puk and Sjo. These opponents are no beginners and they hit hard. Sjo realizes the threat they pose and resorts to his magical arsenal for battlefield control. His {\itshape hold person} freezes his attacker in place. Quint seeks refuge behind his friends and patches up the worst of his cut with a  {\itshape cure light wounds} . Meanwhile Puk and Spyder engage the third guard, seeing how the head of Vendra's security now focuses his powerful swings on Balian, succeeding in another bloody gash. Sjo takes the man out of the action as well by paralyzing him with another  {\itshape hold person} , as Quints attempts a new spell on Vendra. His  {\itshape cacaphonous call} nauseates her so she has to give up fighting as well. The heroes are now clearly in control of the battle: they put down the remaining guard, slip the greatsword from the leader's grasp and push him to the floor. He fights off the paralyzing effects of Sjo's magic and tries to make for his weapon, but the heroes bear down on him from all sides and hit him into unconsciousness. While Sjo stabilizes the bleeding guard to prevent him from dying, Vendra and her last guard surrender. Puk tells the four cowering customers to get the hell out of here, but Balian stops one of them to get his identity, since he witnessed what transpired in here. The heroes heal their wounds and tie up Vendra and her men. Quint tries to get more information on the ointment from Rita, the frightened shop assistant, but she has little to offer and dreads acting against her boss. Sjo figures that he will find out more if he investigates the scene himself. He leads Vendra to the back of the building and uses her keys to unlock her personal living quarters and her laboratory. Here he finds confirmation for professor Sirtane Leroung's analysis of Lavender's Luxuriant Liniment: two barrels of animal fat, a bunch of cut up weeds and cheap perfume to scent the ointment. Still Vendra sustains her belief in the effectiveness of her cure, claiming that for a pharmacist there is no difference between weeds and herbs.\\

The companions decide to leave the rest in the hands of justice. They bring the four prisoners to the Longacre building to have them locked up and head over to the citadel to give a full report to Cressida Kroft. They also hand the Field Marshal all weapons and armor they confiscated, including some magical items. Kroft is actually surprised at how 'peacefully' and lawfully the companions concluded their business and admits that she made a mistake in not giving them a document to assert their authority. She suggests that the companions actually join the Korvosan Guard, although she quickly decides that might not be the best option, since the Gray Maidens were given full control over her soldiers.\\

Afterwards Sjo wants to follow up on the medic task force. In the Bank of Abadar he learns that Darb Tuttle is talking to the Jeggare and Arkona families to procure a building that can serve as a new hospital. He also informs professor Sirtane Leroung that his own illness has been conquered, affirming her suspicion and hope that the human body can fight off the plague. When she questions him about his 'treatment', he says that he's been using {\itshape lesser restoration} to keep up his vigor, which was definitely a strong weapon in overcoming the disease, but such a 'cure' is obviously not available on a large scale. Meanwhile Puk, Balian and Quint return to the villa, where they discover that Madam Nesia is entertaining a guest. It's Meep Gildenglare, the old seamstress and more notably, the friendly wererat lady. Meep confirms that it took her a while to remember the companions from their days in the 'Pied Piper' play five years ago, but now she does. She recalls the children who peeped under the floorboards from where she was directing the rats on stage in her wererat form and realizes that they have grown up. She now freely admits to being one of the oldest lycanthropes in the city, one of the few who was {\itshape born} with the affliction. Unlike most of her kin she has managed to find her place in regular society, which makes her a 'coward' or even 'traitor' in the eyes of most of her own sort. One such lycanthrope, who's never been able to integrate in the human world and has always felt suppressed and shunned, is Girrigz, a young but strong wererat who is also a born werecreature. Girrigz has been nursing his grudge against human even more since he was shot with silver arrows by the Korvosan Guard a couple of years ago. He has gathered a number of like-minded brethren around him and like most stereotypical members of his kin, he has made his home somewhere in the sewers. Although Meep does not entertain cordial relations with these wererats, recent development in the city have caused her to worry. She has witnessed how the plague is ripping through Korvosa and has not failed to notice that rats play an important part in spreading the disease. She has picked up various rumors that blame the wererats for this epidemic and fears that this news will not sit well with the likes of Girrigz. He already feels frustrated at being condemned to live in the filth of the humans and will be greatly offended by the accusation that he is the cause of this malady, as if any wererat would ever purposely poison a real rat brother or sister. Their bond with the little rodents is just too strong, Meep says as she pets the rat she has in her own lap, which she introduces as Mr. Nibbles. Meep sighs deeply before she implores the heroes to help her kinsmen out. She wants them to go below ground and convince Girrigz and his gang not to do anything stupid, because such an act would only backfire in these rat-hating days. In return she will gladly provide a wardrobe for Nesia, because the girl can hardly put on the same gown day after day, as lovely as it may be.\\

