%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-01
The queen leads those present to the next room, where she sits down at the head of a long table. The nobles take up position close to her majesty, leaving the companions and the magistrates the places at the other end of the table.\\

When everyone has settled, Ileosa speaks again: "Ever since my husband died the city has been sinking away in chaos: riots, destruction, pillaging, battles with the Guard or other representatives of the state, numerous wounded and too many dead ... all in the name of a queen who cannot rule! This has to stop, right NOW! That is the reason why we have all gathered here today.\\

The Sable Company and the Korvosan Guard have been working night and day to prevent us from slipping away completely into the Abyss. I was even forced to call in the help of the Hellknights to enforce order. But disorder overwhelmed us nonetheless.\\

We may count ourselves lucky that we have creative citizens like these heroes and sharp minds like Field Marshal Kroft. Their firm actions saved us from even worse. Field Marshal Kroft, would you please fill us in on what has been going on in the city?"\\

Cressida Kroft rises and addresses the members of the council: "I understand that our citizens were shocked by the King's death. Eodred was a good ruler and the people loved him. But why did they react so vehemently? I had a hard time understanding that. Grief was normal, but all this anger, hatred and rebellion were out of place. That is why I sent out these gentlemen, to find out what was going on. I'll let them fill you in on what they discovered."\\

Next Quint takes the stage: "When our good king died, it felt like there was a sudden void in power. We have to respect that his widow needed time to bury her spouse and properly grieve him, but some people seemed bent on not allowing her that time. Individuals who had some personal reason to criticize the government, who had their own agenda. They took disadvantage of the moment, swaying the minds of other Korvosan, honest, hard-working citizens who unfortunately don't exactly grasp how politics work. One thing led to another and the situation got out of hand, fast. The city reacted promptly to these challenges, but while actions like closing the gates probably saved innocent lives, it also provided these enemies of the state with more fuel for their fires of rebellion, as food supplies quickly dwindled away and the people grew hungry and malcontent."\\

"I appreciate your report, good master Quintillian," Glorio Arkona interferes, "but you're not telling us anything we don't know yet. Can you give us something more concrete?"\\

"I can. We walked in on a manifestation that almost got out of hand. If we hadn't convinced the misled protesters that killing guards would only make matters worse, the day would have ended in blood. This was the first time we felt that most people were just following some agitators who spewed filth on our beloved queen. We found more evidence to this theory when we stopped a business called {\itshape All the World's Meat} . A clever agitator had duped a lovesick guard and some of his unworthy colleagues into handing out free meat to the poor. The leader didn't even realize it, but his men were actually killing people and carving up their flesh to feed the citizens. We also saved a member of the Sable Company from being torn to pieces by agitated dockworkers and witnessed a troop of Hellknights slaughter a dozen people who had been dumb enough to follow a handful of rabble-rousers into manifesting against the queen. We weren't able to save them all, but I don't even want to imagine the bloodbath that would have taken place if we hadn't been there. We came across honest citizens who were so brainwashed that they almost tore captain Jalento's young son to pieces or who were so hungry that they threatened to kill a baker for food. Finally we were able to track some of the agitators. We shut down their little operation and with the help of the Guard, we were able to prevent another march that was meant to end in violence and blood. Since then we have been using the same weapons as our enemies, a silver tongue, spreading the word on their treasonous, self-serving manipulations and convincing the good people of Korvosa to give queen Ileosa a chance.\\

After all, when you talk to the average John Doe, you quickly find out that all he wants is to be fed and to feel safe. You have all noticed it, but the last couple of days have been more or less quiet again. We have turned the momentum of the enemies of the state, now we have to press on!"\\

"And when you talk about {\itshape enemies of the state} , do you know who they are?" Archbanker Darb Tuttle of Abadar wonders. "I'm afraid not", Sjo replies. "We have been fighting and rooting out the symptoms rather than the cause. But we have been successful nonetheless. Our priority has always been the safety of the people, so that has been our terrain of operation, the common man in the streets. Even an invisible enemy can be beaten if we take away his weapons and prevent his evil schemes."\\

Eliasia Leroung adds: "What these young men are saying is true indeed. There have been people at work who want to taint the queen's reputation. Just a few days ago our presses were abused by such rabble-rousers to print a fake edition of the Herald with all kinds of filth about her majesty. I learned that these heroes intercepted about half of those papers, but several hundred copies were still distributed. You might have seen them. Even when we don't know who is behind these evil plans, we should act! I will make sure that the next edition of the Herald rectifies the situation and reveals the fact that rabble-rousers have been at work."\\

The council readily agrees with this proposal, as Leroung continues: "My family also holds a stake in many of the city's docks. Our laborers have to get back to work, there might be a dozen grain ships waiting in the bay to be unloaded. Getting people back to work and bringing food into the city is the best way to get things back to normal. There's no business than business as usual."\\

Garrick Tann, the tax collector, supports this proposition, as it would allow him to resume his work as well. "People were attacking soldiers in the streets, even without me there. I couldn't risk causing even more of a stir by doing my job. Still, part of these missed taxes will never be recovered. Getting the city back to running will cost money. I propose that those who can afford it, help us out. I think the noble houses should make an extra contribution, lest we go bankrupt."\\

It is clear why Tann is so unpopular, as about half the people at the table raise their eyebrows in surprise and annoyance at his proposal. Glorio Arkona keeps his bearings and replies: "I'd be willing to contribute a little extra, lord magistrate, but I'd have to be sure that the money goes to the right place, to the people of Korvosa, who are starving as we speak. Make sure they don't go hungry and I'll get you your money."\\

"I guess the Bank of Abadar could always allow the city an extra loan to bridge this difficult period", Archbanker Tuttle adds. " We could even discuss profitable terms this time, as long as Korvosa continues paying off its other debts."\\

"There are ways to solve these monetary issues, no doubt", Commander Marcus Endrin steps in. "Let's focus on more pressing matters. The Hellknights are trouble. Their presence seems to backfire. The stringent way in which they handle things is not right for this complicated situation. They see everything in black and white, while things are mostly grey. These young heroes confessed to it, the Hellknights respond to disorder with the blade rather than with common sense and words of peace. That is not the way to restore order. I say they should go!"\\

"I agree, Lord Commander," the queen says. I will speak to the Order of the Nail about leaving. But your marines and the guards will have their hands full. Even during this last week I've had my own bodyguard, the Gray Maidens, stand guard over my palace. But my Maidens are at the end of their game; there are only a handful of them and there is more work than they can cope with. I would like to expand their ranks so your men in the Sable Company and the soldiers of the Korvosan Guard can concentrate on the city."\\

"An excellent suggestion, your majesty", Quint jumps in. "We will need every able-bodied soldier in the coming weeks. Which is why I believe we should talk about forgiving the deserters ... A few soldiers refused to come to work since the beginning of the riots because they felt they needed to protect their families. They were wrong and should probably be disciplined in some way, but we would be fools to have them executed, as the law demands, because we need them. A royal pardon would secure their help and send out a message that the queen is both capable of ruling and kind."\\

"True, sir Quintilian," Commander Endrin agrees. "Still, having the Grey Maidens guard the palace gives me pause. Although the day-to-day security of the Castle is customarily in the hands of the Guard, it legally befalls to the Sable Company. The presence of the seneschal normally ensures our presence in these walls, but with Lord Kalepopolis missing, the company has lost its watchful eye in here. I think we should talk about a replacement."\\

Sjo and Quint nod in agreement, as Darb Tuttle wonders whether it wouldn't be disrespectful towards the current seneschal to put someone else in his place while he might still be alive." He also adds that the post of the seneschal will not be crucial in solving the problems at hand, like resuming trade, so the matter of the seneschal should probably be saved for a later date.\\

Valdur Bromathan remarks that resuming trade is indeed high on their agenda, not only through the city's docks, but a lot of food comes from the mainland and is presently stuck at the gates. "We should open the gates again, but the farmers will need military protection if we want to prevent new acts of pillaging."\\

Mercival Jeggare likes the idea of feeding the people, but he also wants to feed them mentally. "By exposing the agitators and resuming trade, we will show our citizens that Ileosa is capable of ruling, but we can do more. I'm thinking of the ancient concept of {\itshape bread and games} . We should entertain the public as well, with a positive message!" Quint takes this cue: "Ileosa is our new queen. You and I know and respect that. But the position of monarch is a highly respected one. If we want to entertain the people, why don't we give them a coronation?"\\

"An excellent idea," Glorio Arkona affirms, "crowning her majesty will serve all kinds of goals, we could feed the people, give them festivities and at the same time confirm the legitimacy of Ileosa's rule."\\

"The only question is", Quint continues, "how long should we wait? We can't just expect the Korvosans to happily dive into a public coronation so soon after Eodred's death and the riots."\\

"There is also the matter of how much this would cost", Syl Gar interjects. "Your ideas are wonderful, but costly as well. We'll need funds to pay for them."\\

"I think all this talk of partying is balderdash", Toff Ornelos throatily remarks. "The Acadamae has just cancelled the Breaching Festival as we didn't want to celebrate during these hard times, and now everyone is talking about fun and games! And not only that, now they also expect us, the noble houses, to pay for all this? We aren't the only ones in this city who have money. If I look at those young upstarts over there", he complains, pointing at the heroes, "they look all fancy in their new attire and shiny armor! Let them pay as well. They have come out of these troubled days as richer men, as have several other money-sharks in the city who used the scarcity of food to spice their own purses. A house like mine, that took a discreet stand in the background by closing the doors to the Acadamae and keeping our students off the streets, should not be punished. Find your money where it actually is and spread the effort evenly over all those shoulders!"\\

Lord Ornelos raises a sensitive point, but the approving looks in other noblemen's eyes give away that he made an important point. "Moreover, if we are to pay to clean up the mess, we should have more of a say in how it should be cleaned up. Give the council more power and I'll make a bigger contribution, but I refuse to pay for trouble I'm not responsible for and for solutions I have no say in."\\

"Well, maybe we should make the people who were more involved pay", Quint says. "Bakers and butchers were asking for higher prices when times were bad, maybe they can return the favor when times are good?" His suggestion is met with raised eyebrows, but the bard assures the council that he'd be willing to try and convince these people to contribute.\\

Sjo offers a refinement to that idea. "Why don't we turn it into a contest? Bakers will contend with each other to make the best bread and the best man will win a price!"\\

"That is an interesting line of thought, dear Sjo", Ileosa concludes. "Getting money will prove hard, and I still hope that the noble houses will contribute, although I cannot promise the council more power right away. Korvosa's laws and charters will have to be studied carefully before we can rewrite them. The precarious balance between the different stakeholders in the city has been overanalyzed and every little detail has been put into writing. Your ancestors have been so meticulous in constructing the power balance that it will prove a monster job to change it. For now, I can offer you this, though, Lord Ornelos, that I will ask the council for advice more often on a voluntary basis. I do agree with Magistrate Tann that common tax collection should resume as soon as possible. And I wouldn't object to a celebration in my honor, so if you want a coronation, I'd happily go along with it, certainly if all the noble houses would use the opportunity to show the people that they support my rule."\\

The queen looks around the table: "I think we've heard a lot of interesting ideas tonight. I thank you all for giving me your honest opinions. We'll have to investigate how plausible and affordable some of your suggestions are. My lords magistrate, I want you to study these ideas and give me a report on their feasibility. A few of us will reconvene tomorrow to discuss these plans further. Thank you again for being here. May the gods bless Korvosa!" Then the queen takes her leave and the council is over.\\

While walking out, Sjo seizes the opportunity to tell Sabina Merrin about Amarice, informing the commander of the Gray Maidens that his friend would make an excellent addition to her ranks. Merrin assures him she will look up this Amarice, a capable and motivated young woman would be most welcome.\\

