%!TEX root = ../crimson_throne_book_main.tex
% 2014-01-11
The companions continue their search in the dock area to find the mysterious rabble-rousing Vudran beauty, Selena. The anti-queen sentiments flow strong in the northern ward of the Midland district. Although the Korvosan Guard still patrols this area, the soldiers seem self-conscious and wary.\\

Suddenly two shadows sweep over the young friends, as two Sable Company marines fly over on their hippogriffs. A third rider is falling behind: his flying mount is bleeding from several wounds and struggles to remain in the air. The black-armored pilot cannot keep his animal airborne any longer and crashes around the corner, immediately followed by a crowd of angry dockworkers: "Over there! He went down! Get him!" Puk promptly sets off in pursuit, followed by the others. The halfling surprises one of the hot-headed rioters in the back, while Quint weaves his bardic magic to put another troublemaker to sleep. Balian's greatsword cleaves down another two, so the remaining hooligans quickly abandon their efforts to kill the soldier - whose leg is trapped under his wounded mount - and flee the scene.\\

Sjo pulls the marine from under his hippogriff and heals both the man and riding animal. The soldier is grateful and recognizes Sjo from his days at the Great Tower, the headquarters of the Sable Company. He warns him to be careful in this neighborhood, as things are getting more out of hand every day. After another well deserved 'thank you' he leaves for his home base.\\

The information gathering trail finally leads to the {\itshape Bailer's Retreat} , a rough tavern that is actually pretty close to the companions' home at Zellara's shop. This place is normally frequented by a high number of Korvosan Guards who like the strong coffee, but rumors say that soldiers avoid the spot at the moment. The young investigators decide to don a disguise before continuing their hunt for Selena. Quint dresses up as a dockworker, Balian takes off his armor and reconnects with his simple oarsman outfit. Sjo ties a strip of cloth over his eyes and hides his big frame in a dirty cloak, assuming the guise of a blind beggar. Puk trusts his ability to keep to the shadows and remain from sight, allowing him to track his friends and step in when necessary. At the {\itshape Bailor's Retreat} Quint finds no clues to Selena, but he does learn the name of another rabble-rouser, a man named Birold who frequents  {\itshape The Bountiful Mermaid} , an alehouse in West Dock. A witness who dislikes the riots attests to having seen the man inspire hatred for the queen and government in others. Quint decides to give the watering hole a quick look-over, but at this nightly hour there are only drunks left at the bar and Birold is not among them, although - when served with a drink - one of the patrons states he will most likely be in tomorrow evening. 