%!TEX root = ../crimson_throne_book_main.tex
% 2014-05-17
\section{9 Sarenith 4708}

The complete cast gathers early at the Marbledome for dress rehearsals in an atmosphere of nervous excitement. Touran Palastus is all wound up, but Quint and Sjo manage to calm him down. Just a bit though, since the director quickly falls into his role of grousing, with his assistant Leiny as the main focus of his wrath. Varric Bedan has to repeat his opening aria a couple of times before Palastus is satisfied. Fortunately the scene with Aisha Leroung, Diederik Lodann and Quint runs smoother, which finally relaxes the director enough to break the tension.\\

When act one is over, the actors witness the sleek scene change for the first time. Dargo the Hump pulls a couple of strings and the fort scenery gives way to an outdoor landscape. Act two works out great as well. Dario Darnas might be an ass, he does know how to put on a show. Even sour-faced Marco Ebhart puts down a decent Shoanti assassin and the gnome joker Lumenos summons the correct illusion for a change, heralding the surprise attack.\\

The third part advances more slowly again, as much more people are on stage and Palastus hands out numerous instructions to all involved. His nerves get the better of him once more, especially when he is not pleased with the visual effects of the storm that is summoned by Lumenos. Palastus calls for an overdue lunch break before exploding in a furious rage against the gnome, who actually did his best to leave his jokes behind and conjure the wanted effects. While everyone is eating, their argument continues in the background. Touran Palastus calls Lumenos a stubborn bastard who never does what he is told and annoys everyone with his childish pranks that no one enjoys. This is the most important production of the year, possibly of the decennium, and an off course stage hand is the last thing they need. Rimando throws his own insults in the mix, reproaching the director for being blind to change and experimentation. In the end the gnome simply states that, if he's not good enough, Palastus will have to do without him! Then he turns around to leave.\\

Quint hurries after the furious illusionist. Arguments that he actually likes the gnome's art cannot convince the angry little man to come back, at least not until Quint promises to conspire with him: they will ridicule Palastus tomorrow night at the end of the show. When the director will appear on stage to greet the audience, Quint will use {\itshape ghost sound} to make Palastus fart while he bows, at the same time Lumenos will conjure up a green cloud behind the man's behind. The second part of the third act runs smoothly again. Even though Bedan's song is not entirely perfect, it is good enough to please Palastus, who is obviously worn out by the fight with Rimando Lumenos. The director regains his bearings in the next part, when he complains that the Shoanti dancers are not giving it their best shot. Marco Ebhart suggests giving them some pesh tomorrow to spice up their act. He even offers to bring some for Palastus, although he admits that cabble tea would be better ... to calm him down.\\

The rehearsals for the final act go well. By now the orchestra is all fired up and the musicians carry along the rest of the cast. When Dario Darnas finishes his love song, he kisses Aisha for real. Although she is not pleased with his underhand tricks, the actress tries not to show it. Balian is the only one who notices a flash of anger in her eyes. The illusions are a success as well, as is the whirling battle and the love triangle scene with Aisha, Dario and Quint. But the finale tops it all, just like two days ago Palastus is overjoyed. Before retiring for the night, the director addresses his cast briefly:\\

"My dear friends, you've all worked hard this week. It hasn't always been plain sailing, but I think we nailed it. Especially that final scene was bang on target! Let's hope tomorrow will be just as spectacular. Congratulations to you all!\\

Tomorrow's show starts at eight. That means you all have to be here at four, so we can start hair and make-up. Get a good night sleep and make sure you're well rested and full of energy. Tomorrow will see the most exquisite audience this theater has ever welcomed. All the noble houses will be here, so will be all other dignitaries and of course, the queen herself! Let's give them the show of a life-time. For how often do you get the chance to perform for royalty? Do it for Korvosa and for Saint Alika!"\\

When the companions get home to the villa, they are exhausted. The three ex-little lambs who are still living with them want a full report of the dress rehearsals. Mouse also mentions that he picked up new rumors about the king today at the baker's. It wasn't the queen who killed him, but the commander of her Gray Maidens, Sabina Merrin. People say she's in love with the queen and she couldn't bear the competition anymore.\\

Again Quint reprimands the boys for listening to gossip. When little Heldrin wonders how this Sabina Merrin killed the queen, Mouse cannot answer him. "I don't know, she probably stabbed him with her sword, you know, tssschuk and dead", he tries.\\

"Sure, with her sword, and it has taken so long for them to figure out that the king had a stab wound?" Korwick laughs.\\

"Whatever, I wasn't there", Mouse defends himself. "Maybe she did what Korwick said yesterday and pushed a pillow in his face."\\

When the discussion finally quiets down, Heldrin remembers something else. A letter arrived today, with a seal from the castle. He presents it to Balian. It reads:\\

"Loyal citizen of Korvosa\\

On Sunday the Twelfth of Sarenith Ileosa Arvanxi, widow of Eodred II, will solemnly swear allegiance to the laws of Korvosa, before being anointed and coronated with her late husband's crown. This ceremony is to take place on the terraces of Castle Korvosa, where all Korvosans may witness her oath.\\

You are invited to partake in the festivities. Please present yourselves at no later than 10 o'clock on the terraces of the Castle, bringing this letter. Afterwards you will join the banquet in the throne room.\\

Please dress appropriately."\\

Quint points out that it is customary to present the monarch with a gift at such an occasion. The companions start thinking about an appropriate present. They come up with an original idea, but they realize they will have to act quickly to get it ready in time. Fortunately they don't have to be at the Marble Dome until 4 o'clock.\\

