%!TEX root = ../crimson_throne_book_main.tex
% 2014-01-26
\section{24 Desnus 4708}

This morning Sjo makes some time for the three remaining ex-lambs: Mouse, Korwick and Heldrin. He gives them some basic weapon practice and tests their ability for the divine and arcane arts, discovering that Heldrin shows some spiritual talent. Meanwhile Balian trains his dog Spyder and Quint goes into the city to gather more information on ambassador Amprei. He locates the man's impressive villa in South Shore. He already knew that Amprei frequented the gambling ship {\itshape Twin Tigers} in Eel's End, but now he learns that the ambassador also likes to visit the  {\itshape House of Clouds} , the brothel ship. In the evening Quint, Sjo and Puk head for the brothel in Eel's End, hoping to find out more about the Chelish nobleman. It's a hard job, but someone has to do it ... Sjo disappears with ginger-haired Danarella in one of the rooms, while Quint visits with his favorite Vudran girl, Yuuna, and Puk meets the cute halfling Reena. The rogue is so overwhelmed by this new experience that he forgets to ask about the ambassador, but Sjo and Quint pick up that the Chelaxian prefers the twin sisters Lani and Leni.\\

Later in the evening the three friends pay Lani a drink. When they inform about the ambassador, she lets on that he is a client, but she is reluctant to share what happens between the sheets. Quint's smooth talking finally gets her to admit that Amprei never sleeps with her and her sister at the same time, but always with just one of them. During his climax he addresses them as "Vera", as if the girls remind him of someone by that name. Quint wonders if there is a link with Verana Ornelos, a noble born girl from House Ornelos (she is Lord Toff's grand niece).\\

Since the {\itshape Twin Tigers} gambling den is another of Amprei's favorite haunts, the three friends stop over there as well. Quint joins a game, and while winning some money, he learns that the Chelish ambassador occasionally enters the private quarters of Eel's End's big boss, Devargo Barvasi. When the heroes enquire if they can meet with the 'spider king', they are told to return the next day in the afternoon, when Barvasi will be interviewing candidates to join the enforcers that guard his docks. 