%!TEX root = ../crimson_throne_book_main.tex
% 2014-05-26
OK, I've finally caught up with the log. :)\\

Very, very nicely done. This last part with the play was a very interesting change from the adventure. I hope all the players loved it. I didn't see the assassination attempt coming until the end, that was a nice twist... especially since you linked it to a character from the campaign.\\

The motivational speeches of Mercival Jeggare were well-written, did you prepare them ahead of time or improvise?\\

I was also amazed that the PC's sent their money on such a thoughful gift for the queen, instead of keeping it to upgrade their gear. That's unthinkable for most parties!\\

As before, I enjoyed seeing some NPC names from my campaign serving as inspiration for this one. :) Also, your encounter locations look great for the miniatures... I love how you did the courthouse and the Marbledome. It must add a whole level of immersion during the game.\\

It was also fun to read the Hangman's Noose section. Were the players suitably scared while going through it?\\

One thing I noticed in particular was that the fight against Father Kelgaard seemed rather easy. It was almost a TPK when I tried it (the PC's had to flee to survive). Did you nerf him, or did they get lucky, or was being level 3 sufficient to go over that encounter easily?\\

I also noticed that the "intestine" encounter was used for a different character; was it because the "normal" encounter for whom this is supposed to happen seemed to have a good chance of surviving?\\

Anyway - really good work. Looking forward to seeing how this develops.\\

