%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-02
Thanks for the compliments, guys.\\

We set out to do a very roleplay-heavy campaign and this part of the adventure really lends itself perfectly to that. The fact that the players are so pro-active and not acting because Kroft tells them to, is a very nice bonus. The players seem to be a step ahead of the scenario, so I reward their roleplaying and information gathering efforts with the next part of the scenario, thus creating a very natural flow of events.\\

The big terrain set-ups have always been done at my own house. I've brought most of my terrain pieces back home and I take what I need every week to the gaming table. The villa pictures were done a couple of weeks ago and I showed them to my players at the table to give them a better idea of what their new villa looks like. The terrain set-ups we do at the table are not as elaborate, usually just the rooms in which a combat takes place.\\

Having the PCs interact with the 'movers and shakers' is a lot of fun. It really binds them to the city and they have a big influence on what happens. Quint's and Sjo's players are the most active role-players, Balian's player has been absent from time to time, as has Puk's. They both enjoy the game, but take a less active role at the table anyway. Fortunately Quint and Sjo are the best at social interaction on paper as well, being a bard and an oracle, they are charisma-based characters with good social skills.\\

And yes, Moonbeam, your campaign was an inspiration: names and plots will appear from time to time. Thanks again.\\

Tels, since the city taxes everyone, it taxes the heroes as well. There is a flat 10 % tax rate on everything you earn (every month), so gaining several magical items worth maybe 20 000 GP in total and a house which will be estimated at 30 000 GP, will leave them with a 5 000 GP tax debt for this month. They don't have that much cash at the moment, so that will be nice ... I guess that playing an urban campaign comes with some disadvantages.\\

The PCs have their own figurine: Balian, Sjo and Quint were painted specifically for this campaign (as were a lot of NPCs), Puk is playing with an older painted miniature, but he might get a new fig soon. I'm painting a Reaper Bones plastic mini and if I'm happy with that, it will serve as Puk's new mini. Strangely enough it is hard to find a decent two weapon wielding halfling miniature. The Bones fig I'm painting only has one sword, but he's holding his other hand perfectly to attach a second weapon. The only problem is that these plastic Bones versions are slightly less detailed and that shows even better in a small halfling mini. I carry the miniatures in a foam-filled miniature case from Warhammer, which serves its purpose perfectly.\\

To keep the spoiler content in this thread to a minimum, I'll be answering your other questions in a new thread on the {\itshape Curse of the Crimson Throne} boards. 