%!TEX root = ../crimson_throne_book_main.tex
% 2014-04-19
\section{2 Sarenith 4708}

Today the villa is turned into a great practice hall, as Quint and Sjo study their roles and learn their songs, while Puk practices on the drums. Balian has an easier job since his only line in the play is "Fire!"\\

By 4 o'clock the companions swing by the Marbledome, where Diederik Lodann is still being fitted into his costume of Alika's father. The ginger-haired merchant welcomes the heroes of the city and congratulates Quint on landing the part he wanted to play as well, Garamon. The role of Alika's father is substantially smaller, but he is also a nicer character, so Lodann doesn't feel too bad about getting to play him.\\

The seamstress, Delindra, turns out to be a very old elven lady, who is very good at her job. While she skillfully fits Quint, Sjo and Balian into their costumes and even compliments the bard on his elf-like build, Diederik Lodann hangs around a bit longer and offers the companions his services as a merchant. Being heroes they likely need the best and finest equipment available and Lodann boasts he can get them anything they want.\\

Leiny, the shifty assistant, tells the actors they have to be here at 10 o'clock tomorrow. Musicians have to come earlier though, as they start training at 8.30 already.\\

\section{2 Sarenith 4708}

The first day of rehearsals covers the first act of {\itshape The Passion of Saint Alika} . When the actors arrive, the orchestra is already in full swing and the set of Fort Korvosa is partly built. Puk whispers to his friends that Xerxes Jeggare, the conductor, was already late this morning. The costumes are finished, so every actor who is in the first act gets dressed, while the others take a seat. Sjo, who doesn't appear until act four is seated between other people who play Shoanti. He is quite annoyed by Dario Darnas, who is not in act one either. The popular actor turns out to be very haughty and self-centered and constantly shouts out rude comments to the people on stage. Only Aisha Leroung gets nothing but praise from him, although even these words of encouragement are interspersed with sexist subtext. Touran Palastus, the director, lives up to his reputation of being a tyrant, although he obviously knows his trade well. Auralia Lazanne, the vocal coach, is slightly kinder. She has lots of patience with Varric Bedar, who is struggling to get commander Waydon Endrin's song right and reserves her sharper words for the girl who everyone else loves, Aisha Leroung. Quint uses his natural grace to charm Palastus and Lazanne and hits it off well with the lead actress, which gives him confidence for his future performances. Puk also hits the right notes.\\

During the break Xerxes Jeggare looks up the companions again. He has already found a friend in Puk and invites the heroes to the celebration of Charter Day at his uncle's Museum tonight. The high society of Korvosa will be present there to remember the 303th anniversary of emperor Halleck IV of Cheliax signing a charter which led to the founding of Korvosa. The musical genius also offers to give Sjo and Quint extra singing lessons, which he starts immediately after rehearsals, although he does insist on a couple of drinks first.\\

Meanwhile Balian arranges for a horse and driver, so they can use ambassador Amprei's beautiful coach - which is still in the stables of the villa - to arrive at the museum in style. The celebration turns out to be quite the red-carpet event, with Korvosa's jet set in attendance.\\

