%!TEX root = ../crimson_throne_book_main.tex
% 2014-11-15
High priestess Keppira d'Bear is pleased to see Cedrik is safe and is sighs when he tell her what happened. She offers the companions her full support in their efforts to fight the plague, provided they get her help for a number of more mundane tasks. She also wishes them luck trying to convince the churches of Abadar and Asmodeus to join the 'medic task force'.\\

The Grand Vault of Abadar is composed of well-kept grey-veined white marble walls with gleaming bronze friezes, all of which radiantly reflect the light of the sun. The structure towers over surrounding buildings and, along with its steep stairs and ramps leading up to the temple's great bronze doors, boasts an aura of divine luxuriance. Today however, the great stairs do not exhume an aura of grandeur, but rather of chaos. Dozens of desperate civilians - mostly of the working class - throng the entry, scarcely being held back by a group of gold-armored guards. Puk sees one man dressed in fine silks pushing through the pock-scarred crowd. To all everyone's dismay, this rich man is allowed inside. The protectors at the gate are heavily pressed by the angered bystanders when Quint speaks out to calm everyone down. He urges the sick to return home, so they can rest and get better instead of tiring themselves here and infected even more fellow citizens while they're at it. He promises them to talk to the Archbanker and work out an arrangement so they can be helped. After the crowd disperses the guards let the companions in.\\

Archbanker Tuttle welcomes his guests and can be convinced that he will serve order and civilization better by joining in an organized effort to fight the plague. Unlike the churches of Pharasma and Sarenrae, he is not looking for extra hands to help out in his temple, on the contrary, he does not want strangers running around his Bank. So he will help, but at another location. He agrees to meet with the representatives of the other churches tomorrow and already feels like he should be the one to be the overall coordinator. If the companions want to appeal to the general public to help, they might just as well ask for donations, which would serve the Bank of Abadar better than 'helping hands'. Despite his willingness to join in the medic force, Tuttle will keep back some spells for his own followers, he says. After all, if they are sick, they deserve to be treated just as much as everyone else!\\

The church of Asmodeus is one of the most magnificent buildings in the city, built from red marble in the shape of a five-pointed star, and situated upon Citadel Crest in the wealthiest ward of the city. The church competes with Abadar for the right to verify and witness oaths and contracts. Since his initial error in judgement - when he sacrifices thirteen maidens to his deity - high priest Ornher Reebs has taken great pains to operate on the right side of the law. Despite this focus on its lawful nature, many Korvosans see the church of Asmodeus as an evil entity in the city and carry a deep mistrust for the infernal religion.\\

Unlike the other temples the church of Asmodeus is not overrun with people. The sturdy bodyguard Mallas summons his master and hangs around to keep an eye on things while his superior talks to the companions. Ornher Reebs is not happy to see Sjo, who attempted a short apprenticeship in the temple, before turning his back on it. To Reebs that kind of cowardly behavior smells like breach of contract. Quint plays the 'pride' card when he says that all the other churches have agreed to help out, so it would be a 'shame' if Asmodeus would not join in. Reebs wants to know how much the Bank of Abadar is being paid for its help and when he learns that the companions plan to raise money through donations, he demands half of the proceeds. He also wants the companions to communicate about his church's involvement in a positive light, so more people in the city might grow to appreciate his faith. He even draws up a contract stipulating the exact lines of his conditions. In return he offers his full array of disease fighting spells, as well as the couple of useful spells that his subordinate Tyresha can cast. He knows that there are only two priest in his church who can cast {\itshape remove disease} , but the weight of one high priest easily overshadows a dozen low level clerics. Reebs is the third most powerful priest in the city, so the companions will need his help. Quint and Sjo realize that the man is right: high priests can ask their god for many  {\itshape remove disease} spells when they fill all their higher level slots with this power as well. Moreover, the chance at success depends on how powerful the caster is, so Reebs would certainly add value to the task force. The negotiators agree and put their signature plus a drop of their blood at the bottom the contract that Ornher Reebs draws up. 