%!TEX root = ../crimson_throne_book_main.tex
% 2014-06-14
The throne room has been filled to the brim with tables. The companions are seated with the 'children' of the Jeggare and Leroung family. Vencarlo Orisini is at their table as well and Puk and Balian notice the famous sword fighter is missing two fingers from his right hand. He turns out to be a very charming and chatty man. At the start of the banquet the guests offer all kinds of gifts to the new queen, mostly jewelry, gems, perfumes, expensive fabrics and pieces of art. Her majesty seems quite taken when Quint presents their plaque with the pseudodragon token that allows her to summon the bard and his friends when she needs their help.\\

During the meal one of the Leroung children says that the king's murderer has been caught, but our friends are quick to explain that the person arrested is just a {\itshape suspect} . She's innocent until proven guilty. Vencarlo also remarks that there is no representative from Cheliax at this coronation. The ambassador left town a few weeks ago for health reasons and no replacement has arrived yet. Moreover, Cheliax has never recognized the Korvosan monarchy, although it hasn't condemned it either. Maybe Ileosa will succeed in making Cheliax accept Korvosa as an ally, rather than a forgotten province, he muses. After the main course Puk and Balian pick up the sound of hooves on stone coming from the hallway. A heavily armored horse strides into the throne room with a female rider on its back, clad in full plate but missing the helmet. It is Sabina Merrin, the head of the Gray Maidens. Her mount stops in the middle of the hall and rears, while Sabina shouts:\\

"If any person here present, high or low born, denies our new monarch her sovereignty, disputes her right to rule or questions her righteousness, here is her champion, who says that he lies! Let this false traitor rise and cross blades with me, for his words are untrue and I shall disprove them myself!"\\

Merrin throws her glove on the ground and meets the gaze of everyone in the crowd. No one accepts the challenge and Quint breaks the tension by shouting: "Bravo! Hail to the Queen's Champion!" He explains that this challenge fits in an old Chelish tradition, where the new ruler's champion gives adversaries the opportunity to make their own claims. The fact that no one reacted actually enforces the new queen's legitimacy.\\

When the fine dining is finally over the party moves to the stage hall, a large room with a theatrical wooden platform. The ceiling of this hall is open to reveal the balustrade of a balcony and the interior of a lantern dome some sixty feet above. A colonnade along the room's perimeter supports the balcony. Aisha Leroung expresses her hope that the Queen will give a performance, as she is rumored to be an accomplished harpist. The young opera star takes to the stage herself, as do other artists like Auralia Lazanne, the Chelish diva, or Xerxes Jeggare, who invites Puk to join him on the drums. Quint also sings a song with a humorous undertone mocking devils, and in the process offends the highpriest of Asmodeus, who is among the guests as well.\\

Unfortunately Queen Ileosa does not perform, but her champion seeks the spotlight again by climbing the stage. She takes a deep bow and says: "I have never been a woman of many words, but on this special night I have something to tell you. All of you know me as Sabina Merrin, the queen's personal guard. First of all, I wish to congratulate her majesty. I am confident she will rule  us well. When she arrived here five years ago and married King Eodred, she was given ten bodyguards. I was one of them. Our numbers have grown since that day, but now that queen Ileosa is no longer the queen-spouse, but the queen-ruler, she needs more than a security detail. So ladies and gentlemen, I give you THE NEW GRAY MAIDENS!"\\

At that moment the balconies above suddenly fill with row upon row of armored women. They greet their queen by beating their swords on their shields. There must be about 200 of them. Most people in the room seem surprised at their number, even Cressida Kroft. The Field Marshal confirms that about 40 soldiers left the Korvosan Guard to join the Maidens, but that does not account for this military force at all. She wonders if more warriors were recruited from Cheliax, while someone else even suggests that it might just be a bunch of girls who have been dressed up as Gray Maidens to underline the Queen's  power.\\

Quint seizes the opportunity to dance with as many girls as possible, while Sjo concentrates solely on the beautiful Larella Semyr. He is quite the charmer tonight and the priestess of Shelyn is not insensitive to his affection. Puk and Balian have more eyes for the food and wine.\\

At one point during the evening, the companions see how Marcus Endrin and Cressida Kroft are having a discussion. When Quint asks the Field Marshal about it during a dance, she says that Marcus Endrin insisted on speaking to Trinia Sabor. Being the commander of the Sable Company, Endrin does not believe the girl is guilty of killing the king. After all, the painter was hired by Neolandus Kalepopolis. The seneschal was a wise man, Endrin served with him before he was elected to represent the Sable Company in Castle Korvosa. He would never have hired anyone without doing a thorough background check. Not only that, Kalepopolis was very familiar with the Korvosan art scene, so his choice would have been well considered. Kroft denied Endrin his request, though. She does not wish to raise more doubts about the Guard's integrity. There have already been too many stories of corrupt guards lately. One of her own men is even involved in the whole Trinia affair, so Kroft did not judge it wise to bend the rules again and allow someone in to see the suspect who has nothing to do with the case or the investigation.\\

The party lasts until late at night. By the time the companions head home, they are quite satisfied, having enjoyed the finest food, excellent wine, top class entertainment and marvelous company. How far they have come, it was only a few years ago that they were suffering under Lamm's harsh rule, scouring the streets for opportunities to rob people or make a {\itshape dis} honest buck. Now they dine and dance with Korvosa's finest and are regular guests at the castle. 