%!TEX root = ../crimson_throne_book_main.tex
% 2014-08-09
\section{Sarenith 4708}

While Jasan takes his guests around the ranch to select his best mounts, a simple farmer woman stumbles onto the porch of his house. She looks desperate. Jasan hurries over, explaining she is his neighbor Mia, and inquires what is wrong. Mia falls into his broad arms crying and sobs that her husband Barold and her boys did not return from the field last night and are nowhere to be found. Jasan asks his wife to see to Mia and happily accepts the companions' offer to join him to Barold's farm. Trinia wants to come as well, but no one feels comfortable exposing her to potential danger, so she has to stay at the ranch.\\

Jasan leads his new allies to his neighbor's place, some fifteen minutes away. The farmhouse is much more modest than Blackbird Ranch, but still looks like a decent dwelling. Jasan has a quick peek around and then heads to a field down the path. "It seems like they were working the northern field", he states as he takes the companions further. While he gets off his horse to check for tracks, Puk notices a throwing spear in a nearby tree. When they move in to examine it, the companions find an unconscious man with a bloody wound to the head in the bushes. It is Barold, Jasan's neighbor. After he has received some healing, he explains that he and his two sons were surprised by four mean-looking bugbears last night. They knocked him out and left him for dead, but there is no trace of Vern and Sender, his sons, or Bianca, his cow. Jasan orders his horse to take Barold to the ranch and continues on foot, following the tracks of the bugbears into the wood, who obviously made no effort to hide their footprints.\\

After two hours the adventurers happen upon an open spot in the forest, backed by a rocky outcropping with a cavelike entrance. Barold whispers it is an old Shoanti tumulus, from back when the barbarians still roamed the lush lowlands and buried their dead in hillside graves, a custom they have long since abandoned as the inhospitable Cinderlands are more suited for burning the deceased than burying them.\\

Puk scouts ahead and spots four bugbears around a campfire in front of the tumulus entrance. A cow is tied to a tree off to the right. The companions waste no time and take the feral brutes by surprise. Puk and Balian charge the creature to the right, inflicting bloody cuts, but he still stands and returns the favor by viciously clubbing Balian with his morningstar. Sjo picks out the biggest warrior, who is wielding a morningstar in his right hand and a light hammer in his left, and casts {\itshape hold person} on him, freezing him in place. Then the Shoanti moves in to engage the left bugbear. Quint demoralizes the opponents with his  {\itshape satire} while Jasan peppers the creatures with his arrows. The wounded beast facing Balian is felled with one more mighty blow and the two other bugbears get beaten, bitten and shot from various angles while getting in only minor hits themselves. As they both sink to the ground dead, their leader snaps out of his paralysis and opts for the safety of the tumulus. Despite his hulking build he is no fool, realizing that facing five opponents out in the open spells certain death. 