%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-01
\section{26 Desnus 4708}

The next morning the companions finally get their second audience at Castle Korvosa they have been hoping for. Before they leave they wonder what they should talk about with the queen. Opening up the gates so trade can resume and food can get back into the city is definitely a priority. Quint also wants the Hellknights out of the city, as those narrow-minded fools cause more problems than they solve. As far as increasing the popularity of the queen is concerned, 'bread and games' are a sound concept. Maybe there should be some kind of official coronation with festivities.\\

A knock at the door pulls the young friends out of their brainstorm. A Korvosan guard is waiting outside. The shape of the soldier's armor betrays that she is of the female sex. As she takes off her helmet, the heroes immediately recognize Amarice, the woman who was in Lamm's lambs with them when they were children.\\

"Good morning," she says, 'I'm here to officially remind you of your appointment with the queen at ten o'clock. Meeting her majesty ... that's a great honor! You've been doing a fabulous job for our city, I've been told. Preventing riots, arresting deserters and what not? You even helped out my dear colleague Grau when he was down. I guess the city and the queen owe your their gratitude. Not bad for three little lambs ... I see Lamm's cruel upbringing didn't spoil your true hearts, it even strengthened them." Amarice looks a bit self-conscious before continuing: "Anyway, enough with the big words, I also sought you out to ask for a personal favor. You remember when we were kids and we witnessed King Eodred showing off his new bride to Korvosa. The Field Marshal presented Ileosa with her own private guard, the Gray Maidens. We were only a few yards away, as you recall. Well, ever since then it has been my dream to serve her majesty as one of her Maidens. I wonder if you'd be willing to put in a good word for me ... please." Amarice holds her head slightly slanted and bats her long eyelashes. "For old times' sake ..." Sjo is open to Amarice's request, but tells her that they have more urgent matters to discuss with her majesty, so he can't make any promises. Still, he'll see what he can do.\\

At the castle the companions walk in on a familiar scene: in the entrance hall they meet the impatient and nagging man in impeccable clothes again, ambassador Amprei. He looks as haughty as ever and immediately starts ranting as the company comes in: "By all the gods, good and evil, what is wrong with this stupid, boorish dump? You maggots are here again while I'm wearing a hole through the floor, being made to wait like ...uch ... a servant? An outrage!"\\

At the same moment Sabina Merrin steps in and interferes: "You'll be right up, mister ambassador ... thanks to these heroes no less. Enjoy the peace and quiet, while you can!" Then she welcomes the companions and escorts them to the throne room. Seated on the crimson chair of power is Ileosa, dressed in black. The only ornament she is wearing is her father's brooch. Despite her sober outfit she still looks gorgeous. Field Marshal Cressida Kroft is already in there with the queen.\\

"Your majesty," she bows, " these are the heroes I've been telling you about." Quint kneels and his friends quickly follow his example. Ileosa lifts her black veil as her sweet voice resounds through the great hall: "Noble heroes of Korvosa, you have my thanks ... again", the queen smiles radiantly. "This time you do not only prove a favor to me, but to the entire city of Korvosa. If I'm to believe the Field Marshal, you singlehandedly prevented a bloody manifestation and took out several agitators who were plotting against me. But worst of all is this low-life Amprei who thinks that he can turn my own people against me! The traitor! Fortunately you've provided me with the prefect weapon to get him out without burning our bridges to Cheliax." Ileosa's hands shake as she holds up the two compromising letters from Verania Tvastiox.\\

"But first things first. I would like to reward you for your services to the city." Ileosa rises and approaches the companions. Sabina Merrin steps forward as well, presenting a small box to the queen. Ileosa opens the lid and takes something from inside. "Quintilian of Korvosa, Sjo the great, Balian the bold and Puk of the small-folk, for services provided to the city of Korvosa I hereby proclaim you honorary members of the Order of the Pseudodragons." She hangs a medal around each of the four men's necks. The gleaming medallion portrays a tiny dragon in flight.\\

"And now we must see to more pressing matters, the unfortunate case of ambassador Amprei. I would like you to bear witness to the fruit of your good deeds, although I must ask you not to interrupt. This is between Amprei and me!"\\

Sabina Merrin leaves the hall and returns a few moments later with the Chelish ambassador. "Your majesty! Finally I get to see you! You won't believe how long I've had to wait. Truly, a disgrace! I've been waiting here from well before your husband passed away ... for which I offer my condolences, by the way. But now to more urgent matters ..."\\

"Indeed, there are other matters we need to discuss!" the Queen bellows. "Time for each of us to learn their rightful place!"\\

"And that starts on your knees, KNEEL!" Sabina Merrin hisses as she forces the surprised Chelaxian to the ground.\\

"Your Highness! Now you can witness firsthand what I have to go through in this hellhole. You come from beautiful Cheliax, just as I do. These primitives don't know the meaning of the word {\itshape manners} ", Amprei grunts as he tries to rise, but Sabina Merrin clutches his shoulder and keeps him down. "Primitives, you say?" I see only one primitive here, even though the term sounds too kind for you. A worm, a conniving lowlife ... that is what you are!" Ileosa spits out.\\

"But, your majesty, please, I do not understand ..."\\

"What is it that you don't understand? That I'm on to you and your cowardly plans? Do you take me for a fool? Because I'm a woman, perhaps? Do you deny your ambitions to buy up buildings and lands in this 'hellhole', as you so condescendingly call it?" the queen rages.\\

"What do you mean? I've never bought anything here, except for my villa ..." Amprei stammers.\\

"Of course you haven't bought anything yet! Everything is still too expensive. Allow chaos and disorder to run wild in the streets a little while longer ... and then our little ambassador will open his wallet to save the poor citizens by purchasing their properties for next to nothing. Why would you buy today what you can get for half the price tomorrow? Oh, don't get me started on the likes of you!" Ileosa counters.\\

"Ileosa Arvanxi, I have to warn you, when her Infernal Majestrix learns of how you're treating me ..." the ambassador attempts, while he slips from Merrin's hold and rises to his feet.\\

"I think her Infernal Majestrix would rather know how you are treating her cousin's wife, Verania Tvastiox," the queen retorts, "who likes to please you with every hole of her body!" Ileosa pulls out the two letters the companions gave her and stares down Amprei, who pales and is left lost for words.\\

"Oh no, what's this? Don't know what to say anymore? You can count your blessing that you are here as the official ambassador to Cheliax, or I'd have you quartered and beheaded for such an offence! Here's what you are going to do, Darvayne Gios Amprei! You're going to resign your post and get the hell out of this city forthwith! Let's call it {\itshape health issues} , because if you stay for even one more day, your health will most certainly be at risk! Even this far-away hellhole won't protect you from the ire of Agmanar Thrune when he gets a hold of his wife's letters! And that piece of property you already own here in Korvosa, you'll sign it over ... well to Korvosans who truly deserve it, these brave heroes!" Ileosa gestures. Amprei is shaking in his shoes while the companions are dumbstruck by this sudden turn of events. The Chelaxian throws the heroes a venomous glance and turns around. Then he walks out without speaking another word.\\

"That takes care of business", the queen smiles as she straightens her dress and reclaims her throne. "As far as you are concerned, my loyal citizens, I could use your help again. The unsettling first week of my rule as queen of Korvosa has not been a success. Time for mourning the king is over, however. It is time I prove to Korvosa once and for all that I'm capable of ruling her and that I can restore order. In two days time I'm calling the great council to the palace. I would like for the four of you to be present as well, so you can report on what you've witnessed in the streets. I don't have to remind you that we cannot discuss the Chelish ambassador, as we do not want to lose our hold over him by exposing his dirty laundry. But you can inform the council of all the other things you've discovered. Furthermore, I'd appreciate any ideas you have to offer to improve the image of the Korvosan government in general and my person in particular. Can I count on you?"\\

"It will be our pleasure, your majesty", Quint replies.\\

"Then I will see you in two days. We'll convene at eight in the evening. And you, Field Marshal Kroft, are expected as well"; the queen concludes.\\

"I'll be there, your majesty", Kroft replies. She bows and signals for the companions to follow her out.\\

As they step into the open air again, Cressida beams with pride: "Congratulations! You've made quite an impression on the queen, Order of the Pseudodragons, a villa in the finest district of the city and an invitation to the council, alongside the high and mighty of Korvosa. Not bad, not bad at all."\\

Back in Zellara's parlor the companions examine their medallions. The amulets carry magic that slightly hardens their wearers' skin, making them harder to hit. A precious gift.\\

In the evening Quint and Sjo spread the word in various inns and alehouses that the great council will gather in two days. Apparently the government is getting ready to take control again. They also find out that the common people of Korvosa are mostly interested in getting fed and feeling safe. Others also add that they would like to get back to work. Quint will make sure to mention this at the council.\\

\section{27 Desnus 4708}

Two Gray Maiden show up at our friends' place to guide them to their new home, Amprei's villa. Sjo tells the three kids, Mouse, Heldrin and Korwick, to remain in Zellara's shop while he and his friends go and check out the new place. The kids are very disappointed, but their sad faces and teary eyes cannot convince the Shoanti to let them come.\\

While walking to South Shore, Balian suddenly gets a broad smile across his face, but his mates cannot get him to tell them why he's smiling. When they arrive on the villa's doorstep, the urban ranger grins again, as he signals the three kids closer who have been following them secretly. The children are beaming with enthusiasm as the double doors open and the magnificent edifice lays before them. The Gray Maidens hand Quint the deed to the place and take their leave.\\

The building looks mostly intact, as Amprei only got time to pack his personal items. His clothes and papers are missing, but all the furniture is still in place. The villa also includes a large walled garden and a coach house with stables. There are no horses anymore, but there still is dashing carriage. The companions are overwhelmed by the beauty and luxury of their new home, but decide to get settled in nonetheless. They spend the rest of the day moving in their meager possessions and waiting for a locksmith to replace the lock on the front doors.\\

