%!TEX root = ../crimson_throne_book_main.tex
% 2014-03-08
The companions decide to continue their search; with some luck they will run into the missing blacksmith on the way. Their next stop is the gallows. When they enter this cold and gloomy room with its large instrument of death, Puk's eyes turn white as a new vision washes over him. He finds himself swinging from the end of a rope again. Most of the onlookers are laughing and cheering as he is desperately trying to draw breath, others seem sad or shocked, but only one man has a satisfied, almost relieved look on his face. He is a handsome fellow with blond locks and piercing blue eyes. His fingers run across a fresh, thin scar on his lower left cheek. The halfling shares his new insight with his friends, wondering who the blond-haired person is. Could it be the cleric of Sarenrae who entered the courthouse one year after Mord's death and who never came out? He was said to be good-looking and cradled a burst of golden manes. Still, if he had anything to do with Mord's murder, why hadn't the curse ended when he perished nine years ago? Zenobia Zenderholm cannot really place the blond man either, so his identity remains a mystery for now.\\

Zenobia leads her protectors to another room which she identifies as the executioner's preparation room. Mord used to come here to ready himself before delivering justice. The windowless chamber only contains a small table, a stool and a chest. A black hood hangs from a hook on the wall, a length of rope coiled on the floor beneath. The chest holds an unopened bottle of Chelaxian Daemon-Spirit, which is just over 25 years old. The strong whiskey must be worth at least 150 gold sails, Balian says.\\

The far corner of the courthouse holds the cell block. In the lane between the cells lies a headless skeleton, obviously all that remains of the wizardess Sashrala. This time it is Sjo's turn to go through another flash back. Again he holds Sashrala's severed head in his blood-covered hands. He notices a shadow on the wall and suddenly feels a cold hand grasping his throat. Its iron fingers start crushing his neck. White spots dance before his eyes and then everything goes black before the Shoanti returns to the present. As he tries to shake off the disturbing aftereffects of this unnerving mind trip, Balian and Quint discover Hal in the last prison cell. The burly man is sitting on the floor, gently rocking to and fro with his back to the onlookers. In front of him is the jar that held his toes, its fluid spilled over the floor. Gazing over his shoulder they are horrified to see he has tried to reattach his pickled toes to his foot. The rot from his putrefied digits has already spread over his stomp. When he turns around the real horror becomes clear: the blacksmith has turned into a gangrenous ghoul. He sinks his teeth into Balian's neck, but the ranger fights off the paralyzing effect of this bite and chops his greatsword in the undead's body in return. Puk quickly finishes the job with his flashing short swords\\

The cell opposite Hal's turns out to the brig where Mord spent his final days. The executioner used a piece of rock to scratch a message in the wall: "I served as an angel of death my entire life. I shall have my own justice, even if it be in death. Sveth, my only friend, you will find this when you clean the cell. You are my avenging angel now. Bring these liars and fools back to me after I swing, so that I may have my peace. Ten years to the day, then they will pay. When the true murderer of my beloved Malene and my boy Gabe swings from the gallows as I did, on the tenth anniversary of my hanging, then at long last I shall be free. J.M."\\

Zenobia identifies Sveth as the son of the cleaning lady who served in the courthouse. The young man was indeed friends with Mord and his family. Quint connects the dots and says it is probably this Sveth guy who jumped lady Zenderholm in the streets of Korvosa and gave her the message to come here tonight. The judge nods in agreement.\\

One more room remains in this part of the building, the torture room. Brutal machines to coax confessions from the accused fill this mournful chamber. A flaying rack rests against the far wall, an iron maiden stands in one corner. Next to it sits a restraining chair adorned with all manner of crushing vices and punishing screws. Suddenly the spirit of a small boy rushes out of thin air, trying to push Sjo into the chair, but when his attempt fails the translucent figure disappears again, leaving no proof of his existence. Using a {\itshape detect magic} spell Quint sees a faint outline of magic appearing through the cracks of the iron maiden. As Sjo pulls free the lid he stands eye to eye with the dried corpse of Kelgaard, the blond priest of Sarenrae who was one of the adventurers that invaded the place one year after Mord's death. The undead horror emerges and uses his paralyzing touch to freeze the Shoanti in place while tearing through his flesh. Balian and Puk jump to the rescue and make short work of the former priest of Sarenrae. He drops to the floor with a loud bang as the weight of his full plate hits the stone tiles. The magic Quint saw a few moments earlier seems to emanate from this piece of armor. Sjo wipes it clean of the worst muck and sees the chest is decorated with a radiant image of the sun goddess. Quint cleans the armor properly with a  {\itshape prestidigitation} , allowing Sjo to admire the true beauty of this full plate. Although the Shoanti's free spirit was too fierce to be tamed by the lore of just one god, he does feel a close connection to the Dawnflower and her power over fire, so he is proud to don the armor that bears her resemblance. 