%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-08
\section{30 Desnus 4708}

Another rainy day keeps the companions locked in their villa, until they are summoned to the Citadel. Field Marshal Cressida Kroft informs them that supreme judge Zenobia Zenderholm was attacked in the streets yesterday. Fortunately for her a patrol of the Guard was nearby and chased away the assailant. It is unclear who the aggressor was. Was he a chance mugger? Was his attack related to the unrest in the city or was the man a criminal out for revenge? The hanging judge has made a lot of enemies over the years, so the last possibility seems most likely.\\

Anyway, Kroft insisted that lady Zenderholm be protected, but the judge only agreed to that when the Field Marshal promised her to enlist the help of Korvosa's new heroes, as she seemed to like the young men. They must have made a good impression on her. Sjo jumps to the task and leads his friends to the Longacre Building, where the judge is still hard at work.\\

Zenobia Zenderholm welcomes the companions and immediately clarifies that she didn't tell Kroft the whole truth:\\

"An unknown assailant did jump me in the streets yesterday, that's true, and some soldiers of the Guard saw what was happening and came to my aid. They thought the man was trying to kill me, but I'm quite confident that wasn't the case. You see, my attacker was carrying no weapon and only whispered something in my ear before running off. If I wanted to know what had happened to my friend {\itshape Jarbin Mord} I'd have to go to the old courthouse tonight. I don't know if you've ever heard of Jarbin Mord; he used to be the groundskeeper and executioner at the old courthouse. He was convicted ten years ago to the day for hewing his lovely wife and six-year-old son to pieces in their attic apartment above the courthouse with his executioner's axe. I was a public prosecutor in those days and I was friends with the executioner and his family. Jarbin Mord was not a handsome man by any definition of the word, although his wife Malene was absolutely ravishing. Many wondered what she saw in her droopy-eyed husband, but knowing Mord myself, I see why she chose him, because he had a heart of gold.\\

I fear that his last execution, the hanging of the {\itshape Key-Lock Killer} , somehow took its toll on him. This serial killer haunted Korvosa from 4692 to 4697, butchering 38 women in the confines of their own room while their doors were locked. Every time it looked like the murderer had come in through the keyhole, but when he was finally caught in 4698, we found out that he owned a magical device to open and close doors. I was the one to prosecute him and of course Mord hanged him. The Key-Lock Killer was completely mad ... maybe he cursed his executioner with his dying breath, because the Mord I knew would never have harmed his wife. Tonight I hope to find out what really transpired a decade ago. Mord's case was the last one to be tried in the old courthouse. The day after his execution the building, which loomed over the cliffs of the Heights, became instable as the ground underneath started to shift. The entire edifice was declared a safety hazard and abandoned. To prevent innocents from entering, its doors were boarded up and its windows nailed shut. Ever since it became known as a haunted house. People say that the old wood constantly creaks, even on windless nights, or claim to have caught a glimpse of a pale form inside. Others claim they still hear Jarbin Mord rasping through his crushed throat - the sound of breath pushed over bone and rot, a miserable inhuman echo of life."\\

"They call him the {\itshape Croaker} , don't they?" Quint interjects. Zenderholm nods. "You remember that bastard gnome who worked for Gaedran Lamm," Quint goes on, "Hookshanks Gruller. He loved humming this stupid nursery rhyme: On Croaker day, on Croaker day   On Croaker day, on Croaker day   This song is about Jarbin Mord, then. The horror story even continued one year later, if I recall correctly", Quint muzes. "Some heroes ventured into the building and were all killed, weren't they?"\\

"Indeed," Zenobia confirms. "Father Kelgaard, a famed cleric of Sarenrae, led a band of adventurers into the moldering courthouse. Seeking glory and hoping to prove that they were Korvosa's greatest heroes, they tried to banish the restless soul of Jarbin Mord to the Abyss. They were quite famous at the time: young girls used to swoon over Kelgaard's blond locks and crystal blue eyes, captain Grisdom Twin-axe was a favorite among the men of the Guard and nobles lauded one of their favored scions, the highborn wizard Sashrala Ornelos. The best loved of Korvosa marched into the Heights courthouse at sundown on the first anniversary of Mord's hanging.\\

At dawn the next day only Grisdom Twin-axe emerged. Blind, his eyes hulled from his face, the guard captain cradled Sashrala's decapitated head as a lantern, a lit candle inside her silently screaming mouth. The man had gone completely insane. No one has crossed the building's threshold since.\\

I don't want to force anyone to join me, but I will be going to the old courthouse tonight. I want to understand what happened to my friend and I'm hoping to find some answers there. I don't believe in ghosts, but I've seen some horrible things in my career, so I'm not quite sure what to expect. I'd appreciate the company, but I'd certainly understand if you don't dare to join me ..."\\

"You can count on us, lady Zenderholm", Sjo assures the judge. "We'll stand by you."\\

Zenobia Zenderholm locks up her office and puts on a cloak. "Let's go then, and let's hope we have more luck than Kelgaard and his friends."\\

