%!TEX root = ../crimson_throne_book_main.tex
% 2014-11-01
Evening has already started when the companions leave Meep Gildenglare's shop. Since they haven't eaten anything yet, they head to Eel's End for a quick meal and some entertainment. Sjo swings by Shelyn's temple first, to see if Larella is there now and when he finds her there he asks her to join him. He is a bit embarrassed when one of the girls of pleasure waves at him while he leads his date across the docks of Eel's End. It is the redheaded girl who helped him lose his virginity.\\

The boats of Eel's End are open for business as usual and there is little sign of the plague here, although there are considerably less visitors. Quint spends some time in the brothel in the arms of his favorite, Yuuna, feeling even more enticed by her Vudran heritage than before since that other dark skinned beauty Selena has been eluding him. According to Balian the two girls look quite alike, although Selena possesses a more natural flair. Quint also inquires about the ship that sunk in the harbor. Yuuna didn't see it herself, but some of her colleagues witnessed the burning ship go down further up the river a few nights ago. News of the queen's physicians hasn't reached the House of Clouds yet. Yuuna explains that Old Korvosa is usually the last district to deserve the palace's attention, so it doesn't surprise her that the doctors didn't make it here yet.\\

When our friends finally return home, Korwick tells them that Vencarlo Orisini came by earlier today. He was in the neighborhood as he had to go the temple of Pharasma. Someone died ... although Korwick does not remember who exactly. Anyway, master Orisini had to be in the temple about this guy's funeral, so he decided to stop by, but he went home when he found out the companions were not there, without leaving a message.\\

\section{27 Sarenith 4708}

Sjo feels a bit under the weather that morning and Mouse is doing worse as well. The big man uses his {\itshape lesser restoration} spell to take away the worst of the sickness's effects. He also pays another visit to young Brienna in Trail's End and cares for her too. Then he retires home to his bed to get some rest. Meanwhile his friends go to Vencarlo Orisini. The fencing master's academy is closed today. Quint immediately notices that Vencarlo didn't get much sleep last night. He also smells alcohol on his breath. Vencarlo explains that his loyal servant Raldo passed away yesterday. He got sick with the plague a few days ago and, as he was already advanced in years, quickly succumbed to its devastating effects. When Vencarlo Orisini went to the temple of Pharasma to make arrangements for his servant's burial, he heard that 37 citizens had died already and a lot more people were sick. The mysterious illness that had just popped out of nowhere had taken a choking hold on the city in just a few days time. Old Korvosa and North Point were hit the hardest.\\

Vencarlo worries about the feeble attempts of the city's churches to fight the disease. He feels that they could work much more efficiently if they were to coordinate their efforts. The church of Sarenrae has good intentions, but seems to be overrun, Pharasma is dedicating all her efforts to burying the dead, while Abadar's Bank has even closed its doors to the public, letting in only those who can pay. If the companions want to do something for the city, they should see to it that the temples get organized. Quint and Puk agree wholeheartedly and decide to take action right away.\\

They go to the temple of Sarenrae first, figuring that they'd better start with the one who is most likely to accept. It will be easier to convince the harder cases if you can say that other churches have already consented. Ezekiel Sollux, the highpriest of Sarenrae, is tending to the sick himself when the companions walk into the improvised hospital that his temple has become. When Quint explains his idea of coordinating the churches' efforts better to allow the priests to administer the most healing possible, Sollux agrees. Although he is doing everything within his power to help the sick, he has no clear overview of what his priests are doing, of who they are helping and who not. If there were more people to lend a hand with the simple stuff, like feeding the patients or changing their sheets, the clergy would be free to focus on providing care. Quint asks him who in his temple would be a good representative, someone who can supervise the work within the church and consult with the other faiths, Sollux has just the man for the job: Lord Valdur Bromathan. Although the head of House Bromathan possesses some priestly magic, his powers are limited. He is a good organizer, though, and his age and title give him the necessary authority to carry out the job.\\

The next destination is the church of Pharasma. On the way over there Balian has to shake off a woman who grabs him by the shoulder, screaming that this disease is all an evil wererat plot. The cathedral in the Gray district is also flooded with people, although not many of them look especially sick. Most of the visitors are mourners who have come to make arrangements for the deceased. Archbishop Keppira d'Bear is ashamed to admit that she and many of her priests make it through the day without even spending all the magical healing they are capable of, simple because their work with the dead keeps them so busy. She even has priests digging graves since some of her usual grave diggers have fallen ill or have bolted as they fear getting infected by handling the corpses. As a priest of Pharasma d'Bear does not consider her task of burying the victims of the plague mundane or menial, but she does recognize that healing potential is being wasted. If there were people around to help with the administration, preparing the dead for interment or for digging the graves, that would definitely open up time for her clergy to focus on healing people and saving lives. She suggests making brother Aldrick the church's representative. His high position in the church's ranks earns him a great deal of respect, both inside and outside the cathedral, but being a paladin, his powers to heal are more limited than his priest colleagues.\\

