%!TEX root = ../crimson_throne_book_main.tex
% 2014-04-26
The grand feast in the museum kicks off with Lord Mercival Jeggare welcoming his guests from the grand staircase: "My dear friends, welcome. The last couple of weeks have definitely put us to the test and - as you all know - we're not out of the woods yet. But will we go down with this ship? I tell you NO! Will we allow ourselves to be weakened? I tell you NO! Will we be challenged to rise above ourselves? I tell you YES!\\

For who are we, the people of Korvosa? We're the heirs of a stubborn, persevering and combative lot! Just look around you, despite all the conflicts and challenges from the past we live in a beautiful city.\\

We wouldn't be here if it hadn't been for the crazy idea of one man who decided to tame the wild shores in Varisia. Field Marshal Korvosa was tasked by emperor Halleck IV of Cheliax to colonize the ground on which we stand. The charter that stipulated this mission was signed on the third of Sarenith exactly 304 years ago. This is why we remember this day as the Day of Destiny.\\

And which location could fit the occasion better than a museum dedicated to the history of this glorious city? A history that has tried Korvosans a hundred times over, but also a history that saw our ancestors rise to those challenges and meet them head-on. Each time they triumphed, coming out stronger than before.\\

We too live in hard times, my friends! So let us learn from the past! Let us join hands and face those challenges together! Her majesty, Queen Ileosa, has been tested harder than any of us. But she does not give up! She fights to give her subjects a Korvosa to be proud of. I fight by her side, but what do you do? Can her majesty count on you? Can Korvosa count on you? Then celebrate this day, not as some meaningless holiday, but as a reminder of what being a Korvosan really stands for! Celebrate for Korvosa! Celebrate for Ileosa!\\

Most onlookers burst out: "For Korvosa! for Ileosa!" Still, the cheering is not joined by everyone: commander Marcus Endrin of the Sable Company and his family remain silent.\\

Mercival Jeggare continues: "To repair the trust in our city-state, my friends, the Marbledome organizes an opera in honor of one of our greatest heroes. In just a seven days time you will enjoy {\itshape The Passion of Saint Alika} in this temple of the arts. It will star the rising promise in the world of acting, Miss Aisha Leroung! Ladies and gentlemen, please welcome her to the stage as you get a little preview of this wonderful opera!" Aisha joins Lord Jeggare on the staircase under a thunder of applause. Then the first notes of the aria Aisha practiced earlier today fill the air. The young star brings a very successful version of the song, moving everyone in the audience. When she is finished the room explodes in a tidal wave of applause again, after which the orchestra starts playing a lighter tune and servants supply trays of snacks and drink.\\

