%!TEX root = ../crimson_throne_book_main.tex
% 2014-02-22
Since there is no obvious way out, the companions decide to search the old courthouse. The next door in the great hall leads to the luxurious quarters of a former judge, Rayndros Felgor. There is marble on the walls and a mangy polar bear-skin rug on the floor. Behind an ornate darkwood desk with motifs of cherubs and vipers rests a skeleton in judge's regalia. His white beard still clings to his jaw and falls upon a rusted iron spiked chain which has been twisted around his neck. It looks like the judge was strangled. Zenobia Zenderholm confirms that Felgor disappeared around the time that the old courthouse was abandoned. At the dead lawman's feet is another skeleton, a large dog with a few broken ribs and a cracked skull. The animal bones come to life when Sjo steps into the room, but the undead hound is no match for Balian's blade.\\

Inside the desk are three vials with magical liquid, potions of {\itshape lesser restoration, bear's endurance} and  {\itshape cure moderate wounds} . There is also a note on the table. It reads:  {\itshape Most honorable colleague Zenderholm,}  It is with great remorse that I script this. The chaos of our time has eaten many innocent souls, but this one was lost not to catastrophe, but to an evil deed of injustice. Lies have killed a man this morning and I for my part did nothing to stop it. My esteemed colleague Silman Trabe knowingly sent an innocent man to the gallows, as I stood silently. I only hope that Jarbin Mord's soul may find some rest if the truth comes out.\\

