%!TEX root = ../crimson_throne_book_main.tex
% 2014-04-26
Aisha Leroung suddenly shows up at Quint's side. The lead actress of {\itshape The Passion} is trying to get away from her co-star Dario Darnas, who continually follows in her wake. "Ah, my love, there you are", he whispers. "Listen, they're playing my song, come and dance with me, so we can show these idiots some true talent." "How unfortunate," Aisha sighs, "I just promised Quint here the next dance." She grabs the young bard by the arm and leads him to the dance floor. Dario hangs around Sjo, Balian and Puk and belittles Quint's performance. "Ouch, if this is supposed to promote our show, color me unimpressed. Palastus is right though, amateurs ... Fortunately I'm around to make amends. Still, the damage is done, I'm afraid. Moreover, what is this fool doing with Aisha? Everybody knows that girl is mine!"\\

Meanwhile Aisha is free to vent her irritation: "Brrr, this macho has been hanging on my tail all evening. {\itshape Watch me, Aisha, here I am! I'm so great. Fall at my feet and adore me.} This conceited mannequin thinks he's a god on earth. I'm sorry for dragging you along, but I was at wit's end. I hope you forgive me", she pouts while batting her big emerald eyes. When the dance is only halfway through, Dario tries to step in: "Let me save you both further embarrassment and interrupt this bungling of a dance." Still Quint puts the man to shame with a few sharp remarks, sending the foppish fool running. Dario tries to get back at Quint later in the evening by 'accidentally' spilling his drink on the bard. "Ow, looky here, how clumsy of me ... I'm almost like an amateur on stage. I'm so sorry ... about the delicious wine." Quint confirms Dario's clumsiness publicly and then graciously waves his hands in a {\itshape prestidigitation} to clean up his clothes. Again Dario is left the fool. Meanwhile Sjo has been chatting with Maud Jeggare, Xerxes' sister. As a member of the Jeggare family, she knows her way around the museum. When she learns that Sjo is not really familiar with the Shoanti culture, she takes him to see the Shoanti wing, which houses day-to-day objects and several pieces of jewelry made out of bone and rough gems. Since the Shoanti are first and foremost a race of fighters, she show her guest some typical tools of battle as well, like the {\itshape earthbreaker} , an enormous hammer with blunt spikes, or the  {\itshape klar} , a short blade bound to the skull of a large horned lizard, which can function both as a weapon or a shield. The bola is a throwing weapon, made of three weights on interconnected cords, designed to capture someone by entangling his legs. The Shoanti version of this weapon is not meant to knock someone down, but to injure or even kill. The weights are covered in sharp spikes and they have holes that make them wail when spun overhead. There are also various armors made of animal skin, bones and lizard scales, making them quite light so as to allow for great mobility. The hour is late when the companions finally return to the villa.\\

