%!TEX root = ../crimson_throne_book_main.tex
% 2015-04-03
The companions tie up Lady Andaisin and leave her in the room leading up to the sanctuary, with the green alchemic vats and the dead leukodaemon. Then they return to the cell block - where Rolth, Saulus and Alika are still locked up - letting the boy and girl they rescued earlier know that the priestess and her minions down here are all dead. They drag Rolth's unconscious body to the hall with the huge basin and the catwalks and use a {\itshape cure light wounds} to wake him up. It takes the necromancer a while to realize who About two and a half months ago Doctor Saulus sought him out in his secret den in the graveyard, Rolth confesses. He adds that he no longer uses this hideout as it was discovered during his time away from the city. He is not surprised to learn that the companions were the ones who shut the place down and killed his derro friends. Doctor Saulus - or Devils as he preferred to be called - promised Rolth to help him build his flesh golem if the necromancer took him in and allowed him to use his laboratory. Seeing an opportunity to achieve his life-long ambition, Rolth quickly agreed. When Sjo and Balian tell him that the golem was not nearly as powerful as Rolth believed, since they destroyed it very easily, a twitch of disappointment sweeps over his blotchy face.\\

Quint and Balian have trouble hiding their absolute disgust for their prisoner and tell him that his interrogation will determine whether he gets a quick or a long and painful death. They already butchered all the physicians and cultists in here, and they won't hesitate to give him what he deserves either. Rolth nods and chuckles: {\itshape``You may free Korvosa of the old Rolth, but it looks like there are four new Rolths ready to take his place, just as ruthless and deadly. I guess the city will be even worse off with the four of you \ldots}'' Sjo grabs the necromancer by the head and pushes him in the foul water of the room's central pool. Of course, this kind of torture only proves Rolth's point, who no longer feels inclined to answer the companions' questions if they will just kill him afterwards. Quint argues that the judicial system in Korvosa would only come to the same conclusion and condemn him to be hanged, seeing how he's been wanted by the law for many years. Hanging judge Zenobia Zenderholme is famous for her harsh judgments, so someone with Rolth's record would be judged very quickly.\\

{\itshape``Well, if you're so sure that the judge will hang me, you won't mind handing me over to the law. I'll make you a deal, I'll tell you everything I know if you can guarantee that I will get a fair trial. As you say, I'll die anyway, so it hardly matters to you. Give me your word and I'll tell you, but if you want to kill me here and now, you might as well do it now, for then I won't tell you anything.}'' Quint leaves it up to Balian to decide, being Alika's brother he harbors the deepest grudge. The ranger agrees, but the deal will be off if Rolth tells even the slightest lie, he says.\\

After this promise Rolth continues his confession. He bought the young female lambs from Gaedran Lamm for himself, but gave them to Doctor Saulus when he needed test subjects for his experiments. He took Alika so many years ago and he somehow liked her enough to keep her alive. He did play mind games with her, constantly telling her that her brother Balian had abandoned her and that he was a coward and a traitor. He repeated this over and over until she ended up believing him and voluntarily chose to join him.\\

As far as Saulus is concerned, the doctor looked Rolth up in the month of Gozran because he needed a place to brew a poison. Rolth did not know Saulus before that, but was willing to help out a fellow follower of Urgathoa. Although the doctor never told him what the poison was for, Rolth figured it was for the king. He does not know who Saulus was working for or who collected the poison, though. Then Saulus got a new assignment and asked Rolth to join him in Lost End, where they were joined by Lady Andaisin and her followers. These new allies all came from Cheliax and must have used teleportation magic to get there, though Rolth claims having no knowledge of who transported them. This was where the high priestess of Urgathoa enchanted the avian masks and she and Saulus developed the plague by experimenting on a number of people, including Rolth's girls. The necromancer himself spent most of his days constructing his flesh golem. They finally returned to Korvosa aboard the Delivery, but they abandoned ship and landed their sloops on the shores south of the city, where they set up camp. Rolth sneaked back in to the city, only to discover that his hideout had been compromised and his derro associates killed. He rejoined the Urgathoans and came to the Hospice after they acquired the place. He also claims that the Urgathoans entered the city undercover and somehow got into the castle, where they were supposedly 'teleported' to. This suggests that at least someone in Castle Korvosa was in on the conspiracy.\\

The companions tie up Rolth again and put him back in his cell. First they want to examine the three doors in the hall they used to interrogate Rolth, since they skipped those earlier. Two doors lead to storerooms, one with all kinds of trash and one with supplies. The other door opens into Andaisin's office. Balian finds a chest with a top-notch alchemy set, while Quint and Sjo examine the many books and notes. Puk, who is still blind, has to limit himself to listening if no one else approaches. There seems to be a large collection of volumes from the {\itshape Andoran Alchemical Society} , as well as extended notes on the experiments that Andaisin and Saulus carried out. The scribblings are quite complicated, though, and would definitely require a trained mind to be correctly interpreted. Professor Sirtane Leroung could certainly use these in her quest for a cure. A secret door leads to a bedroom with a very luxurious bed. There is a traveling chest with woman's clothes and a small box which holds some jewelry. Next on the companions' interrogation list is doctor Saulus. They head back to the cell block to get the bastard, but they are stupefied to find out that Alika and Rolth are missing, and Saulus is dead, his throat cut! Stable boy Dalvun and Jaelle, who are both resting in the bedroom that leads to the prison, have seen or heard nothing or no one. Alika's bonds lie on the floor of her cell, as if she slipped out of them. Damn those rogues and their slippery tricks! Balian also discovers two small iron needles, part of a thieves' toolkit, which Alika used to open the locks. Quint finds a lingering aura of {\itshape conjuration} magic in Rolth's prison cell, probably pointing at some kind of teleportation magic. The companions are very disappointed and swear never to make this mistake again. Fortunately, Lady Andaisin is still in their hands, as they kept her in another room. They drag her back into the inner sanctuary, determined to test out what effect the colored basins will have on her. Lady Andaisin, only smiles when threatened with submersion in these waters: {\itshape``Urgathoa is at my side! I've done her proud with my work in this city, so I'll be in her best graces when I cross over to the other side.}'' Sjo grabs the woman by the hair and pushes her face below the waterline of the blue liquid. In the process he gets his own hands wet as well and feels the liquid draining him. In reaction he drops the priestess to the floor, where she starts mocking him. Quint realizes that he and his friends are starting to behave irrationally, as Rolth's words still ring in his ears: {\itshape``four new Rolths ready to take my place}''. Andaisin remains confident that she will be rewarded in the next life, and one of the many pleasures she will be awarded with, will be the power to create undead. She will make sure that the companions' earthly remains will be used in such perversions. Quint gets quite angry with her while she claims she does not know who hired the Red Mantis. And even if she did, she would never tell them. Sjo also tires of her haughty behavior, she has nothing left to tell them, so he just bashes her skull.\\

As morning is fast approaching, the companions head back up to the hospice. They lure the last remaining doctors into the backroom and dispose of them. Next they collect the books and the survivors downstairs and simply walk out of the building, telling the remaining guards and Gray Maidens to check downstairs, leaving them behind dumbstruck. First they head to the university to give the books and notes they found to professor Sirtane Leroung, who is very happy to get this vital information. Next they want to inform the Field Marshal, but for the first time since they've met her, they do not find her at the Citadel, but rather at home. After waking her from her bed, they bring her up to date. Quint gets quite angry with her for allowing her Guard to be used for evil. Aiding the enemy is a grave mistake and in this case, assisting the physicians resulted in many deaths.\\

