%!TEX root = ../crimson_throne_book_main.tex
% 2015-09-13
Sjo's player wrote down his version of the end of the session:\\

The Necromancer just escaped with a dimension door and Sjo - driven by the momentum of his charging attack- lands on the balcony where Mouse is still lying gagged. The healer suppresses his urge to go to the kid to undo his bindings but instead spies the sky in search of Rolth. Where did that filthy piece of s!~\% go? Acting on his instincts Sjo jumps off the balcony and summons his fiery wings to glide down, back to the basement of the belfry tower. Getting more and more confident with his new form of movement the Shoanti takes his time to flutter down while quaffing 2 healing potions before his feet touch the ground.\\

Sjo pushes the doors of the building for the second time and is surprised to see Rolth standing in the big entrance hall. "You filthy piece of Shoanti-s~\#\$" the Necromancer shouts. "Why you just don't die as everybody else?" and 5 missiles shoot from his fingertips targeting the Oracle. Sjo starts to charge towards the necromancer, stoically taking in the missiles without giving a glimpse. Luckily the Shoanti was almost completely healed using his remnant potions.\\

In a final leap Sjo throws his full weight at Rolth and both crash to the ground. The necromancer tries again to escape the clutches of the furious Shoanti by casting a spell which would take him farther away from his nemesis. But this time he is not so lucky and the spell fizzles before it takes effect. Sjo seizes the opportunity to slip his arm around the filthy death-reeking man's neck and starts to strangle him. In his rage he calls out to the domain of Asmodeus to get that all-consuming fire. By setting his own arms ablaze and ever squeezing harder, Rolth only has a couple of feeble attempts left before all the life fades away from his body. While the necromancers' consciousness slips away, Sjo whispers in the dying mans ear: "I sentence you to die Rolth and hope you'll burn in hell for all what you did to us and the kids ..."\\

Even when the body goes limp, Sjo keeps getting on to that burning fire until he's exhausted.\\

---\\

Asmodeus is sitting in audience, listening bored and half-heartedly to the umpteenth dispute about some contract. Suddenly the Prince of Darkness' attention is caught by a little disturbance in one of his domains. Something is pulling fire with that much hate and force that it gets to his attention.\\

Shifting his attention away from this ever-dull audience the Ruler of Hell notices that the power is drawn by some Shoanti warrior in an amusing attempt to fry someone's head.\\

There's something about these two that gets the Dark Lords attention: This Shoanti must be that runaway pupil Reebs keep ranting about in his communes, and the other one... yes, that's the necromancer who - not even a day ago- haggled endlessly about a contract he wanted to sign.\\

The Lord of the Pit is amused with the situation: this filthy worm will fulfill his end of the contract very soon it seems. And the bigger irony is that this Shoanti-runaway is now fulfilling a service to him without even having a clue.\\

Burning his head every day for at least a hundred years seems like a good start to teach this would-be necromancer a little lesson in humbleness. As for this Shoanti-character: might be worth keeping an eye on that one.\\

The Prince of Darkness stand up from his throne - dismissing the audience- with his thoughts full of crispy heads ...\\

