%!TEX root = ../crimson_throne_book_main.tex
% 2015-12-19
Although {\itshape The Flame that Binds} offers a nice array of magical goodies, the party has no real money to spend, so Quint just buys a handful of scrolls and the remainder of the budget goes to some extra  {\itshape wands of cure light wounds} from the local temple of Pharasma. Balian is also curious about the troll prophets in the augur temple and decides to have his fortune read. The temple is a vast and columned affair of stone, with wide steps too tall for a human. Balian sees an ugly troll wrapped in coarse linen clothes. She beckons him over and gestures to a small bowl for a donation. The ranger throws a handful of coins at her and wonders about Korvosa's future, at which the augur draws a knife across her own belly and pulls out her steaming entrails, studying them carefully. Then she speaks: {\itshape``Who beats who in this hodgepodge revue?   When she has finished her prediction, the troll shoves her bowels back inside her abdominal cavity, waiting for her natural regeneration to heal her. Although her words are short and cryptic, they ring true. She does not know the heroes and yet she can tell from her own bloody insides what they are up to \ldots so the augur's abilities must be real! Quint approaches another soothsayer and asks her about their future in the Cinderlands. She replies:\\

{\itshape``No help without trust, no trust without friends, no friends without help.}''\\

After this mystifying experience in the augur temple the companions return to the inn, where Derdra rejoins them. She has news about the Shoanti: apparently the Cinderland tribes are gathering for war on Korvosa, having learned that recent troubles have weakened the city. The biggest of the clans, the Sklar-Quah or Sun clan, leads these war efforts.\\

\section{9 Arodus 4708}

The next morning the party leaves on foot, since Derdra cautions against using horses. She claims that the Cinderlands' treacherous undergrowth and shifting sands will prove too dangerous for inexperienced riders. The first stretch of the trip leads through the most fertile parts of the wastelands, in the proximity of the Yondabakari River where rough grasses and small bushes grow. The further away the party moves from the river, the more desolate the landscape becomes. Since the companions are looking for the Skull clan, Derdra takes them east, to the Kallow Hills, where the Skoan-Quah live. The dry prairie and the beating sun make for a tiring journey. Dusty winds of sand and ashes give everyone a burning throat.\\

In the afternoon a big cloud of dust and a thundering rumble of hooves breaks from the horizon. Derdra explains that it is a great herd of aurochs, big, horned oxen that live here. The animals are dangerous, but make for a great source of food and leather skins for the local tribes. Fortunately the beasts of the prairie do not cross paths with the travelers.\\

In the evening Derdra looks for a good place to set up camp. She gathers some tumbleweed and bushes to make a fire, for nights here get quite cold. During Sjo's shift in the night watch, a group of four large beetles makes straight for the camp. The tall half-Shoanti shouts out to his companions and throws up a {\itshape wall of fire} to halt the vermin's approach, but the creatures seems unaffected by the flames. Quint casts  {\itshape haste} on his friends, who quickly learn that the jewel  beetles are not much of a challenge, but then the bard notices that one of the large insects has a bony spike sticking through its carapace. Suddenly four more of these spikes soar through the air and plant themselves in Derdra and Puk. The attack came from the dark sky above! Quint covers the party in an  {\itshape invisibility sphere} , which gives them the opportunity to heal and grab their ranged weapons. Derdra recognizes the spikes as the weapons of a manticore: a winged lion with a humanoid head. The creature swoops over the camp a couple of times, doing serious damage with its volley of spikes, but Sjo manages to heal these wounds in time. It is hard for the companions to hurt this creature that just flickers in and out of sight to fire off another set of bony arrows. But since the heroes do not appear fazed by its attacks either, the manticore quickly abandons its offensive. The party moves camp, this time without the warmth of a fire, and makes it through the rest of the night unharmed. 