%!TEX root = ../crimson_throne_book_main.tex
% 2015-04-30
Meanwhile at the Castle, Quint has been watching the grand stairs leading up the pyramid. Four Gray Maidens stand guard at its foot. By half past nine the doors of a nearby building, just left of the stairs, open and a strapping young man, about Quint's age, leads out a horse and cart. He seems familiar with the animal and talks to it soothingly while staring up the stairs to a small group of people coming down. A middle-aged woman and a young girl, who looks no older than fifteen, are accompanied by four Maidens. The girl waves vigorously at the young man and allows herself to be helped on the box. She fakes having trouble getting up, so the man has to lift her. She clearly enjoys the attention. The driver also aids the other woman take a seat before he sits down himself and gently urges the horse to move. The four Gray Maiden fall in line behind the wagon and follow it to the east.\\

Quint pursues the wagon from a safe distance to the market. The middle-aged lady buys all kinds of supplies, enough to feed at least  two dozen people easily. The merchants greet her kindly and allow her to cut in line. The goods she requires are already waiting for her and while she pays and specifies what she'll be needing tomorrow, the merchants' helpers load the merchandise in the wagon. The whole process runs very smoothly and Quint sees no opportunity to interfere without raising suspicion. He does learn the woman's name, as the merchants address her as {\itshape Mrs. Karina} . The young girl remains at her side at all times and while they're buying meat, the butcher hands her an extra piece of sausage and calls her  {\itshape Mikki} . The man is obviously charmed by the lass and again she seems to welcome the attention with a warm smile. Quint then decides to try and approach the driver while he's waiting, but the Gray Maidens step up immediately and urge him to move along. Perhaps he'll have better luck at the stables, where at least there are no annoying Maidens around.\\

When the shopping is done, the wagon returns to the castle, where a broad-shouldered, but simple-looking man is already waiting for it to arrive. He picks up a heavy basket and joins the four guards and the two women up the stairs to the castle. The man comes back two times more to carry up the rest. Next the driver takes the wagon back to the stables.\\

In the streets at the foot of the pyramid Quint addresses a woman who also looks like she's just returning from the market. She puts her basket on the ground and reaches for her keys to open the door.\\

"I"m sorry, ma'am, I just noticed a sweet little dog around the corner. It looked well cared for ... white, with a long fur and a face like a fox. It can't have been a stray, but its owner was not around. Maybe it slipped out of the house or something. You wouldn't happen to know who owns such a pet?"\\

"A white dog, you say? Sorry, I can't help you there. No one around here owns such an animal." The woman pushes her door open and reaches for her basket.\\

"Are you okay with the groceries, ma'am? Too bad you don't have a strong man to help you carry your things, like that fellow I just saw on the steps of the castle. He seemed like a friendly chap, though not too bright."\\

"Well, we can't all be queens, can we? That Jorn fellow is indeed somewhat of a simpleton, but he's a good boy. He's been working there for as long as I can remember.\\

"Like part of the furniture?" Quint laughs. "Do you know if they're hiring people up there? I'm actually from Old Korvosa, but ever since the quarantine I've been locked out. I can't go home and I can't do my job. It doesn't look like I'll be able to get back any time soon, so I'll have to find something to earn a living in the meantime."\\

"Oh no, poor boy, here ... have some of my bread."\\

Quint refuses to take the loaf: "That's not what I mean ma'am. I have a few coppers left, I don't need a pittance. My mum didn't raise me to be a beggar. I want to work for my money and make an honest living. Such a big castle always needs people, doesn't it?"\\

"Well, it's mainly women, up there. This Jorn fellow is an exception because he's been there for so long. The men work down here, in the stable with Master Jacob."\\

"Aha, I might give him a try, then. Thanks for the tip, ma'am. I wish you a wonderful day."\\

"That very kind of you, young man. I wish you the same." At that the woman goes inside.\\

Quint keeps an eye on the castle for the rest of the day. At two o'clock two dozen Gray Maidens arrive from the east and go up the stairs. Fifteen minutes later the same number of female warriors comes down again. Four of them relieve the sentries at the foot of the stairs, while the others leave again. Quint follows them over the High Bridge into the East Shore district, at the other side of the river. They enter a walled complex just across the water. So these are the Maidens' barracks, good to know.\\

---\\

Sjo is still working on finding out whether seneschal Kalepopolis is still alive. He decides to check with archbishop Keppira d'Bear herself at the temple of Pharasma to find out if she can help him. She confirms his suspicion that high level priests have an excellent spell for just such a purpose: {\itshape commune} . With this magic she can contact her deity and ask a number of questions that can be answered with a simple yes or no. She is not surprised that brother Cedrik did not know about this spell; he was always better at keeping the books than at weaving magic, as his tragic mishap under the mortuary clearly illustrated. Keppira d'Bear is also the only priest in her church who masters this level of complexity. While she dislikes the fact that she would have to give up a spell that might cure another plague victim, she does agree that Pharasma is the prime authority on life and death. If Sjo can offer some relief for her cure-wasting guilt, she'd be willing to pray for a  {\itshape commune} spell tomorrow. She also explains that he has to prepare his questions carefully. The magic allows her only a short time to ask about a dozen things, wasting these precious seconds to come up with new questions is not an option. Sjo freely offers one of his  {\itshape wands of remove disease} - the one with 11 charges left - to d'Bear as compensation, which she gladly accepts. ---\\

Puk decides to dive into the villa's library. He is quite ambitious, putting one book on top of the other, he wants to make a pile as high as he is and read that! Still, looking at all those books, he realizes that he'd better start with some light reading and takes a small book on halflings in Korvosa. Perfect! Now he can find out which other famous kinsmen were here before him. It turns out that the history of famous halflings still has to be written. The book details how the Leroung family uses ships with halfling crews, who are lighter and take up less space than human sailors, so the ships can carry more goods and turn in a bigger profit. So the chronicles of the smallfolk in the city limit themselves to servants and workers. Even the most 'famous' halfling in Korvosa was once a servant. Old Orkatto, the owner of {\itshape Orkatto's Feathers and Furs} , used to serve a lord in Magnimar as his master of the hunt. The country squire saved his coppers well and retired to Korvosa to set up a shop in exotic pets. His caged wonders go from rainbow-plumed songbirds and snowdust badgers to emerald-back nightbelly boas and even the odd dream spider. Apparently, the shop is in South Shore, quite close to the villa. ---\\

Later that day Balian sneaks off on a private mission. He remembers the Sczarni thugs who attacked him and his friends when they were in Path's End for the first time. Back then his party was no match for these gangsters and needed Grau Soldado's help to escape, but the ranger's skill has grown considerably since that time and now he feels confident that he can handle a little trip to Thief Camp by himself. He does take Spyder along, just in case things come to blows and he needs a flanking partner. His goal is to find the Scarni's {\itshape godfather} , a man called Batista Cadabrani, and enlist his help in tracking down his sister Alika. Being a fellow Varisian, Balian hopes that these Sczarni will agree to sell him their services. After all, the Sczarni are notorious for standing up for Varisian rights and punishing the Chelaxians on their high horses. Located just outside the city walls beyond Dwarfwalk Gate is the shantytown {\itshape Thief Camp} . Balian notices that the poor people here have not been spared from the plague: there are crosses on several doors and a dozen dead rats and people lie by the road, ready to be carried off. Balian spots a few local thugs and approaches them without showing any hesitation: "I want to meet with Batista Cadabrani. Take me to him", he calmly speaks. The biggest gang member mocks the ranger: "And who is this little mouse in a rats' nest? It looks like you need an urgent lesson in humility!"\\

Balian sighs and holds his head at an angle. "I bet I can take you down without even taking my hands out of my pockets", he claims. The man fumes and reaches for his club, but Balian simply whistles for Spyder to jump at the brute. A few breaths later the man is squirming on the ground, bleeding from several bites, begging for mercy. Balian calls off his canine and repeats his request to see Cadabrani.\\

The ranger is guided into one of the bigger stone houses, where an older man is cutting onions at a table. He's wearing a black brimmed hat and his gaunt face sports a shade of gray stubble. Despite the sting of onion in the air his eyes show no sign of tears. "Do you like onion soup, Varisian?" he asks. "It stimulates the bowels. When you get my age, not everything runs as smoothly as you'd like anymore, just like my men in the street. They seem to be having a hard time as well keeping things in hand. Sit down and tell me why you're here."\\

Balian explains that his sister has disappeared and that she was last seen in the company of Rolth the necromancer. Batista concurs that this Rolth character is like an eel, slippery and repulsive at the same time. He is also extremely hard to track down. Finding someone who is with him will prove very hard. Such a service will be expensive. Batista wants 100 gold sails per day for sending his men out to look for her and an extra 1,000 gold if they locate her. The payment for the daily search has to be paid in advance. If the money stops, so does the search. Balian stipulates that Alika has to remain unharmed or consequences will be dire. He also demands a daily report. "Do not try to con me, old man, or you'll pay the price that so many have paid who tried to cross me. I'll return shortly with the money."\\

As Sjo controls the group's income, Balian has no personal money to speak of. Asking his Shoanti friend is not an option, since the righteous healer might not agree to hiring an underworld gang to do some shady work. Selling one of his magic items looks like the only alternative. Fortunately he has just the item: Lady Andaisin's {\itshape headband of inspired wisdom} . The temple of Pharasma would definitely be interested in such an item, but Balian doubts if they will be discreet about it, so he visits a merchant who will do anything to make a profit, including keeping quiet: Diederik Lodann. Lodann was the merchant-actor who played alongside the companions in  {\itshape The Passion of Saint Alika} , portraying the seer's father. Balian secures a neat 2,000 gold sails for the headband and negotiates a buy-back option within ten days for a 10 % increase. With two bags of 100 platinum pieces Balian returns to Batista to seal the deal. He pays the gangster his first 100 gold and expects a detailed report tomorrow of what his money has bought him. "Of course, my dear Balian, for a Varisian hero like you, we will certainly do our best", Batista smiles. Although it sounds like a compliment, Balian senses that the old man wanted him to know that he already figured out who he was in this short time span. Well, at least this proves that the man has resources to gather information, but Balian will have to watch his step around him.\\

---\\

Concluding that he has done enough reading for the day, Puk sets out again to check the quarantine situation of Old Korvosa. Since halflings in Korvosa are considered simple workers or servants, no one notices the small rogue, who also uses his skill to blend into the shadows to remain unseen. The Narrows of Saint Alika, as the channel of water between the mainland and Endrin Isle (the actual name of the island on which harbors the district of Old Korvosa) is called, is mostly obscured from view by sturdy city walls that line the northern coast of the mainland. The many gates in the wall, which used to lead to the 20 or so wooden bridges over the Narrows, have all been closed, and the bridges behind them burned. A score of Gray maidens man the walls.\\

The only 'breach' in the wall is where the stone bridge crosses the channel. The opening has been thoroughly barricaded and is also heavily guarded. Peeking over the blockade, Puk notices several skiffs in the water with even more Maidens, who are guarding both the Narrows and the mouth of the Jeggare river on the other side of the Isle. In all, the security of Endrin Island seems pretty tight. Puk counts at least five dozen Gray Maidens. The halfling also gets a glimpse of the district on the far end of the bridge. Old Korvosa looks desolate; several buildings have been vandalized or burned and no one dares to show himself so close to the deadly guards on the bridge. The most gruesome discovery is the fact that the protestors who were killed when the bridge was closed, are still on the ground Their cadavers have been left to rot. This sight makes the halfling sick to the stomach. He can only pray that his appetite returns by the time he gets back to the villa, since he left a note for the boys: "Days in Korvosa always get me hungry, mountain man scale!"\\

---\\

Quint spends the rest of the afternoon spying on the castle, where nothing happens until early in the evening. Three hippogryphs carrying Sable Company marines land on the castle's terrace. From his vantage point in the street Quint can't make out what they do. Half an hour later they fly off again.\\

When the sun starts sinking towards the horizon Quint decides to take his chances at the stables. He addresses two boys who are filling troughs with water. "I beg your pardon, friends," he says, "I'm looking for master Jacob." One of the lads runs off and quickly returns with strapping man, who looks about 45. "You wanted to see me, good sir?"\\

"Good evening, master Jacob. My name is Marcus. I live in Old-Korvosa, or at least I used to, before the quarantine." Quint produces a sad puppy look on his face. "I'm actually looking for a job on the mainland and some of the neighbors told me to talk to you. Could you use an extra pair of hands around the stables? Or somewhere else, I'm flexible and I'm a hard worker ... I don't ask for much ... just enough to get by, you know."\\

"Well, I am actually short a few hands at the moment. I lost three of my men to the plague and three more are in the hospital. I can't promise you it'll be forever, but for now I could definitely use the help. Why don't you come back tomorrow, at sunset? We'll give it a try ..."\\

"That would be great, sir ... or should I call you master?"\\

"Master Jacob is fine. I'll see you tomorrow, Marcus. Don't be late. I run a tight shift."\\

"I'll be there, sir ... erh, master Jacob. You can count on me." Quint makes an awkward bow and walks out. That went well. Satisfied he returns to the villa.\\

