%!TEX root = ../crimson_throne_book_main.tex
% 2015-12-05
Derdra leads the companions to the inn. While she approaches the duskwardens to secure passage to the city above, Puk notices some halfings and a dwarf at a table nearby, who raise their glass at him in a gesture of friendship. Rungo Halfmoon and his cousins Bosco and Nolo are traders from Kaer Maga, on their way to Palins Cove to sell leather from the Cinderland aurochs. They tell the heroes more about the city atop the cliff.\\

Kaer Maga is a melting pot of citizens from all cultures, religions and races. Most of its inhabitants are humans, but there is a sizeable number of halflings, dwarves, half-elves and half-orcs as well. On top of that the city is the home to gnomes, elves, orcs, trolls, centaurs and nagas. The absence of a central government makes Kaer Maga an anarchic civilization, but it still functions quite well through the influence of several power groups who have achieved somewhat of a balance. Each factions has agreements with the other power groups, and while most of them are constantly looking for ways to undermine the letter of these contracts, they ensure the peace. This strange equilibrium makes the city a place where everyone is welcome and everything can be traded.\\

Perhaps the most selfless group within the city, the Duskwardens represent the first -- and often only -- line of defense between the city of Kaer Maga and the Undercity below. Trained to defend against all manner of undead, monster, abomination, or whatever else might crawl up from the dark, the Duskwardens patrol the tunnels below the city to ensure their safety. Organized from their headquarters in Bis, they not only clear the tunnels for the city's expansion, but attempt to map the maze below. The only profitable enterprise the Duskwardens undertake are the guides through the Halflight Tunnel -- the fastest, and most dangerous, way from the cliff's base to the city. As a group that truly represents the benefit of Kaer Maga as a whole, they are supported by the entire city. No reasonable request from a Duskwarden is refused, and they are honored guests wherever they may choose to go.\\

If it's magical and it's in Kaer Maga, then the Arcanist's Circle probably has a hand in it. As the center of the city's magical research and experimentation, it houses a number of wizards and mages, all in the interest of learning and sharing information to the benefit of all involved. This involvement with magical devices has made them a powerful mercantile power -- they not only sell magical items, but take commissions to construct new (and untested) devices.\\

The city also houses a relatively large population of hemotheurges. These so-called Bloatmages are arcanists who cast spells strengthened by their own blood. They produce excess blood to be used for power in spells and rituals. This blood pools in the folds of skin as blood vessels burst, giving the hemotheurge a grotesquely overweight look. They use leeches to increase the blood flow in their bodies and clean the blood of toxins left behind from the spells they create.\\

Controlling the district of Bis, the Ardoc Family is an age-old group of golemcrafters. Despite the city's fluid alliances and residents, the Ardocs have managed to stay strong -- and present themselves as such. They hold Bis with an iron fist, ensuring that gangs and crimes are punished accordingly. Yet, they are not exactly virtuous -- the order they impose on Bis is equivalent to that of the city's strongest crime family. Truly bound by blood, the family is made of brothers -- both blood and those married in. Those family members without magical ability are second class, only just above the average Bis citizen, and among the Ardoc's children and women. The mages, however, all bow before the family's patriarch, an aging wizard named Merriman Ardoc.\\

One of the newest factions to make an impression on Kaer Maga, the Freemen have made themselves known through their zealous defense of both freedom and democracy. Founded by a group of escaped slaves, the Freemen actively seek out slavers and end their human cargo's plight. Any escaped slave is welcome, regardless of his history -- and the Freemen will gladly give their lives to ensure none of its members find themselves back in chains. Working out of the Bottoms, the district has become a bastion of democracy in a city with no real government. Led by the man who masterminded the first escaped Freemen, Halman Wright, the group has come to an uneasy truce with the other, slave-owning factions of Kaer Maga. In a delicate balancing act between freedom and foolishness, the Freemen often find themselves at odds with the mercantile interests of the rest of the city.\\

Originally founded as a means of standardizing market procedures to maximize profits across the board, The Commerce League has grown to little more than a white-collar mafia. Focusing on businesses like price fixing, protection rackets, and loan sharking, the Commerce League undeniably has its hands in the criminal ring. Yet, it still holds its original principles to heart, as it protects the commercial interests of its investors and members with a tenacious fervor. As such, they keep the core largely free of the inter-gang squabbles that plague the rest of the city -- after all, such things are bad for business.\\

Augurs are trolls who have taken up fortune-telling. They answer their client's questions by cutting their own stomachs open and reading their own intestines. This method of fortune telling has questionable accuracy. They use this practice as a fa\c{c}ade to broker information.\\

Twice-Born is a polite term for referring to undead, and typically only used within the Ankar-Te district of the Varisian city of Kaer Maga. Here, necromancy and the creation of undead is commonly practiced and accepted, and the twice-born can often be found working as servants for wealthy individuals. Being generally mindless, the tasks assigned to these Twice-Born are naturally quite simple, but can include such jobs as household servant, litter bearer, waiter, and even prostitute. This does not imply that the undead are held in the same esteem as the living. They are considered to be the property of their owner who think of them as little better than pack-animals, and who are also responsible for keeping them under control; destructive or aggressive undead are quickly put down by the general population, with the owner held responsible for any damage or injury caused. Their owners will often spray them with perfume, or hang them with fragrant herbs or flowers to mask the stench of decay. The city's infamous White Lady brothel even uses Twice-Born as prostitutes\\

The Sweettalkers are a group of unusual traders from far to the east of Avistan who follow a little-understood monotheistic religion that imposes strict rules. The Sweettalkers of Kaer Maga believe that to utter anything but the most perfect true name of their god is heresy, yet none so far encountered have felt that they are worthy of this honor. In order to not speak an impure word, they sew their lips shut and communicate with each other in a code of clicks, whistles and sighs.\\

Seeing that the companions are hardened adventurers, Rungo recommends them to pay a visit to The Flame That Binds, a shop specializing in the sale of magical goods and services, found in the commercial Tarheel Promenade district.\\

