%!TEX root = ../crimson_throne_book_main.tex
% 2015-11-14
Soaring through the air on the back of a hippogriff is an exhilarating experience. The companions make a quick stop at the Endrin Academy on Old Korvosa to pick up the kids and then make an easy escape from the city.\\

\section{24 Erastus 4708}

The heroes have never seen the sun rise quite as spectacular as from their seats in the sky. They continue for several hours until Neolandus Kalepopolis orders them to land. The flying mounts are tired and he can tell that they have not been properly fed during the last few days. The company buys some sheep and goats from a local farmer to feed its mounts and spends the rest of the day and the following night resting up.\\

\section{25 Erastus 4708}

It takes a few more hours to get to Blackbird Ranch, the home of Vencarlo's former adventuring companion, Jasan Adriel. The party makes sure to avoid the village of Harse itself, deeming it wise not to be seen in the neighborhood. Jasan is over the moon to see his old friend Vencarlo again. He welcomes his guests with open arms and his booming voice and ready grin bear witness to his warm-hearted intentions. Trinia Sabor is still at the farm as well. The young painter is eager to reunite with her former rescuers and after having exchanged big hugs and honest laughs, the ranchers are curious to learn all about recent events in Korvosa.\\

Fortunately the countryside has been mostly spared from the plague that hit the capital so hard. There have been a few isolated cases, but farmers usually stick to themselves, keeping the chance of getting infected to a minimum. Moreover, few merchants are coming to and from the city lately and patrols by the Korvosan Guard have all but ceased, so the disease has been mostly contained to the capital.\\

The heroes spend the rest of the day skinny dipping in the brook and relaxing under the sun. Neolandus Kalepopolis notices Quint's scorpion-shaped mark on his shoulder, and wonders whether it is a tattoo, but the bard tells him it is a birthmark.\\

That evening Jasan treats his guests to a pleasant and filling dinner. Mouse, Korwick and Heldrin settle in well and quickly make friends with Jasan's children. Sjo is pleased to see them recount the heroic acts of their masters, demonstrating that the boys have not been traumatized by what happened recently. Jasan says he will be happy to provide the three kids with a home, but he fears that he cannot take care of the hippogriffs, since they require too much meat to be fed. He suggests that Kalepopolis look for sanctuary in a safer haven, and feels that Janderhoff, the dwarven sky citadel on the edge of the Willspin Mountains, might serve such a purpose. When he learns that the companions are planning to travel to the Cinderlands to look for the Shoanti, he recommends finding a guide, since both the city of Kaer Maga, the entry point into the Cinderlands, and the desolate scrublands themselves are fraught with peril. Jasan's sister-in-law, Derdra, is an excellent and trustworthy guide. The retired ranger expects her on his ranch in about a week. He suggests the companions enlist her help. In the meantime they can take some time to catch their breath and visit Janderhoff to aid seneschal Kalepopolis in procuring the dwarves' support for their cause.\\

At the end of the evening Jasan digs up an oak chest from a cupboard. He takes out a scroll and hands it to Quint. It contains a {\itshape teleport} spell. It is one of the treasures that remains from his adventuring days with the Blackbirds, but since neither he nor Vencarlo can use the scroll, he hopes it might serve the companions on their quest. He advises them to use it for long-distance travel, possibly when they want to return home from the Cinderlands. It will certainly save on traveling time. \section{26 Erastus 4708}

Janderhoff, the monumental dwarven Sky Citadel, is a firm trading partner of Korvosa. Its miners and smiths are well-known throughout the region. Using Neolandus's hippogriff mounts, it takes the companions the better part of the day to travel there. The first thing visitors to Janderhoff see are the massive iron curtain walls of the city, proud reminders of the glories of dwarven architecture and engineering at their peak.\\

Captain Durrag of the city guard takes the party through a long series of tunnels to see clan lord Ragnar Ironfist. Seated on a stone throne at the far end of a great mountain hall is a pensive dwarf. Although he does not bear the title of King, the sober crown on his brow suggests his station is similar. An older dwarf stands next to him and introduces himself as the lord's advisor, Bronn Silverheart.\\

Neolandus Kalepopolis has met these dwarves before and enjoys enough respect to be heard. He informs the dwarven rulers of the hard times that have befallen Korvosa, making sure to point out the queen's foul role in this crisis. Although the seneschal spins a good tale, the companions pick up a lot of hesitation on the dwarves' part. Quint, Sjo and Puk chime in, trying to convince the mountain folk of their plight. Quint refers to the treaty of Crystalrock, in which both nations pledged to protect each other. With a murderous usurper on the crimson throne, the people of Korvosa appeal to the dwarves to honor their agreement. Sjo also points out that Torag, the dwarves' patron deity, is the father of honor and protection, so he would certainly approve. Ironfist admits that honor is a value that greatly exceeds other, worldly matters. Trade with Korvosa is booming at the moment, since the queen has been making huge orders of female suits of armor lately. But if she is really as evil as the seneschal claims, it might be unwise to support her in building up an army. Quint agrees, the queen won't stop with Korvosa. Once she solidifies her grip on the city and its hinterlands, she will look for ways to expand her power. Janderhoff will be one of her first targets. In over nine millennia, Janderhoff is the only dwarven Sky Citadel that has never fallen to an enemy, a fact that the dwarves are justly proud of. Surely Ragnar Ironfist does not want to be remembered as the clan lord who lost the citadel. No, he has to defend his home as his predecessor have done since the time of Boldrak Rockcourage, the dwarven explorer who discovered these caves and carved the {\itshape gladdringgar} in the wall, Quint pleads, pointing to the rune behind Ironfist's stone throne. The companions' fiery speech succeeds where the seneschal's words fell short. The clan lord nods: this Ileosa character cannot be trusted. He will cease all trade with her. He will also open his halls to those who seek sanctuary, beginning with the seneschal. The dwarves are also prepared to sell weapons and armor to the 'rebels' and if necessary, they will even provide a number of soldiers to help battle the queen, if it should come to that.\\

The companions can immediately make good use of the dwarves' offer. They leave some of their armors and bucklers in the hands of Father Bardin Bronzebeard in the temple of Torag. The highpriest and his staff will strengthen the magical enhancement on these over the next few days.\\

