%!TEX root = ../crimson_throne_book_main.tex
% 2015-10-17
The first order of business is getting Vencarlo out of his state of unconsciousness. He is lying on the bed, apparently unhurt, but with a lost look on his face. Sjo examines him and determines that his mind is fractured. Using two spells of {\itshape lesser (or rather minimal) restoration} the healer succeeds at having Vencarlo open his eyes, but the man still does not recognize the companions. Quint digs up the documents he retrieved from the scrivenite that contain the fencing master's lost memories and hands them to him. Orisini starts reading them. Meanwhile Puk and Balian examine every corner of the room. The halfling notices that the two braziers next to the throne are magically burning, but they look too heavy to take home. More important, though, is the vague line he discovers in one of the frescoes, framing a secret door in the painting where a crazed Eduardo has killed his father. They study the scene more closely: Eduardo has apparently used some kind of magic bolt to kill his father. The arrow protrudes from the dead man's chest and black lines have spread across his flesh, indicating that the father was possibly killed by an {\itshape arrow of human slaying} . Nerio's sword still lies in his open hand, while Eduardo's six-armed and three-faced mother is watching the scene from behind a pillar. She is wearing a heart-shaped necklace. Nerio himself looks like a madman: he towers over his father's body with his head clutched in his hands; both of his faces are screaming madly. Upon further inspection of the mural Puk and Balian first find a secret button in the eye of Eduardo's second head and then they locate three more buttons: one in the pommel of Nerio's sword, one in the feather at the end of the bolt and the last one in the upasunda's heart medallion. The explorers find no traps in this configuration and assume that the buttons are meant to open the secret door, but do not push anything yet until the party is ready to leave.\\

It takes Vencarlo about three hours to catch up with his own memories and thus restore his mind. Now he does remember the heroes and thanks them for saving him. When Quint informs him that they discovered Blackjack's gear in his house, Vencarlo admits that he is the caped crusader. Quint thanks him for saving their lives five years ago, when he and Sjo were still kids and Gaedran Lamm was taking out his anger on them because he had lost heavily in a game of chance - the same game that put Balian in the shackles of an oarsman. Vencarlo smiles: "I guess we're even, then."\\

Vencarlo wonders if the companions also snuck in here, but when he learns that they have been talking to Glorio Arkona and that it was the nobleman who showed them in, he is amazed. It is clear that master Orisini harbors no love for the lord of House Arkona, and he remains suspicious, even after learning that it was Glorio himself who suggested that Vencarlo be saved from the labyrinth because he might make a valuable ally. He is even more surprised when he hears that Glorio Arkona has agreed to tell the companions where seneschal Neolandus Kalepopolis is.\\

When the companions are ready to leave, they try pushing all four buttons at the same time, but the secret door does not open. After experimenting a bit, Puk figures out that the order in which the buttons have to be pushed reflect the challenges of the labyrinth. The first test of {\itshape balance} and the air elemental stood for agility, which is reflected in the arrow. Then there was the test of smarts leading up to the book creature. Intelligence is in the head, so the eye should be second. The puzzle with the chessboards and the six-armed fighting machine are represented by the sword; while the final challenge with the fire and water elemental took place in a vaguely heart-shaped room, protecting the true heart of this maze. So the order is : arrow, eye, sword and heart amulet. When our friends push these buttons, they hear the grinding of wheels for about a minute, before the secret door sinks back in the wall and slides open. The turning entrance chamber has grinded into position behind the door, allowing the companions to exit the labyrinth. Outside one of Glorio's bodyguards is waiting in contemplation. He leads his master's guests up again and takes them to see his lord. Glorio Arkona is very interested in learning what the heroes discovered in the Vivified Labyrinth, and he looks truly shocked when he finds out that one of his forefathers was the son of an upasunda. Quint even summons a projection of her, using {\itshape silent image} . Sjo concludes that lord Arkona still must have a hint of upasunda blood running through his veins. Glorio makes good on his promise and orders Selena to fetch Neolandus Kalepopolis. The seneschal is dressed in common clothes and looks worried, but healthy. He claims that Lord Arkona was a generous host, thus silencing suspicions that he was a prisoner here. He has some rather interesting information about queen Ileosa, but has to start his story much earlier:\\

"When the Chelish settlers came here 300 years ago, they found the Shoanti who had been living here for over two millennia. The tribal warriors defended their territories with great tenacity, not only because they it was their homeland, but also because it was their sacred duty. The mighty mastaba, a relic from Thassillonian times, which now serves as the base for Castle Korvosa, was a holy site of immense importance to them. But the pyramid was more than holy, it harbored an unspoken evil that the Shoanti shamans were sworn to protect. I don't know the nature of this evil, but I fear that Ileosa has uncovered it. That explains her sudden change in character leading up to Eodred's death.\\

I truly realized that things had got out of hand when Eodred's half brother disappeared. You see, the Arabasti family had a secret of its own: when queen Domina came over from Cheliax, she did not only bring her son Eodred, she had a second child whom she never revealed to the outside world. Domina was known for her close relations with the devil-worshipping church of Asmodeus and had, at one time, conceived a baby with a devil. The offspring, a child named Venster, was a blemish on her crown, for Chelish society hated tieflings as badly as it loved devils. Venster had his own quarters in the attic of Castle Korvosa and very few people knew of his existence. Only Eodred and I visited the lonely soul from time to time. Ileosa knew about him too, but like all true Chelaxians she loathed him for even being alive and refused to set foot in his quarters. That is, until the final days of the king's life, when she suddenly started going up to see her brother-in-law for long stretches of time.\\

Around that time I also found out that Ileosa had stolen the key to the vaults a few weeks before. It might just have been because she was bored and curious about the riches in Korvosa's treasury, but the gods only know what she found underneath the castle. From my meetings with the Shoanti ambassador Thousand Bones, I had learned about an unspoken evil lying in the vaults and I started to worry. Not only had Ileosa changed how she felt about Venster, she had also become very cranky, she got almost hostile towards Trinia Sabor, the young girl who was painting Eodred's portrait and she locked her husband away in a dark room, keeping all but a select few from seeing him. The king's improving health took a deep plunge and before long he was on his deathbed. And then I found out that Venster had disappeared.\\

That is when I decided to confront the queen. She was not the docile, albeit somewhat annoying woman that I had always known. No, she scoffed at my concerns and laughed in my face when I told her about what troubled me. I implored her to change her treatment of the king's illness, but she cried out that he would not live to see another day and, with a malicious glare in her eyes, informed me that I wouldn't either. At that point three red mantis assassins broke from the shadows and attacked me. I can only thank my years of training at the Sable Company for making it out alive, but I was badly wounded and grievously poisoned. I fled to a last place where people would come looking for me, my dear, but very weird friend, Salvator Scream. He took me in, but was of little use in my recovery, so it took many weeks for the poison to get out of my system.\\

In the meantime I heard rumors about the chaos that swarmed the city: the king dying on the same day that I was attacked, the people rebelling and being slain by guards or Hell Knights, and finally a terrible plague consuming our dear citizens. When Old Korvosa got quarantined, Scream became truly paranoid, claiming that he was being watched, so I decided to look for a new place to hide and Salvator suggested this place. I've been here for two weeks now, and my host, lord Arkona, is most kind, but has not kept me up to date on what's going on in the city. So, you came to me looking for stories, but now I aks you to tell me some yourselves."\\

The party informs the seneschal on the goings-on of the last two weeks. He is happy to hear that a cure for the plague is on its way, but is horrified when he learns about Marcus Endrin's fate and the queen's decimation of the Sable Company. The fact that Ileosa survived a bolt to the head tells him that she has become more than human and Kalepopolis fears that her new crown of fangs might actually be the evil that she has dug up. If Ileosa has become so powerful that she can simply shrug off an arrow to the temple like a mosquito bite, it will be nearly impossible to stop her. Maybe the Shoanti shamans know of a way to fight the evil that has taken hold of the queen, so Sjo and Quint see no other option than to go to the Cinderlands and find out. Still, Sjo is reluctant. The Shoanti who used to live here, were members of the Sklar-Quah or Sun clan, the same clan his mother came from. The fact that his mother would rather throw him in the river than take him to her people, is proof enough that the Shoanti do not like bastards. Maybe they should try and find Thousand Bones, the shaman of the Skull clan first. At least he's a friend.\\

The seneschal and Vencarlo Orisini also want to abandon Korvosa. Vencarlo suggests going to his friend Jasan Adriel in Harse, the man who already took in Trinia Sabor. Neolandus Kalepopolis agrees, but has a request of his own. He suspects that the Sable Company's hippogriffs are still alive in their stables in the Great Tower. He does not want to leave the animals in the hands of Ileosa's troops and feels that there is no better way to get out of the city than atop his company's majestic mounts. He asks the heroes to aid him in this endeavor and they are happy to oblige ... at least, they will be tomorrow, after having rested.\\

Sjo also considers the children's fate: Mouse, Heldrin and Korwick might not be safe in the city any longer, so it is finally decided that the children will accompany their saviors to Harse. Tonight they want to return to the villa to rest up, so they will be ready to attack the Great Tower tomorrow night. Glorio Arkona allows them the use of the barge in his hidden sea cave. Arkona's men are skilled at avoiding detection and easily transport the party, Vencarlo and the seneschal to South Shore. But first the sword master picks up his {\itshape Blackjack} gear, inquiring whether Quint would be interested in taking up the rapier in his place and protect the people of Korvosa. Quint is honored to accept. \section{23 Erastus 4708}

\section{Level up: level 8.}

The party spends the next day selling their loot and getting some new {\itshape wands of cure light wounds} . Balian also acquires a dusty rose ioun stone which enhances his defenses. Sjo takes some time to visit Larella. The priestess of Shelyn is still working with the sick in the city's hospital. When Sjo asks her to flee to the country, she refuses, as she has work in the city, helping the people. She does accepts another offer he makes, though. Taking the best looking {\itshape ring of protection} he and his friends found yesterday, Sjo gets on one knee and asks her to marry him, once this trouble is over. The beautiful priestess beams as she says yes. 