%!TEX root = ../crimson_throne_book_main.tex
% 2015-05-09
\section{10 Erastus 4708}

On this radiant Sunday morning Sjo attends a service at the temple of the sun goddess, Sarenrae. Meanwhile Balian hangs around the Gray Maiden barracks on Eastshore. With Maiden guards at the gate, on the walls and in the towers of the walled complex, the ranger does not risk a look inside, but he clearly hears the sound of military training inside, even on a Sunday. The ranger makes a quick stop at Thief Camp as well: Cadabrani's men have been widening their search for Alika to the whole of Midland, but they have come up blank. Balian asks them to continue their efforts and pays the crimelord for another day.\\

While Quint spends one more day in the stables, Puk keeps an eye on the castle. No one goes shopping today, but at 11 o'clock a coach arrives with Archbanker Darb Tuttle and a handful of Abadarian guards. The highpriest of Abadar stays in the castle for about an hour and a half. Asking around, the halfling gathers that Tuttle comes here regularly, at least once a week. Actually, he has been doing so for years, even dating back to before Eodred met Ileosa. In the afternoon Puk follows up on Sirtane Leroung's progress. She claims to be close to a solution, but she is missing a crucial ingredient: blood cap mushrooms. This very rare fungus only grows in the {\itshape Bloodsworn Vale} . Puk agrees to travel there and gather toadstools for her. At home the halfling brings his friends up to speed on their new quest. They search the books in the library for more information on the Bloodsworn Vale. Nestled between the lofty peaks of the Mindspin Mountains, the valley lies on an ancient road connecting Korvosa to Nirmathas. This once well-worn path used to serve as an overland route between the empire of Cheliax and its remote colonies in the north. The trail, however, fell into disuse after the death of Aroden and the ensuing civil war, during which Molthune and Nirmathas declared independence. The state of animosity between these fledgling countries and the old empire saw an end to merchants using this route for trade. A century of neglect has erased the road and allowed the woods and monsters to reclaim the vale.\\

The Bloodsworn Vale is named for the bloody battles that were fought there during the Everwar, Cheliax's war of expansion. It was the site of a large, months-long struggle in 4396 - over three centuries ago - between the Chelaxian army led by Field Marshal Korvosa and the defending Shoanti natives. Fields of blood-red roses are said to mark the graves of the many Shoanti barbarians and Chelaxian soldiers who laid down their lives in the conflict.\\

Balian actually knows the valley, as he travelled through it after he freed himself from slave duty in Cheliax and returned to Korvosa. Since he had served as a galley slave for over four years, the ranger swore not to travel north aboard a vessel, but rather on foot, thus choosing this forgotten itinerary. He remembers that the eerie sounds and morbid atmosphere of the vale greatly troubled him, but somehow he managed to get through undisturbed without running into any of the cruel monsters or hungry predators that supposedly hunt the place.\\

\section{11-15 Erastus 4708}

The next morning the companions prepare to travel to the Bloodsworn Vale. They buy supplies and warn the field marshal of their impending absence. A one-way trip should take five days, two days to reach the Mindspin Mountains and three more to traverse the treacherous mountain passes before arriving in the notorious valley. Balian visits Batista Cadabrani and pays him 1,000 gold to keep the search for Alika going while he's away. Quint will join his friends on this wilderness trip as well, so he has to make up an excuse to have Marcus miss his new job at the stables: he tells master Jacob that he's come down with the plague.\\

The first two days go smoothly and the companions reach the mountain range without difficulty. The old pass proves harder to travel; the heroes are forced to lead their horses by the bit. The road was once wide enough to allow for wagons, but now it is overgrown with weed and bushes or blocked by numerous landslides that no one has cleared in a hundred years.\\

