%!TEX root = ../crimson_throne_book_main.tex
% 2015-07-18
The companions fill a bag with red mushrooms and then seek their way out of the swamps. Although Furian is very happy to see Mirala alive, he has a troubled heart when he tells her that her brother avenged her 'death' by killing over a dozen of his kin. Mirala feels guilty about her part in this tragedy, as it was her irresponsible behavior that triggered her brother's madness. She wants to confront her brother alone, so the heroes accompany Furian to the pixie court, while the centaur girl makes for Pointer's Rock.\\

Pixie king Tirmando is pleased to hear that Mirala survived, but no amount of good news can sway his mournful mood. Still, he remembers his promise to the adventurers and hands his green-leaf cloak to Puk as a reward. This wonderful cape functions as a {\itshape cloak of resistance} , but it also allows the wearer to  {\itshape dimension door} once per day. The king invites his guests to spend the night at his court before they return home tomorrow. Later that evening Mirala arrives, explaining that her brother is distraught about his own heinous deeds and has decided to leave the vale to seek atonement for his sins. \section{Level up: level 7}

\section{17-19 Erastus 4708}

The next morning the companions head back to Korvosa. On the evening of the 18th Zellara's ghost appears to them from her Harrow deck to do another reading. She removes the nine {\itshape book} cards from the deck and has everyone draw one. Sjo evokes a healthy dose of laughter when he draws the  {\itshape idiot} , which Zellara interprets as a warning not to be too naive. Quint goes for the  {\itshape inquisitor} , who accepts only the truth. Zellara says that Quint will be instrumental in uncovering an important hidden truth. Balian draws the  {\itshape raksasha} as a warning not to be manipulated. Balian should be careful not to act differently than what his true nature prompts him to do. Puk's card is the  {\itshape vision} : he will meet a man whose insanity and genius will be intertwined. Next Zellara reshuffles the cards and lays them out for each of the companions. In Sjo's present she finds the {\itshape crows} , who represent a group of dangerous people who violently take possession of what is not theirs. The  {\itshape desert} is in his future, as a sign of a harsh environment in which he will have to survive. Quint has the  {\itshape foreign trader} in his past, representing a hidden truth whose unveiling will surprise some and shock others. The future reveals the  {\itshape uprising} : a leader will be overthrown, but it remains unclear which part Quint will have to play in this. Puk has the  {\itshape tangled briar} in his past. Bad events in his younger days defined his path, but set him on a journey towards hope. Puk's future reveals the same card he picked in the choosing, the  {\itshape vision} . Zellara concludes from this that the mad genius will play a key role in days to come. Balian's fortune also shows important facts about the past. The  {\itshape empty throne} signifies a great loss that still defines his life today. The  {\itshape idiot} also comes up here, indicating that Balian made a rash decision in the past and the fact that he fooled others about it will not be received kindly. The  {\itshape marriage} in Balian's present stands for big changes that are about to happen. Zellara says that the positive position of the card expresses the hope that Balian will be able to sail the waves of change and maybe even help shape them. His future is less clear, although Zellara interprets the  {\itshape forge} card as a sign that a great heat that has burned everything to cinders might be part of Balian's fate. 