%!TEX root = ../crimson_throne_book_main.tex
% 2015-04-25
Upon returning to the villa, the companions find that Madam Nesia's condition has grown worse. She is delirious, suffering from high fever and hardly aware of her surroundings. Our friends decide to summon Zellara's ghost from the Harrow deck to consult her. Maybe she can find out if the girl is cursed. The ethereal gypsy bends over the sick woman and holds her hands over her head and body, sinking into an intense trance. Her face betrays the effort it costs her and Balian is sure he sees drops of sweat dripping down her ghostly face. After what seems like an eternity Zellara gets up again, obviously exhausted. She states that she has trouble finding the poor girl's soul.\\

"Does that imply that she has no soul?" Quint wonders.\\

"There is something there," Zellara replies, "but it keeps slipping out of my reach."\\

Having heard stories of people who sell their souls to devils, Sjo immediately suspects the church of Asmodeus to be involved. Balian suggests to take the girl there and have the priests of the {\itshape Prince of Hell} look at her. It might be risky, but it seems like the most direct route to an answer. The others agree and prepare the carriage to transport Nesia across town. However, when they try to lift her from the sofa, her arm bruises badly from the slightest touch. Using the sheet on which she lying instead to carry her, the party gets her to the coach and takes her to the steps of the Archfiend's house. Sjo knocks on the door and is met by Mallas, the highpriest's grim personal bodyguard. The stern warrior does not feel inclined to help the Shoanti who once came to the temple as an aspiring acolyte and then betrayed this 'contract' by turning his back on the Lord of Oaths. It takes some convincing until he finally agrees to let them in. The heroes gently place Nesia on the altar, which is conveniently shaped to support a person's body, and wait for highpriest Reebs to arrive. Reebs does not understand why the party brings him a sick girl, he is not the city's prime authority on healing and his contract with the medic task force - which the companions helped negotiate - has already cost him all of his healing magic for the day. Sjo explains that they are not here for his medical expertise, but rather for his extensive knowledge on the nature of souls.\\

When Ornher Reebs turns towards the girl Sjo detects a hint of surprise on his face, which the man quickly hides. He gives her a fairly shallow look-over while Quint explains how they found the girl in the street, devoid of any memory. Reebs looks at the companions and chuckles. "She's naught but an empty shell", he claims. "Just take a dagger and prick her with it".\\

Puk draws his blade and carefully sticks the point in Nesia's upper arm, where the bruises are. Blood pours profusely from the tiny wound, while the girl starts shaking badly. Her body jerks upward in a sudden, spastic motion and completely turns into blood. The fluid spatters the bystanders and falls down on the altar and floor, leaving no trace of any person: no body, no bones, no skin, nothing but blood. The companions are flabbergasted and even Ornher Reebs regards the spectacle with a shocked look in his eyes.\\

"Well, that is a new experience, all right," the highpriest utters, breaking the silence. It is obvious that he's never seen anything like this either. Quint's mind races to find an answer: Was Nesia ever human? Maybe she was some kind of simulacrum, a copy of someone else, although those are normally made of snow and ice, not blood. Reebs claims not to be familiar with the concept of blood clones, but supposes that it could be possible. Of course, this might mean that the original version of Nesia is still around somewhere. Puk takes a bit of the blood for later examination and the companions leave after making a contribution to the temple's coffers of 50 gold pieces - which Mallas finds insultingly low.\\

Before turning in for the night, the young heroes get the sole surviving plague doctor from the old fishery and hand him over into the custody of the Sable Company.\\

