%!TEX root = ../crimson_throne_book_main.tex
% 2015-02-28
The young heroes of Korvosa keep an eye on the Hospice of the Blessed Maiden for the rest of the day. In the evening all the doctors who have been patrolling the city return. While the guards accompanying them leave after a few minutes for their barracks, the physicians themselves do not come out of the warehouse again. So they must have their own sleeping quarters in the building, possibly in the backroom, which the companions haven't seen yet. Most doctors also bring some new patients with them, who will probably occupy the beds of the dozen cadavers that are carried off by body carters before the sun sets. However, no patient has left the Hospice alive or cured today.\\

The companions wait for darkness before attempting to break in. Their goal is to get Puk into Doctor Saulus' office to compare his handwriting to the plague plan notes they found in Lost End. The huge backdoor to the Hospice is unguarded. Puk puts his keen ear to the wood and hears nothing on the other side. If a dozen doctors are staying in there, they must either be very quiet or already fast asleep. The halfling also fails to see any light coming through the cracks of the door. He feels quite comfortable that there is no one in there, at least not awake. The door is barred, so Quint uses his magic bell to open it. When no reaction comes to the bar dropping on the ground, Puk looks inside: this backroom is an unlit loading bay that is filled with empty crates, containers and barrels, the remnants of the Arkona venture that occupied this building in the past. Two curtains lead to the main hall. Puk slips in the backroom and peeks under the heavy drapes into the sick ward. There are two doctors left to look after the patients and a pair of Korvosan guards plus three Gray Maidens to provide security. The halfling informs his friends outside. Quint hopes that things in the ward will get even quieter (and hopefully even less crowded) in the middle of the night, so the young men decide to come back after midnight.\\

\section{7 Erastus 4708}

The companions return after a couple of hours. The backdoor is still open, so Puk slips back into the loading area. The number of guards and doctors in the sick ward hasn't changed, but the two doctors are no longer among the patients' beds, they have taken a seat at a table in the back instead. Damn, now they are effectively blocking Puk's path to the stairs! The halfling quietly calls over Quint, who might be able to draw the physicians back into the main area with a {\itshape ghost sound} spell. Unfortunately, the bard stumbles into one of the crates in the unlit loading bay: "THUCK!". He does not hesitate and quickly runs out again, pushing the door shut behind him. Puk tries to hide behind a container as one of the Gray Maidens pulls away the curtain and peers into the backroom. Lighting her way with a flickering torch, she walks over to Puk's hiding place and discovers the little rogue in the corner with a sheepish smile on his face. "Who are you? Get out of there!" the woman orders. Puk stands up and shrugs, but then jumps between the lady's legs and bolts for the backdoor, which his friends open from the outside. The Gray Maiden pursues him and suddenly finds herself facing four men instead of one.\\

"We are the pseudodragons, heroes of the city, and we're here on official business", Quint tries.\\

"Official business my ass! ALARM! I'm giving you one chance only, lay down your arms, NOW!" the woman cries as she holds out her blade threateningly. She quickly gets the company of her two colleagues, the two Korvosan guards and one plague doctor. One of the other Gray Maidens is clearly an officer, who immediately takes command. Quint and Sjo pull out Kroft's charter and wave it in her face, claiming they are here to examine potential treason by the queen's physicians.\\

"If you are sent by the Guard, you are under our orders as well, since we are in charge of all military forces in the city now", the officer throws back.\\

"Well, we're not actually with the Guard as such, so we're not really taking orders from anyone, but we are on the same side", Quint replies. "You see, I know that you are loyal to her majesty, the magnificent Ileosa. But I fear that both her majesty and you are being misled by darker forces, forces we should actually fight together." Resorting to his powers of bardic persuasion Quint tries to fascinate the commander and the Gray Maiden who discovered Puk with his words. He is obviously successful, as she relaxes her stance and seems prepared to listen to him. "Maybe I might even {\itshape suggest} that you help us", Quint tries, attempting to pull the officer further in his charming ploy, but she resists his wiles now. Puk, Sjo and Balian feel the tension dropping and take advantage of the moment to bid the mesmerized guards goodnight, slipping away around the corner. Realizing that he will not be able to get this Gray Maiden to cooperate with his plans, Quint changes his tactics now. "I guess it was all just an {\itshape innocent} mistake, I see that now", Quint continues, activating his  {\itshape innocence} spell to boost his bluff. "We were clearly mistaken, I apologize for disrupting you. You're doing an excellent job, by the way, keep up the good work! I'm sorry again for the misunderstanding, I'll just take my leave now." The bard slowly walks backwards to the corner of the warehouse while sweet talking the guards. Then he slips around the building as well, leaving the stupefied security at the backdoor. That was close! This was the first time in my long roleplaying career that I actually saw the bardic powers of persuasion being put to full use. We usually have a bard in our parties who makes ample use of skill in 