%!TEX root = ../crimson_throne_book_main.tex
% 2015-04-18
The sun is already rising over the horizon when the companions finally get home. The kids greet them enthusiastically and want to know everything that happened, but Sjo just tells them that he and his friends have completed their mission successfully and want to go to bed. The Shoanti quietly sneaks into his bedroom, where Madam Nesia is sleeping in the other bed. He noticed that her breathing is heavy and she's coughing. The tall healer puts his hand on her forehead and feels that she has a temperature. He pulls out his {\itshape wand of remove disease} and heals the ailing woman without waking her up. When her breathing eases, the weary warrior quickly slips between his own sheets for a couple of hours of overdue rest. Our young friends get up in the afternoon, slightly surprised that no one came to get them out of their beds to ask them about their deeds last night. Madam Nesia is still sick, despite the fact that Sjo was sure he cured her last night. Her eyes are red and she is feverish. Sjo examines her and comes to the conclusion that she is not suffering from the plague. He wonders if she might be cursed and shares his concerns with the others.\\

After a hearty meal the companions head over to the temple of Sarenrae to get Puk's blindness removed. There they learn that the patients of {\itshape the hospice of the Blessed Maiden} are all being moved to the hospital of the medic temple task force, after the Queen's physicians have been exposed as traitors who were spreading the plague in the name of Urgathoa. Fortunately the  {\itshape Gray Maidens} discovered this deception and took care of the problem, permanently! Quint is shocked by these rumors: so now the Gray Maidens, who were foolish enough to let themselves be tricked by the doctors, think they can steal the glory of solving the problem?!? And no one even thought it necessary to consult the true heroes about this fabricated story?!? Quint is quite upset and wants to confront the Gray Maidens, but Sjo convinces him to go to Kroft first. After all, Puk figures, if the companions want to keep a low profile, this story is the perfect cover. It wouldn't be smart to shout all over town that they are the ones who really cleared the Urgathoan temple of its cultists. Those Red Mantis assassins might still be out there and it wouldn't be wise to call too much attention to themselves, the rogue explains. Field Marshal Kroft already knows the truth, so talking to her might be smarter. Perhaps she can shed some light on the Maidens' motive behind this lie. In the Citadel Quint first apologizes for his outburst this morning, when he accused the Field Marshal of - unknowingly - aiding the enemy. Kroft is happy that he is not angry at her anymore, but says that he was right: she feels bad about the Guard's involvement in the physicians' foul plans. When the bard asks her about the reasons why the Gray Maidens want to claim the honor of clearing the temple of Urgathoa, Kroft replies that she was not consulted in that decision either - she is never consulted anymore; she is just told what to do. If she has to guess, she would say that the Maidens feel ashamed as well for assisting the cultists in spreading the plague, so maybe they want to make up for their mistake in the eye of the public by claiming to be the saviors who solved the problem. Kroft and her guards who were present at the Hospice this morning, have been ordered to keep quiet about the true heroes' involvment.\\

Quint starts wondering who is behind all these evil schemes. The list of possible suspects is just too long. Is Ileosa herself evil? If she wanted the throne for herself, she could be responsible for having Eodred killed, but why would she kill off half her subjects by ordering a plague to be brought down on Korvosa? Sjo utters the possibility that she is an Urgathoa fanatic herself. Or is Sabina Merrin corrupted? As commander of the Gray Maidens she has certainly moved her own troops into a position of power. Maybe one of the noble families is involved: they killed the king, hoping his queen would prove incompetent and one of them might step up to take the empty throne. Or are the banished Porphyria's engineering a return to Korvosa and its highest seat?\\

According to Kroft Ileosa also has a new advisor, a wizard from the Acadamae. Is he the puppeteer who controls the queen and her entourage, possibly working in the service of the Ornelos family? And what is Selena's role in all of this? The manipulator has always claimed that the queen is evil and that she is working for someone who wants to save Korvosa. There are so many options. One thing is sure, someone in the castle has been compromised. They worked with the doctors, allowing them inside the castle and then making up some story that the physicians were teleported in from Cheliax. Still this knowledge makes reporting to the castle a risky venture. How can you figure out what goes on in the castle without being in the eye of the traitor? Field marshal Kroft says that this has always been the task of the seneschal, but with Kalepopolis gone, there is no one to keep an eye on things. She could possibly get an audience with the queen herself if she insisted, but what would be her goal? She could never find out anything about the traitor without raising suspicion. Maybe commander Endrin of the Sable Company could be of more help, since the seneschal always comes from his ranks. Moreover, the Company is not tied down by the Gray Maidens as the Korvosan Guard is and Commander Endrin has been known to question the castle's recent politics before.\\

The companions decide to pay the commander a visit. Sjo is still welcomed in the Great Tower with open arms and immediately gets an audience with Marcus Endrin. The commander is pleased to see the Shoanti and thanks him for saving his stable boy Dalvun last night, but he is also baffled by the Gray Maidens' claim that they cleared the Urgathoan temple. Still, just like the young heroes, he cannot tell whether this Gray Maiden lie is inspired by treachery or a feeble attempt to mask their own incompetence. Sjo comes clean and informs the commander of everything he and his friends found out over the last couple of months. He also presents the commander with the evidence they uncovered: the Red Mantis letters to Doctor Devils, ordering him to first concoct a poison for the king and then to bring down the plague on Korvosa. Endrin is definitely on the same page as his visitors. He has no love for the queen, fearing that she is the evil behind all of Korvosa's recent trouble, and even if she is not, she allows herself to be manipulated, which also makes her incompetent to rule. If only the seneschal were here to take control: he could remove the monarch from power to regain control of the city and weed out the evil at its heart. Endrin has pleaded for a new seneschal before, but his request has been countered with the uncertainty of the last seneschal's fate. Is Kalepopolis really dead or is he still alive, and if so, where is he? Quint and Sjo wonder if his fate could be determined magically? The commander encourages them to enlist the help of one of the temples and try to find out. He will also resume his efforts to see the seneschal replaced with a new Sable Company man. First he will appeal to the queen herself to install a new seneschal and if she refuses, the council of nobles could enforce it. Quint fears that a new seneschal might quickly be manipulated himself by the evil force in the castle, but the commander argues that this new seneschal could act immediately. He feels that there is enough evidence to remove the monarch from power, permanently of temporarily, to regain control of the situation. Quint doubts that this law-abiding approach will succeed, but cannot offer a better alternative. He and his friends will continue their efforts to find out more while the commander exhausts all legal ways to see order restored. The two parties agree to keep each other informed of their progress.\\

