%!TEX root = ../crimson_throne_book_main.tex
% 2015-08-01
The first assassin uses the element of surprise well by slicing into Quint's flesh with his curved, serrated blade. His comrade never gets the chance, however, as Balian brings down his greatsword in a devastating arch, tearing apart the man's carapace armor. When the heavily injured hitman tries to stumble out of the way, the ranger follows up with another bloody sweep, finishing off his opponent once and for all. As his corpse hits the floor, the room is suddenly filled with a red mist. The first trained killer realizes that newcomers aren't simple students of the Orisini Academy and vanishes from view. The next moment a giant real-life red mantis appears behind Balian. The ranger easily deflects the insect's claws and continues his deadly attacks, quickly chopping the creature down. Meanwhile Puk reaches into his pocket and draws out some {\itshape dust of appearance} , which he blows into the air, making the invisible assassin reappear. The opponent now finds himself cornered and summons four  {\itshape mirror images} , but facing overwhelming odds, this act only prolongs his suffering. He manages one more feeble hit, before being overrun. As he falls down, more red mist arises and the companions notices that both assassins' corpses have completely disappeared, as if they were never there. So these are the dreaded red mantis? By the gods, how they failed to live up to their reputation! Sjo suggests using Vencarlo's house to rest up, the hour is growing late and tomorrow promises to be a rough day. At the same time they can wait here for the fencing master to come back home. The heroes quickly scan the building and discover a hidden lockbox in Vencarlo's closet. It contains a {\itshape bag of holding} , which Balian empties on the floor. The black cloak, mask, boots and gloves and the fancy rapier leave no doubt as to its proprietor: this gear is Blackjack's. So Vencarlo is the caped crusader, just as the companions expected. Sjo puts the items back in the bag and return the box to its secret compartment. Let's just hope that the old pro gets home soon, the party could definitely use an accomplished ally at its side to steer through the murky waters of Old Korvosa. \section{21 Erastus 4708}

Morning breaks and still there is no sign of Vencarlo Orisini. As the party leaves his house, Balian spots a shadowy figure trying to hide in the ruins of the burned training facility. The ranger rushes over, his greatsword blazing in the light of the morning sun. The shadow scurries backwards, stumbling over his own heels and falling flat on his bottom in the ashes. In the black dust Balian recognizes the face of one of Vencarlo's students: Amin Jalento, captain Jalento's boy.\\

"You are alive! I saw you enter that deathtrap yesterday evening ... those assassins were waiting inside. And when you didn't come out, I feared the worst!"\\

"So, what are you saying? You saw us walk into this ambush without warning us?" Quint raises his eyebrows.\\

"I'm sorry, I was hidden in that building up there, squeezed between the beams of the roof. A narrow hiding space, not easy to get out of, but a good place to remain from view. Anyway, after the master was forced to flee the day before yesterday, I've been waiting for him there."\\

"Wow, too much information at once, Amin, why don't you start at the beginning?" Sjo interjects.\\

"Of course, I apologize. You know I'm a student at master Orisini's school. I was on the island attending classes when the quarantine hit. My master was gracious enough to allow me to stay as his guest. My fellow students have all either left or died from the plague, but fortunately Vencarlo and I did not get sick. Then, two nights ago, we were set upon by five of those red killers in their ant helmets ..."\\

"Not ants, mantises actually, red mantis assassins to be exact", Quint clarifies.\\

"Gods, no ... those notorious slayers are after my master? They say the red mantis don't quit until they finish their contract. Then it's even worse than I feared. Anyway, my master held them at bay while he shouted for me to run. As I glanced over my shoulder, I saw how he took down one of them, but there were too many, so master Orisini knocked over a brazier and set the academy on fire, giving him the opportunity to flee as well. I haven't seen him since. I've been hiding, waiting for him to return. That's how I saw those two killers sneak into the house yesterday. They even lighted the fireplace, perhaps they were trying to suggest that I was in the building."\\

"And then we arrived. It didn't occur to you to shout a warning?" Balian grumbles.\\

"To be fair, I had dozed off, it was late after all. I was awakened by you knocking on the door ... before I could react, you had entered. By the time I had crawled out of my hiding place and made it to the door, I heard the sound of battle inside. When you did not come out again, I assumed you had been slain. So I hid once more ... I'm a coward, I know, keeping out of harm's way is the only tactic I know to survive."\\

"And what of you master, where could he be?" Quint asks.\\

"I don't know where he has gone. The master never tells me where he goes. Even in the days after the quarantine he left the house regularly, mostly at odd hours in the night, sometimes not returning until the morning. At one such return his clothes were bloody - he told me he had fought off a thief, but I'm sure there was more to it than that. Furthermore, in the days before the red mantis attack, my teacher had a singularly strange houseguest visit him on three separate occasions - a man with wild hair and a jittery habit of looking about. I guess he was some kind of artist, for he had blue stains on his hands and clothes."\\

"Salvator Scream, a doom-thinking painter who has been going through an extended 'blue period', no doubt", Sjo muses.\\

"That is probably correct, he definitely had this 'po\'ete maudit' vibe going for him. Still, Vencarlo always spoke to him behind closed doors. On their last meeting I heard my master raise his voice in anger, a rare thing, I assure you. Vencarlo Orisini is known for his patience and control. In over a year, he never got mad at me even once, despite my clumsiness and lack of progress."\\

"Don't sell yourself short, friend. You will find your courage yet", Sjo balms. "Still, one thing is clear, this place is no longer safe, not with the red mantis about. Do you have any other place to stay?"\\

"I don't. I live on the mainland, I just come here for my classes. Master Orisini is the only one I know here."\\

"So you don't know anyone at the Endrin military academy either?" Balian asks.\\

"Well, I knowof "Well, the academy is where we're going right now, perhaps you can stay there, you're the captain's son, after all", Balian smiles.\\

