%!TEX root = ../crimson_throne_book_main.tex
% 2015-12-24
Sjo and Balian both accept Krjoun's challenge. Sjo enters the game of Sredna first. He removes his armor and steps up to his opponent fearlessly. Although the healer is of impressive height, Krojun still towers over him and the barbarian's chest is as broad as an ox's. Krojun gets on all fours and signals for Sjo to do the same. Next both men swing a loop of leather behind their necks and crawl back until the thin cord is pulled tight between them. Sjo already feels the leather dig in the back of his neck and skull. He fears this will get quite uncomfortable.\\

One of the Sun clan burn riders explains that the opponents have three breaths to try and stare each other down before they start pulling. Krojun lets out a deep growl and gnashes his teeth, but Quint mocks his effort, giving Sjo the upper hand in this first part of the battle. Then the tugging part begins. Krojun tries to go for a quick victory, but his hasted attempt fails as the sand on the ground slips underneath his hands and Sjo manages to withstand his force. Frustrated the barbarian slips into {\itshape rage} , fuming at the mouth and pulling like a madman, but still Sjo resists and the healer is actually the first to drag his adversary forward. He sees a glimmer of respect in Krojun's eyes, who now flexes all his muscles and claws his fingers deeper into the ground to get a better grip. Now the barbarian pulls Sjo backward, but our friend tugs him right back and it seems that their tug-of-war competition does not budge far from its starting point. In the end it is the towering barbarian's natural stamina that wins out, as the bite of the leather strap in his skull forces Sjo to bow his head and relent. Still he resisted Krojun much longer than expected and the great burn rider has to catch his own breath after the game. {\itshape``You fought like an auroch calf, you should be proud}'', he compliments Sjo. Next up is Balian. Quint gives him a quick pep-talk and throws in a {\itshape heroism} spell to boost his friend's power. Although the ranger is broader than Sjo, he does not stand as tall, so standing opposite Krojun, he looks almost dwarfed. {\itshape``It is a good thing we're getting to the ground for this,}'' Balian smiles, {\itshape``won't be as much of a height difference.}'' The staring competition gives him a slight advantage over the barbarian, but when the tugging starts, Krojun manages to pull the ranger back a couple of steps. Again the hulk activates his  {\itshape raging} powers and pulls Balian even further. Fortunately the ranger has better luck resisting the sting of the leather in his neck than Sjo and as the match continues he regains the territory he lost in the beginning. Both men's heads turn red and purple as they growl and pull like great beasts of burden. The excitement of the spectators grows as the contest lasts and Balian even gets some cheers from several Skull clan warriors. The cord tears into the back of both contestants' skulls, drawing blood on either side. Sweat runs wildly over their backs and foreheads as they try to bite down the pain. The ranger is hoping to hold out until Krojun's  {\itshape rage} wears down, but a final cut of the leather cord forces him to admit defeat right before the barbarian's frenzy runs out. Exhausted Krojun rolls over on his back to recover from the effort, before getting up again. He offers his hand to Balian to pull him to his feet as well. {\itshape``Congratulations, lowlander, it must have been five years or more since I came across an opponent like you}'', he sighs with a gleam of true respect in his eyes. He pats the ranger cheerfully on the shoulder and then returns to his own men, who hail him for winning this formidable match. Sjo's and Balian's valiant show of force has gained them the admiration of several Skoan-Quah warriors and Quint takes advantage of the fact that he has their ears to convince them of the fact that Korvosa is far from defenseless. In fact, the number of warriors in the city grows day by day, for the new queen is building her own great army. At the end of the evening, the companions are given a yurt in which they can sleep.\\

