%!TEX root = ../crimson_throne_book_main.tex
% 2015-07-18
Quint takes the note from her.\\

 {\itshape "Dear Cressida}  It has been a while since we have talked. Since the Gray Maidens locked off Endrin Island from the rest of the city, I have been stuck here. At least officially. Let's just say that one does not simply walk out of Old Korvosa these days.\\

Things have been chaotic here. The plague has ravaged the district. No family has been spared. Without the support or hope from the city's churches many people have fallen prey to despair or disorder. Several buildings lining the quays have been torched and gangs have taken over the streets. Some madman has crowned himself 'emperor of Old Korvosa', you might have heard of him, Pilts Swastel, the deranged owner of a detestable and perverse theatre, Exemplary Execrables. Fort Korvosa is the only place that is still safe, for that is where the Arkona's rule. But the rest of our district is in dire straits.\\

Anyhow, Old Korvosa might very well be the garbage dump of Korvosa, it is in the city's filth that one finds the most surprising information. I have uncovered some vital clues regarding the queen. You know that I have distrusted her from the very beginning. I do not grasp the full picture just yet, but I fear that dark magic is at work here, possibly a pact with a devil of some sort.\\

Can you get in touch with our new friends? You know, those young heroes who have helped out before. I have not been able to follow their adventures of late. Are they still safe and in good health? Can you ask them to pay me a visit? The likes of them should have no trouble crossing the Narrows of Saint Alika to Old Korvosa, despite the quarantine. They might even be safer here than on the mainland, after all, there are no Gray Maidens here. The queen has left Old Korvosa to rot, but at least this frees us from her choking grasp.\\

I greet you cordially and remain your faithful friend,\\

you know who ..."\\

