%!TEX root = ../crimson_throne_book_main.tex
% 2015-06-06
\section{16 Erastus 4708}

During the third watch Balian perceives a noise outside and silently wakes up his partners. As they rise from their bedrolls a cute little bunny hops in through the front door. It looks at the companions with big, innocent eyes and speaks: "Greetings, you brave men of Fort Thorn. Are you the heroes from the stories of old? We are looking for fearless warriors to protect us from the terror of the Vale." Puk looks charmed by the fuzzy bunny, but his human friends see the rabbit for what it really is, an illusion. Sjo walks over to the window and yells out into the night: "Stop this ridiculous charade and show yourself if you want to talk to us!" He peers into the darkness outside, hoping to pick up someone with his darkvision, but he is surprised by the sweet voice that comes from behind him, inside the keep: "Okay then, here I am."\\

A ginger-haired female pixie suddenly appears out of thin air. "My name is Lorana. It looks like the gods have answered our prayers and sent you to help us."\\

"And what is it that we are supposed to help you with, then?" Quint wonders.\\

"Oakenbrow, the nasty horseman, of course. He is the one who killed my second cousin Lendil who you found nailed to the door. We have no idea why, but since a fortnight the horseman has been on a killing spree, he's killed over a dozen of my kinsfolk. Our king Tirmando is in desperate need of help against this murderer. Will you please come with me and speak with our majesty, mighty heroes?"\\

"Well, we don't know you or this Oakenbrow, so we can't make any promises. Still, it certainly looks like something is amiss in this little paradise of yours", Sjo answers. "Of course, we're not here by chance, we're looking for something that we can only find in this valley. Do you know of any red mushrooms growing anywhere?"\\

"His highness will definitely be willing to aid you with that quest, noble strangers. If only you come with me."\\

"Well, give us until morning to rest up. Then we will go with you", Sjo tells the tiny fey.\\

And so it goes, when the sun has risen again, the red-haired fairy returns and leads the companions across the river into the forest. After two hours through the dense woods the travelers reach the court of the pixie king: a tall hollowed-out tree. Lorana takes her guests to the royal hall in the heart of the tree. Puk immediately loves these cozy quarters, but his friends have to bend over backwards to fit into the tiny rooms. On a green throne, with a leaf mantle on his shoulders, sits the troubled king, Tirmando. His eyes betray a touch of relief as the heroes enter.\\

The king explains that the centaur Oakenbrow, who has lived in the valley for many years with his younger sister Mirala, has suddenly become aggressive for no apparent reason. So far he has killed fourteen pixies and he shows no sign of stopping. Tirmando has no clue what motivates the centaur, but is in dire need of help. He requests the adventurers' aid in neutralizing the threat. In exchange he will gladly show them where the blood cap mushrooms grow, but he also offers his cloak as a reward.\\

The companions agree to help the pixie king, as he does not require the centaur's death, but rather an end to the hostilities. Quint inquires where they can find Oakenbrow and asks for a guide to show them the way. "The centaur and his sister live at Pointer's Rock. Furian, my subject, you know the girl well. You play with her all the time. You will take these gentle folk there." A tiny pixie, even small for his kind's size, reluctantly steps forward, but he does not dare to refuse his king's command.\\

The trek to Pointer's Rock takes the companions back north through more dense forest. Their guide Furian seems ill at ease. When the PCs question him about the centaurs, they quickly sense he is hiding something. It turns out he played with the centaur girl all the time, but her older brother never appreciated their frivolous games. He used to warn his sister time and again that she shouldn't waste her time with the irresponsible fairy, but she never heeded his advice. Three weeks ago things went wrong, terribly wrong. Furian took Mirala on a scouting trip to the dangerous Mistmoors in the south of the valley. Oakenbrow had always forbidden his sister to go there, but she went anyway ... because Furian talked her into it. While they were playing Mirala suddenly stepped into quicksand and started sinking into the muck. Furian lacked the strength to pull her out and desperately rushed back to Pointer's Rock to get Oakenbrow. By the time they returned, Mirala had completely disappeared below the surface. Her brother exploded in rage and would have killed Furian on the spot if he had had the right weapons. The pixie fled and has since witnessed how the centaur ranger has been exacting his revenge on the fairyfolk with newly forged cold iron weapons. Furian is the only pixie who knows the truth, but he fears informing his kin, because they will hate him for it. He is obviously heartbroken about what happened, but he begs the companions not to tell the king.\\

After a while the forest gives way to rocky hills. Furian draws attention to the highest one, which has some kind of stone spire on its back: Pointer's Rock. A small brook springs from somewhere on top of the hill and sends its water down in a magnificent waterfall. The entrance to Oakenbrow's lair is behind the chute, Furian explains. Sjo and Quint call out to the ranger before entering the centaur's home, but they find it empty. When they emerge an arrow flies past them and buries itself in Furian's little chest. The pixie falls to the ground, bleeding from a deadly wound. The arrow came from the bushes, some 100 yards beyond. Balian, Quint and Puk form a living shield in front of Furian while Sjo hurries over the treat the fey's injury. Quint calls out to Oakenbrow, offering his condolences and asking the enraged bowman to parley instead of fight. The centaur orders the companions out of the way, claiming that this is not their fight. He gives them one chance to retreat; all he wants is the malicious forest imp who led his sister to her death. "Oh, I warned him so many times to keep his hazardous games away from her, but the naughty trickster never wanted to listen. Now it's too late. All that counts is revenge!"\\

The companions try to reason with the grief-stricken centaur. They understand his sorrow, but no matter how many fey he kills, he will never get his sister back. They urge him to reconsider his plans for revenge, there has to be a better way than violence. In the end Oakenbrow concedes, he'll agree to a seize-fire until he has spoken to the pixie king. He wants the party to send Tirmando here, alone, so they can negotiate. He even gives his word not to harm the king during these talks.\\

