%!TEX root = ../crimson_throne_book_main.tex
% 2015-11-21
Our heroes spend the next couple of days in the great city of Janderhoff, sniffing up dwarven culture. Quint gets the opportunity to practice his mastery of the Dwarven language, while Balian refines his fighting technique, facing axe-wielding dwarves in mock combat. Sjo spends some time in the temple of Torag, admiring the art of enchanting armor. He also starts reading lessons, since he does not want to be an illiterate'barbarian' when he's going to marry a sophisticated priestess.\\

\section{30 Erastus 4708}

When their armor is ready, the companions prepare to leave. Puk also picks up a small range of special metal weapons and Balian buys a silver heavy mace. It might come in handy when fighting devils. Borrowing Kalepopolis' hippogriffs once more to return to the Blackbird Ranch, the party makes it there by the end of the day. The seneschal himself stays in Janderhoff.\\

Trinia is happy to see her friends again. She started painting a group portrait of them and she'd like them to pose for her so she can get their faces right. Balian tries to impress her by taking his shirt off and flexing his muscles, but the young girl smilingly tells him he'll be depicted in armor, so there is no need for this machoism.\\

\section{1 Arodus 4708}

That evening Zellara appears again, ready to perform another Harrow reading. Taking only the 'hammer' cards, she invites the heroes to draw one. Sjo picks the {\itshape the uprising} , a card that has shown up before in the readings. It is becoming abundantly clear that the path of rebellion that the companions have chosen offers no way back. Quint's hand falls on  {\itshape the beating} . Threats are arising from all sides and there are people out there who are specifically after the heroes. They will need to be prepared to face those challenges. Balian goes for  {\itshape the bear} , a card that depicts a 'docile' circus bear, but these wild animals are not so easily tamed. Danger can indeed hide in the guise of innocence. Puk ends up with  {\itshape the big sky} , in which slaves throw off their shackles under a bright sun. The companions will be instrumental in throwing off the yoke on the necks of those who are suppressed. In their full spread reading, Balian's past 'backfires' when {\itshape the idiot} now shows up in his draw. The ranger had so much fun last time, when Sjo drew this card, but now the joke is on him as his previous loss of dignity is laid bare.  {\itshape The liar} in his present clearly stands for fraud and deceit, which need to be exposed. His future is determined by  {\itshape the marriage} , which is Sjo's token card. But here it indicates that different people will have to be united. Quint is next. As always, his reading is much more unclear. Zellara suspects that Quint might have more freedom in writing his own destiny that people normally do, which is quite remarkable. {\itshape The midwife} in his past tells us that his arrival in this world was not a welcome one. The rakshasa lies on top of his present. Normally this creature is treacherous and deceitful, but the card's position in the positive top row suggests that Quint's mastery over influencing other people might actually be a force of good.  {\itshape The crows} are part of his future: they are dangerous, even deadly opponents who can attack at any moment, but there is hope, because justice can prevail.  {\itshape The theatre} in Sjo's past reveals he played a lot of roles before he finally came into his own. The present has  {\itshape the mute hag} : dark pacts are being forged and are working against the party.  {\itshape The trumpet} is normally a good card, as it depicts the most loyal of angels, but its opposite position in the spread, in the negative bottom row, reveals that Sjo might be forced to take steps that conflict with his character, to get the job done. Puk's reading is the clearest one again. {\itshape The tanlged briar} stands for hard times in the past, but its positive position in the spread indicates that the Halfling overcame his demons.  {\itshape The owl} in the present has a needle and thread in its beak. The Halfling will play an important part in sewing together parts that will be hard to unite.  {\itshape The lost} stand for a future in which the 'insane' will try to take over. The companions will have quite a struggle on their hands if they want to stop these forces of insanity. Sjo also asks Zellara's ghost how she felt in Korvosa of late. She confirms his suspicion that it's getting increasingly harder for her to manifest in the city, as if otherworldly forces are preventing her from revealing herself. She does not feel this resistance here in Harse, though.\\

\section{3 Arodus 4708}

By three in the afternoon Jasan's sister-in-law arrives at his ranch. Derdra is a seasoned ranger, not the 'urban Balian' type, but an outdoor one. She is well into her thirties and makes a solid first impression. She seems to have a close bond with her horse, a brown mare who goes by the name of Sasha and whose manes match Derdra's hair. The woman picked up the latest copy of the {\itshape Korvosa Herald} from a merchant in Harse. The companions read up on recent events in Korvosa; they are happy to learn that the cure is finished and that it is working miracles. Even the quarantine of Old Korvosa has been lifted. Derdra agrees to act as a guide to the party. \section{4 Arodus 4708}

The companions return to Janderhoff on the hippogriffs and return the flying mounts to seneschal Neolandus Kalepopolis. Derdra takes a number of horses from Jasan's ranch and meets up with the party in the Dwarven citadel.\\

\section{5-6 Arodus 4708}

The companions leave Janderhoff on horseback and make their way across the Korvosan hinterlands. While the lands are still suited for farming, the fertile stretches of farmland seem to creep ever closer to the river, the more the companions travel north.\\

At the end of the second day, they arrive in Sirathu, the poorest and farthest removed of Korvosa's holdings. It is a simple town indeed, with simple and dusty houses, although the center square is quite refreshing. The air smells sweet here and colorful flowers surround a white marble fountain which supplies a steady stream of the clearest water. The heroes find a place to sleep in {\itshape The Royal Hare} , a stable turned inn. Balian sarcastically remarks that Sjo will feel right at home here. Derdra draws the party's attention to a straight line that marks the horizon to the north. She explains that it is the Storval Rise, an enormous cliff that separates Korvosa from the barren Cinderlands. {\itshape``Kaer Maga is right about there}'', she points. Quint remembers the stories of the local young girl who revealed herself to be some sort of prophet of Pharasma, a new Saint Alika, so to speak She was also the one who issued the warning that the opera in which the companions participated - {\itshape The Passion of Saint Alika} - faced a great danger in the last act, readying the heroes to interfere when former thug Erik Brolan tried to assassinate lead singer A\"isha Leroung. Quint seeks the girl out to thank her. She has unsettling blue eyes that constantly seem to stare in the distance. She reacts rather coldly to any interaction, as if she is in higher spheres, but she does tell the companions that the Lady of Bones has a soft spot for them. \section{7 Arodus 4708}

As the companions travel further up the road, the cliffs on the horizon become ever clearer and more impressive, finally rising to a gigantic stone wall of a 1,000 feet high. Even more daunting is the massive waterfall that crashes down, where the Yondabakari River breaks through the stark line of the cliff's top. A couple of miles down the road another monumental feature stands atop the Storval Rise: the cliff-top city of Kaer Maga. It is supposedly built inside the ruins of an ancient fortress: a six-sided ring of 80-foot-high seamless stone, stretching for more than half a mile in diameter. The city has been a refuge for exiles, misfits and ne'er-do-wells for many centuries and houses a wide variety of races. It is a place where anyone can fit in.\\

It feels as if Kaer Maga actually stares down at travelers at the foot of the Rise, for the rocks supporting the fabled city have been hewn into the massive likeliness of long-forgotten kings. These colossal heads spew forth the city's sewage from their open mouth; the foul-smelling water cascades down a thousand feet of vertical cliff, but as much as they offend the nostrils, they are a delight to behold.\\

A small tent camp surrounds a couple of stone buildings and a set of huge bronze double-doors at the foot of the cliff: the Twisted Doors to the Halflight Path, the only way into the city above. The way up winds through endless ancient tunnels in the rocks and treacherous goat paths along the exposed cliff face. Derdra explains that they will have to enlist the services of the Duskwarden, the guardians of the Halflight Path.\\

