%!TEX root = ../crimson_throne_book_main.tex
% 2015-04-25
\section{8 Erastus 4708}

The next morning Sjo pays his girlfriend Larella a visit in the medic force hospital ,which is overflowing with the extra patients who were brought over from the Hospice of the Blessed Maiden. He helps out for a while, taking care of the many sick.\\

Quint has set his mind on infiltrating the castle as a servant and decides to stake out the place for a couple of days to get a picture of the every-day comings and goings at the palace. He dresses up as a commoner and hangs around Castle Korvosa for the rest of the day.\\

Meanwhile his friends head over to the temple of Pharasma to sell off some of the loot they found. Brother Cedrik, the priest they saved from the undead in the catacombs under the mortuary, is the acting accountant they have to deal with. Sjo asks him if anyone in the temple would be able to find out if a certain person has already passed through Pharasma's Boneyard or not. Cedric is no expert on the matter, but says that the Lady of Graves is not known for sharing such knowledge with mortals. Strange as it may seem, divination is much more the domain of wizards than priests, especially if you have specialists on the subject. The Acadamae definitely has an accomplished diviner, as every school of magic is taught there by an experienced professor. Of course, the Acadamae has never had an open-door policy and since the death of the king they have secluded themselves even more from Korvosan society than before. So getting in touch with this person might prove very challenging. Sjo uses some of the new funds to pay off last month's tax debts and buys two magical bucklers for Quint and himself. He also gets a {\itshape potion of remove blindness} for the next time Puk gets robbed of his sight. Better safe than sorry, he figures. At the university of Korvosa, alchemist Sirtane Leroung is still working on a cure for the plague. She is very hopeful: the books and notes which the party brought her from the temple of Urgathoa, prove a big help in her research, even though they do not mention a remedy as such. She is also performing tests with the immune Varisians' blood. Puk pulls out the vial he filled with Nesia's blood last night and asks professor Leroung to take a look at that too when she has the time. He does not tell her where it comes from, though. Sirtane says that her priorities lie with the cure for now, so it may take a while before she can spare a moment, but when she does, she will be glad to examine the blood. She also refers the companions to Tepest Geezlebottle, the gnome professor and headmaster of Theumanexus College, Korvosa's smaller school of wizardry, for advice on divinations.\\

Puk, Sjo and Balian make a quick stop at the Citadel and ask Field Marshal Kroft to have a wanted poster made for Rolth. They agree to put up the reward money of 1,000 GP if the necromancer is brought in alive. Afterwards they head to Geezlebottle's school. The gnome wizard is no master of divination, explaining that the most efficient spell to get an answer to the question if someone is still alive, is {\itshape contact other plane} , but such powerful magic comes at a high risk: the wielder of this magic runs a substantial chance of losing his mind for a couple of weeks, the worst fate a magician can suffer. Moreover, Geezlebottle does not know this spell, as far as he knows, only Norva Allesain, the head of the divination ward in the Acadamae, does. The gnome does master the art of  {\itshape scrying} , which might indirectly prove that someone is still alive. He agrees to study two of these spells for tomorrow. 