%!TEX root = ../crimson_throne_book_main.tex
% 2015-07-18
\section{20 Erastus 4708}

Late in the afternoon of the 20th the companions reach the gates of their home city. They immediately head to the university, to hand the blood cap mushrooms to professor Sirtane Leroung. She instantly sends an envoy to warn the castle. Quint feels a bit surprised, but Sirtane eases his mind by saying that the whole city is eagerly awaiting her cure. She gives him the latest issue of the {\itshape Korvosa Herald} , which has an article on the topic:  {\itshape Cure for the plague just around the corner!} . Her brother-in-law, who publishes the newspaper, insisted on it, Sirtane explains. There is also a report on the treacherous plague doctors and the quarantine of Old Korvosa. The history of Korvosa on the back is devoted to the reign of queen Domina and her son Eodred II. Puk also informs about Madam Nesia's blood which he collected after she exploded into a sea of sanguine fluid. Fortunately Sirtane has found some time to examine it. The blood clearly showed signs of residual transmutation magic of a very high order. She believes it to be a weird modification of the {\itshape simulacrum} spell, powerful magic that allows a magic-user to construct an illusionary double of someone from snow and ice. This spell requires a very accomplished caster and costs thousands of golden sails in ingredients. In Nesia's case blood was used instead of ice and snow, which is clearly a more powerful ingredient, but the fact that Nesia had no memories and became sick and died, shows that the spell that created her had not been perfected yet. Mages who master this level of magic are extremely rare, in Korvosa they can probably only be found in the Acadamae, Sirtane muses. By the time Sirtane has finished her expos\'e on Nesia's condition, her messenger returns from the castle. He says that the queen has ordered her and her family, and also the companions, to come to the castle tonight, where Ileosa will address her people for the first time in weeks. Our friends decide to return home to bathe the dust of travel from their skins and dress up for the occasion.\\

Upon arriving at the villa the companions notice that the three kids are nowhere to be found. There is no note either. Sjo is worried that the children got sick again; after all, it's been ten days. A sudden knock at the front door pulls the healer from his contemplation. There is a beautiful Varisian woman at the front door who insists on talking to Balian. She introduces herself as Ravenna and Sjo sees that she is not alone, another man is waiting for her in the street. Balian joins the Varisians and agrees to go with them, without telling his friends where he is going. It looks important, as the ranger is willing to give up a visit to the castle for it. Puk decides to follow the ranger stealthily and tails him to a house in Thief Camp. The building looks well guarded, so the halfling sees no easy way in and returns to the villa to prepare for the queen's speech instead. Unlike Balian he does not want to pass an opportunity to gaze on the beauty of the queen.\\

In their smartest attire Sjo, Puk and Quint go to the castle, where a small crowd of the city's finest has already gathered. Everyone is quite curious. At the foot of the grand stairs up the mastaba Puk spots Cressida Kroft. She wonders as well what this meeting is about and points out that there are a lot of Gray Maidens present. The Castle almost looks like a fortress preparing for battle.\\

The guests are allowed into the throne room where the waiting continues. The room buzzes with impatience when the queen suddenly appears out of thin air, flanked by the commander of her Gray Maidens and a heavy, bald man - clearly a spellcaster. His robes cling tightly to his firm body. Ileosa is wearing a new crown with spikes that look like giant shark teeth. While everyone falls silent, Quint calls out: "Queen Ileosa, it has been too long, it is good to see you again." The queen returns his words by briefly piercing him with her gaze, which she then sends over the other guests in the room. She beams with confidence when her lips curl into a smile and she addresses the crowd:\\

"My dear citizens, there is light at the end of the tunnel. Hold on a bit longer and the plague that fell over us will be a thing of the past. We have a cure!\\

I know, our recent path has been riddled with hardship and challenges. There were many casualties and fear overtook us all. But rest assured, the nightmare will soon be over. The university of Korvosa has developed a medicin. Just a few more days and life will rule the streets again instead of death.\\

Korvosa is indeed a beautiful city and many envy her for her riches and pleasures. They try to crush us with riots, but we resist! They try to starve us, but we survive by sheer will. They try to cut us down with disease, but we arise stronger than ever. The enemy comes to us in many guises, as opponents or as allies. Treachery runs deep sometimes. The physicians who came to the city, weren't healers who were trying to make us better, but the true architects of the plague itself! But we triumphed over them all!\\

Still, all these attacks have taken a heavy toll. Thousands of citizens fell to the disease, everyone of us has lost friends or family. The Korvosan Guard is crippled and the Sable Company is broken by numerous losses. None of these troops have the strength left defend our city properly. So I proclaim that henceforth the Gray Maidens are the new protectors of the realm and their commander Sabina Merrin is the general of all military forces in Korvosa."\\

A wind of discomfort waves through the crowd, but Ileosa is not finished yet. She hails the heavy man to her side: "This gentleman is Togomor, my new advisor who will take up the duties of castle seneschal from now on.\\

I have also decided to dissolve the Sable Company and merge their depleted numbers with the Guard, making one whole from two halves. Commander Endrin of the Sable Company, please approach!"\\

The crowd is baffled as Marcus Thalassinus Endrin steps forward. Quint uses the consternation to utter the words of a {\itshape detect magic} spell and sees that the queen, Merrin and Togomor all bear powerful magic. Especially the crown radiates a strong glow. In the meantime Endrin makes his way to the podium. "Commander, I hereby strip you of your command and ask you to surrender your badge of honor."\\

As Endrin does so, he trembles. He reaches for his badge, but instead of handing it over, he throws it at the queen, cutting her left cheek. Everyone, including Ileosa, is shocked into paralysis for a few moments, long enough for Endrin to bellow out: "Your shameful reign ends now! Korvosa will be free again!" At that point his other hand appears from under his cloak, firmly grasping a loaded crossbow. He aims at the still-locked queen and pulls the trigger. His bolt strikes Ileosa straight in the temple: a deadly shot!\\

Yet the queen does not fall.\\

She doesn't even tremble.\\

With incredible speed she regains her composure and yanks the bolt from her head. Before the blood from her wound has time to trickle down her cheek, she rushes over to Endrin. With her free hand she grabs the man by the throat and lifts him off the ground. Her other hand wields the bolt as a dagger, which she hammers between Endrin's eyes. The commander's lifeless body tumbles to the floor, as Ileosa turns to the crowd and cries out: "This shall be the fate of all enemies of Korvosa! Mark well his death! All traitors will suffer the same fate!"\\

A second later Togomor steps forward, laying his hand on Ileosa's shoulder and teleporting her out of the throne room. Sabina Merrin orders everyone out and her Gray Maidens start pushing the crowd towards the exit. Field Marshal Cressida Kroft is stunned and horrified by what she has seen. She takes the companions to her office in the citadel to speak with them freely. Her gut tells her to step down from office, but she fears that a Gray Maiden puppet will replace her then, so she decides against her gut feeling. She hopes that by complying with the queen, she can exert the largest possible amount of control to see her soldiers safe. Quint is angry: Endrin's peaceful approach has only lead to the man's untimely death. The bard feels like the city is slowly being murdered in front of his eyes.\\

A knock on the door disrupts the conversation. A guard from the Longacre Building bears a letter for the Field Marshal. It was given to him by a boy who was arrested for escaping from Old Korvosa. Kroft thanks him and starts reading. "This comes from Vencarlo Orisini," she says, "it looks like he is looking for you. Here, read it."\\

