%!TEX root = ../crimson_throne_book_main.tex
% 2015-05-09
\section{9 Erastus 4708}

Quint gets two rooms at an inn, one in his own name and the one next to it as Marcus. This place will serve as his place of operations during his undercover mission. This means he will have to miss out on the {\itshape commune} session, though. Puk, Sjo and Balian attend the morning service in the Cathedral of Pharasma. Afterwards they meet up with Archbishop d'Bear for the divination attempt. "As I told your friend Sjo yesterday, you have come to the right place to ask your questions. Pharasma shepherds our world's recently-departed souls to their final reward. All have to stand before her throne in the {\itshape Boneyard} , to be judged. She alone decides where each of us will spend eternity. As goddess of life and death, she already foresees what our ultimate fate will be, which is why she is also the mother of prophecy. Still, she accepts that we all have room to shape our own destiny, which is why she reserves her ultimate judgement until we finally stand in front of her. You have proven yourselves friends of the {\itshape Lady of Graves} , and as such you have deserved this favor of her. But since we are all free to shape our own lives, the  {\itshape Mother of Souls} frowns upon divine interference, so she will bestow the honor of her insight upon you only once. I hope you came prepared, for your window of opportunity will close fast. Be ready, my friends, for you will not face the high one again until your day of judgement." Keppira d'Bear raises her hands to the skies, takes a deep breath, closes her eyes and utters the holy words. All goes silent and it feels like the world around the companions disappears, leaving only the here and now. When the archbishop opens her eyes again, they are white and she speaks in a voice that is not her own.\\

"MORTALS, YOU HAVE COME TO ME FOR GUIDANCE. ASK AND I WILL ANSWER."\\

Sjo can't help but feel impressed and needs a little nudge from Puk to snap out of his wonderment: "Gulp ... my Lady, we are humbled in your presence ..."\\

"Ask the questions", Balian grumbles under his breath.\\

"Oh yes, my Lady, is Neolandus Kalepopolis, the seneschal of Korvosa, still alive?"\\

"YES."\\

"Is he being held prisoner?"\\

"YES."\\

"Are Kalepopolis and Blackjack the same person?"\\

"NO."\\

"Is queen Ileosa Arvanxi a follower of Urgathoa?"\\

"NO."\\

"Is the one who ordered the plague on Korvosa a member of an old Chelish noble house?"\\

"YES."\\

"Is queen Ileosa involved in the murder of her husband Eodred Arabasti?"\\

"YES."\\

"Are there members of the Red Mantis assassins present in Korvosa at the moment?"\\

"YES."\\

"Are there Red Mantis assassins in the Castle?"\\

'YES."\\

"Was the Red Mantis contacted by Ileosa or someone of her entourage?"\\

"YES."\\

"Was the initiative to contact the Red Mantis taken by Ileosa?"\\

"UNCLEAR."\\

"Is the queen being misled by one of her advisors?"\\

"YES."\\

"Are Rolth the necromancer and Balian's sister Alika still in Korvosa?"\\

"YES."\\

"Did the artists Lucian Lycan, Guy Nolin and Archibald Meerwater die because of a shift in the pantheon?"\\

"NO."\\

Keppira closes her eyes again, releases a deep sigh and lowers her head. When she looks up again, she is trembling. "I have not performed this ritual often," she breathes, "it is the most wonderful paradox you can imagine, to feel the wisdom of the goddess flow through your veins, but our simple mortal coils were not meant for such wonders, so it leaves me exhausted and wanting at the same time. So strange, like a drug addicted drug addiction. You must excuse me, I must rest. I hope you found what you were looking for."\\

---\\

Meanwhile Quint has made sure to arrive at master Jacob's at sunrise, disguised as Marcus from Old Korvosa. The head of the castle's stables puts him to work immediately, helping to muck out the horses' stalls alongside the two boys he saw here yesterday: Wade and Pip. Although Wade is the older of the two, it quickly becomes clear that Pip is the smarter one. The twelve-year old boy is very helpful and tells Quint what to do. "Cleaning up horse manure is not a difficult job, as long as you are willing to get your hands dirty", the boy teases. "Or you can just be smart about it and use a pitchfork", he laughs, while showing the newcomer how to swoop up the wet and dirty bedding while leaving the clean stuff on the floor. "All horses are different", he explains, "it gets easier once you get to know them. Just make sure to be thorough, or it'll be twice as hard to clean up tomorrow." Afterwards he also teaches Quint how to empty the wheelbarrow in a large cart. "You'll have to take that out of the city later, with Curtis", he says.\\

Quint really digs in and makes an excellent impression on the boy. In the meantime he learns who else works in the royal stables. Old Docus is an experienced horse trainer who hails from the breeders in Harse. His sight has diminished greatly with old age, but he knows his way around the stables blindly. He walks the animals in the yard with the aid of Billy and Bowen, twin brothers who are about Quint's age. They were hired four years ago by king Eodred himself after their father, who was a hippogriff rider in the Sable Company, lost his life in the line of duty. Quint also meets Ron again, the man who took the cook and the servant girl to the market yesterday. Ron is new at this job, since Greg, the old driver died of the plague.\\

When the stalls have been cleaned, Quint joins Curtis Kortval on a trip outside the city to get rid of the manure. Curtis turns out to be a hard worker, although he complains a lot. Apart from Greg, two more of his colleagues lost their battle to the plague, Matt and Kirk. Three others are still out sick, Porter, Ekkels and the only girl who works with them, master Jacob's own daughter Red Lisa. So everyone has had to step up to take over their chores. Curtis can also give Quint some insight on who works at the castle. Most of them are women, like Karina the cook and Mikki the kitchen help. There are also a number of cleaning ladies. The only male servants are Jorn, the simpleton who has to do the heavy lifting, and Scotty, the gnome handyman who's in charge of the repairs. Jacob's lads, as the stables workers are often referred to, were allowed into the castle on rare occasions, for example to celebrate a holiday with the other servants there, but they haven't been inside the palace since king Eodred took ill and died. Curtis has never met the queen's new advisor, but he knows the man's name: Togomor.\\

---\\

In the villa Puk tries his hand again at reading, but he quickly gets bored and heads off to the market instead to check out {\itshape Hedge Wizardry} , a shop that specializes in alchemy. Since he saw what alchemists like doctor Saulus or Sirtane Leroung are capable of, he's developed a bit of an interest in the matter. Phaeton Skoda, the shop owner, shows the halfling interesting goods that might be of use in his adventures, like smokesticks, sunrods or thunderstones. The small rogue is most intrigued by alchemist's fire, some kind of splash bomb, and the tanglefoot bag, which can be used to glue down people to the floor. Afterwards the halfling swings by Sirtane Leroung's laboratory. She claims to be making good progress on the cure, but she hasn't had time to investigate the blood sample yet. She'll only be able to do that when the crisis has been conquered.\\

---\\

At noon Balian slips off to Thief Camp again, to get an update on the search for his sister. Mob leader Batista Cadabrani tells him that his men have been searching around Westdock , the harbor ward where the {\itshape Hospice of the Blessed} was located, but they have found no trace of the necromancer Rolth or his dark-haired companion. With a deep sigh and a long silence Balian expresses his malcontent at the lack of progress. Batista explains that Rolth has evaded the law for over a decade, so the ranger should not expect him to be found easily. In the end Balian puts up the money for another day and takes his leave. ---\\

After lunch Sjo, Balian and Puk head over to the Theumanexus college, where the gnome headmaster merrily greets them. Sjo gravely explains that his scrying attempt will have to be done with the utmost discretion: no one can know who he scried on or which information the results of his attempts yielded. Geezlebottle promises to keep it all a secret. Then Sjo reveals the name of the first target: Neolandus Kalepopolis, who - he assures - is still alive. Since the gnome has never met the seneschal in person, he asks for a personal item that used to belong to the man in question, to facilitate his scrying, but the companions have nothing to offer him. Slightly disappointed the gnome weaves his hand over a bowl of murky water and starts mumbling the words of a spell. Puk picks up the name {\itshape Neolandus Kalepopolis} in the otherwise incomprehensible string of words. After a few seconds the wizard looks up: "I feared this would happen, my attempt did not succeed, I'm sorry. Maybe the target resisted my spell or he might also be protected from this kind of magic, I don't know. In either case, it's no use trying again today, it won't work anymore. Who would you like to spend the second scrying on, good sirs?" Balian asks him to scry on his sister Alika. Fortunately he has a personal item of hers to increase the chances of success: the little wooden dolls she made of herself and her brother as children. Geezlebottle says that this will be of great help. Again he does the incantation and this time he remains concentrated much longer, although the companions see nothing in the water. When the wizard finally opens his eyes again, he confirms that this time his attempt met with success. He saw a pretty black-haired girl, dressed in leather armor, sitting at a table with a skinny, blotchy man - clearly Rolth - and another thuglike individual. Geezlebottle's magic does not reveal any clue on her location, however. Sjo pays the small magic-user and takes his friends back to the villa.\\

In the evening Quint joins them as well. He gives them a full report on what he found out. The queen's advisor Togomor apparently is a professor at the Acadamae, the head of the transmutation department. If the rumors are true, he should be a quite powerful individual. Sjo also informs Quint on the {\itshape scrying} and  {\itshape commune} attempts. The friends discuss the divine answers to their questions until late at night. 