%!TEX root = ../crimson_throne_book_main.tex
% 2016-02-13
This tale contains even more inspiration from Eando Kline's adventure in Urgir. Walking through the gates of Urgir, the companions immediately see for themselves that this was once one of the greatest cities in the world, bearing a grandeur that not even a hundred generations of orcs could completely tarnish. Having witnessed the Sky Citadel of Janderhoff, the travelers thought they had seen dwarven architecture at its best, but the splendor of ancient Koldukar, as Urgir was formerly known, must have been truly breathtaking. A huge boulevard paved with marble fit for queen Ileosa's throne room stretches into the city, winding between monumental buildings and imposing statues that seem to grow from the stone itself. Supported by vast arches and buttresses edifices are crowned one atop another in a seemingly endless heap. Some of the grand avenues soar up this hill, while other thoroughfares become tunnels that dig into the city's heart, where the architecture is so dense as to become subterranean. This is the lifework of generations of dwarven master builders, a triumph of engineering and imagination.\\

Still, this wonderful city also bears undeniable signs of degradation: statues have been crudely defiled, a line of crumbled buildings sloughs down the mountain like a landslide, stonework meant to last millennia is cracked and buckles under the weight of ancient wounds. Sewage flows down the streets and gives the city entry a reek that clashes with its awe-inspiring glamor. And everywhere, truly everywhere, throngs of orcs, grunting, fighting, pushing and shoving, shouting and groping! There even seem to be some orc kids groping at Sjo's cloak, checking out how good it would look on them. Automatically the healer lifts his hand to strike the closest youth in the face, when another orc boy pulls the overconfident pest back and urges Sjo to keep his calm: {\itshape``Mister, mister, you are in Urgir, you not hit orc!}'' Next the kid tells the other teens off in Orcish.\\

{\itshape``Thanks, I guess,}'' Quint says, {\itshape``and what might be your name, lad?}''\\

{\itshape``I'm Uri, mister.}''\\

{\itshape``You think you could show us around town, Uri?}''\\

{\itshape``Sure, mister, you give me a hundred gold and I help you.}''\\

{\itshape``One hundred gold? How about one?}'' Sjo screams.\\

{\itshape``Uri not stupid, mister, one hundred gold for me being your guide}'', the boy answers.\\

{\itshape``Let's split it in half, twenty gold and you have yourself a deal}'', Sjo suggests.\\

{\itshape``Okay, mister, you pay me now and twenty gold it is.}''\\

Sjo digs up the cash and hands it to the little orc.\\

{\itshape``I take you to market, where all pinkskins go}'', the boy says while putting the money in his pocket. {\itshape``You follow.}'' At that he takes off and slinks through the crowd, looking around for possible threats and steering the party from left to right to avoid trouble. He might be small, but he definitely seems to know what he's doing. He leads his customers down some tunnels to a large underground square that buzzes with activity. Everywhere merchants haggle and hawk at their stalls, the only difference with other markets the companions have seen before, is the amount of aggression and violence. The best traders seem to be the burliest and most scarred. There is also a fair number of humans in the crowd, although they keep a relatively low profile and move with purpose. They mostly dress in dull colors made to blend in. Puk does spot one particularly well-dressed pinkskin trader, though, an elf at a stall with magic products, flanked on either side by an especially bestial orc guard.\\

Sjo and Quint walk up and ask him about his wares. He is in the business of arcane potions, he explains. Sjo ends up buying a {\itshape potion of blur} and a  {\itshape potion of fly} , realizing how costly these magical brews actually are on the open market. As the companions conclude the trade, a firm hand suddenly closes on Quint's shoulder. {\itshape``You, come along!}'' a deep voice barks. The bard spins and looks upon six orcs, armed with spears, in a ragged semblance of military formation. Upon their chests hangs the same black-fisted icon that the guards at the gate bore. The largest of these soldiers is the one with his nails biting in Quint's flesh. He is obviously in charge, not looking like the smartest one, but definitely the strongest. Yeah, orc logic!\\

{\itshape``You come now}'', he demands, {\itshape``if you fight, you will be broken, and then you come!}''\\

Uri eyes the offended bard with a look of submission and nods for him to follow this orc's command.\\

{\itshape``Lead the way}'', Quint replies in fluent Orcish. {\itshape``As you ask, we will come.}''\\

The unit marches the party deeper into the city, down a stretch of narrower tunnels. While the streets here are populated with nothing but orcs who clearly do not appreciate the passage of pinkskins, the swine-faced creatures move aside quickly when recognizing the emblem of the Empty Hand on the guards' dirty uniforms. Before long the group arrives at a squat, bunker-like building with a shield bearing the black fist above the door. Several orcs in guard garb mill about throwing dice or wrestling, briefly interrupting their activity to eye the new arrivals.\\

As they walk into the near perfect darkness of the building, Quint and Balian find themselves almost blinded. Sjo has no trouble observing the Spartan room and the ironclad door in the back. The leader of the unit knocks and is answered by a rasping voice from the other side: {\itshape``Come in.}''\\

A single candle illuminates this new chamber, which is furnished with a table and a few chairs. Several pages of parchment scatter across the desk's surface. Looking up from his seat behind the table is a bizarre figure. While obviously once tall and broad-shouldered, the orc's thin frame is hunched and bent. Long, stringy white hair hangs around his hollow face. This is the first time the heroes set their eyes upon a truly aged orc, realizing that this harsh culture does not normally support long lifespans. This orc must be quite gifted if he managed to get so old.\\

{\itshape``Newcomers?}'' he inquires in Orcish. In response the handler nods and points at Quint's pendant: {\itshape``Broken Spine}'', he grunts.\\

{\itshape``Good, go.}'' The guard turns and walks out, leaving the companions alone with the old orc.\\

{\itshape``Sit \ldots or stand}'', he gestures at the chairs in perfect common. {\itshape``Tell me, how did you got these badges?}''\\

While taking a seat, Quint coughs in his hand, hoping to murmur the word of an {\itshape innocence} spell to boost his skill at bluffing, but when he catches the gleam of intelligence in the eyes of the person across the table, he abandons the idea. Instead he informs his questioner of the truth how he and his friends helped the warlord of the Broken Spine clan retrieve some golden bracers from a disobedient underling, taking out a nest of harpies in the process. {\itshape``And why, do pray, are you in Urgir?}''\\

{\itshape``We here to check out the market, hoping to do some trading in the future}'', Quint replies.\\

{\itshape``Really}'', the old one says in a tone that makes it sound more like a word than a question. Meanwhile he toys with a small pebble that glides like water up and down his wiry fingers. {\itshape``What kind of goods?}''\\

{\itshape``Well, we're adventurers,}'' Sjo adds, {\itshape``we pick up some trinkets along the way. Urgir seems like the perfect spot to turn them to cash, without too many questions being asked \ldots except by you, of course, constable.}''\\

{\itshape``Just Ardax}'', the orc interjects. {\itshape``Ardax the White-Hair. Titles are for those without reputation.}'' His eyes shift from one companions to the other, then he tosses the pebble in the air, catching it without taking his gaze of Sjo. {\itshape``Very well, then I bid you welcome in Urgir. Good luck and \ldots be careful. Stay among your own kind. Ad if you ever bring interesting loot to these walls, don't be afraid to look me up. Just ask anyone for me, I'll know.}''\\

Next the old one calls out to the guards and orders them to take the party back to the market district.\\

Exiting the all-orc zone, the companions feel almost relieved to be back in the merchants' square. At least here they don't stand out as much, although Sjo deems it safer to pick up some gray cloaks and mimic the behavior of other pinkskins: look as regular as possible. Uri takes his charge to the {\itshape Pinkhouse} , an inn that caters to pinkskin newcomers. Marlo, the bartender, looks almost human, but upon closer inspection Puk spots some half-orc traits in his features and teeth. There are about two dozen patrons in the room: four half-elves, two elven mages with orc bodyguards, a handful of half-orcs \ldots the rest are humans. Sjo secures a room for three nights and orders a bread and meat platter for his table, along with some pints of stale ale. Quint tries to lighten the mood in this small hall with a bawdy song, but he quickly understands that the crowd finds his singing more troubling than relaxing. {\itshape``Don't stand out,}'' the bard reminds himself, {\itshape``that has to be my new motto here.}''\\

After sending Uri home for the night, Balian muses that he hasn't seen a single dwarf or Shoanti in the city. He can understand dwarves, their hatred for orcs is legendary, and the ranger can only imagine how furious and ashamed the stout fellows must feel at their archenemies' violation of dwarven culture. Sjo adds that in this corner of the world Shoanti and orcs hate each other almost as much as dwarves and orcs. Still, he would have preferred to spot a Cinderland wildling or two in the crowd, he admits. So the question remains: how do the heroes find a Shoanti in a city that does not welcome his kind? How can they locate this Saamesh character? Quint comes up with a brilliant idea. He suggests calling Sjo 'Saamesh' in public from now on, making sure bystanders pick up the name. Maybe that will draw out the real person.\\

The bard walks up to the bar and calls back to his friends: {\itshape``Hey Saamesh, you wanted another beer as well, didn't you?}'' Then he orders another round from Marlo, while inquiring whether dwarves or Shoanti ever visit the city. The bartender chuckles at the idea of dwarves in Urgir and claims not to know any Shoanti either. Quint realizes this search might prove harder than expected. He and his companions quickly finish their second drink and retire to their room.\\

