%!TEX root = ../crimson_throne_book_main.tex
% 2016-04-30
Using a newly acquired {\itshape teleport} scroll the companions magically travel to the gates of Janderhoff, the dwarven city. The guards recognize them and show them in, leading them to a beautiful manor house, where Neolandus Kalepopolis is now staying. The former seneschal is overjoyed to see the heroes again and offers them the hospitality of his dinner table. He is interested in every little detail of what has happened to them since they last met. Quint spins an enthralling tale, leaving out nothing. Kalepopolis delights at the party's success, but the impending war with the Cinderland Shoanti causes him distress. Kalepopolis has news as well. Although the Gray Maidens in Korvosa have been thorough in their efforts to root out the Sable Company, twenty-eight of the marines have escaped persecution and have been granted sanctuary in the city of Janderhoff. Some of them are even staying in the very manor where the young friends are now. The situation in Korvosa has greatly deteriorated over the last couple of weeks. The queen has tightened her iron grip on the city. Her maidens are ever-present and enforce the law without any measure of leniency. Anyone who even dares to utter a word of doubt concerning the new government is suspected of rebellion and immediately arrested. Most arrests quickly end in execution, often without a proper trial. Cadavers of these so-called traitors hang all over the city as warning signs. The common man is scared out of his wits and hardly comes out of his house, fearing the cruelty of the Gray Maidens. The queen's guard terrorizes everyone without discrimination, whether they be low-born or of noble blood. Apart from the merciless manhunt for surviving Sable Company marines, the Maidens invade every house to demand taxes, look for young girls to bolster their own ranks and -- a consequence of the Janderhoff dwarves' decision to cease trade with Korvosa -- to confiscate any and all objects made of iron, to have them reforged into ever more gray maiden suits of armor. The churches of Asmodeus and Abadar have openly proclaimed their support for the queen, while the temples of Sarenrae and Pharasma remain neutral. Vencarlo Orisini has returned to the city and stays in contact with Kalepopolis via carrier pigeons, sending him short messages in code. These updates are sparse and concise. Apparently Vencarlo has joined some kind of rebellion movement, but cannot provide details out of fear that his notes might fall into the wrong hands.\\

\section{24 Arodus 4708}

The next morning the companions are summoned to the palace of clan lord Ragnar Ironfist. Quint explains that an ancient evil has taken hold of queen Ileosa, and that he and his friends will try to fight this malevolence before the Shoanti come down from the Storval Heights to invade the Korvosan lowlands. He also reveals that his party has been to the great city of Koldukar, or rather Urgir as it is known now. Ironfist is excited to hear about the formidable dwarven sky citadel, but cannot hide his sadness at learning about the place's decline. The dwarven lord offers his guests the chance to stock up once more in the temple of Torag, leaving them in the capable hands of its high priest, Bardin Bronzebeard. The companions buy some scrolls of {\itshape heal} and  {\itshape breath of life} , and invest in some extra  {\itshape wands of cure light wounds} . This might be their last chance in a while to do so. Their biggest buy, however, is an adamantine  {\itshape holy} greatsword for Balian. Another {\itshape teleport} scroll takes the companions straight to Zellara's little parlor in Korvosa. Sjo immediately pulls out the Varisian fortune-teller's Harrow cards and summons her spirit. Zellara claims that it is getting ever harder for her to manifest in the city. It is as if a dark veil hangs over the city, clouding and smothering her mind. She offers to read the cards again for the companions before starting her search for the remains of sun shaman Coja Eyes-Aflame. This time the reading is centered around the star cards. During the  {\itshape choosing} , Balian's hand falls upon the Winged Serpent, who cautions him to use more tact. The queen-mother tells Puk to aid the helpless and hopeless, while the carnival card warns Quint to plan ahead. The owl ushers Sjo to combat the unnatural state of things that has taken hold of the city. The {\itshape reading} tells Balian to be careful of sinister and dark pacts that he will come across. Puk is told that he has been making the right decisions so far, though he is warned not to doubt too much and just act. The empty throne in Sjo's cards is a hint that fighting the 'powers that be' should not lead to a vacuum at the top, but the courtesan clearly tells him that masks will have to fall. Finally Quint is shown that what once seemed beautiful, might be rotten at its core. The peacock teaches him that he should do well to stand aside when this thing of apparent beauty passes by, lest he be petrified by it. After the Harrow reading, Zellara opens her mind to try and find a mental trace of the sun shaman. She spreads her arms and closes her eyes to expand her mind. Although spirits do not breath, she starts gasping and shaking uncontrollably. When she opens her eyes again, they have turned white. {\itshape``Oh, no!}'' she heaves, {\itshape``they have found me!}'' The next moment the Varisian spirit is sucked into the deck of cards, which falls lifeless on the floor. Using {\itshape detect magic} Sjo notices that the cards do not radiate magic anymore. When he picks up the deck, he doesn't even feel a trace of the Varisian spirit. It seems as if she has disappeared completely. This turn of events is a huge set-back for the party, since Zellara was to be their guide to Coja Eyes-Aflame. How will they find his remains now? Sjo is eager to see how his fianc\'e is doing and heads to the shrine of Shelyn. Walking up to Five Corners in North Point the party gets to experience the ominous atmosphere of Korvosa's streets for themselves. Very few people are out and about, and those who are, hurry along with their heads hanging low. A patrol of Gray Maidens is making 'house calls' forcing their ways into people's homes to collect taxes and confiscate iron goods. Since the queen's guards have drafted so many new members lately, one would expect at least some of these female soldiers to look inexperienced, but Balian feels they all seem more than comfortable in their full plate armor. Perhaps the new recruits are still in training somewhere, leaving their more seasoned colleagues to patrol the city.\\

Larella is very happy to see her future husband alive. She can update him and his friends on the current situation in Korvosa. Fortunately the plague has been cured, even in Old Korvosa. The quarantine of the island has been lifted as a result, but that does not mean that things are going well in Korvosa's oldest district. Big parts of Endrin Island have always housed some of the city's poorest inhabitants, and the recent plague and quarantine have worsened their plight considerably. Moreover, current circumstances of fear and oppression offer little hope of improvement.\\

Balian wonders about the state of the noble families. Larella says that the Arkona's have been even more withdrawn from society lately than the normally are. After commander Marcus Endrin's failed attempt on the queen's life, his family has been outlawed. His wife was executed. Larella has no idea what became of his three children. House Bromathan has paid dearly for its support to Endrin and the Sable Company. Lord Valdur IV rots away in the city's dungeons, while his wife Lady Merisse and son Valdur V have been placed under house arrest. His daughters were both drafted for the queen's forces. Like all recruits they have not been heard of since. Jeggare is still in place, but being one of the richest families in the city, they've had to pay huge amounts of taxes to the treasury. Members of House Leroung have also lost the queen's favor. They showed quite a lot of criticism for the new government in the latest issue of the Korvosa Herald and have been placed under house arrest as well. Their university has been closed until further notice. Sjo wonders if they would still be able to consult the school's extensive library, hoping he might come across more information that might lead to the discovery of the Sun Shaman's grave.\\

House Zenderholm is still around, but Larella suspects that the extremely lawful nature of its head, Hanging Judge Zenobia Zenderholm, will not mesh well with the queen's policy of playing judge and jury at the same time. House Ornelos is the only family openly supporting queen Ileosa. As a result none of the Ornelos girls have been forced to join the Gray Maiden army.\\

Explaining to the priestess of Shelyn how an ancient evil from the bowels of the mastaba under Castle Korvosa has taken control of the queen, it suddenly dawns on Quint that the 'Teeth of Midnight' might also have been the mysterious 'muse' that inspired several Korvosan artists in the past. These open, creative minds would probably have been quite susceptible to the dragon's feeble influence, which would explain why the Korvosan art scene has always been so morbidly and sinisterly inspired. When queen Ileosa discovered the evil artefact, it must have shifted focus to her completely, suddenly leaving the artists without a muse. Quint fears that Ileosa might be beyond saving: if the 'abandoned' artists already felt so desperate that they took their own lives, how could the queen ever survive a hundredfold stronger hold on her mind being broken? This new insight does not bode well for Ileosa, leaving her virtually no chance of a future.\\

