%!TEX root = ../crimson_throne_book_main.tex
% 2016-04-23
An hour after the Red Mantis ambush the companions leave the Skull Clan camp, joined by both Thousand Bones and Saamesh. After about half a day of traveling the party comes across another group of Skoan-Quah warriors, who are making their way to the shadow of the Great Flame as well. Like the members of Thousand Bones' tribe, they are following the call of the Sklar-Quah. The Burn riders who recruited them are still with them and do not seem overly pleased with the presence of Korvosan {\itshape tshamek} , but they accept the company of the strangers when Thousand Bones and Saamesh vouch for them. \section{22 Arodus 4708}

Over the next two days the group traveling with the heroes grows even more, to about 250 men and women. By the end of the afternoon on the third day they finally reach their destination: an imposing pinnacle of red rock that rises from the earth to a height of more than 200 feet. Millennia of erosion have shaped the stone like a big flame. In normal times this landmark would be an eye-catcher, but now Balian finds his gaze being drawn to the enormous encampment at its foot. Hundreds of tents and campfires cover the landscape.\\

Upon approaching the camp the companions see a delegation of Burn Riders moving in to welcome the newcomers. Puk immediately recognizes the giant that leads them: Krojun Eats-What-He-Kills. When he spots the companions, the barbarian gives them a small frown, but as soon as he picks out Saamesh in the crowd, the towering Shoanti jumps off his horse. With big strides he closes the distance between himself and the former spy. Grinning widely, he pulls his much smaller friend in a bear hug: {\itshape``Brother, have you come to join us in battle? My heart rejoices, you are more than welcome!}'' he smiles. {\itshape``Although I see you have not brought the best of companions}'', he continues, nodding at the Korvosans.\\

Saamesh returns the heartiness of the hug, but when he frees himself from the giant's grip, he replies: {\itshape``On the contrary, brother, my business in Urgir did not end well. These men saved me from the deadly clutches of the orcs. With the exception of you, perhaps, I cannot imagine being in finer company.}''\\

Krojun grins at the party: {\itshape``Then I welcome you as well, welcome to the brave warriors who will crush Korvosa and see justice done.}''\\

Krojun leads Thousand Bones, Saamesh and their Korvosan guests to a huge tent, bordering the foot of the Great Flame. While they make their way through the camp, the companions feel the hostile gaze of hundreds of Shoanti. The forces that have gathered here are truly impressive: there must be over two thousand warriors here, if not three; hundreds of horses and Puk even spots a number of mastodons, immense eliphants. The halfling stares at the titans in awe: {\itshape``Look, oliphaunts, no one at home will believe this!}''\\

The war- {\itshape yurt} is the biggest tent the companions have ever seen, fully covered in animal skins and leather hides. In front of the entrance there are two rows of totems, decorated with different animals and symbols. A plume of smoke rises from a hole in the center of the tent. Quint quickly cleans up everyone's attire with  {\itshape prestidigitation} , casts  {\itshape glibness} upon himself and  {\itshape tongues} on Puk and Balian, who do not speak Shoanti. Krojun motions for the newcomers to enter. Inside a few dozen men and women are gathered around a bonfire. Most of them look like experienced warriors, but others bear the symbols and ornaments of mystics. Upon entering Krojun's loud voice booms out: {\itshape``Honored  {\itshape jothka's} and wise fathers and mothers, we have welcomed many guests in our midst of late, but these visitors will surely draw your attention!}'' Everyone inside eyes the Korvosan heroes with a mixture of surprise and contempt. A broad-shouldered warrior with gray hair and a proud beard seems to share these feelings, but when Saamesh steps into the tent behind Balian, his face lights up. He walks up to the young man, places his hands on the spy's shoulders and calmly speak in a very low voice: {\itshape``So, son, you have finally turned your back on that stinking orc pit. Your father's heart leaps at your return.}''\\

{\itshape``Jothka}'', Saamesh answers with the same calm, {\itshape``the orcs of the Hold of Belkzen are strong and many, but their eyes are not aimed at the Quahs right now. I was less lucky, however, and personally got to experience their false gazes and sharp claws. If it wasn't for these men, you'd be short one son.}''\\

The bearded man turns to the companions, looking each of them in the eye: {\itshape``I offer you my thanks, tshamek. My name is Valkur Burns-In-His-Veins, the Quahjothka of the Sklar-Quah. I am the one who has called together the Shoanti to drive your people back into the sea. I take it that is why you are here. Speak, and we will listen.}'' Quint recognizes the word Quahjothka as the 'chief', not just of a single tribe, but the 'chief of chiefs' of a complete clan or Quah. This man is the head of all the Sun Clan people.\\

Valkur points to an empty place next to the fire where his guests can sit down. He squats on the ground a few yards further, between four other important-looking Shoanti: Laaron Strongbow, Quahjothka of the Lyrune-Quah (the Moon Clan), Fidru Glides-On-The-Wind, daughter of the Quahjothka of the Shriikiri-Quah (the Hawk-Clan), Akbat Whose-Tongue-Gives-Life, Quahjothka of the Shundar-Quah (the Spire Clan) and Durbeth Lifebreath, Quahjothka of the Skoan-Quah (the Skull Clan). The other Shoanti inside the war-yurt sit down as well, curious to witness this intriguing encounter. Krojun, Thousand Bones and Saamesh are among them, as is One-life, the chief of Thousand Bones' tribe.\\

The companions also introduce themselves and Quint explains why they are here. After the death of King Eodred, the 'Quahjothka' of Korvosa, his wife Ileosa took control and has been showing ever more apparent signs of evil and madness. The party has tried to counter this malevolence, but they found themselves insufficiently equipped or skilled to succeed, especially after Ileosa displayed virtual immortality when she was shot in the head by an accomplished warrior who had discovered her evil as well. The arrow to her temple should have felled an auroch bull, but instead it hardly phased her, as she simply plucked the bolt from her head and attacked the warrior with it. The 'feeble' Korvosan woman grabbed the seasoned warrior by the throat and lifted the 200 pound man off the ground as if he were a twig, killing him with one single blow. The companions now suspect that the queen is under the influence of the ancient 'evil' that was supposedly buried under the mastaba. If she is not stopped, queen Ileosa will destroy both of their people, Quint continues, referring to Thousand Bones' spirit quest and the vision of the shadow dragon swallowing the Shoanti horses and Korvosan wolves alike, leaving no one alive. {\itshape``That is why we have come: to learn more about this evil and find out how they can fight it.}''\\

Quint also knows that the Shoanti are wary of outsiders and only truly accept their own: other (full-blood) Shoanti or -- on very rare occasions -- non-Shoanti who have proven themselves worthy. That entails that the companions will have to try and acquire enough of the Shoanti's respect through their past deeds. So the bard spins a story of who the party is and what they have achieved. Sometimes he finds it hard to explain, because many urban concepts are foreign to his audience. The Shoanti do have a word for children who've lost their parents, but the words lacks the undertone of being abandoned as the term 'orphan' does, because the tribes always take care of such children. His listeners also frown when Quint describes the many excesses of 'corruption' he and his friends have fought over the last couple of months in Korvosa, probably reinforcing the wildlings' prejudice that so-called civilized society is actually anything but civilized and definitely not honorable. Throughout his tale Quint makes sure to point out that his party does not seek to cause conflict, but they do not avoid it when it slaps them in the face. Although they prefer a peaceful solution, they will resort to violence if necessary.\\

Sjo supports Quint's story by singling out the deeds he and his friends have accomplished that involved Shoanti. He shows the token of friendship they received from Thousand Bones when they provided aid in dire circumstances in the city of Korvosa, he recounts the time they freed an ancient Shoanti tumulus of vile bugbear intruders and offers the medallion they retrieved from that tomb to Akbat Whose-Tongue-Gives-Life, the Quahjothka of the Shundar-Quah, whose ancestors were buried there. He also points out that he and his friends took the shape of natural animals in their journey to the spirit world, which indicated that their hearts were in the right place, and connects that vision quest to the rescue of Saamesh from the orc city of Urgir. He ends his intervention with the defeat of the Cinderlander and hands the Shoanti killer's vicious weapon, his repeating crossbow, to the Quah's leaders as a sign of closure. Balian also adds an argument by reminding the council that the companions recently accepted Krojun's tests and -- even though they did not beat the Sklar-Quah champion in these challenges -- they did prove themselves capable. The broad-shouldered warrior confirms this claim with a smile of respect on his face.\\

When they have finished their plea, Valkur asks the companions to leave, so the council can deliberate what to do. He offers them the camp's hospitality until the council comes up with an answer. Saamesh leads the companions out and takes them to one of the many campfires. There he is greeted heartily and the tribesmen around the fire immediately offer him and his guests a place by the fire and food. A sassy young girl with bright red hair and white paint around her eyes hugs Saamesh for a long time. When he introduces his rescuers to her, she is very grateful that they saved her brother. {\itshape``My name is D'ari Firehair}'', she says, as she turns to the fire and tears off a chunk of meat from the roast. She offers it to Balian: {\itshape``Here, put some meat on those bones, you look like you enjoy a good piece of chow.}'' The ranger gratefully accepts and sinks his teeth into the savory flesh. {\itshape``Seems like it has been a long time since you had yourself some fine meat. Don't they like flesh in Korvosa?}'' she smiles, bowing forward and offering Balian a clear view into her cleavage. Then she reaches for the ranger's shoulder, letting her hand glide to the hilt of his greatsword and pulling it out of its sheath. She weighs the heavy weapon, lets her eyes glide over the blade and then wields it in grand archers with apparent ease. Her final swing ends just under Balian's chin. She pushes the tip against his skin: {\itshape``Sklar-Quah women are as hot as fire, Korvosan, and as deadly as the rays of the sun.}'' With the gentlest of pushes she draws a single drop of blood from the ranger's throat. Then she flicks the sword around and hands it back to its owner, hilt first. {\itshape``Still, for my brother's savior, I'm willing to make an exception}'', she smiles. As Balian reaches for his greatsword, she pulls him closer and presses a fiery kiss on his lips. {\itshape``Don't ever say that D'ari Firehair knows no gratitude}'', she teases, and gives the ranger a light slap in his behind. The other Shoanti laugh. Apparently this little show has served perfectly to break the ice.\\

During the meal Saamesh expands on his time in Urgir and explains how the party saved him from certain death. By the time the meal is done, the Korvosan heroes feel right at home. None of the Shoanti around this fire show any hostility, on the contrary, they seem to welcome the strangers in their camaraderie. D'ari remains at Balian's side and continues to tease him the whole time. When the final rays of the sun almost sink behind the horizon, the camp bursts out in commotion. Three dark shapes in the sky close in fast against the dying of the light. Each of the giant eagle-like birds carries a rider on its back. These are the mighty rocs of the Tammir-Quah, the Wind Clan. Some enthusiastic young boys cry out in rapture: {\itshape``The rocs are coming, the rocs are coming!}'' D'ari explains that they are expecting at least four thousand warriors and healers. Everyone should be here in two weeks' time. That is when the army will leave for Korvosa.\\

