%!TEX root = ../crimson_throne_book_main.tex
% 2016-02-13
\section{17 Arodus 4708}

At breakfast Balian and Puk study the other humans in the inn more carefully. One of them seems to be a bit taller, six feet four at least, and he sports a broad pair of shoulders under his grey cloak. He might be a Shoanti, though his face does not immediately look very barbarian-like. Guide Uri returns and when Quint asks him if they can go and see the palace, the boy advises against it. Admittedly the palace is marvelous to behold, but it is not located in a quarter that is not frequented by pinkskins. Grask Uldeth does not appreciate strangers snooping about, unless he invites them himself, like that one human who is rumored to stay in the palace at the moment.\\

{\itshape``A human at the palace?}'' Quint wonders.\\

{\itshape``Yes, a \ldots how you call that \ldots pathfinder, you know, those fellows who like looking for old things.}''\\

The Pathfinder Society, Quint explains, is a globe-spanning organization based out of Absalom, the world's largest city. The membership consists primarily of Pathfinders, adventurers who travel throughout Golarion - usually inconspicuously - and explore, delve, and otherwise experience the lesser-seen parts of the world. They send journals documenting their travels back to their venture-captain, who also assigns them new missions and suggests new places to explore. The most exciting and illuminating of these journals are compiled in the Pathfinder Chronicles, an ongoing series of books which collect the history and mystery of Golarion for their membership.\\

The day-to-day management of the Pathfinder Society is in the hands of so-called venture-captains. These are usually older or accomplished Pathfinders who have settled down and claimed a Pathfinder lodge for themselves. They maintain no permanent presence in Korvosa, Quint concludes, although several members of their organization have certainly been in the city in the past, usually hailing from the lodge in Magnimar. Still, the bard has never knowingly encountered a pathfinder himself.\\

When the 'six feet four' tall trader leaves the inn, the companions follow him out. Quint approaches him as he is unloading his wares from storage. He is originally from Sandpoint, but he has been in Urgir for some time now to sell weapons, something the orcs are very interested in. Quint recognizes a Varisian accent in the man's words, ruling him out as a Shoanti. The companions join the man to his stall and after he has set up shop, they go explore the market for themselves. Again Quint shouts out to Sjo regularly, calling him 'Saamesh' instead. The healer sometimes swears out loud in the language of the Shoanti as well, but no one reveals himself to them as the real Saamesh. Balian also spots something nasty: the rooftops surrounding the market are crowned with strange features, no stone gargoyles, though, but pale orc heads impaled on spikes. Uri clarifies what the ghastly crenellations are about: Lord Grask Uldeth has declared that no one bearing a token is to be touched without good cause. Orcs who want to harm token-protected pinkskins anyway, had better do so in a dark alley without witnesses, or they will suffer Uldeth's wrath. Puk is unsure whether this grisly display of merciless force should make him feel abhorred or relieved.\\

Suddenly the earth trembles! Balian immediately calls out for Spyder to stay calm, while Sjo is already searching for a good spot to look for shelter. Then the companions notice that the quake hardly startled anyone. When Quint asks Uri about it, he confirms that tremors like this are quite common. No one really cares about them, unless their own home collapses, he states casually.\\

The companions decide to widen their search by having lunch in another tavern. They can chose between several dozen pubs, inn and taverns that surround the market and could possibly feed the occasional pinkskins. Yet, they pick poorly; the only human in the bar of their choice is a slave who serves food. He strongly advises against drinking the wine, but even the beer he brings tastes awful. Going through all the establishments in the district will not only be a lengthy, but also gruesome process, Sjo concludes. There must be a better way to find the mysterious Shoanti.\\

In the afternoon the young men from Korvosa hang around the marketplace some more. Sjo starts asking around about the Pathfinder in the palace and learns his true name: Arnois Belzig. Still, no one has actually come across the man in person, they have only picked up rumors that the adventurer-explorer serves as the Great Warlord Grask Uldeth's advisor. Upon their return to the {\itshape Pinkhouse} later that evening, another human customer stumbles into Sjo and slips him a note.  {\itshape Be careful. The walls have ears. Don't ask too many questions or the orcs will start wondering about you as well. Keep your heads low and your voices under control if you want to live. Distrust everyone, the orcs, naturally, but also members of your own kind.}  The man slips out of the drinking hall and makes for the toilet; where Quint joins him on a long wooden bench hanging over a reeking pit. Despite the public nature of these facilities, there is no one else around.\\

{\itshape``Good evening, young sir}'', he greets in a steady, monotonous voice and with an even face. Quint senses that the stranger's measure of control is deliberate. The bard returns the hello and identifies himself as Quint from Korvosa.\\

{\itshape``My name is Brugo, from Nimrathas. I deal in cloth and fancy dresses for the occasional uptown orc lady or the frilly frolics in the local brothels. It's a pleasure to meet you.}''\\

{\itshape``Likewise}'', Quint tips his head.\\

{\itshape``If I might be so bold as to offer you some advice}'', Brugo continues in his hushed tone. {\itshape``Do not draw too much attention to yourself. Asking about Grask Uldeth's business too adamantly will sooner get you troubles than answers. Orcish honor and loyalty only extends to their own, and even then it is not assured. But no such qualms exist about us pinkskins. Literally anyone and everyone might tell on you if he feels he can benefit from it. Make no mistake, little brother is watching you at all times, unless you are truly alone, as we are in here, for the moment.}''\\

{\itshape``Thanks for your kind councel}'', Quint replies, considering whether he should ask the man about Shoanti in Urgir, or someone named Saamesh. But the bard decides against it for now. Perhaps he will see this Brugo again tomorrow. For now he judges it wiser to heed the man's warning and remain silent.\\

