%!TEX root = ../crimson_throne_book_main.tex
% 2016-04-23
A messenger arrives at the campfire, saying that the council has its answer. The party is guided back to the war-yurt, which is now almost empty, except for the leaders of the Quahs and Thousand Bones, who are still seated by the bonfire. Valkur has good news; the companions have convinced the council of their good intentions and are {\itshape tshamek} no more, they are now  {\itshape nalharest} , brothers of the Shoanti who will be treated as friends for as long as they do not choose to oppose the tribes. The great chief goes on that he cannot reveal the Sklar-Quah's biggest secret to the party, because even he does not know what it is. Only the mightiest shamans of his tribe share in this privilege. However, with all that is going on in Korvosa, the Shoanti have agreed to make an exception for the heroes and inform them. At that the Quahjothka points at the bonfire in the center of the war-yurt. {\itshape``If you want to learn what is truly plaguing your city, you will have to step into the fire}'', he states. Sjo is the first to step up. Staring in the flames he picks up the outlines of a humanoid shape, that beckons him closer. The healer does not hesitate and walks into the blazing fire, followed by his friends. The heat burns them hard, but then the pain resides and they feel only warmth. The burning figure appears before them: {\itshape``My name is Arunan Lives-Of-Fire, Sun shaman of the Sklar-Quah. Your tales of the jothka-woman in the stone yurt-camp Korvosa confirm our suspicions that she has unearthed the ancient 'evil' from Mashka-saht-puyuhoke, the great mastaba, an evil that was interred there by my predecessors many generations ago. The knowledge of what lies hidden in the mastaba has been handed down over the ages, from one Sun shaman to the other. Now I will reveal the secret to 'others' for the first time in history, for the need is great and you offer one of the best chances to stop the threat.\\

Hundreds of years ago, when my people still walked the lush meadows of the lowlands and lived on the shores of the great water, Sun shaman Coja Eyes-Aflame left his tribe to fight at the side of a legendary hero from the distant lands of Lastwall against a formidable ruler who was known for his unparalleled cruelty and thirst for conquest. When armies failed to halt his advance, the hero from Lastwall assembled a small and secret cabal of warriors, magic-users and mystics, Coja Eyes-Aflame among them. Using power and stealth the heroes infiltrated the tyrant's stronghold. The atrocities they found there tested them to their limits, and when they reached the enemy's throne room, a terrific battle took place. It was during this battle that they stripped away the tyrant's human disguise, revealing a powerful blue dragon who had been empowered by the blessings of his dark god. Assuming his true form, the monster attacked the cabal, and a long and bloody battle ensued. His scales deflected most of their attacks and his claws and lightning breath made short work of many of their best and bravest warriors. In the end it was the hero from Lastwall himself who was able to slip through the dragon's guard and deliver the fatal blow.\\

Yet even in death, the tyrant's body shuddered and grasped. Fire and acid destroyed much of the dragon's corpse, yet seven fragments proved impossible to destroy. These grisly relics were so suffused with evil and malignancy that they refused to burn or melt -- and even as the heroes watched, the bones twitched and writhed as they tried to return to life. The cabal's leader ordered his surviving brothers and sisters to each take one of these seven relics out into the world and go into hiding. None would know where the other members went, least of all their leader, who would remain in the tyrant's stronghold to guard it against ever being used for evil again.\\

And so it is that my predecessor returned to his people, carrying the burden of the {\itshape Fangs of Midnight} , the blue dragon's teeth. Coja was a changed man, his hands shook and his eyes bore an ever-terrified gaze. At night he often screamed out in horror. He shared his story with his fellow shamans and together they opted to hide the  {\itshape Fangs} in the ancient Thassilonian monument on the shore of his people's ancestral lands. They spent the rest of their lives guarding the monument, seeking to ensure that nothing dared enter the hidden chambers within, and when they died, they passed the task down to their successors. And so, for hundreds of years, the descendants of this now forgotten Shoanti mystic guarded and protected the  {\itshape Fangs of Midnight} from discovery, teaching their people that it was their sacred duty to stand watch over the mastaba. During these centuries the Sun shamans learned much about the power of the artifact. Part of the dragon's soul endured and tried to force its will on those around it. But the Sun shamans were aurochheaded and well-trained, and their strong minds resisted the dragon's temptations. As long as no one actually handled the teeth, they lacked the strength to truly dominate anyone and cause further harm. But now I fear that, for the first time since they were entombed in the holy site of Mashka-saht-puyuhoke, the  {\itshape Fangs of Midnight} have been touched by human hands, with unspeakable consequences. The fragment of the dragon's soul is like a plant: it seeks to take root in fertile soil, where it can blossom and grow to become a potent tree. Hearing your stories, I believe that this has happened to the Jothka-woman who you call Ileosa-Queen. If I understand you correctly I'd even say that she is wearing the {\itshape Fangs of Midnight} on her head. Her own cruelty and strength have been multiplied thousand fold by the evil artefact. On top of that the teeth will have given her supernatural powers. But the worst thing is that she now carries two souls Knowledge of how Coja's cabal defeated the dragon will be key to fighting her as well. But what my foregoers handed down to me is vague and fragmentary at best. I cannot give you the weapons to combat this evil, because I do not know them. Still, the fire of my predecessors burn within mel, just like it burned in the chest of Coja Eyes Aflame. Find his bones and rekindle his fire, then he will give you the insight you need to defeat his old nemesis.\\

I am unsure of where the Sun shamans from the days of yore lie buried. The ancient shores have been lost to us for so long that I cannot even begin to imagine what they looked like. I do know that they were not entombed in Mashka-saht-puyuhoke out of fear that the unnatural tendrils of evil would disturb their voyage to the eternal hunting grounds. Lore says that they were laid to rest in burial mounds within sight of the great mastaba, so they could guard over it even in death. Coja Eyes Aflame's bones must lie there as well, somewhere, but if I understand correctly, your people have filled the shores with stone yurts, so it will be hard to locate the Sun shaman's remains. I also fear that I cannot guide you any more than I have done just now. Still, my inner flame tells me that Coja's bones have passed the test of time. Finding them will be your task.}''\\

Then the burning shaman reaches into his own chest and pulls out a white glowing flame. He motions for Sjo to open his mouth and then places the ball of searing fire on his tongue. {\itshape``Breath this flame into the glorious mystic's remains and he will help you}'', Arunan assures. {\itshape``I'm sorry I cannot be of more help and that I cannot send the great spirits of my ancestors with you, they would only get lost in the maze that the mastaba shores have become. Only a spirit that knows the place as it exist today would be able to guide you.}''\\

Upon hearing this, Sjo pulls out the deck of Harrow cards and summons Zellara's spirit. {\itshape``Maybe she can help?}'' he offers. Arunan looks pleased as Zellara's ghost appears. {\itshape``I find myself in strange lands,}'' she says, {\itshape``far from the streets and alleyways I call home. But I feel you are among allies. Though no bonds of friendship have formed yet, mutual respect hangs around your shoulders like a warm blanket. How can I be of help?}''\\

Sjo explains that they will need Zellera's help in recovering the whereabouts of a buried Shoanti shaman, somewhere in the city of Korvosa. Arunan fills in as many details as he can. The Varisian fortune-teller is happy to oblige, but recommends patience: {\itshape``The secrets of the Shoanti lie buried under three centuries of Korvosan history and hatred. Locating the remains of a long-gone mystic will be like finding a needle in a haystack. But I will do my best to help you, although I should warn you not to expect a speedy result. The search will be hard and might prove long. I can only hope that I can provide an answer in time. When we get back home, place my deck of cards on Korvosan soil, so I can begin my search.}'' The next moment Zellara's spirit fades.\\

Arunan looks positively surprised. {\itshape``You are truly blessed by those who have left us. You walk with the spirits, who honor us still with their presence and friendship. Go now with the strength of the spirits and the friendship of the tribes.}'' After these words Arunan disappears as well, his burning body melting into the bonfire. The companions step from the flames and face Valkur and the council again. The big chief regards Sjo carefully, nodding his head in respect when he catches a fiery glimpse in the healer's milky eyes. {\itshape``Now the might of the Sklar-Quah is truly with you. I wish you a speedy journey back and good fortune at the end of your path. We will follow in two weeks, to pick up the fight if you fail. But if you succeed, you should contact us, so we can discuss our people's future together.}''\\

Quint suggests they use magic to stay in touch during their mission. Thousand Bones will be happy to serve as a medium. Depending on the heroes' progress or failure, the Shoanti might have to expedite or postpone their war movements. The companions certainly feel that now there is some room for flexibility on this front. The Quahs are placing a lot of trust in their hands, they hope they can live up to the challenges ahead.\\

\section{23 Arodus 4708}

Balian spends the night in the arms of D'ari Firehair, Saamesh's sister, learning how hot Sklar-Quah women can actually be. The next morning the companions leave for Kaer Maga in horseback. They reach the cliff-top city by the afternoon, which gives them some time to sell off the loot they gathered over the last couple of days and invest in some scrolls and new equipment.\\

