%!TEX root = ../crimson_throne_book_main.tex
% 2016-02-07
Damn those flying creatures! With no powerful ranged attacks at their disposal, the companions learn the hard way that only being strong in close combat has its limits. Balian is still holding down one of the harpies, but this leaves him vulnerable to sneak attacks from the other birdwomen's claws. Quint pulls out a {\itshape scroll of blur} and casts it on the ranger to safeguard him from these vicious attacks. Doing so, the bard singles himself out as the next target of Circeis' arrows. She shoots away his last  {\itshape mirror image} and fires another arrow in his shoulder. Balian finally manages to squeeze his prey into unconsciousness and seeks shelter against the rocks, turning the next swoop he is subject to into a miss. Meanwhile Puk realizes he has been mostly idle in this fight. He has barely damaged his opponents and his small frame keeps the harpies from targeting him, so he is the only one who hasn't suffered any wounds, while his friends are struggling to remain standing. The halfling climbs on Quint's shoulders, both to gain a better reach and offer himself up as a potential target. Sjo sustains even more damage from the next harpy's flyby attack and exhausts his last fourth level spells to heal himself and Balian. Quint buys himself and his friends some more time by covering everyone in an  {\itshape invisibility sphere} , allowing them a few precious moments to patch up further and study the battlefield. The top of this peak, which serves as the harpies' home, holds two extra rock formations. A small needle rises to the right, while a more robust rock rests to the left. An cave opening, about 30 feet from the ground, serves as the entrance to the harpies' lair. Between the two rock masses, a wooden fence has been constructed to contain the imprisoned orcs. The companions find themselves in the open ground in front of the fence, where they are at the mercy of the harpies. Puk contemplates climbing the needle, but quickly decides against it. His adversaries' superior maneuverability would put the rogue at even more of a disadvantage there. With the heroes invisible, the winged witches change their tactics. One of them launches a new {\itshape captivating song} , but Quint's lingering  {\itshape countersong} saves his friends from her bewildering influence. Another harpy flies into the cave and reemerges with a sack, which she tears open above the veiled party. Grain rains from the sky and gives away the position of the cloaked heroes, heralding a new series of swoop attacks on Balian, who has returned to the open ground to retrieve his greatsword. Meanwhile Circeis has flown to the orc prison camp, where she now orders her 'minions' to climb out and locate the enemy. The invisible heroes stand at the ready, prepared to grab the next harpy who flies over, but the creatures refuse to attack blindly and take on a similar approach, biding their time until better opportunities present themselves. Quint takes this chance to recast his  {\itshape mirror image} and is forced to launch another  {\itshape countersong} when Circeis sings her captivating melody once more. Trying to lure out his enemy, the bard summons a  {\itshape silent image} of Sjo, but Circeis arrows reveal that the newly reappeared figure is just an illusion. The first orc has made it over the fence by now and blindly runs into the area where the invisible party is standing. He bumps into Spyder and starts shouting that there is something unseen in front of him. Sjo feels frustrated and breaks the standstill by throwing yet another {\itshape hold person} at Circeis, but again she resists his magic. This action turns the healer visible, triggering a new swoop attack from Circeis' three surviving sisters. Balian grabs the first harpy as she passes, but suffers her sister's claws in return and is forced to let go. Sjo heals his friend, but has to receive a touch from Quint's healing wand himself when Circeis resumes firing at him. The orcs who made it over the fence fall back when one hero after the other turns visible again. In the fray that follow Puk gets hit for the first time in this combat by a claw and Sjo goes down when Circeis' next volley hits him hard. Again Quint has to use his  {\itshape wand of cure serious wounds} to heal Sjo. Balian fails to grab a harpy on her next dive, but Quint, who is the only one that hasn't turned visible yet, can snatch her by surprise and holds her down for Puk to finish her off. Circeis keeps on peppering the party with her nasty arrows, forcing Quint to renew his  {\itshape invisibility sphere} . Sjo depletes his level three spell as well healing himself and Balian, while Circeis makes for the cave and hides inside, just out of sight. This is the opportunity Puk has been waiting for. Using the power of his {\itshape cloak of the pixie king} he  {\itshape dimension doors} the party into the lair. Circeis' eyes tumble with surprise as she realizes she is suddenly cornered. She calls out to one of her sisters, who tries to provide some back-up by assaulting the companions from the back, but these enclosed quarters work to the party's advantage and finally the swerving witch and a third sister fall to their weapons. The last surviving harpy understands that the fight is lost and bolts. After all, with her sisters out of the way, she might return one day as queen of the mountain. The companions take a few breaths to heal up. A {\itshape detect magic} reveals that Circeis' gold bracers hold quite a bit of power. Sjo pulls out Zellara's harrow cards to have the arm bands identified as  {\itshape greater bracers of archery} . The witch's bow is magical as well and -- as the heroes found out over and over in the fight -- bolster arrows fired from it with frost. Sjo makes another very interesting discovery in the back of the cave. Hidden underneath one of the beds is a pouch of gems and jewels, a  {\itshape runestone of power (level 2)} and a  {\itshape tome of leadership and influence (+1)} . These treasures will prove very useful for either him or Quint! Quint addresses the orc survivors and tells them they are free again. As the heroes join them back to their village, they learn that their 'leader' Brugar -- who the companions were forced to kill in battle -- was  not really one of their own. In fact, he was warlord Kroghut's nephew who had grown a bit too ambitious for his own good. His acting lord removed him from court by 'promoting' him leader of his own tribe, a ragtag bunch of lowly shepherds. Quint suspects the family tie between Kroghut and Brugar was also the reason why the Broken Spine warlord sent pinkskins to take care of the problem, rather than his own men, whom he did not trust with his rabble-rousing nephew. Also, if things got out of hand and Brugar did not survive (as is the case), Kroghut would have perfect deniability. Honor prevented him from killing his own nephew before the young orc had actually undertaken a coup, but by having pinkskins take care of the problem before it came to fruition, Kroghut managed to remove a future threat without losing his honor.\\

The companions see the orc shepherds safely to their homes and take the rest of the day off to rest, while the orcs bury and mourn their dead. The heroes are assigned one of the dead orc's huts to spend the night.\\

