%!TEX root = ../crimson_throne_book_main.tex
% 2016-04-05
Quint presses his back tight against the wall. His heart pounds furiously. How could everything go wrong so fast? He had not seen this coming: two powerful casters who could so easily dictate the course of the fight. And they are just around the corner, still under the influence of an {\itshape improved invisibility} spell, standing over the bodies of Quint's fallen companions: one a magic-user who was mighty enough to conjure a  {\itshape cone of cold} , the other one a bard who wielded greater power than Quint. Quint casts an {\itshape invisibility sphere} on himself. Fortunately his voice is still being blocked by Sjo's stone of  {\itshape silence} on the floor, so the enemies can't hear him. Then our hero quickly makes for the spot where Sjo dropped the stone and picks it up. From this position he has a clear view of the battlefield in the second half of the crypt. The two caster figures turn visible again. The first one is an orc dressed in gray robes with a red hand painted on his chest. Huge fangs jut from his jaw, mirrored by two fang-like pieces of bone sticking from his earlobes. He glances about cautiously, expecting the last surviving infiltrator to appear at any moment. At the same time he gathers Balian's, Sjo's and Puk's weapons and checks their bodies for a pulse. He calls out something to his companion, the enemy bard, who is dressed in purple robes and whose face appears to be covered with a mask. Quint suspects this is Wyrnan Koch, the 'Purple Worm', whom he read about in Saamesh's secret journal. This person pulls out a wand and moves over to the four orcs who went down in the battle. Two of them are still alive and the Purple Worm restores them to full health with the wand. The other two are beyond saving, it seems. Quint repositions himself in the mouth of the stairwell. He still has a good view on the orcs from there, but can easily make his escape if he has to. He sees how the two orcs that have just been nursed back to life pick up their weapons and search the first half of the tomb, where Quint was hiding initially. Meanwhile the casters do another spell and focus on the bodies of Quint's friends. They start stripping them of all lose magical items, from spare weapons to jewels and cloaks. Judging from the way the handle his friends, Quint can tell that they are probably still alive.\\

By now the two orc minions reach the end of the crypt and, having discovered no one, are about to return. Before they do so, Quint slips back into the crypt and hides behind a ruined dwarven grave. The orcs walk back - past the bard - and take the stairs leading to the next floor. Now only the two caster remain, who are still plundering the fallen heroes of anything but their armor.\\

Realizing that his {\itshape invisibility} will not last forever, Quint decides to find a better place to hide. A big sarcophagus sits in the overflow of the first and second half of this crypt. It stands a few feet from the wall, leaving just enough space for the bard to hide. It also provides a perfect view of both parts of the crypt and allows Quint to hear his enemies as well, as he now steps out of the  {\itshape silence} zone. The casters are talking in Orcish, a language that Quint masters as well. They seems to be very pleased with the 'fat loot' on the intruders' bodies, even though they will have to examine the items further to determine their exact powers. At the same time they are disappointed, because they can't find 'the key'. They wonder if the 'one who got away' might have it. The Shoanti 'spy' always denied having the key, but the men were never sure if they could believe him. Just imagine what they could do with that key! Open ancient doors and discover Koldukar's hidden treasures! Once the two casters have finished stripping down their opponents, they pull out some rope to tie them up. They obviously don't feel like lifting up a heavy bloke like Sjo to wrap the ropes around him, so they settle for rolling him over and tying his hands behind his back. They also bind his feet together. The other fallen companions get the same treatment. The orc with the large fangs also jokes about cooking and eating Spyder later on, although Quint seriously doubts it actually is a joke. He's seen dog on the menu in the market square.\\

Quint's {\itshape invisibility} wears off, but he chose his hiding place well, so the two figures do not notice him and continue their tedious work. When they're done securing the prisoners, they attach a length of rope to Balian's feet and start pulling him to the end of the gallery, towards a set of double doors. The floor is covered in stone rubble, and even though they advance slowly, the casters laugh over the unconscious ranger's rough ride through the debris. When they disappear through the exit, Quint finds himself alone in the crypt. He jumps to action, hurrying over to Sjo and Puk while pulling out his wand of  {\itshape cure serious wounds} . Two gentle touches with the magic timber restore his friends to consciousness. 