%!TEX root = ../crimson_throne_book_main.tex
% 2016-04-09
Quint tries to make the most of the time he is given. He ushers his friends over to the other half of the room, where they can proceed unnoticed. Using Quint's wand and Sjo's {\itshape curing} spells the companions patch up again. Quint also hands Puk the  {\itshape bag of holding} and the halfling picks out a number of Blackjack's masterwork daggers for himself and Sjo. Since the enemies still haven't returned, the party decides to set a trap. Puk drops back to the floor where he went down in battle. Since he is the one who will be in immediate view when the bad guys come back, they might not notice anything is wrong until they are close. Spyder, who has been healed as well, also lays down in a pool of his own blood and plays dead. Sjo hides next to Puk, behind a pillar, while Quint waits just around the corner. The plan works! When the enemy casters come back a few moments later, chatting merrily about their victory, they remain relaxed and unalarmed until they reach Puk's position. Sjo launches the attack by cleverly casting {\itshape silence} on a coin, while Quint casts  {\itshape haste} on his friends from just outside the silenced zone. Spyder and Quint get behind the enemies, closing off their way of escape and Puk proves that a rogue does not need magical daggers to deliver serious damage. The figure in the purple robes draws his rapier and returns the favor, giving the halfling a nasty cut. Sjo finds out that wielding a dagger is not really his thing and misses his mark. The orc mage realizes that there is nothing he can do, being surrounded in melee in a zone where he can't voice his spells, so he tries to make a run for it, but Quint trips him. His attempt to get back up is foiled and Puk's quick little stabs make short work of him. It is astounding how much of a difference the circumstances make. Where the mage proved a formidable and illusive opponent in the last fight, he now turns into a complete push-over. The enemy bard lasts a few breath longer, as his defenses are actually quite decent. He also seems to have some skill with his rapier, slicing a few more gashes in Puk, but then the halfing gets lucky and finds three gaps in the man's guard. The purple figure drops to the floor. Sjo reclaims his heavy mace from the enemies' sack of loot, and hands back Puk's daggers as well, while Quint pulls off the Purple Worm's mask. His face is human. He wonders whether this might be Arnois Belzig, the Pathfinder in Grask Uldeth's service. {\itshape Detect magic} reveals that the men carry some potent magic. The party moves over to the next room, a large round chamber with a floor that drops into the darkness, deeper than Sjo's 60 feet of  {\itshape darkvision} . There is a stone platform that stretches across the room, leading to a blank wall on the other side, but a lever in the middle of the platform can make the whole construction turn 90 degrees to reach a stone door with a small porch in the left wall. Balian's body lies on the platform, while another bound and unconscious figure lies on the porch in front of the door. The companions quickly restore Balian to full health and turn the platform to reach the prisoner on the porch. It is Saamesh, the Shoanti spy they were looking for. When Quint frees him and nurses him back to consciousness, he recognizes the companions from their previous encounter in the spirit world, even though they were all in animal form then. Saamesh has been beaten and tortured, not just as punishment for being a spy, but also to extract information. The Purple Worm was after two things in particular: he wanted to know where the Koldukar key was and who Saamesh's allies were. The Shoanti could only answer truthfully by denying that he had either of those: no key and no allies! His torturer obviously did not believe him and kept on tormenting the spy to get him to talk. Saamesh tried using an old Shoanti trick to detach his spirit from his body. That is how he entered the spirit world and was able to get a message to the heroes. But the Purple Worm quickly succeeded in breaking his mental escape.\\

The door behind Saamesh is made of stone and radiates strong magic. It is one of the Koldukar doors that can only be opened with the Koldukar key. Saamesh marvels at how absurd life can be sometimes. He came here looking for the Purple Worm, believing that man had the mysterious key, while the Worm captured him and was convinced that {\itshape he} knew more about this notorious dwarven unlocking device. The Shoanti also admits that he had seriously underestimated the Purple Worm's forces. The man had more troops than expected and was actually quite powerful, as was his magic-wielding orc ally. In hindsight, that might not be such a bad thing, Puk jokes, as he glances over the mighty loot he gathered from the two casters' bodies. Anyhow, the spy realizes that his cover in Urgir is blown and that his role in the orc city has come to an end. He is happy to be alive and rescued, and now he just wants to return home. He does wonder, however, how four Korvosans came to save him. From his visit in the spirit world, he knows that he can trust his rescuers, but he does not understand why they came for him: the Shoanti and Korvosa are not exactly on friendly terms. Quint explains that Korvosa's new queen is under the influence of something evil that she unearthed in the great mastaba, and they need the Shoanti's help and insight to fight it. Saving the son of the Sun Clan's most influential chief might go a long way with the people of the Cinderlands, who only accept non-Shoanti if they prove themselves worthy. Saamesh promises that he will aid their cause and plead to his leaders to help his rescuers. Sjo also has a question of a more personal nature. He wants to know if Saamesh knows his mother, Aithn\'e. The young spy nods affirmatively. She is one of the famous burn riders, a proud and capable warrior. Her father (and Sjo's grandfather), Sun shaman Yundur Firestorm, passed away some years ago, unfortunately. She has no children, though, at least, not in the tribe, the rescued Shoanti sighs.\\

While Saamesh begins to formulate plans how to get out of the orc city and travel back to the Cinderlands, Quint pulls out the {\itshape scroll of teleport} he got from Jasan Adriel. Saamesh is delighted: traveling home overland could take up to three weeks and the journey would be fraught with danger. This magical short-cut could both figuratively and literally be a life-savior. Quint decides to take the Skull clan's encampment, where they found Thousand Bones' tribe, as his focus point. The magic does its work and the next moment the heroes and their new friend are back in the Kallow Hills. The camp is still there, but it looks emptier then when the party left here six days ago. Most of the able-bodied men and women have left for the meeting in the shadow of the Great Flame. Only the elderly, children and some women remain here. Even jothka One-life and shaman Ashdancer have joined the warriors. Thousand Bones, however, is still here, waiting for the companions. He is overjoyed to see them and find out that they succeeded in their quest. Now he wants to follow his tribesmen to the gathering as quickly as possible, suggesting the party joins him there. The companions agree and take the rest of the day off to recover and distribute the loot they recovered from the orc magic-user and the Purple Worm. There are two mighty {\itshape cloaks of resistance} , both caster were also wearing  {\itshape headbands of alluring charisma} , which were more powerful than the one Quint is wearing at the moment. There are other magical upgrades as well: a good  {\itshape amulet of natural armor, mithral buckler} and  {\itshape chain shirt} , better  {\itshape rings of protection} for some of the party members, but the nicest item is the Purple Worm's silver rapier. The blade has small holes that whistle in a high pitch when the weapon is wielded and deliver sonic damage. But its most wonderful property is the fact that it allows a bard to use his bardic performance to charge the weapon, allowing him to use his charisma instead of his strength to guide his strikes and deliver damage. Quint is usually the last to join melee, but with this rapier he will much better at it. 